### 2010-08-12 ms.tex
Initial check-in

%\documentclass[apj]{emulateapj}
\documentclass[12pt,preprint]{aastex}

\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{natbib}
\usepackage[section] {placeins}
\bibliographystyle{apj}
\citestyle{apj}

%%%%%%%% Begin custom definitions %%%%%%%%%%%%%

\input macros.tex

%%%%%%%% End custom definitions %%%%%%%%%%

\begin{document}

\shorttitle{AMR SIMULATIONS WITH ADAPTIVE RAY TRACING}
\shortauthors{WISE ET AL.}

\title{Enzo+Moray: Radiation Hydrodynamics Adaptive Mesh Refinement
  Simulations with Adaptive Ray Tracing}

\author{John H. Wise\altaffilmark{1,2}, 
  Tom Abel\altaffilmark{3}, 
  Ji-hoon Kim\altaffilmark{3}, 
  Peng Wang\altaffilmark{3,4},
  Peter Iannucci\altaffilmark{5}}

\altaffiltext{1}{Department of Astrophysical Sciences, Princeton
  University, Peyton Hall, Ivy Lane, Princeton, NJ 08544}
\altaffiltext{2}{Hubble Fellow}
\altaffiltext{3}{Kavli Institute for Particle Astrophysics and
  Cosmology, Stanford University, Menlo Park, CA 94025}
\altaffiltext{4}{NVIDIA}
\altaffiltext{5}{Massachusetts Institute of Technology}
\email{jwise@astro.princeton.edu}

\begin{abstract}

  We describe a photon-conserving numerical method that solves the
  radiative transfer equation, using a spatially-adaptive ray tracing
  scheme, and its parallel implementation into the adaptive mesh
  refinement (AMR) code, Enzo.  Coupling the solver with the energy
  equation and non-equilibrium chemistry network, our radiation
  hydrodynamics framework can be utilized to study a broad range of
  astrophysical problems, such as stellar and black hole (BH)
  feedback.  Inaccuracies can arise from large timesteps and poor
  sampling, therefore we devised an adaptive timestepping scheme and a
  fast approximation of the optically-thin radiation field with
  multiple sources.  We test the method with several radiative
  transfer and radiation hydrodynamics tests that are given in
  \citet{RT06, Iliev09}.  We further test our method with more
  dynamical situations, for example, the propagation of an ionization
  front through a Rayleigh-Taylor instability, time-varying
  luminosities, and collimated radiation.  This method linearly scales
  with the number of point sources and number of grid cells.  To
  combat this, we use a novel method of merging rays at large radius,
  using a tree method, which we briefly describe.  Our implementation
  is scalable to O(10$^3$) processors on distributed and shared memory
  machines and can include radiation pressure and secondary
  ionizations from X-ray radiation.  Our implementation is included in
  the newest public release of Enzo.

\end{abstract}

\keywords{cosmology --- methods: numerical --- hydrodynamics ---
  radiative transfer}

\section{Introduction}

Radiative transfer is ubiquitous in many astrophysical problems,
encompassing topics such as stellar atmospheres, the interstellar
medium (ISM), galaxy formation, and cosmology.  Thus it is a
well-studied problem \citep[e.g.][and more!]{Rybicki}; however, its
treatment in multi-dimensional calculations is difficult because of
the dependence on seven variables --- three spatial, two angular,
frequency, and time.  The non-local nature of the thermal and
hydrodynamical response to radiation sources further adds to the
difficulty.  In the general case, one must consider all radiation
sources at every point in calculation.  (add: simplify by symmetries
and special cases)

There are several methods to solve the radiative transfer.

\section{Treatment of Radiative Transfer}

Radiation trnasport is a well-studied topic, and we begin by
describing our approach in solving the radiative transfer equation,
which in comoving coordinates \citep{Gnedin97} is
%
\begin{equation}
  \label{eqn:rteqn}
  \frac{1}{c} \; \frac{\partial I_\nu}{\partial t} + 
  \frac{\hat{n} \cdot \nabla I_\nu}{\bar{a}} -
  \frac{H}{c} \; \left( \nu \frac{\partial I_\nu}{\partial \nu} -
  3 I_\nu \right) = -\kappa_\nu I_\nu + j_\nu .
\end{equation}
%
Here $I_\nu \equiv I(\nu, \mathbf{x}, \Omega, t)$ is the radiation
specific intensity in units of energy per time $t$ per solid angle per
unit area per frequency $\nu$.  $H = \dot{a}/a$ is the Hubble
constant, where $a$ is the scale factor.  $\bar{a} = a/a_{em}$ is the
ratio of scale factors at the current time and time of emission.  The
second term represents the propagation of radiation, where the factor
$1/a$ accounts for cosmic expansion.  The third term describes both
the cosmological redshift and dilution of radiation.  On the right
hand side, the first term considers the absorption coefficient
$\kappa_\nu \equiv \kappa_\nu(\mathbf{x},\nu,t)$, and the second term
$j_\nu \equiv j_\nu(\mathbf{x},\nu,t)$ is the emission coefficient
that includes any point sources of radiation or diffuse radiation.

Solving this equation is difficult because of its high dimensionality;
however, we can make some appropriate approximations to reduce its
complexity in order to include radiation transport in numerical
calculations.  Typically timesteps in dynamic calculations are small
enough so that $\Delta a/a \ll 1$, therefore $\bar{a} = 1$ in any
given timestep, reducing the second term to $\hat{n} \partial
I_\nu/\partial \mathbf{x}$.  To determine the importance of the third
term, we evaluate the ratio of the third term ot the second term.
This is $HL/c$, where $L$ is the simulation box length.  If this ratio
is $\ll 1$, we can ignore the third term.  For example at $z=5$, this
ratio is 0.1 when $L = c/H(z=5)$ = 53 proper Mpc.  In large boxes
where the light crossing time is comparable to the Hubble time, then
it could be important to consider cosmological redshifting and
dilution of the radiation, which we will describe later in
\S\ref{sec:ART}.  Thus equation (\ref{eqn:rteqn}) reduces to the
non-cosmological form in this local approximation,
%
\begin{equation}
  \frac{1}{c} \frac{\partial I_\nu}{\partial t} + 
  \hat{n} \frac{\partial I_\nu}{\partial \mathbf{x}} =
  -\kappa_\nu I_\nu + j_\nu .
\end{equation}
%
We choose to represent the source term $j_\nu$ as point sources of
radiation (e.g. stars, quasars) that emit radial rays that are
propaged along the direction $\hat{n}$.  Next we describe this
discretization and its contribution to the radiation field.

\input table1.tex

\subsection{Adaptive Ray Tracing}
\label{sec:ART}

Ray tracing is an accurate method to propagate radiation from point
sources on a computational grid, given that there are rays passing
through each cell.  Along a ray, the radiative transfer equation reads
%
\begin{equation}
\label{eqn:rtray}
\frac{1}{c} \frac{\partial P}{\partial t} + \frac{\partial P}{\partial
  r} = -\kappa P,
\end{equation}
%
where $P$ is the photon number flux along the ray.  To sample the
radiation field at large radii, ray tracing requires at least $N_{ray}
= 4\pi R^2 / (\Delta x)^2$ rays to sample each cell with one ray,
where $R$ is the radius from the source to the cell and $\Delta x$ is
the cell width.  If one were to trace $N_{ray}$ rays out to $R$, the
cells at a smaller radius $r$ would be sampled by, on average,
$(r/R)^2$ rays, which is computationally wasteful because only a few
rays per cell, as we will show later, provides an accurate calculation
of the radiation field.

We avoid this inefficiency by utilizing adaptive ray tracing
\citep{Abel02_RT}, which progressively splits rays when the sampling
becomes too coarse and is based on Hierarchical Equal Area isoLatitude
Pixelation \citep[HEALPix;][]{HEALPix}.  In this scheme, the rays are
traced along normal directions of the centers of HEALPix pixels, which
evenly divides a sphere into equal areas.  The rays are initialized at
each point source with the photon luminosity (ph s$^{-1}$) equally
spread across $N_{\rm pix} = 12 \times 4^l$ rays, where $l$ is the
initial HEALPix level.  We usually find $l$ = 0 or 1 is sufficient
because these coarse rays will be usually be split before traversing
the first cell.

The rays are traced through the grid in a typical fashion
\citep[e.g.][]{Abel99_RT}, in which we calculate the next cell
boundary crossing.  The ray segment length crossing the cell is
%
\begin{equation}
  \label{eqn:trace}
  dr = R_0 - \min_{i=1 \rightarrow 3} \left[(x_{\rm cell,i} - x_{\rm src,i}) /
    \hat{n}_{\rm ray,i} \right],
\end{equation}
%
where $R_0$, $\hat{n}_{\rm ray}$, $x_{\rm cell,i}$, and $x_{\rm
  src,i}$ are the initial distance travelled by the ray, normal
direction of the ray, the next cell boundary crossing on the $i$-th
dimension, and the position of the point source that emitted the ray,
respectively.  However before the ray travels across the cell, we
evaluate the ratio of the face area $A_{\rm cell}$ of the current cell
and the solid angle $\Omega_{\rm ray}$ of the ray,
%
\begin{equation}
  \label{eqn:split}
  \Phi_c = \frac{A_{\rm cell}} {\Omega_{\rm ray}} = 
  \frac{N_{\rm pix} (\Delta x)^2} {4\pi R_0^2}.
\end{equation}
%
If $\Phi_c$ is less than a pre-determined value (usually $>2$), the
ray is split into 4 child rays.  We investigate the variations in
solutions with $\Phi_c$ in \S\ref{sec:ang_dep}.  The pixel numbers
of the child rays $p^\prime$ are given by the ``nested'' scheme of
HEALPix at the next level, i.e. $p^\prime = 4 \times p + [0,1,2,3]$,
where $p$ is the original pixel number.  The child rays (1) acquire
the new normal vectors of the pixels, (2) retain the same radius of
the parent ray, and (3) gets a quarter of the photon flux of the
parent ray.  Afterwards the parent ray is discontinued.

A ray propagates and splits until 
%
\begin{enumerate}
\item its photon flux is almost fully absorbed ($>99.9\%$) in a single
  cell, which significantly reduces the computational time if the
  radiation volume filling fraction is small,
\item the photon has travelled $c \times dt_P$, where $dt_P$ is the
  radiative transfer timestep,
\item the photon leaves the computational domain with isolated
  boundary conditions, or
\item the photon travels $\sqrt{3}$ of the simulation box length with
  periodic boundary conditions.
\end{enumerate}
%
In the second case, the photon is halted at that position and saved,
where it will be considered in the solution of $I_\nu$ at the next
timestep.  In the next timestep, the photon will encounter a different
hydrodynamical and ionization state, hence $\kappa$, in its path.
Furthermore any time variations of the luminosities will be retained
in the radiation field.  In this sense, our method retains the time
derivative of the radiative transfer equation.

\subsection{Ray Merging}

Unfortunately the computational work of ray tracing scales with the
number of sources.  To resolve this barrier, rays can be merged in
cases with either nearly parallel rays from clustered sources of
radiation, whether it be diffuse radiation or point sources, or where
rays exit a region with high resolution into a coarsely resolved
region.  In each case, the factor $\Phi_c$ can be much higher than the
desired value, and it would be efficient to merge these rays.  We have
devised a new scheme that merges rays from clustered sources based on
a hierarchical binary tree, which is analogous to the gravity tree
solvers.  We show the performance improvements in the strong scaling
tests (\S\ref{sec:strong_sc}).  However we leave its full details for
a later paper.

\subsection{Radiation Field}

The radiation field is calculated by integrating equation
\ref{eqn:rtray} along each ray, which is done by considering the
discretization of the ray into segments.  In the following section, we
assume the rays are monochromatic.  For convenience, we express the
integration in terms of optical depth $\tau = \int \kappa(r,t) \;
dr$, and for a ray segment,
%
\begin{equation}
  \label{eqn:dtau}
  d\tau = \sigma_{\rm abs}(\nu) n_{\rm abs} dr.
\end{equation}
Here $\sigma_{\rm abs}$ and $n_{\rm abs}$ are the cross section and
number density of the absorbing medium, respectively.  We use the
cell-centered density in our calculations but have experimented with
trilinearly interpolated densities \citep[see][]{Mellema06} without
producing considerable artifacts.  Equation (\ref{eqn:rtray}) has a
simple exponential analytic solution, and the photon flux of a ray is
reduced by
%
\begin{equation}
  \label{eqn:flux}
  dP = P \times (1 - e^{-\tau})
\end{equation}
as it crosses a cell.  We equate the photo-ionization rate to the
absorption rate, resulting in photon conservation \citep{Abel99_RT,
  Mellema06}.  Thus the photo-ionization $k_{\rm ph}$ and
photo-heating $\Gamma_{\rm ph}$ rates associated with a single ray are
%
\begin{equation}
  \label{eqn:kph}
  k_{\rm ph} = \frac{P (1 - e^{-\tau})}{n_{\rm abs} \; V_{\rm cell} \; dt_P},
\end{equation}
\begin{equation}
  \label{eqn:gamma}
  \Gamma_{\rm ph} = k_{\rm ph} \; (E_{\rm ph} - E_i),
\end{equation}
where $V_{\rm cell}$ is the cell volume, $E_{\rm ph}$ is the photon
energy, and $E_i$ is the ionization energy of the absorbing material.
In each cell, the photo-ionization and photo-heating rates from each
ray in the calculation are summed, and after the ray tracing is
complete, these rates can be used to update the ionization state and
energy of the cells.  Considering a system with only hydrogen
photo-ionizations and radiative recombinations, these changes are very
straightforward and is useful for illustrative purposes.  The change
in neutral hydrogen is
%
\begin{equation}
\frac{dn_{\rm H}}{dt} = \alpha_B n_e n_p - C_{\rm H} n_e n_{\rm
  H} - k_{\rm ph},
\end{equation}
where $\alpha_B = 2.59 \times 10^{-13} \mathrm{cm}^3 \mathrm{s}^{-1}$
is the recombination coefficent at 10$^4$ K in the Case B on-the-spot
approximation, in which all recombinations are locally reabsorbed,
\citep{Spitzer78}, and $C_{\rm H}$ is the collisional ionization rate.
However for more accurate solutions in calculations that consider
several chemical species, the photo-ionization rates are better
utilized in solvers that consider chemical networks
\citep[e.g.][]{Abel97}.

\subsection{Additional Physics}
\label{sec:addphysics}

Other radiative processes can also be important in some situations,
such as attentuation of radiation in the Lyman-Werner bands, secondary
ionizations from X-ray radiation, Compton heating of from scattered
photons, and radiation pressure.

\subsubsection{Absorption of Lyman-Werner Radiation}

Molecular hydrogen can absorb photons in the Lyman-Werner bands that
are composed of 76 absoprtion lines ranging from 10.2 to 13.6 eV.
Each of these spectral lines can be modelled with a typical
exponential attenuation equation \citep{Ricotti01}, but
\citet{Draine96} showed that this self-shielding is well modeled with
the following relation to total \hh~column density
%
\begin{equation}
  \label{eqn:lwband}
  f_{\rm shield}(N_{\rm H2}) = \left\{ \begin{array}{l@{\quad}l}
      1 & (N_{\rm H2} \le 10^{14} \; \mathrm{cm}^{-2})\\
      (N_{\rm H2}/10^{14} \; \mathrm{cm}^{-2})^{-0.75} & (N_{\rm H2} >
        10^{14} \; \mathrm{cm}^{-2})
    \end{array} \right. .
\end{equation}
To incorporate this shielding function into the ray tracer, we store
the total \hh~column density and calculate the \hh~dissociation rate
by summing the contribution of all rays,
%
\begin{equation}
  \label{eqn:lwRT}
  k_{\rm diss} = \sum_{\rm rays} \frac{P \; \sigma_{\rm LW} \;
    \Omega_{\rm ray} \; r^2 \; dr}{A_{\rm cell} \; dV \; dt_P},
\end{equation}
where $\sigma_{\rm LW} = 3.71 \times 10^{18} \mathrm{cm}^2$ is the
effective cross-section of \hh~\citep{Abel97}.  To account for any
absorption in each photon package, we attentuate the photon number
flux by
%
\begin{equation}
  \label{eqn:LWdP}
  dP = P [f_{\rm shield}(N_{\rm H2} + dN_{\rm H2}) - f_{\rm shield}(N_{\rm H2})],
\end{equation}
where $dN_{\rm H2}$ is the \hh~column density in the current cell.

\subsubsection{Secondary Ionizations from X-rays}
\label{sec:xrays}

A high-energy ($E_{\rm ph} \gsim 100$ eV) photon can ionize multiple
neutral hydrogen and helium atoms, and this should be considered in
such radiation fields.  \citet{Shull85} studied this effect with Monte
Carlo calculations over varying electron fractions and photon energies
up to 3 keV.  They find that the excitation of hydrogen and helium and
the ionization of \ion{He}{2} is negligible.  The number of secondary
ionizations of H and He is reduced from the ratio of the photon and
ionization energies ($E_{\rm ph} / E_i$) by a factor of
%
\begin{equation}
  Y_{\rm k,H} = 0.3908 (1 - x^{0.4092})^{1.7592},
\end{equation}
\begin{equation}
  Y_{\rm k,He} = 0.0554 (1 - x^{0.4614})^{1.6660},
\end{equation}
where $x$ is the electron fraction.  The remainder of the photon
energy is deposited into thermal energy that is approximated by
%
\begin{equation}
  Y_{\rm \Gamma} = 0.9971 [ 1 - (1 - x^{0.2663})^{1.3163} ]
\end{equation}
and approaches one as $x \rightarrow 1$.  Thus in gas with low
electron fractions, most of the energy results in ionizations of
hydrogen and helium, and in nearly ionized gas, the energy goes into
photo-heating.

\subsubsection{Compton Heating from Photon Scattering}

High energy photons can also cause Compton heating by scattering off
free electrons.  During a scattering, a photon loses $\Delta E(T_e) =
4kT_e \times (E_{ph} / m_e c^2)$ of energy, where $T_e$ is the
electron temperature.  For the case of monochromatic energy groups, we
model this process by considering that the photons are absorbed by a
factor of 
\begin{equation}
  \frac{dP_C}{P} = (1 - e^{-\tau_e}) \frac{\Delta(T_e)}{E_{ph}},
\end{equation}
which is the equivalent of the photon energy decreasing.  Here $\tau_e
= n_e \sigma_{KN} dl$ is the optical depth to Compton scattering, and
$\sigma_{KN}$ is the non-relativistic Klein-Nishina cross section
\citep{Rybicki}.  The Compton heating rate is thus
\begin{equation}
  \Gamma_{\rm ph,C} = \frac{dP_C}{n_e \; V_{\rm cell} \; dt}.
\end{equation}

\subsubsection{Radiation Pressure}

The absorption of radiation transfers momentum from photons to the
absorbing medium, i.e. radiation pressure.  This is easily computed by
considering the momentum
\begin{equation}
  d\mathbf{p}_\gamma = \frac{dP \; E_{\rm ph}}{c} \; \hat{r}
\end{equation}
of the absorbed radiation from the incoming ray, where $\hat{r}$ is
the normal direction of the ray.  The resulting acceleration of the
gas due to radiation pressure is 
\begin{equation}
  d\mathbf{a} = d\mathbf{p}_\gamma / (\rho \; V_{\rm cell}),
\end{equation}
where $\rho$ is the gas density inside the cell.  This acceleration is
then added to the other forces, e.g. gravity and gas pressure, in the
calculation.

\subsection{Geometric Corrections}
\label{sec:meth_fc}

\begin{figure}[t]
  \plottwo{fig/covering.eps}{fig/calc_fc.eps}
  \caption{\label{fig:covering} (a) A two-dimensional illustration of
    the overlap between the beam associated with a ray $\gamma$ and a
    computational cell.  The ray has a segment length of $dr$ passing
    through the cell.  The covering area is denoted by dark grey,
    where the full area $(dr \times L_{\rm pix})$ is colored by the
    dark and light grey.  The photo-ionization and photo-heating rates
    should be corrected by this overlap fraction $f_c$.  (b)
    Annotation of quantities used in this geometric correction.}
\end{figure}

Consider the solid angle $\Omega_{\rm ray}$ and photon flux $P$
associated with a single ray, and assume the flux is constant across
$\Omega_{\rm ray}$.  There exists a discrenpancy between the geometry
cell face and HEALPix pixel when the pixel does not cover the entire
cell face, which is illustrated in Figure \ref{fig:covering}.  This
mismatch causes non-spherical artifacts and is most apparent in the
optically thin case, where the area of the pixel is dominant over $(1
- e^\tau)$ when calculating $k_{\rm ph}$.  One can avoid these
artifacts by increasing the sampling $\Phi_c$ to high values,
e.g. $>10$, but we have formulated a simple geometric correction to
the calculation of the radiation field.  This correction is not unique
to the HEALPix formalism but can be applied to any type of
pixelization.

The contribution to $k_{\rm ph}$ and $\Gamma_{\rm ph}$ must be
corrected by a covering factor $f_c$.  When the pixel is fully
contained within the cell face, $f_c \equiv 1$.  Because the geometry
of the pixel can be complex, i.e. curved edges, we approximate $f_c$
by assuming the pixel is square.  The covering factor is thus related
to the width of a pixel, $L_{\rm pix} = R_0 \, \theta_{\rm pix}$, and
the distance from the ray segment midpoint to the closest cell
boundary, which is depicted in Figure \ref{fig:covering}.  To estimate
$f_c$, we first find the distance $d_{\rm center,i}$ from the midpoint
of the ray segment to the cell center $x_{\rm 0,i}$ in orthogonal
directions,
%
\begin{equation}
  \label{eqn:midpoint}
  D_{\rm c,i} = \left| R_{\rm 0,i} + \hat{n}_i\,\frac{dr}{2} - x_{\rm
      0,i} \right|.
\end{equation}
The distance to the closest cell boundary is $D_{\rm edge} = dx/2 -
\min_{i=1 \rightarrow 3} (D_{\rm c,i})$.  Thus the covering
factor is related to the square of the ratio between the $L_{\rm pix}$
and $d_{\rm mid}$ by
%
\begin{equation}
  \label{eqn:fc}
  f_c = \left( \frac{1}{2} + \frac{D_{\rm edge}}{L_{\rm pix}} \right)^2
\end{equation}
One half of the pixel is always contained within the cell, which
results in the factor of 1/2.  Finally we multiply $k_{\rm ph}$ and
$\Gamma_{\rm ph}$ by $f_c$ but leave the absorbed radiation $dP$
untouched because this would underestimate the attenuation of the
incoming radiation.  Using $f_c$ calculated like above, the method is
no longer photon conserving.  In our implementation, we felt that the
spherical symmetry obtained outweighed the loss of photon
conservation.  We show the deviations from fully conservative in
\S\ref{sec:test_fc}.

We briefly next describe how to retain photon conservation with a
geometric correction.  Notice that we compute $f_c$ by only
considering the distances in orthogonal directions.  A better estimate
would consider the distance between the cell boundary and ray segment
midpoint in the direction of $\mathbf{x}_{\rm mid} - \mathbf{x}_{\rm
  center}$.  However we find that the method outlined here provides a
sufficient correction factor to avoid any non-spherical artifacts.
Furthermore in principle, the ray should also contribute to any
neighboring cells that overlap with $\Omega_{\rm ray}$, which is the
key to be photon conservative with such a geometric correction.

\subsection{Optically Thin Approximation}

When the medium is optically thin to the radiation, radiation is only
attentuated by geometric dilution in the local approximation to
Eq. (\ref{eqn:rteqn}), i.e. the inverse square law.  We can minimize
the computational work of ray tracing in the optically thin regime by
utilizing this fact.  Here we track the total column density $N_{\rm
  abs}$ and the equivalent total optical depth $\tau$ traversed by the
photon.  If $\tau < \tau_{\rm thin} \sim 0.1$ after the ray exits the
cell, we calculate the photo-ionization and photo-heating rates
directly from the incoming ray instead of the luminosity of the
source.  This should only be evaluated once per cell per radiation
source.
\begin{equation}
  \label{eqn:optthin}
  k_{\rm ph} = \frac{\sigma_{\rm abs} \; P}{dt_P \; \theta_{\rm pix}}
  \; \frac{r_{\rm cell}}{r_{\rm ray}}.
\end{equation}
Note that the photon number $P$ in the ray has already been
geometrically diluted by ray splitting.  Here $r_{\rm cell}$ and
$r_{\rm ray}$ are the radii from the radiation source to the cell
center and where the ray exits the cell.  Thus the last factor
corrects the flux to a value appropriate for the cell center.  The
photo-heating ray is calculated in the same manner as the general
case, $\Gamma_{\rm ph} = k_{\rm ph} (E_{\rm ph} - E_i)$.  No photons
are removed from the ray.  With this method, we only require one ray
travel through each cell where the gas is optically thin, thus
reducing the computational expense.

We must be careful not the overestimate the radiation when multiple
rays enter a single cell.  In the case of a single radiation source,
the solution is simple --- only assign the cell the photo-ionization
and photo-heating rates when $k_{\rm ph} = 0$.  However in the case
with multiple sources, this is no longer valid, and we must sum the
flux from all optically thin sources.  Only one ray per source must
contribute to a single cell in this framework.  We create a flagging
field that marks whether a cell has already been touched by an
optically thin photon from a particular radiation source.  Naively, we
would be restricted to tracing rays from a single source at a time if
we use a boolean flagging field.  However we can trace rays for 32
sources at a time by using bitwise operations on a 32-bit integer
field.  For example in \texttt{C}, we would check if an optically thin
ray from the \texttt{n}-th source has propagated through cell
\texttt{i} by evaluating \texttt{(MarkerField[i] $\gg$ n \& 1)}.  If
false, then we can add the optically thin approximation
(Eq. \ref{eqn:optthin}) to the cell and set \texttt{MarkerField[i] |=
  (1 $\gg$ n);} to mark the cell.

\section{Numerical Implementation in Enzo}

\enzo~is a parallel block-structured AMR \citep{BergerAMR} code that
is publicly available\footnote{http://lca.ucsd.edu/enzo}
\citep{BryanNorman1997, OShea2004}.  In this section, we describe our
parallel implementation of the adaptive ray tracing method into \enzo.
First we explain the programming design of handling the ``photon
packages'' that are traced along the adaptive rays.  We use the terms
photon packages and rays interchangably.  Next we focus on the details
of the radiation hydrodynamics and then the importance of correct
timestepping.  Last we give our parallelization strategy of tracing
rays through an AMR hierarchy.  This implementation is included in the
\texttt{v2.0} public version of \enzo.

\subsection{Programming Design}
\label{sec:design}

Each photon package is stored in the AMR grid with the finest
resolution that contains its current position.  The photon packages
keep track of their (1) photon flux, (2) photon type, (3) photon
energy, (4) the length of its emission, (5) emission time, (6) current
time, (7) radius, (8) total column density, (9) HEALPix pixel number,
(10) HEALPix level, and (11) position of the originating source,
totaling 60 (88) bytes for single (double) precision.  When \enzo~uses
double precision for grid and particle positions and time, items 4-7
and 11 are double precision.

We only treat point sources of radiation in our implementation;
therefore all base level photon packages originate from them.  As they
travel away from the source, they generally pass through many AMR
grids, especially if the simulation has a high dynamic range.  This is
a challenging programming task as rays are constantly entering and
exiting grids.  Before any computation, the number of rays in a
particular grid is highly unpredictable because the intervening medium
is unknown.  Furthermore, the splitting of parent rays into child rays
and a dynamic AMR hierarchy add to the complexity.  Because of this,
we store the photon packages as a doubly linked list
\citep{Abel02_RT}.  Thus we can freely add and remove them from grids
without the concern of allocating enough memory before the tracing
commences.

\begin{figure}[t]
  \plotone{fig/RTcoupling.eps}
  \caption{\label{fig:MainAlgorithm} Flow chart for the overall
    algorithm of the radiative transfer module in \enzo~that
    illustrates (1) the creation of photon packages, (2) ray tracing,
    (3) the transport of photon packages between AMR grids, and (4)
    coupling with the hydrodynamics.  The ray tracing algorithm, which
    is contained in the ``Trace Rays'' is detailed in Figure
    \ref{fig:RTalgorithm}.}
\end{figure}

\begin{figure}[t]
  \plotone{fig/RTalgorithm.eps}
  \caption{\label{fig:RTalgorithm} Flow chart for the ray tracing
    algorithm for one photon passing through a grid.  Note that only
    one step is needed in the routine to adaptively split rays.  The
    remainder is a typical ray tracing method.}
\end{figure}

We illustrate the underlying algorithm of the ray tracing module in
\enzo~in Figure \ref{fig:MainAlgorithm} and the ray tracing algorithm
is shown in Figure \ref{fig:RTalgorithm}.  The module is only called
when advancing the finest AMR level.  We describe its steps below.

\step{1} Create $N_{\rm pix}$ new photon packages on the initial
HEALPix level from point sources.  Place the new rays in the highest
resolution AMR grid that contains the source.

\step{2} Initialize all radiation fields to zero.

\step{3} Loop through all AMR grids, tracing any rays that exist in
it.  For each ray, the following substeps are taken.

\step{3a} Compute the ray normal based on the HEALPix level and pixel
number of the photon package with the HEALpix routine
\texttt{pix2vec\_nest}.  One strategy to accelerate the computation is
to store ray segment paths in memory \citep{Abel02_RT,
  Krumholz07_ART}; however this must be recomputed if the grid
structure or point source position changes.  We do not restrict these
two aspects and cannot employ this acceleration method.

\step{3b} Compute the position of the ray ($\mathbf{r}_{\rm src} + r
\mathbf{\hat{n}}$), the current cell coordinates in floating point and
its corresponding integer indices.  Here $\mathbf{r}_{\rm src}$ is the
position of the point source, $r$ is the distance travelled by the
ray, and $\mathbf{\hat{n}}$ is the ray normal.

\step{3c} Check if a subgrid exists under the current cell.  If so,
move the ray to a linked list that contains all rays that should be
moved to other grids.  We call this variable \texttt{PhotonMoveList}.
Store the destination grid number and level.  Continue to the next ray
in the grid (step 3a).  We determine whether a subgrid exists by
creating a temporary 3D field of pointers that either equals the
pointer of the current grid if no subgrid exists under the current
cell or the child pointer that exists under the current cell.  This
provides a significant speedup when compared to a simple comparision
of a photon package position and all of the child grid boundaries.
Note that this is the same algorithm used in \enzo~when moving
collisionless particles to child grids.

\step{3d} Compute the next cell crossing of the ray and the ray
segment length across the cell (Equation \ref{eqn:trace}).

\step{3e} Compare the solid angle associated with the ray at radius
$r+dr$ with a user-defined splitting criterion (Equation
\ref{eqn:split}).  If the solid angle is larger than the desired
minimum sampling, split the ray into 4 child rays (\S\ref{sec:ART}).
These rays are inserted into the linked list after the parent ray,
which is subsequently deleted.  Continue to the next ray (step 3a),
which will be the first child ray.

\step{3f} Calculate the geometric correction (Equation \ref{eqn:fc}),
the optical depth of the current cell (Equation \ref{eqn:dtau}),
photo-ionization and photo-heating rates (Equations \ref{eqn:kph} and
\ref{eqn:gamma}), and add the column density of the cell to the total
column density of the ray.

\step{3g} Add the effects of any optional physics modules
(\S\ref{sec:addphysics})---secondary ionizations from X-rays, Compton
heating from scattering, and radiation pressure.

\step{3h} Update the current time ($t = t + cdr$), photon flux ($P = P
- dP$, Equation \ref{eqn:flux}), and radius of the ray ($r = r + dr$).

\step{3i} If the photon flux is zero or the total optical depth is
large ($>20$), delete the ray.

\step{3j} Check if the ray has travelled a total distance of $c dt_P$
in the last timestep.  If we are keeping the time-derivative of the
radiative transfer equation, halt the photon.  If not (i.e. infinite
speed of light), delete the photon.

\step{3k} Check if the ray has exited the current grid.  If false,
continue to the next ray (step 3a).  If true, move the ray to the
linked list \texttt{PhotonMoveList}, similar to step 3c.  If the ray
exits the simulation domain, delete it if the boundary conditions are
isolated; otherwise, we change the source position of the ray by a
distance \texttt{-sign(n[i]) * DomainWidth[i]}, where \texttt{n} is
the ray normal, and \texttt{i} is the dimension of the outer boundary
it has crossed.  The radius is kept unchanged.  In essence, this
creates a ``virtual source'' outside the box because the ray will be
moved to the opposite side of the domain, appearing that it originated
from this virtual source.

\step{4} If any rays exist in the linked list \texttt{PhotonMoveList},
move them to their destination grids and return to step 3.  This
requires MPI communication if the destination grid exists on another
processor.

\step{5} If all rays have not been halted (keeping the time-derivative
of the radiative transfer equation), absorbed, or exited the domain,
return to step 3.

\step{6} With the radiation fields updated, call the chemistry and
energy solver and update only the cells with radiation, which is
discussed further in \S\ref{sec:coupling}.

\step{7} Advance the time associated with the photons $t_P$ by the
global timestep $dt_P$ (for its calculation, see
\S\ref{sec:timestepping}).  If $t_P$ does not exceed the time on the
finest AMR level, return to step 1.

\subsection{Energy groups}

In our implementation, photon packages are mono-chromatic and are
assigned a photon type that corresponds whether it is a photon that
(1) ionizes hydrogen, (2) singly ionizes helium, (3) doubly ionizes
helium, (4) has an X-ray energy, or (5) dissociates molecular hydrogen
(Lyman-Werner radiation).  One disadvantage of mono-chromatic rays is
the number of rays increase with the number of frequency bins.
However this allows for early termination of rays that are fully
absorbed, which are likely to have high absorption cross-sections
(e.g. \ion{H}{1} ionizations near 13.6 eV) or a low initial intensity
(e.g. \ion{He}{2} ionizing photons in typical stellar populations).
The other approach used by some groups \citep[e.g.][]{Trac07} is to
store all energy groups in a single ray.  This reduces the number of
the rays generated and the computation associated with the ray
tracing.  Unless the ray dynamically adjusts its memory allocation for
the energy groups as they become depleted, this method is also memory
intensive in the situation where most of the energy groups are
completely absorbed but a few groups still have significant flux.

In practice, we have found that one energy group per photon type is
sufficent to match expected analytical tests.  For example when
modeling Population III stellar radiation \citep[e.g.][for hydrogen
  ionizing radiation only]{Abel07, Wise08b}, we have 3 energy
groups---\ion{H}{1}, \ion{He}{1}, \ion{He}{2}---each with an energy
that equals the average photon energy above the ionization threshold.

\subsection{Coupling with Hydrodynamics}
\label{sec:coupling}

Solving the radiative transfer equation is already an intensive task,
but coupling the effects of radiation to the gas dynamics is even more
difficult because the radiation fields must be updated on a timescale
such that it can react to the radiative heating, i.e. sound-crossing
time.  The frequency of its evaulation will be discussed in the next
section.

\enzo~solves the physical equations in an operator-split fashion over
a loop of AMR grids.  On the finest AMR level, we call our radiation
transport solver before this main grid loop in the following sequence:
\begin{itemize}
\item \textbf{All grids:}
  \begin{enumerate}
  \item Solve for the radiation field with the adaptive ray tracer
  \item Update species fractions and energies for cells with radiation
    with a non-equilibrium chemistry solver on subcycles (Equation
    \ref{eqn:rate_dt}).
  \end{enumerate}
\item \textbf{For each grid:}
  \begin{enumerate}
  \item Solve for the gravitational potential with the particle mesh
    method
  \item Solve hydrodynamics
  \item Update species fractions and energies for cells without
    radiation with a non-equilibrium chemistry solver on subcycles
    (Equation \ref{eqn:rate_dt}).
  \item Update particle positions
  \item Star particle formation
  \end{enumerate}
\item \textbf{All grids:} Update solution from children grids
\end{itemize}
%

Since the solver must be called many times, the efficiency of the
radiation solver is paramount.  After every radiation timestep, we
call the non-equilibrium chemistry and energy solver in \enzo.  This
solves both the energy equation and the network of stiff chemical
equations on small timesteps, i.e. subcycles \citep{Anninos97}.  The
timestep is
%
\begin{equation}
  \label{eqn:rate_dt}
  dt = \min\left(
    \frac{0.1n_e}{|dn_e/dt|}, 
    \frac{0.1n_{\rm HI}}{|dn_{\rm HI}/dt|}, 
    \frac{0.1e}{|de/dt|}, 
    \frac{dt_{\rm hydro}}{2}\right),
\end{equation}
where $n_e$ is the electron number density, $e$ is the specific
energy, and $dt_{\rm hydro}$ is the hydrodynamic timestep.  This
limits the subcycle timestep to a 10\% change in either electron
density, neutral hydrogen density, or specific energy.  In simulations
without radiation, \enzo~calls this solver in a operation-split manner
after the hydrodynamics module for grids only on the AMR level that is
being solved.  In simulations with radiative transfer, the radiation
field can change on much faster timescales than the normal
hydrodynamical timesteps.

For example, a grid on level $L$ might have no radiation in its
initial evaluation, but the ionization front exists just outside its
boundary.  Then radiation permeates the grid in the time between
$t_{\rm L=1} \rightarrow t_{\rm L=1}+dt_{\rm L=1}$, and the energy and
chemical state of the cells must be updated again to advance the
ionization front accurately.  If one does not update these cells, it
will appear that the ionization front does not enter the grid until
the next hydrodynamical timestep!  Visually this appears as
discontinuities in the temperature and electron fraction on grid
boundaries.  One may avert this problem by solving the chemistry and
energy equations for every cell on every radiative transfer timestep,
but this is very time consuming and unnecessary, especially if the
radiation filling factor is small.

We choose to dynamically split the problem by cells with and without
radiation.  In every radiation timestep, the chemo-thermal state of
\textit{only} the cells with radiation are updated.  For the solver
subcycling, we replace $dt_{\rm hydro}$ with $dt_P$ in Equation
\ref{eqn:rate_dt} in this case.  Once the radiative transfer solver is
finished with its timesteps, the hydrodynamic module is called, and
then the chemo-thermal state of the cells without radiation are
updated on a subcycle timestep stated in Equation \ref{eqn:rate_dt}.

For cells that transition from zero to non-zero photo-ionization
rates, the initial state that enters into the chemistry and energy
solver does not correspond to the current time of the radiation
transport solver $t_{\rm RT}$, but either time $t_{\rm L}$ if the grid
level is the finest level because its chemo-thermal state has not been
updated or time $t_{\rm L}+dt_{\rm L}$ on all other levels.  In
principle, one could first revert the cell back to time $t_{\rm L}$
and then update to $t_{\rm RT}$ with the chemistry and energy solver
if the cell is on the finest level.  However in practice, the
timescales in gas without radiation are small compared to the
ionization and heating timescales when radiation is introduced.
Therefore, we do not perform this correction and find that this does
not introduce any inaccuracies in both test problems (see
\S\ref{sec:rt_tests}) and real world applications.

\subsection{Temporal evolution}
\label{sec:timestepping}

There have been several methods of choosing a timestep to solve
radiation transfer equation because an accurate yet large timestep is
not trivial to compute.  With a small enough timestep, the solution is
guaranteed to avoid any inaccuracies (ignoring any systematic ones)
due to timestepping, but the solver must be called many times.  These
frequent calls may be unneccesary because the same solution may be
accomplished with a longer timestep.  Furthermore with ray tracing,
the photon packages only advance a short distance, and they will exist
in every $dx/dt_P$ cells with radiation and are stored between
timesteps, excessively consuming memory.  If the timestep is too
large, the solution will become inaccurate; specifically, ionization
fronts will advance too slowly, as radiation intensity exponentially
drops with a scale length of the mean free path
\begin{equation}
  \label{eqn:mfp}
  \lambda_{\rm mfp} = \frac{1}{n_{\rm abs} \; \sigma_{\rm abs}}
\end{equation}
past the ionization front.  For example in our implementation, the
chemo-thermal state of the system will remain constant as the rays are
traced through the cells.  Thus in the case of a single \ion{H}{2}
region, the speed of the ionization front is limited to approximately
the $\lambda_{\rm mfp} / dt_P$.  We can investigate this further by
evaluating the ionization front velocity in a growing Str\"{o}mgren
sphere, where $\dot{N}_\gamma = 4 \pi R^2 n_{\rm H} v_{\rm IF}$.
Using $\kph \propto \dot{n}_{\rm H} / n_{\rm H}$ and $\kph =
\dot{N}_\gamma \sigma / 4\pi R^2 A_{\rm cell}$, we can make
substitutions on both sides of the equation to arrive at the
ionization front velocity
%
\begin{equation}
  \label{eqn:vifront1}
  v_{\rm IF} \propto \frac{n_{\rm H}}{\dot{n}_{\rm H}}.
\end{equation}

On the shortest timescale, one can safely set the timestep to the
light-crossing time of a cell \citep{Abel99_RT, Trac07} but encounters
the problems stated above.  Next we describe several methods to
calculate the radiative transfer timestep.

\subsubsection{Minimizing neutral fraction change}
\label{sec:dt_hi}

\begin{figure}[t]
  \plottwo{fig/dtp_test3noavg.eps}{fig/dtp_test3.eps}
  \caption{\label{fig:dtsmooth} Radiative transfer adaptive timestep
    in shadowing test (Test 3; \S\ref{sec:test3}) while restricting
    the neutral fraction change to 5\% in the ionization front.  The
    unmodified timestep (left) is slightly more noisy and the minima
    are more prominent than the timestep computed with a running
    average of the last two timesteps (right).  The points show every
    tenth timestep taken into account for the running average.  The
    sawtooth behavior is created by the ionization front advancing
    into the next neutral cell in the overdensity.}
\end{figure}

Another strategy is only allowing the neutral fraction of the ionized
gas to change a small amount, i.e. for a single cell,
%
\begin{equation}
  \label{eqn:dtelec}
  dt_{\rm P,cell} = \epsilon_{\rm ion} \frac{n_{\rm HI}}{|dn_{\rm HI}/dt|} =
  \frac{\epsilon_{\rm ion}}{|k_{\rm ph} + n_e (C_{\rm H} + \alpha_B)|},
\end{equation}
where $\epsilon_{\rm ion}$ is the maximum fraction change in neutral
fraction.  \citet{Shapiro04} found that this limited the speed of the
ionization front for the same reasons described in Equation
\ref{eqn:vifront1}.  We have implemented this method but we only
consider cells within the ionization front (by experiment we choose
$\tau > 0.5$) because we are interested in evolving ionization fronts
at the correct speed.  In the ionized region, the absolute changes in
neutral fraction are small and will not significantly affect the
ionization front evolution.  In other words, $n_{\rm HI}/(dn_{\rm
  HI}/dt)$ may be large but $(dn_{\rm HI}/dt) \sim 0$, thus we can
safely ignore these cells when determining the timestep without
sacrificing accuracy.

We search for the cell with the smallest $dt_P$ based on Equation
\ref{eqn:dtelec}.  In principle, one could use this value without
modifications as the timestep, but there is considerable noise both
spatially and temporally.  In order to make this technique stable, we
first spatially smooth the values of $dt_{\rm P,cell}$ with a Gaussian
filter over a $3^3$ cube.  Because we only consider the cells within
the ionization front, we set $dt_{\rm P,cell}$ to the hydrodynamical
timestep outside the front during the smoothing.  After we have
smoothed $dt_{\rm P,cell}$, we select the minimum value as $dt_P$.
Significant noise in $dt_P$ can exist between time discretizations.
Because the solution can become inaccurate if the timestep is allowed
to be too large, we restrict the next timestep to be less than twice
the previous timestep,
%
\begin{equation}
  \label{eqn:dtchange}
  dt_{\rm P,1} = \min(2 dt_{\rm P,0},\; dt_{\rm P,1}).
\end{equation}
Otherwise, we still restrict the change in timestep by setting the
next timestep to be the average of the previous timestep $dt_{\rm
  P,0}$ and $\min(dt_{\rm P,cell})$.  Figure \ref{fig:dtsmooth} shows
the smooth evolution of $dt_{\rm P}$ in a growing Str\"{o}mgren sphere when
compared to the values of $\min(dt_{\rm P,cell})$.

\subsubsection{Time averaged quantites within a timestep}

\citet{Mellema06} devised an iterative scheme that allows for large
timesteps while retaining accuracy by considering the time-averaged
values ($\tau$, $k_{\rm ph}$, $n_e$, $n_{\rm HI}$) during the
timestep.  Starting with the cells closest to the source, they first
calculate the column density to the cell.  Then they compute the
time-averaged neutral density for the cell and its associated optical
depth, which is added to the total time-averaged optical depth.  With
these quantities, one can compute a photo-ionization rate and update
the electron density.  This process is repeated until convergence is
found in the neutral number density.  In a test with a Str\"{o}mgren
sphere, they found analytical agreement with $10^{-3}$ less timesteps
than a method without time-averaging.  Another advantage of this
method is the use of pre-calculated tables for the photo-ionization
rates as a function of optical depth, based on a given spectrum.  This
minimizes the energy groups needed to accurately sample a spectrum.
We are currently implementing this method into Enzo+Moray.

\subsubsection{Physically motivated}
\label{sec:dt_const}

In our implementation, a constant timestep is necessary when solving
the time-dependent radiative transfer equation.  It should be small
enough to evolve ionization fronts accurately, as discussed earlier.
The timestep can be based on physical arguments, for example, the
sound-crossing time of an ionized region at $T > 10^4$ K.  To be
conservative, one may choose the sound-crossing time of a cell
\citep[e.g.][]{Abel07, Wise08b}.  Alternatively, the diameter of the
smallest relevant system (e.g., an accretion radius, transition radius
to a D-type ionization front, etc.) in the simulation may be chosen to
calculate the sound-crossing time.

If the timestep is too large, the ionization front will propagate too
slowly, but it evenutually approaches the correct radius at late times
(see \S\ref{sec:dt_dep}).  This does not prevent one from using a
large timestep, particularly if the system is not critically affected
by a slower I-front velocity.  One example is an expanding \ion{H}{2}
region in a power-law density gradient.  After a brief, initial R-type
phase, the I-front becomes D-type phase, where the ionization and
shock front progress jointly at the sound speed of the ionized region.
A moderately large (\textbf{show how large!}) timestep can accurately
follow its evolution.  However after the I-front passes a critical
radius \citep[show this!][]{Franco90}, the I-front detaches from the
shock front and accelerates.  The I-front velocities in these two
stages differ up to a factor of $\sim100$ (\textbf{check this!}).
Although the solution is accurate with a large timestep in the D-type
phase, the I-front may lag behind because of the constant timestep.
After a few recombination times, the numerical solution evenutally
approaches the analytical solution.  If such a simulation focuses on
the density core expansion and any small scale structures, such as
cometary structures and photo-dissociation regions, one can cautiously
sacrifice temporal accuracy at large scales for computational savings.

\subsubsection{Change of incident radiation}
\label{sec:dt_tau}

Ionization front velocities can approach significant fractions of the
speed of light in steep density gradients and in the early expansion
of the \ion{H}{2} region.  If the ionization front position is
critical to the calculation, the radiation transport timestep can be
derived from an estimate of the ionization front velocity
%
\begin{equation}
  \label{eqn:dt_incident}
  v_{\rm IF}(\mathbf{r}) \approx \frac{F(\mathbf{r})}
  {n_{\rm abs}(\mathbf{r})},
\end{equation}
%
based on the incident radiation field at a particular position.  The
timestep is then chosen so that the ionization front only crosses one
cell per timestep $dt_{\rm P, cell} = dx / v_{\rm IF}$, and the global
timestep is $dt_{\rm P} = \min(dt_{\rm P, cell})$.

To make this approach computationally straightforward, we consider a
spherically symmetric case without recombinations.  Thus all photons
emitted from the source result in an ionization (see
Eq. \ref{eqn:vifront1} and its derivation).  Ultimately in any
approach, we are focused on accurately following the time evolution of
the radiation field.  In this method, we base the timestep directly on
the change in radiation field, the specific intensity, $I/\dot{I}$.
We consider the field after propagating through the cell, so $I = I_0
\exp(-\tau)$, where $\tau = n_{\rm H} \sigma dl$ is the optical depth
through the cell.  The change in specific intensity is
%
\begin{equation}
  \label{eqn:vifront2}
    \frac{dI}{dt} = I_0 \exp(-\tau) (-\dot{n}_{\rm H} \sigma dl),
\end{equation}
%
which can be expressed in terms of local optical depth and neutral
fraction,
\begin{equation}
  \label{eqn:vifront3}
    \frac{dI}{dt} = -I \frac{\tau \dot{n}_{\rm H}}{n_{\rm H}}.
\end{equation}
%
This results in a local timestep
%
\begin{equation}
  \label{eqn:vifront4}
  dt_P = \frac{I}{|dI/dt|} = C_{\rm RT,cfl} \frac{n_{\rm H}}{\tau \dot{n}_{\rm H}},
\end{equation}
%
where $C_{\rm RT,cfl}$ is a safety factor that restricts the change in
intensity to its inverse.  In practice, we have found that a ceiling
of 3 can be placed on the optical depth, so optically thick cells do
not create a very small timestep.  We still find excellent agreement
with analytical solutions with this approximation.  We show the
accuracy using this timestep method in \S\ref{sec:dt_dep}.

\subsection{Parallelization Strategy}

Parallelization of the ray tracing code is essential when exploring
problems that require high resolution and thus large memory
requirements.  Furthermore, \enzo~is already parallelized and scalable
to $O(10^2)$ processors in AMR simulations, and $O(10^3)$ in unigrid
calculations.  \enzo~stores the AMR grid structure on every processor,
but only one processor contains the actual grid and particle data and
photon packages.  All other processors contain an empty grid
container.  As discussed in \textit{Step 4} in \S\ref{sec:design}, we
store the photon packages that need to be transferred to other grids
in the linked list \texttt{PhotonMoveList}.  In a single processor
(serial) run, moving the rays is trivial by inserting these photons
into the linked list of the destination grid.  For multi-processor
runs, we must send these photons through MPI communication to the
processors that host the data of the destination grids.  We describe
our strategy below.

The easiest case is when the destination grid exists on the same
processor as the source grid, where we move the ray as in the serial
case.  For all other rays, we organize the rays by destination
processors and send them in groups.  We also send the destination grid
level and ID number along with the ray information, which is listed at
the beginning of \S\ref{sec:design}.

For maximum overlap of communication and computation, which enables
scaling to large numbers of processors, we must employ
``non-blocking'' MPI communication, where each processor does not wait
for synchronization with other processors.  We use this technique for
the sending and receiving of rays.  Here we desire to minimize the
idle time of each processor when it is waiting to receive data.  In
the loop shown in Figure \ref{fig:MainAlgorithm} with the conditional
that checks whether we have traced all of the rays, we aggressively
transport rays that are local on the processor, and process any MPI
receive calls as they arrive, not waiting for their completion in
order to continue to the next iteration.  We describe the steps in
this algorithm next.

\step{1} Before any communication occurs, we count the number of rays
that will be sent to each processor.  The MPI receive calls
(\texttt{MPI\_Irecv}) must have a data buffer that is greater than or
equal to the size of the message.  We choose to send a maximum of
$N_{\rm max}$ (= 10$^5$ in \enzo~\texttt{v2.0}) rays per MPI message.
Therefore, we allocate a buffer of this size for each
\texttt{MPI\_Irecv} call.  We then determine the number of MPI messages
$N_{\rm mesg}$ and send this number in a non-blocking fashion,
i.e. \texttt{MPI\_Isend}.

\step{2} Pack the photon packages into a contigious array for MPI
communication while the messages from Step 1 completes.

\step{3} Process the number of photon messages that we are expecting
from each processor, sent in Step 1.  Then post this number of
\texttt{MPI\_Irecv} calls for the photon data.  Because we strive to
make the ray tracing routine to be totally non-blocking, the
processors will most likely not be synchronized on the same loop
(Steps 3--5 in \S\ref{sec:design}).  Therefore, there might be
additional $N_{\rm mesg}$ MPI messages waiting to be processed.  We
check for these messages and aggressively drain the message stack to
determine the total number of photon messages that we are expecting
and post their associated \texttt{MPI\_Irecv} calls for the photon
data.

\step{4} Send the grouped photon data with \texttt{MPI\_Isend} with a
maximum size of $N_{\rm max}$ photons.

\step{5} Place any received photon data into the destination grids.
We monitor whether the processor has any rays that were moved to grids
on the same processor.  If so, this processor has rays to transport,
and we do not necessarily have to wait for any MPI receive messages
and thus use \texttt{MPI\_Testsome} to receive any messages that have
already arrived.  If not, we call \texttt{MPI\_Waitsome} to wait for
any MPI receive messages.

\step{6} If all processors have exhausted their workload, then all
rays have been either absorbed, exited the domain, or halted after
travelling a distance $cdt_P$.  We check this in a similar
non-blocking manner as the $N_{\rm mesg}$ calls in Step 1.

Lastly we have experimented with a hybrid OpenMP/MPI version of \enzo,
where workload is partitioned over grids on each MPI process.  We
found that parallelization over grids for the photon transport does
not scale well, and threading over the rays in each grid is a better
approach.  Because the rays are stored in a linked list in each grid,
we must manually split the list into separate lists and let each
thread work on each list.

\section{Radiative Transfer Tests}
\label{sec:rt_tests}

Tests plays an important role in creating and maintaining
computational tools.  In this section, we present tests drawn from the
Cosmological Radiative Transfer Codes Comparison Project
\citep[][hereafter RT06]{RT06}, where results from 11 different
radiative transfer codes compared results in four test problems.  The
codes use various methods for radiation transport: ray tracing with
short, long, and hybrid characteristics, Monte Carlo casting;
ionization front tracking \citep{Alvarez06_IFT}; variable Eddington
Tensor formalism \citep{Gnedin01_OTVET}.  They conducted tests that
investigated (1) the growth of a single Str\"{o}mgren sphere enforcing
isothermal conditions, (2) the same test with an evolving temperature
field, (3) shadowing created by a dense, opticlally thick clump, and
(4) multiple \ion{H}{2} regions in a cosmological density field.  In
all of the tests presented here, we use the method of restricted
neutral fraction changes (\S\ref{sec:dt_hi}) for choosing a radiative
transfer timestep.  We cast 48 rays (HEALPix level 1) from the point
source and require a sampling of at least $\Phi_c = 5.1$ rays per
cell.

\subsection{Test 1. Pure hydrogen isothermal \ion{H}{2} region
  expansion}
\label{sec:test1}

\begin{figure}[t]
  \plottwo{fig/test1_ionfrac.eps}{fig/test1_ifront.eps}
  \caption{\label{fig:test1_ifront} Test 1 (\ion{H}{2} region
    expansion with a monochromatic spectrum of 13.6 eV).  Left:
    Radially averaged profile of neutral (solid) and ionized (dashed)
    fraction at 10, 30, 100, and 500 Myr.  Right: Evolution of the
    calculated (top, dashed) and analytical (top, solid) Str\"{o}mgren
    radius.  The ratio of these radii are plotted in the bottom panel.}
\end{figure}

\begin{figure}[t]
  \epsscale{0.8}
  \plotone{fig/test1_HI500.eps}
  \caption{\label{fig:test1_HI} Test 1 (\ion{H}{2} region expansion
    with a monochromatic spectrum of 13.6 eV). Slice of neutral
    fraction at the origin at 500 Myr.}
  \epsscale{1.0}
\end{figure}

The expansion of an ionizing region with a central source in a uniform
medium is a classic problem first studied by \citet{Stroemgren39}.
This simple but useful test can uncover any asymmetries or artifacts
that may arise from deficiencies in the method or newly introduced
bugs in the development process.  In this problem, the ionized region
grows until recombinations balance photo-ionizations, which happens at
a radius of
%
\begin{equation}
  \label{eqn:Rstr}
  R_s = \left(\frac{3\dot{N}_\gamma}{4\pi \alpha_{\rm B} n_H^2}\right)^{1/3},
\end{equation}
where $\dot{N}_\gamma$ is the ionizing photon luminosity, $\alpha_{\rm
  B}$ is the recombination rate, and $n_H$ is the ambient hydrogen
number density.  The evolution of the radius $r_s$ and velocity $v_s$
of the ionization front has an exact solution of
%
\begin{equation}
  \label{eqn:rstr}
  r_s(t) = R_s [ 1 - \exp(-t/t_{\rm rec}) ]^{1/3}
\end{equation}
\begin{equation}
  \label{eqn:vstr}
  v_s(t) = \frac{R_s}{3t_{\rm rec}} \frac{\exp(-t/t_{\rm rec})} {[1 -
    \exp(-t/t_{\rm rec})]^{2/3}},
\end{equation}
where $t_{\rm rec} = (\alpha_{\rm B} n_H)^{-1}$ is the recombination
time.

We adopt the problem parameters used in RT06.  The ionizing
source emits $5 \times 10^{48}$ ph s$^{-1}$ of monochromatic radiation
at 13.6 eV and is located at the origin in a simulation box of 6.6
kpc.  The ambient medium is initially set at $T=10^4$ K, $n_H =
10^{-3} \cubecm$, $x = 1.2 \times 10^{-3}$, resulting in $R_s = 5.4$
kpc and $t_{\rm rec} = 122.4$ Myr.  The problem is run for 500 Myr.
In the original tests, the temperature is fixed at $10^4$ K; however,
our solver is inherently tied to the chemistry and energy solver.  To
mimic an isothermal behavior, we set the adiabatic index $\gamma =
1.0001$, which ensures an isothermal state but not a fixed ionization
fraction outside of the Str\"{o}mgren sphere.

In Figure \ref{fig:test1_ifront}, we show (a) the evolution of the
neutral and ionization fraction as a function of radius at $t = $ 10,
30, 100, and 500 Myr, and (b) the growth of the ionization front
radius as a function of time and its ratio with the analytical
Str\"{o}mgren radius (Eq. \ref{eqn:rstr}).  The ionization front has a
width of $\sim0.7$ kpc, which is in agreement with the inherent
thickness of $\sim18 \lambda_{\rm mfp} = 0.74$ kpc, given a 13.6 eV
mono-chromatic spectrum.  There are small kinks in the neutral
fraction at 1.5 and 3 kpc that corresponds to artifacts created by the
photon package splitting at these radii.  However these do not affect
the overall solution.  One difference between our results and the
codes presented in RT06 is the increasing neutral fraction outside of
the \ion{H}{2}.  This occurs because the initial ionized fraction and
temperature is set to $1.3 \times 10^{-3}$ and 8000 K, which are not
the equilibrium values.  Over the 500 Myr in the calculation, the
neutral fraction increases to 0.2, which is close to its equilibrium
value.  In the right panel of Figure \ref{fig:test1_ifront}, the
ionization front radius exceeds $R_s$ by a few percent for most of the
calcuation.  This difference happens because the analytical solution
(Eq. \ref{eqn:rstr}) assumes the \ion{H}{2} region has a constant
ionized fraction.  The evolution of the ionized fraction as a function
of radius can be analytically calculated \citep[e.g.][]{Osterbrock89,
  Petkova09}, causing the ionization front radius to be slightly
larger, increasing from 0 to 3\% in the interval 80--350 Myr.  Our
results are in excellent agreement with this more accurate analytical
solution.  In Figure \ref{fig:test1_HI}, we show a slice of the
neutral fraction through the origin.  Other than the ray splitting
artifacts that generate the plateaus at 1.5 and 3 kpc, one sees
spherical symmetry in our solution.

\subsection{Test 2. \ion{H}{2} region expansion: temperature evolution}

\begin{figure}[t]
  \plottwo{fig/test2_ionfrac.eps}{fig/test2_neutral.eps}
  \caption{\label{fig:test2_1} Test 2. (\ion{H}{2} region
    expansion with a $T=10^5$ K blackbody spectrum).  Left:
    Radially averaged profile of neutral (solid) and ionized (dashed)
    fraction at 10, 30, 100, and 500 Myr.  Right: Evolution of the
    average neutral fraction.}
\end{figure}

\begin{figure}[t]
  \plotone{fig/test2_ifront.eps}
  \caption{\label{fig:test2_2} Test 2. (\ion{H}{2} region expansion
    with a $T=10^5$ K blackbody spectrum).  Top: Evolution of the
    radius of the simulated ionization front (dashed) and analytical
    (solid) Str\"{o}mgren radius.  Bottom: The ratio of the calculated
    and analytical Str\"{o}mgren radius.}
\end{figure}

\begin{figure}[]
  \plotone{fig/test2_slices}
  \caption{\label{fig:test2_3} Test 2. (\ion{H}{2} region expansion
    with a $T=10^5$ K blackbody spectrum).  Top: Slices through the
    origin of neutral fraction at 10 and 100 Myr.  Bottom: Slices of
    temperature at 10 and 100 Myr.}
\end{figure}

This test is similar Test 1, but the temperature is allowed to evolve
The radiation source now has a blackbody spectrum with a $T = 10^5$ K.
The initial temperature is set at 100 K.  The higher energy photons
have a longer mean free path than the photons at the ionization
threshold in Test 1.  Thus the ionization front is thicker as the
photons can penerate deeper into the neutral medium.  Here we use 4
energy groups with the following mean energies and relative
luminosities: $E_i = (16.74, 24.65, 34.49, 52.06)$, $L_i/L = (0.277,
0.335, 0.2, 0.188)$.

In Figure \ref{fig:test2_1}, we show the neutral and ionized fraction
as a function of radius at $t = $ 10, 30, 100, and 500 Myr, and the
total neutral fraction of the domain.  Compared with Test 1, the
ionization front is thicker, as expected with the harder spectrum.
The total neutral fraction decreases to 0.67 over 4$t_{\rm rec} = 500$
Myr, which is in agreement with the analytical expectation and other
codes in RT06.  In Figure \ref{fig:test2_2}, we show the ratio of the
ionization front radius $r_{\rm IF}$ in our simulation and $R_s$.
Before $1.5t_{\rm rec}$, $r_{\rm IF}$ lags behind $R_s$, initially by
10\% and then increases to $R_s$; however afterwards, this ratio
asymptotes to a solution that is 4\% greater than $R_s$.  This
behavior puts our code is approximately the median result in RT06,
where this ratio varies between 1 and 1.1, and the early evolution of
$r_{\rm IF}$ is underpredicted by almost all of the codes.  If we use
one energy group with the mean energy (29.6 eV) of a $T=10^5$ K
blackbody, we find that $r_{\rm IF}/R_s$ = 1.08, which is
representative of the codes in the upper range of RT06.  In Figure
\ref{fig:test2_3}, we show slices of neutral fraction and temperature
through the origin at $t = $ 10 and 100 Myr.  Here one sees the
spherically symmetric \ion{H}{2} regions and a smooth temperature
transition to the neutral ambient medium.

\subsection{Test 3. I-front trapping in a dense clump and the
  formation of a shadow}
\label{sec:test3}

\begin{figure}[t]
  \plottwo{fig/test3_HI.eps}{fig/test3_temp.eps}
  \caption{\label{fig:test3_1} Test 3. (I-front trapping in a dense
    clump and shadowing).  Left panel: Line cut from the point source
    through the middle of the dense clump at $t = 1, 3, 5, 15$ Myr.
    of the average neutral fraction (left) and temperature
    (right) of the clump.}
\end{figure}

\begin{figure}[t]
  \plotone{fig/test3_clump.eps}
  \caption{\label{fig:test3_2} Test 3. (I-front trapping in a dense
    clump and shadowing).  Evolution of the average ionized fraction
    (top) and temperature (bottom) of the overdense clump.}
\end{figure}

\begin{figure}[t]
  \plotone{fig/test3_slices}
  \caption{\label{fig:test3_3} Test 3. (I-front trapping in a dense
    clump and shadowing).  Clockwise from upper left: Slices through
    the origin of neutral fraction (1 Myr), temperature (1 Myr),
    temperature (15 Myr), and neutral fraction (15 Myr).}
\end{figure}

The diffusivity and angular resolution of a radiative transport method
can be tested with the trapping of an ionization front by a dense,
neutral clump.  In this situation, the ionization front will uniformly
propagate until it reaches the clump surface.  Then the radiation in
the line of sight of the clump will be absorbed more than the ambient
medium.  If the clump is optically thick, a shadow will form behind
the clump.  The sharpness of the ionization front at the shadow
surface can be used to determine the diffusivity of the method.
Furthermore the shadow surface should be aligned with the outermost
neutral regions of the clump, which can visually assess the angular
resolution of the method.

The problem for this test is contained in a 6.6 kpc box with an
ambient medium of $n_H = 2 \times 10^{-4} \cubecm$ and $T = 8000$ K.
The clump is in pressure equilibrium with $n_H = 0.04 \cubecm$ and $T
= 40$ K.  It has a radius of $r_c = 0.8$ kpc and is centered at
$(x,y,z) = (5, 3.3, 3.3)$ kpc.  In RT06, the test considered a plane
parallel radiation field with a flux $F_0 = 10^6$ ph s$^{-1}$
cm$^{-2}$ originating from the $y=0$ plane.  Our code can only
consider point sources, so we use a single radiation source located in
the center of the $y=0$ boundary.  The luminosity of $\dot{N}_\gamma =
3 \times 10^{51}$ ph s$^{-1}$ corresponds to the same flux $F_0$.  The
location where the ionization front trapping can be calculated
analytically \citep{Shapiro04}, and with these parameters, it should
halt at approximately the center of the clump.  We use the same four
energy groups as in Test 2.

In Figure \ref{fig:test3_1}, we show neutral fraction and temperature
of a one-dimensional cut through the center of the dense clump at $z =
0.5$ at $t = 1, 3, 5, 15$ Myr.  The ionization front is halted at a
little more than halfway through the clump, which is consistent with
the analytical expectation.  The hardness of the $T = 10^5$ K
blackbody spectrum allows the gas outside of the ionization front.
Where the gas is ionized, the temperature is between 10,000 and 20,000
K, but decreases sharply with the ionized fraction.  Figure
\ref{fig:test3_2} depicts the average ionized fraction and temperature
inside the dense clump, which both gradually increase as the
ionization front propagates through the overdensity.  Our results are
consistent with RT06.  Finally we show slices of neutral fraction and
temperature in the $z = 0.5$ plane in Figure \ref{fig:test3_3}.  The
neutral fraction slices prominently show the sharp shadows created by
the clump and demonstrates the non-diffusivity behavior of ray
tracing.  The discretization of the sphere creates one neutral cell on
the left side of the sphere.  This inherent artifact to the initial
setup carries through the calculation.  We did not smooth the clump
surface like in some of the RT06 codes, in order to remove this
artifact.  It is seen in the neutral fraction and temperature states
at all times and is not a caused by our ray tracing algorithm.

\subsection{Test 4. Multiple sources in a cosmological density field}

\begin{figure}[t]
  \epsscale{0.75}
  \plotone{fig/test4_ion}
  \caption{\label{fig:test4_1} Test 4. (Multiple cosmological
    sources).  Evolution of the mass- (dashed) and volume-averaged
    (solid) ionized fraction.}
  \epsscale{1}
\end{figure}

\begin{figure}[t]
  \epsscale{0.9}
  \plotone{fig/test4_slices}
  \caption{\label{fig:test4_2} Test 4. (Multiple cosmological
    sources).  Top: Slices through the origin of neutral fraction at
    50 and 200 kyr at the coordinate $z = z_{\rm box}/2$.  Bottom:
    Slices of temperature at 50 and 200 kyr.  No smoothing has been
    applied to the images.}
  \epsscale{1}
\end{figure}

The last test in RT06 involves a static cosmological density field at
$z=9$.  The simulation comoving box size is 0.5 $h^{-1}$ Mpc and has a
resolution of 128$^3$.  There are 16 point sources that are centered
in the 16 most massive halos.  They emit $f_\gamma = 250$ ionizing
photons per baryon in a blackbody spectrum with an effective
temperature $T = 10^5$ K, and they live for $t_s = 3$ Myr.  Thus the
luminosity of each source is
%
\begin{equation}
  \label{eqn:cosmo_lum}
  \dot{N}_\gamma = f_\gamma \frac{M \Omega_b} {\Omega_m m_H t_s},
\end{equation}
where $M$ is the halo mass, $\Omega_m = 0.27$, and $\Omega_b =
0.043$.  The radiation boundaries are isolated so that the radiation
leaves the box instead being shifted periodically.  The simulation is
evolved for 0.4 Myr.

We show the growth of the \ion{H}{2} regions by computing the
mass-averaged $x_m$ and volume-averaged $x_v$ ionized fraction in
Figure \ref{fig:test4_1}.  Initially $x_m$ is larger than $x_v$, and
at $t \sim 170$ kyr, the $x_v$ becomes larger.  This is indicative of
inside-out reionization \citep[e.g.][]{Gnedin00, Miralda00,
  Sokasian03}, where the dense regions around halos are ionized first,
then the voids are ionized last.  At the end of the simulation, $x_v =
0.65$, which is lower than all of the codes in RT06.  However by
visual inspection in the slices of electron fraction
(Fig. \ref{fig:test4_2}), there appears to be very good agreement with
C$^2$-ray and FTTE.  By first glance, our result appears to be
different than the RT06 because of the color-mapping.  Our results are
also in good agreement with the multi-frequency version of TRAPHIC
\citep[][see also for better representations of the electron fraction
  slices]{Pawlik10}.  In the slices of electron fraction and
temperature, Figure \ref{fig:test4_2}, the photo-heated regions are
larger than the ionized regions by a factor of 2--3 because of the
hardness of the $T = 10^5$ K blackbody spectrum.

\section{Radiation Hydrodynamics Tests}
\label{sec:radhydro}

In this section, we show results from radiation hydrodynamics test
problems presented in \citet[][hereafter RT09]{Iliev09}.  They involve
(1) the expansion of an \ion{H}{2} region in a uniform medium, similar
to Test 2, (2) an \ion{H}{2} region in an isothermal sphere, and (3)
the photo-evaporation of a dense, cold clump, similar to Test 3.  We
expand on this test suite to include more complex situations, such as
a Rayleigh-Taylor problem illuminated by a radiation source, champange
flows, collimated radiation, an irradidated blast wave, and an
\ion{H}{2} region in a rotating sphere.  For the \citeauthor{Iliev09}
tests, we turn off self-gravity and AMR in accordance with them.  In
the latter tests, we will indicate whether we use those capabilities
of \enzo.  Lastly, we use the new MHD implementation in \enzo~v2.0 in
the problem of a growing \ion{H}{2} region in a magnetic field.

\subsection{Test 5: Classical \ion{H}{2} region expansion}
\label{sec:test5}

\begin{figure}[t]
  \epsscale{0.75}
  \plotone{fig/test5_ifront}
  \caption{\label{fig:test5_1} Test 5. (\ion{H}{2} region in a uniform
    medium).  Top: Growth of the computed ionization front radius at
    an ionized fraction $x_e = 0.5$ (dashed) and at a temperature $T =
    10^4$ K (dotted) compared to the analytical estimate (solid;
    Eq. \ref{eqn:test5_r}).  Bottom: The ratio of the computed
    ionization front radii to the analytical estimate.} 
  \epsscale{1}
\end{figure}

\begin{figure}[t]
  \plotone{fig/test5_profiles}
  \caption{\label{fig:test5_2} Test 5. (\ion{H}{2} region in a uniform
    medium).  Clockwise from the upper left: Radial profiles of
    density, temperature, ionized fraction, and pressure at times $t
    =$ 10, 200, and 500 Myr.}
\end{figure}

\begin{figure}[t]
  \plotone{fig/test5_slices}
  \caption{\label{fig:test5_3} Test 5. (\ion{H}{2} region in a uniform
    medium).  Clockwise from the upper left: Slices through the origin
    of ionized fraction, neutral fraction, temperature, and density at
    time $t =$ 500 Myr.}
\end{figure}

Here we consider the expansion of an \ion{H}{2} region into a uniform
neutral medium including the hydrodynamical response to the heated
gas.  The ionized region has a greater pressure than the ambient
medium, causing it to expand.  This is a well-studied problem
\citep{Spitzer78} with an analytical solution, where the ionization
front moves as
%
\begin{equation}
  \label{eqn:test5_r}
  r_s(t) = r_{s,0} \left(1 + \frac{7c_s}{4R_s}\right)^{4/7},
\end{equation}
where $c_s$ is the sound speed of the ionized gas and $r_{s,0}$ is the
$r_s$ in Equation \ref{eqn:rstr}.  The bubble eventually reaches
pressure equilibrium with the ambient medium at a radius
%
\begin{equation}
  \label{eqn:test5_final}
  r_f = R_s \left(\frac{2T}{T_0}\right)^{2/3},
\end{equation}
where $T$ and $T_0$ are the ionized and ambient temperatures,
respectively.  These solutions only describe the evolution at late
times, and not the fast transition from R-type to D-type at early
times.

The simulation setup is similar to Test 2 with the exception of the
domain size $L = 15$ kpc.  Here pressure equilbrium occurs at $r_f =
185$ kpc, which is not captured by this test.  However more
interestingly, the transition from R-type to D-type is captured and
occurs around $R_s = 5.4$ kpc.  The test is run for 500 Myr.

The growth of the \ion{H}{2} region is shown in Figure
\ref{fig:test5_1}, using both $T = 10^4$ K and $x_e = 0.5$ as
ionization front definitions, compared to the analytical solution
(Eq. \ref{eqn:test5_final}).  We define this alternative measure
because the ionization front becomes broad as the D-type front creates
a shock.  Densities in this shock, as seen in Figure
\ref{fig:test5_2}, are high enough for the gas to recombine but not
radiatively cool.  Before $2t_{\rm rec} \approx 250$ Myr, the
temperature cutoff overestimates $r_s$ by over 10\%; however at later
times, it provides a good match to the $t^{4/7}$ growth at late times.
With the $x_e = 0.5$ criteron for the ionization front, the radius is
always underestimated by $\sim20\%$.  This behavior was also seen in
RT09.

Figure \ref{fig:test5_2} shows the progression of the ionization front
at times $t$ = 10, 200, and 500 Myr in radial profiles of density,
temperature, pressure, and ionized fraction.  The initial \ion{H}{2}
region is overpressurized and creates an outward shock wave.  The
high-energy photons can penerate through the shock and partially
ionizes and heats the exterior gas, clearly seen in the profiles.  As
noted in RT09, this heated exterior gas creates an photo-evaporative
flow that flows inward.  This interacts with the primary shock and
creates the double-peaked features in the density profiles at 200 and
500 Myr.  Figure \ref{fig:test5_3} shows slices through the origin of
the same quantities, including neutral fraction.  These depict the
very good spherical symmetry of our method.  The only apparent
artifact is a very slight diagonal line, which is caused by the
HEALPix pixelization differences between the polar and equatorial
regions.  This artifact diminishes as the ray-to-cell sampling is
increased.

\subsection{Test 6: \ion{H}{2} region expansion in an isothermal
  sphere}

\begin{figure}[t]
  \epsscale{0.75}
  \plotone{fig/test6_ifront}
  \caption{\label{fig:test6_1} Test 6. (\ion{H}{2} region in a 1/$r^2$
    density profile).  Top: Growth of the computed ionization front
    radius as $T=10^4$ K and $x_e = 0.5$ as definitions for the front.
    Bottom: Velocity of the ionization front, computed from outputs at
    0.5 Myr intervals.  The velocity is calculated from $r_{\rm IF}$,
    whose coarse time resolution causes the noise seen in $v_{\rm
      IF}$.  It is smooth within the calculation itself.}
  \epsscale{1}
\end{figure}

\begin{figure}[t]
  \plotone{fig/test6_profiles}
  \caption{\label{fig:test6_2} Test 6. (\ion{H}{2} region in a 1/$r^2$
    density profile).  Clockwise from the upper left: Radial profiles of
    density, temperature, ionized fraction, and pressure at times $t
    =$ 3, 10, and 25 Myr.}
\end{figure}

\begin{figure}[t]
  \plotone{fig/test6_slices}
  \caption{\label{fig:test6_3} Test 6. (\ion{H}{2} region in a 1/$r^2$
    density profile).  Clockwise from the upper left: Slices through the origin
    of ionized fraction, neutral fraction, temperature, and density at
    time $t =$ 25 Myr.}
\end{figure}

A more physically motivated scenario is an isothermal sphere with a
constant density $n_c$ core, which is applicable to collapsing
molecular clouds and cosmological halos.  The radial density profile
is described by
%
\begin{equation}
  \label{eqn:test6_rho}
  n(r) = \left\{ \begin{array}{l@{\quad}l}
      n_c & (r \le r_0)\\
      n_c (r/r_0)^{-2} & (r > r_0)
    \end{array} \right. ,
\end{equation}
where $r_0$ is the radius of the core.  If the Str\"{o}mgren radius is
smaller than the core radius, then the resulting \ion{H}{2} region
never escapes into the steep density slope.  When the ionization front
propagates out of the core, it accelerates as it travels down the
density gradient.  There exists no analytical solution for this
problem with full gas dynamics but was extensively studied by
\citet{Franco90}.  After the gas is ionized and photo-heated, the
density gradient provides the pressure imbalance to drive the gas
outwards.

This test is constructed to study the transition from R-type to D-type
in the core and back to R-type in the density gradient.  Thus the
simulation focuses on small-scale, not long term, behavior of the
ionization front.  The simulation box has a side length $L = 0.8$ kpc
with core density $n_0 = 3.2\;\cubecm$, core radius $r_0 = 91.5$ pc
(15 cells), and temperature $T = 100$ K throughout the box.  The
ionization fraction is initially zero, and the point source is located
at the origin with a luminosity of $10^{50}$ ph s$^{-1}$ \cubecm.  The
simulation is run for 75 Myr.

Because this problem does not have an analytical solution, we compare
our calculated ionization front radius and velocity, shown in Figure
\ref{fig:test6_1}, to the RT09 results.  Their evolution are in
agreement within 5\% of RT09.  As in Test 5, we use an extra
definition of $T=10^4$ K for the ionization front.  We compute the
ionization front velocity from the radii at 50 outputs, which causes
the noise seen Figure \ref{fig:test6_1}.

For the first Myr, the radiation source creates a weak R-type front
where the medium is heated and ionized but does not expand because
$v_{\rm IF} > c_s$.  When $v_{\rm IF}$ becomes subsonic, the medium
can react to the passing ionization front and creates a shock, leaving
behind a heated an rarefied medium.  This behavior is clearly seen in
the radial profiles of density, temperature, ionized fraction, and
pressure in Figure \ref{fig:test6_2}.  The inner density decreases
over two order of magnitude after 25 Myr.  To illustrate any
deviations in spherical symmetry, we show in Figure \ref{fig:test6_3}
slices of density, temperature, neutral fraction, and ionized fraction
at the final time.  The only artifact apparent to us is the slight
broadening of the shock near the $x=0$ and $y=0$ planes.  This causes
the ionization front radius to be slightly smaller in those
directions.  In the diagonal direction, the neutral column density
through the shock is slightly smaller, allowing the high-energy
photons to photoionize and photoheat the gas to $x_e = 5 \times
10^{-3}$ and $T = 2000$ K out to $\sim50$ pc from the shock.  The
reflecting boundaries in Enzo might be responsible for this artifact
because this is not seen when the problem is centered in the domain,
removing any boundary effects.

\subsection{Test 7: Photo-evaporation of a dense clump}

\begin{figure}[t]
  \plotone{fig/test7_lines}
  \caption{\label{fig:test7_1} Test 7. (Photo-evaporation of a dense
    clump).  Line cuts from the point source through the middle of the
    dense clump at $t = 1, 10, 50$ Myr of (clockwise from the upper
    left) density, temperature, pressure, and neutral fraction.}
\end{figure}

\begin{figure}[t]
  \plotone{fig/test7_slices10}
  \caption{\label{fig:test7_2} Test 7. (Photo-evaporation of a dense
    clump).  Clockwise from the upper left: Slices through the clump
    center of neutral fraction, pressure, temperature, and density at
    time $t =$ 10 Myr.}
\end{figure}

\begin{figure}[t]
  \plotone{fig/test7_slices50}
  \caption{\label{fig:test7_3} Test 7. (Photo-evaporation of a dense
    clump).  Same as Figure \ref{fig:test7_1} but at $t = 50$ Myr.}
\end{figure}

The photo-evaporation of a dense clump in a uniform medium proceeds
very differently when radiation hydrodynamics is considered instead of
a static density field.  The ionization front first proceeds as a very
fast R-type front, then it slows to a D-type front when it encounts
the dense clump.  As the clump is gradually photoionized and heated,
it expands into the ambient medium.  The test presented here is
exactly like Test 3 but with gas dynamics.  In this setup, the
ionization front overtakes the entire clump, which is then completely
photo-evaporated.

Figure \ref{fig:test7_1} shows cuts of density, temperature, neutral
fraction, and pressure in a line connecting the source and the clump
center at $t = 1$, 10, and 50 Myr.  At 1 Myr, the ionization front has
propagated through the left-most 500 pc of the clump.  This heated gas
is now overpressurized, as seen in the pressure plot in Figure
\ref{fig:test7_1}, and then expands into the ambient medium.  This
expansion creates a photo-evaporative flow, seen in many star forming
regions \citep[e.g. the Carina Nebula][]{Ref?} as stars irradiate
nearby cold, dense overdensities.  These flows become evident in the
density at 10 Myr, seen both in the line cuts and slices (Figure
\ref{fig:test7_2}).  These outflows have temperatures up to 50,000 K.
At this time, the front has progressed about halfway through the
clump, if one inspects the neutral fraction.  However the high energy
photons have heated all but the rear surface of the clump.  At the end
of the test ($t = 50$ Myr), only the core and its associated shadow is
neutral, as seen in Figure \ref{fig:test7_3}.  The core has been
compressed by the surrounding warm medium, thus causing the higher
densities seen at $t = 50$ Myr.  The non-spherical artifacts on the
inner boundary of the warm outermost shell are caused by the initial
discretization of the sphere, as discussed in \S\ref{sec:test3}.

\subsection{Test 8: Champange flow from a dense clump}

\begin{figure}[t]
  \plotone{fig/test8_slices}
  \caption{\label{fig:test8_1} Test 8. (Champange flow from a dense
    clump).  Slices of density through the initial clump center in the
    x-y plane (top) and x-z plane (bottom) at $t = 10, 40, 100, 150$
    kyr.  Notice the instabilities that grow from perturbations
    created while the \ion{H}{2} region is contained in the dense
    clump.}
\end{figure}

Radiation-driven outflows from overdensities, known as champange
flows, is a long studied problem \citep[e.g.][\S3.3]{Yorke86}.  We set
up a spherical tophat with an overdensity of 10 and radius of 1 pc in
a simulation box of 8 pc.  The ambient medium is 290 \cubecm~and 100
K.  The radiation source is offset from the overdensity center by 0.4
pc.  It has a luminosity of \tento{49} ph s$^{-1}$ and a $T=10^5$ K
blackbody spectrum.  The resulting Str\"{o}mgren radius is 0.33 pc,
just inside of the overdense clump.  These parameters are the same
used in \citet{Bisbas09}.  The entire domain initially has an ionized
fraction of \tento{-6}.  We do not consider self-gravity.  The
simulation has a resolution of 128$^3$ on base grid, and we refine the
grid up to 4 times if a cell has an overdensity of $1.5 \times 2^l$,
where $l$ is the AMR level.  The simulation is run for 150 kyr.

We show slices in the x-y and x-z planes of density in Figure
\ref{fig:test8_1} at $t = 10, 40, 100, 150$ kyr.  In the direction of
the clump center, the ionization front transitions from spherical to
parabolic after it escapes from the clump in the opposite direction.
At $t = 10$ kyr, the surface of the \ion{H}{2} region is just
contained within the overdensity.  In the x-z plane, there are density
perturbuations only above a latitude of 45 degrees.  We believe that
these are caused by the mismatch between HEALPix pixels and the
Cartesian grid, even with our geometric correction.  After the
ionization front escapes from the clump in the negative x-direction,
these perturbations grow from Rayleigh-Taylor instabilities as the gas
is accelerated when it exits the clump.  As the shock propagates
through the ambient medium, it is no longer accelerated and has a
nearly constant velocity, as seen in Test 6.  Thus these perturbations
are not as vunerable to Rayleigh-Taylor instabilities at this point.
The ambient medium and shock are always optically thick, even in the
directions of the bubbles.  \citeauthor{Bisbas09} found that the shock
fragmented and formed globules; however we find the density shell is
stable against such fragmentation.  To investigate this scenario
further, our next tests involve radiation driven Rayleigh-Taylor
instabilities.

\subsection{Test 9: Irradiated Rayleigh-Taylor instability}

\begin{figure}[t]
  \epsscale{0.5}
  \plotone{fig/test9thick_rho}
  \plotone{fig/test9thick_temp}
  \plotone{fig/test9thick_efrac}
  \caption{\label{fig:test9_thick} Test 9. (Irradiated Rayleigh-Taylor
    instability; optically thick case).  Slices at $y=0$ of density
    (top), temperature (middle), and electron fraction (bottom).}
  \epsscale{1}
\end{figure}

\begin{figure}[t]
  \epsscale{0.5}
  \plotone{fig/test9thin_rho}
  \plotone{fig/test9thin_temp}
  \plotone{fig/test9thin_efrac}
  \caption{\label{fig:test9_thin} Test 9. (Irradiated Rayleigh-Taylor
    instability; optically thin case).  Slices at $y=0$ of density
    (top), temperature (middle), and electron fraction (bottom).}
  \epsscale{1}
\end{figure}

Here we combine the classic case of a Rayleigh-Taylor instability and
an expanding \ion{H}{2} region.  The Rayleigh-Taylor instability
occurs when a dense fluid is being supported by a lighter fluid,
initially in hydrostatic equilibrium, in the presence of a constant
acceleration field.  This classic test alone evaluates how subsonic
perturbations evolve.  We consider the case of a single-mode
perturbation.  We let the system evolve without any radiation until
the perturbation grows considerably and then turn on the radiation
source.

We run two cases --- an optically-thick and optically-thin case.  In
the former, we take the parameter choices from past literature
\citep[e.g.][]{Liska03, Stone08} by setting the top and bottom halves
of the domain to a density $\rho_1 = 2$ and $\rho_0 = 1$,
respectively.  The velocity perturbation is set in the $z$-direction
by
\begin{equation}
  v_z(x,y,z) = 0.01 [1 + \cos(2\pi x / L_x)] \times 
  [1 + \cos(2\pi y / L_y)] \times [1 + \cos(2\pi z / L_z)]/8.
\end{equation}

We set the accleration field $g_z = 0.1$ and the adiabatic index
$\gamma = 1.4$.  We use a domain size of $(L_x, L_y, L_z) = (0.5, 0.5,
1.5)$ with a resolution of (64, 64, 192).  For hydrostatic equilbrium,
we set $P = P_0 - g \rho(z) z$ with $P_0 = 2.5$.  In order to consider
a radiation source with a ionizing photon luminosity of $10^{42}$ ph
s$^{-1}$, we scale the domain to a physical size of (0.5, 0.5, 1.5)
pc; time is in units of Myr; density is in units of $m_h$, resulting
in an initial temperature of $(T_0, T_1) = (363, 726)$ K.  The
radiation source starts to shine at $t = 10$ Myr.

The optically-thin case is set up similarly but with three
changes---(1) a density constrast of 10, (2) a luminosity of $10^{43}$
ph s$^{-1}$, and (3) the source is born at 6.5 Myr. The time units are
decreased to 200 kyr so that $(T_0, T_1) = (1.8 \times 10^3, 1.8
\times 10^4)$ K.  Note that in code units, pressure is unchanged.  We
adjust the physical unit scaling, so the light fluid has $T > 10^4$ K,
$x_e \sim 1$, and thus optically-thin.  A possible physical analogue
could be a radiation source heating and rarefying the medium below.

The $x$ and $y$-boundaries are periodic, and the $z$-boundaries are
reflecting.  The radiation source is turned on at $t = 7.5$ of
evolution and placed at the center of lower $z$-boundary face.  The
periodic boundaries will cause features that are non-physical,
considering a more realistic plane-parallel case.  Nevertheless, these
tests provide a good check on a radiation hydrodynamics solver.

\subsection{Test 10: Photo-evaporation of a blastwave}

A supernova blastwave being irradiated by a nearby star is a likely
occurence in massive-star forming regions.  In this test, we set up an
idealized test that mimics this scenario.  The problem is similar to
Test 5 with two changes --- (1) the domain has been decreased to
$L_{\rm box} = 1.5$ kpc; and (2) a mild blastwave is initialized in
the center of the domain.  We use 3 levels of AMR with a base grid of
64$^3$, which is refined if the density slope is greater than 0.4.
The blastwave is initially in the free expansion phase with a total
energy of $10^{50}$ erg and total mass of $100 \Ms$, corresponding to
$E = 315$ eV per particle or $E/k_b = 3.66 \times 10^6$ K.  The
blastwave is setup with a linearly increasing velocity profile
according to \citet{Truelove99} with $v_{\rm max} = 130$ km s$^{-1}$
and a radius of $L_{\rm box}/50 = 30$ pc.  The blastwave initially has
a uniform density of $\rho_0 = 0.06 \cubecm$.  The initial kinetic
energy is converted into thermal energy as the shock propagates away,
and the blastwave transitions into the Sedov-Taylor phase at $r \sim
100$ pc and $t \sim 225$ kyr after it has accumulated an equal amount
of ambient material into the shock.  The simulation is run for 25 Myr.

\subsection{Test 11: Collimated radiation from a dense clump}

Some astrophysical systems produce collimated radiation either
intrinisically by relavistic beaming or by an optically-thick torus
absorbing radiation in the equatorial plane.  The latter case would be
applicable in a subgrid model of an AGN or a protostar, for example.
Simulating collimated radiation with ray tracing is trivially
accomplished by only initializing rays that are within some opening
angle $\theta_c$.

We use a domain that is 2 kpc wide and has an ambient medium with
$\rho_0 = 10^{-3}$ \cubecm, $T = 10^4$ K, $x_e = 0.99$.  We place a
dense clump with $\rho/\rho_0 = 100$, $T = 100$ K, $x_e = 10^{-3}$,
and $r = 250$ pc, at the center of the box.  Radiation is emitted in
two polar cones with $\theta_c = \pi/6$ with a total luminosity of
$10^{49}$ erg s$^{-1}$ and a 17.6 eV mono-chromatic spectrum.  This
results in $t_{\rm rec} = 1.22$ Myr and $R_s = 315$ pc, just outside
of the sphere.  The base grid has a resolution of 64$^3$, and it is
refined with the same overdensity criterion as Test 8.

% \subsection{Test 12: \ion{H}{2} region in a rotating medium}
% 
% Angular momentum is prevalent throughout all astrophysical systems.
% We construct a problem with an \ion{H}{2} region that is completely
% contained within a sphere with solid-body rotation.  Self-gravity is
% considered in this test.  The sphere initially has $R = 40$ pc with a
% uniform density $\rho = 200~\cubecm$, temperature $T = 50$ K, and
% electron fraction $x_e = 10^{-6}$.  The sphere is partially
% rotationally supported by a factor of 0.25, i.e. the tangential
% velocity $v_\theta(r) = r\sqrt{GM_{\rm tot}/R}/4$, where $M_{\rm tot}
% = 1.3 \times 10^6 \Ms$.  The sphere and radiation source are located
% in the center of the domain.  The sphere is in pressure equilibrium
% with the ambient medium that has $\rho_0 = 1 \cubecm$, $T = 10^4$ K,
% and $x_e = 0.99$.  The radiation source has an ionizing luminosity $L
% = 10^{50}$ ph s$^{-1}$ with a 17.6 eV mono-chromatic spectrum.  The
% test uses AMR with a base grid of 64$^3$ and 2 levels of refinement,
% using the same density criterion as in Test 8.

\subsection{Test 12: \ion{H}{2} region in a static potential}

Next we construct a problem that is similar to the Rayleigh-Taylor
test problem (Test 9) in nature but is spherically symmetric.  We use
the same physical setup as Test 5 with a uniform medium and the
radiation source at the origin.  It has a luminosity of $5 \times
10^{48}$ ph s$^{-1}$ and a mono-chromatic spectrum of 14.6 eV.  We
choose this energy so the ionization front is relatively sharp but
still heats the gas to $10^4$ K.  The ambient medium has a density of
$10^{-3} \cubecm$ and an initial temperature of 100 K.  A point source
of gravity also resides at the origin.  To have an equal gravitational
acceleration $g(r) = g_0 / r^3$ at the Str\"{o}mgren radius $R_s =
5.4$ kpc ($r = 0.36$) as Test 9, we set the strength of the point
source $g_0 = 4.67 \times 10^{-3}$.  The gravity point source has the
same effect on any pertubations as the constant gravitational force in
Rayleigh-Taylor instability test.

\subsection{Test 13: Time variations of the source luminosity}

Our implementation retains the time derivative of the radiative
transfer equation (Eq. \ref{eqn:rteqn}) if we choose a constant ray
tracing timestep, which saves the photon packages between timesteps if
the $c\;dt_{\rm P} < L_{\rm box}$.  This effect only becomes apparent
when the variation timescale of the point source is smaller than the
light crossing time of the simulation.  Furthermore, the timestep
should resolve the variation timescale by a few times.  To test this,
we can use an exponentially varying source with some duty cycle.  In a
functional form, this can be described as
%
\begin{equation}
  \label{eqn:test13}
  L(t) = L_{\rm max} \times \exp(t_f/t_0 - 1),
\end{equation}
%
where $t_f = \mathrm{mod}(t,t_0)$ and $t_0$ is the duty cycle.  To
illustrate the variations in the photo-ionization rates due to a
varying source, we remove any dependence on the medium by considering
an optically-thin uniform density.  We take $L_{\rm box} = 1$ Mpc,
which has a light crossing time of 3.3 Myr.  Thus we consider a source
at the origin with $L_{\rm max} = 10^{50}$ ph s$^{-1}$ and $t_0 = 0.5$
Myr.  We use a radiative transfer timestep of 50 kyr to resolve the
duty cycle by 10 timesteps.

\subsection{Test 14: \ion{H}{2} region with MHD}

\begin{figure}[t]
  \plotone{fig/test14_slices_xy}
  \caption{\label{fig:test14_1} Test 14. (\ion{H}{2} region with MHD).
    Left to right: slices of density at $t = 0.18, 0.53, 1.58$ Myr in
    the x-y plane.  The streamlines show the magnetic field.}
\end{figure}

\begin{figure}[t]
  \plotone{fig/test14_slices_yz}
  \caption{\label{fig:test14_2} Test 14. (\ion{H}{2} region with
    MHD). Slices of density (top) and the x-component of the magnetic
    field (bottom) in the y-z plane at $t = 0.18, 0.53, 1.58$ Myr
    (left to right).}
\end{figure}

Another prevelant physical component in astrophysics is a magnetic
field.  We utilize the new magnetohydrodynamics (MHD) framework
\citep{Wang09} in \enzo~v2.0 that uses an unsplit conservative
hydrodynamics solver and a hyperbolic $\nabla \cdot \mathbf{B} = 0$
cleaning method of \citet{Dedner02}.  This marriage of radiation
transport and MHD has already been demonstrated in \citet{Wang10}, but
for illustrative purposes, we show a test problem with an expanding
\ion{H}{2} region in an initially uniform density field and constant
magnetic field.  We use the same problem setup as
\citet{Krumholz07_ART} --- $\rho = 100~\cubecm$, $T = 11$ K, $L_{\rm
  box} = 20$ pc with a resolution of 256$^3$.  This ambient medium is
threaded by a magnetic field $\mathbf{B} = 14.2 \hat{\mathbf{x}} \;
\mu\mathrm{G}$.  The Alfv\'{e}n speed is 2.6 \kms.  The radiation
source is located in the center of the box with a luminosity $L = 4
\times 10^{46}$ ph s$^{-1}$ with a 17.6 eV mono-chromatic spectrum,
resulting in a Str\"{o}mgren radius $R_s = 0.5$ pc.  The simulation is
run for 1.58 Myr.  The hydrodynamics solver uses an HLL Riemann solver
\citep{HLL} and piecewise linear method (PLM) reconstruction
\citep{PLM} for the left and right states in this problem.

As the \ion{H}{2} region grows the magnetized medium, shown in Figures
\ref{fig:test14_1} and \ref{fig:test14_2}, it transforms from
spherical to oblate as it is magnetically confined in directions
perperdicular to the magnetic field.  This occurs at $t > 0.5$ Myr
because the magnetic pressure exceeds the thermal pressure, and the
gas can only flow along field lines.  \citeauthor{Krumholz07_ART}
observed some carbuncle artifacts along the ionization front; whereas
we see smooth density gradients, which is most likely caused by our
more diffusive choice of the HLL Riemann solver when compared to Roe's
Riemann solver used in \citet{Krumholz07_ART}, which also uses PLM as
a reconstruction method.  The evolution of the magnetic field lines
evolve in a similar manner as their results.

\section{Resolution Tests}

Resolution tests are important in validating the accuracy of the code
in most circumstances, especially in production simulations where the
initial environments surrounding radiation sources are unpredictable.
In this section, we show how our adaptive ray-tracing implementation
behaves when varying spatial, angular, frequency, and temporal
resolutions.

\subsection{Spatial resolution}

\begin{figure}[t]
  \epsscale{0.75}
  \plotone{fig/ifront_res}
  \caption{\label{fig:dx_dep1} Growth of the ionization front radius,
    compared to the analytical radius, in Test 1 with varying spatial
    resolutions.  At resolutions of $16^3$ and $32^3$, the ionization
    front is underestimated for the first $\sim25$ Myr but converges
    within 0.5\% of the higher resolution runs.}
  \epsscale{1}
\end{figure}

Here we use Test 1 (\S\ref{sec:test1}) as a testbed to investigate how
the evolution of the Str\"{o}mgren radius changes with resolution.  We
keep all aspects of the test the same, but use resolutions of 16$^3$,
32$^3$, 64$^3$, and 128$^3$.  In Figure \ref{fig:dx_dep1}, we show the
ratio $r_{\rm IF}/r_{\rm anyl}$, similar to Figure
\ref{fig:test1_ifront}, using these different resolutions.  The radii
in the $64^3$ and $128^3$ runs evolve almost identically.  Compared to
these resolutions, the lower $16^3$ and $32^3$ resolution runs only
lag behind by 1\% until 300 Myr, and afterwards it is larger by 0.5\%
than the higher resolution cases.  This shows that our method gives
accurate results, even in marginally resolved cases.

\subsection{Angular resolution}
\label{sec:ang_dep}

\begin{figure}[t]
  \epsscale{1}
  \plotone{fig/phic_slices}
  \caption{\label{fig:ang_dep1} Variations in the photo-ionization
    rates for different ray-to-cell samplings $\Phi_c$.  The colormap
    only spans a factor of 3 to enhance the contrast.  In comparision,
    the photo-ionization rate actually spans 4 orders of magnitude in
    this test.}
  \epsscale{1}
\end{figure}

\begin{figure}[t]
  \epsscale{0.75}
  \plotone{fig/phic_dep}
  \caption{\label{fig:ang_dep2} Standard deviations of the difference
    between the computed photo-ionization rates and an inverse square
    law as a function of ray-to-cell samplings $\Phi_c$ for different
    spatial resolutions.  There is no dependence on the spatial
    resolution, and the accuracy increases as $\sigma \propto
    \Phi_c^{-0.6}$.}
  \epsscale{1}
\end{figure}

The Cartesian grid must been sampled with sufficient rays in order to
calculate a smooth radiation field.  To determine the dependence on
angular resolution, we consider the propagation of radiation through
an optically thin, uniform medium.  The radiation field should follow
a $1/r^2$ profile.  As the grid is less sampled by rays, the deviation
from $1/r^2$ should increase.  This test is similar to Test 1, but the
medium has $\rho = 10^{-3}~\cubecm$, $T = 10^4$ K, and $1 - x_e =
10^{-4}$.  The radiation source is located in the center of a 6.6 kpc
domain.  The simulation is only run for one timestep because the
radiation field should be static in this optically-thin test.

We consider minimum ray-to-cell ratios $\Phi_c = (1.1, 2.1, 3.1, 5.1,
10.1, 25.1)$.  Slices of the photo-ionization rates through the origin
are shown in Figure \ref{fig:ang_dep1} for these values of $\Phi_c$.
In this figure, we limit the colormap range to a factor of 3 to show
the nature of the artifacts in more contrast.  Unscaled, the rates in
the figures would span 4 orders of magnitude.  When $\Phi_c \le 3.1$,
the cell-to-cell variations are apparent because there are not enough
rays to sufficiently sample the radiation field, even with the
geometric correction factor $f_c$, whose improvements are shown later
in \S\ref{sec:test_fc}.  At $\Phi_c = 5.1$, these artifacts disappear,
leaving behind a shell artifact where the radiation fields do not
smoothly decrease as 1/$r^2$.  At higher values of $\Phi_c$, this
shell artifact vanishes as well.

One measure of accuracy is the deviation from an 1/$r^2$ field because
this problem is optically-thin.  To depict the increase in accuracy
with ray sampling, we take the difference between the calculated
photo-ionization rate and a 1/$r^2$ field, and then plot the standard
deviation of this difference field versus angular resolution in Figure
\ref{fig:ang_dep2}.  We plot this relation for resolutions of $32^3$,
$64^3$, and $128^3$ and find no dependence on spatial resolution,
which is expected because we control the angular resolution in terms
of cell widths, not in absolute solid angles.  We find that the
deviation from an inverse square law decreases as $\sigma \propto
\Phi_c^{-0.6}$.

\subsection{Frequency resolution}

In practice, we find good agreement within 5--10\% of analytical
solutions in Tests 1, 2, and 5 with only one energy group.  We use
Test 5 (\S\ref{sec:test5}; an expanding \ion{H}{2} region with
hydrodynamics) to probe any differences in the solution when varying
the resolution of the spectrum.  In RT09, ZEUS-MP was used to
demonstrate the effect of a multi-frequency spectrum on the dynamics
of the ionization front in this test.  Instead of a single shock seen
in the mono-chromatic spectrum, a the shock obtained a double-peaked
structure in density and radial velocity.  We rerun Test 5 with a
$T=10^5$ K blackbody spectrum sampled by 1, 2, 4, 8, and 16 frequency
bins.

\subsection{Temporal resolution}
\label{sec:dt_dep}

The previous three dependencies did not affect the propagation of the
ionization front greatly.  However in our and others' past experience
\citep[e.g.][\bf{+others!}]{Petkova09}, the timestep, especially too
small of one, can drastically affect the ionization front velocity.
Here we use Test 1 but with $64^3$ resolution to compare different
timestepping methods --- restricted changes in \ion{H}{2}
(\S\ref{sec:dt_hi}), constant timesteps (\S\ref{sec:dt_const}), and
based on incident radiation (\S\ref{sec:dt_tau}).

\section{Methodology Tests}

Here we show tests that evaluate new features in Enzo+Moray, such as
the improvements from the geometric correction factor, optically-thin
approximations, treatment of X-ray radiation, and radiation pressure.
Lastly we test for any non-spherical artifacts in the case of two
sources.

\subsection{Improvements from the covering factor correction}
\label{sec:test_fc}

\begin{figure}[t]
  \epsscale{0.7}
  \plotone{fig/fc_slices}
  \caption{\label{fig:fc_slices} Slices of the photo-ionization rate
    in the x-y plane (top row) and x-z plane (bottom row) with (left
    column) and without (right column) the geometric correction.  The
    slices are through the origin.  In the x-y plane, it reduces the
    shell artifacts.  In the x-z plane, it reduces the severity of a
    non-spherical artifact delinated at a 45 degree angle, where the
    HEALPix scheme switches from polar to equatorial type pixels.}
  \epsscale{1}
\end{figure}

As discussed in \S\ref{sec:meth_fc}, non-spherical artifacts are
created by a mismatch between the HEALPix pixelization and the
Cartesian grid.  This is especially apparent in optically-thin
regions, where the area of the pixel is greater than the
$(1-e^{-\tau})$ absorption factor.  In this section, we repeat the
angular resolution tests in \S\ref{sec:ang_dep}.  Slices of the
photo-ionization rates through the origin are shown in Figure
\ref{fig:fc_slices}, depicting the improvements in spherical symmetry
and a closer agreement to a smooth $1/r^2$ profile.  Previous attempts
to reduce these artifacts either introduced a random rotation of the
HEALPix pixelization \citep[e.g.][]{Abel02_RT, Trac07, Krumholz07_ART}
or by increasing the ray-to-cell sampling.

In the x-y plane without the correction, there exists shell artifacts
where the photo-ionization rates abruptly drops when the rays are
split.  This occurs because the photon flux in the rays are constant,
so \kph~is purely dependent on the ray segment length through each
cell.  Geometric dilution mainly occurs when the number of rays
passing through a cell decreases.  With the correction, geometric
dilution also occurs when the ray's solid angle only partially covers
the cell.  This by itself alleviates these shell artifacts.  In the
x-z plane without the correction, there is a non-spherical artifact
delinated at a 45 degree angle.  In the lower region, the rays are
assoicated with equatorial HEALPix pixels, and in the upper region,
they are polar HEALPix pixels.  This artifact is not seen in the x-y
plane because all rays are of a equatorial type.  The geometric
correction smooths this artifact but does not completely remove it.

\subsection{Optically-thin approximation}

In practice, we have found it difficult to transition from this
optically-thin approximation to the optically-thick regime without
producing artifacts in the photo-ionization rate \kph.  The artifacts
exist in cells that intersect the $\tau_{\rm thin} \equiv 0.1$
surface.  These cells are split into the optically thin and thick
definitions, and we have not determined a good technique to avoid any
artifacts.  We use the optically thin problem used in the angular
resolution test (\S\ref{sec:ang_dep}) to show these artifacts in \kph.

\subsection{X-Ray secondary ionizations and reduced photo-heating}

\begin{figure}[t]
  \epsscale{0.6}
  \plotone{fig/xray_profiles.eps}
  \caption{\label{fig:xray_fig} Radial profiles of temperature and
    ionized fraction showing the effects of secondary ionizations from
    a mono-chromatic 1 keV spectrum.  The high energy photons can
    ionize multiple hydrogen atoms, increasing the ionized fraction.
    In part, less radiation goes into thermal energy, lowering the
    temperature.}
  \epsscale{1}
\end{figure}

Here we test our implementation of secondary ionizations from
high-energy photons above 100 eV, described in \S\ref{sec:xrays} and
used in \citet{Alvarez09} in the context of accreting black holes.  We
use the same setup as Test 5 but with an increased luminosity $L =
10^{50}$ erg s$^{-1}$ and a mono-chromatic spectrum of 1 keV.  Figure
\ref{fig:xray_fig} compares the density, temperature, ionized
fraction, and neutral fraction of the expanding \ion{H}{2} region
considering secondary ionizations and reduced photo-heating and
considering only one ionization per photon and the remaining energy
being thermalized.

\subsection{Radiation pressure}

\begin{figure}[t]
  \plottwo{fig/noRP_profiles.eps}{fig/RP_profiles.eps}
  \caption{\label{fig:rp_profile150} (a) No radiation pressure.
    Radial profiles of (clockwise from top left) density, temperature,
    radial velocity, and neutral fraction.  Time units in the legned
    are in kyr.  (b) Radial profiles with radiation pressure.  The
    momentum transferred to the gas drives out the gas at higher
    velocities than without radiation pressure.  Afterwards the
    central region is underpressurized, and the gas infalls toward the
    center, as seen at t = 60 kyr.  Then the radiation pressure
    continues to force the gas outwards, increasing gas velocites up
    to 50 km/s.}
\end{figure}

Radiation pressure affects gas dynamics in an \ion{H}{2} region when
its force is comparable to the acceleration created by gas pressure of
the heated region.  The imparted acceleration on a hydrogen atom
$\mathbf{a}_{\rm rp} = E_{\rm ph}/c$.  This is especially important
when the ionization front is in its initial R-type phase.  Thus we
construct a test that focuses on a small scales, compared to the
Str\"{o}mgren radius.  The domain has a size of 8 pc with a uniform
density $\rho = 2900 \cubecm$ and initial temperature $T = 10^3$ K.
The source is located at the origin with a luminosity $L = 10^{50}$ ph
s$^{-1}$ and a $T=10^5$ K blackbody spectrum.  We use one energy group
$E_{\rm ph} = 29.6$ eV.  The grid is adaptively refined on overdensity
with the same criteron as Test 8.  The simulation is run for 150 kyr.

\subsection{Consolidated \ion{H}{2} region with two sources}

Here we test for any inaccuracies in the case of multiple sources.  We
use the same test problem as \citet[][\S5.1.2]{Petkova09}, which has
two sources with luminosities of $5 \times 10^{48}$ ph s$^{-1}$ and
are separated by 8 kpc.  The ambient medium is static with a uniform
density of $10^{-3}$ \cubecm and $T = 10^4$ K.  This setup is similar
to Test 1.  The domain has a resolution of $128^3$ and is 20 kpc in
width, and the problem is run for 500 Myr.

The \ion{H}{2} regions grow to $r = 4$ kpc where they overlap.  Then
the two sources are enveloped in a common, elongated \ion{H}{2}
region.

\section{Parallel Performance}

Last we demonstrate the parallel performance of Enzo+Moray in weak and
strong scaling tests.  For large simulations to consider radiative
transfer, it is imperative that the code scales to large number of
processors.

\subsection{Weak Scaling}
\label{sec:weak_sc}

Weak scaling tests demonstrates how the code scales with the number of
processors with a constant amount of work per processor.  Here we
construct a test problem with a $64^3$ block per processor.  The grid
is not adaptively refined.  The physical setup of the problem is the
same as Test 5 with a uniform density $\rho = 10^{-3} \cubecm$ and
initial temperature $T = 100$ K.  Each block has the same size of 15
kpc as Test 5.  At the center of each grid, there exists a radiation
source with a luminosity $L = 5 \times 10^{48}$ ph s$^{-1}$ and a 17
eV mono-chromatic spectrum.  The problem is run for 100 Myr.  We run
this test with $N_p = 2^n$ processors with $n = [0,1 \dots 11,12]$.
The domain has $(N_x, N_y, N_z)$ blocks that is determined with the
MPI routine \texttt{MPI\_Dims\_create}.  For example with $n = 7$, the
problem is decomposed into $(N_x, N_y, N_z) = (4,4,8)$ blocks,
producing a $256 \times 256 \times 512$ grid.

\subsection{Strong Scaling}
\label{sec:strong_sc}

Strong scaling tests shows how the problem scales with the number of
processors for the same problem.  The overhead associated with the
structured AMR framework in \enzo~can limit the strong scalibility.
One key property of strong scaling is that each processor must have
sufficient work to compute, compared to the communication involved.
Here we use a small-box reionization calculation with $L_{\rm box} =
3$ Mpc/h, a resolution of $256^3$, and 6 levels of refinement.  We
measure the time spent on the hydrodynamics, non-equilibrium
chemistry, the rebuilding of the AMR hierarhcy, and ray tracing in a
single level-0 timestep, lasting 5 Myr, at $z=8$.  There are ??? point
sources in this calculation at this redshift.

\section{Summary}

\acknowledgments

J.H.W. is supported by the Hubble Fellowship etc.  The majority of the
analysis and plots were done with \texttt{yt} \citep{yt}.

\clearpage
%\input biblio.tex
\bibliography{ms}

\end{document}

### 2010-08-12 fig/box.py

@@ -1,0 +1,245 @@
+import math
+import numpy as np
+from pyx import *
+
+cellsize = 5
+origin = [0,0]
+ray_enter = 0.5   # x-dimension
+normal = [0.7, 0.3]  # both must be positive for this illustration
+unit.set(xscale=0.35*cellsize)
+
+# Normalize ray direction vector
+normal = np.array(normal)
+normal /= math.sqrt((normal**2).sum())
+
+#------------------------------------------------------------------------
+# Figure with true covering factor
+#------------------------------------------------------------------------
+
+def figure1():
+    c = canvas.canvas()
+
+    # Ray properties
+    ray_start = np.array([origin[0] + ray_enter*cellsize, origin[1]])
+    dx = origin[1] + cellsize - ray_start[0]
+    dy = dx * normal[1] / normal[0]
+    ray_end = np.array( [origin[0] + cellsize, origin[1]+dy] )
+    ray_center = 0.5*(ray_start + ray_end)
+
+    exterior = 2.0
+    ray_head = ray_start - exterior*normal
+    ray_tail = ray_end + exterior*normal
+
+    perp = np.array([-normal[1], normal[0]])
+    beam_width = 0.4 * cellsize
+
+    # Column from r to r+dr
+    ray_area = box.polygon([(ray_start[0] - beam_width*perp[0],
+                             ray_start[1] - beam_width*perp[1]),
+                            (ray_start[0] + beam_width*perp[0],
+                             ray_start[1] + beam_width*perp[1]),
+                            (ray_end[0] + beam_width*perp[0],
+                             ray_end[1] + beam_width*perp[1]),
+                            (ray_end[0] - beam_width*perp[0],
+                             ray_end[1] - beam_width*perp[1])])
+    covering = box.polygon([(ray_start[0], ray_start[1]),
+                            (origin[0]+cellsize, origin[1]),
+                            (ray_end[0], ray_end[1]),
+                            (ray_end[0] + beam_width*perp[0],
+                             ray_end[1] + beam_width*perp[1]),
+                            (ray_start[0] + beam_width*perp[0],
+                             ray_start[1] + beam_width*perp[1])])
+    
[…]

### 2010-08-12 ms.tex
Minor changes to the timestepping section.  Adding .hgignore and bbl file.

@@
 radiation transfer equation because an accurate yet large timestep is
-not trivial to compute.  With a small enough timestep, the solution is
-guaranteed to avoid any inaccuracies (ignoring any systematic ones)
-due to timestepping, but the solver must be called many times.  These
-frequent calls may be unneccesary because the same solution may be
-accomplished with a longer timestep.  Furthermore with ray tracing,
-the photon packages only advance a short distance, and they will exist
-in every $dx/dt_P$ cells with radiation and are stored between
-timesteps, excessively consuming memory.  If the timestep is too
-large, the solution will become inaccurate; specifically, ionization
-fronts will advance too slowly, as radiation intensity exponentially
-drops with a scale length of the mean free path
+not trivial to compute.  We describe several methods to calculate the
+radiative transfer timestep in this section.  With a small enough
+timestep, the solution is guaranteed to avoid any inaccuracies
+(ignoring any systematic ones) due to timestepping, but the solver
+must be called many times.  These frequent calls may be unneccesary
+because the same solution may be accomplished with a longer timestep.
+Furthermore with ray tracing, the photon packages only advance a short
+distance, and they will exist in every $dx/dt_P$ cells with radiation
+and are stored between timesteps, excessively consuming memory.  On
+the shortest timescale, one can safely set the timestep to the
+light-crossing time of a cell \citep{Abel99_RT, Trac07} but encounters
+the problems stated above.
+
+If the timestep is too large, the solution will become inaccurate;
+specifically, ionization fronts will advance too slowly, as radiation
+intensity exponentially drops with a scale length of the mean free
+path
 \begin{equation}
@@
 past the ionization front.  For example in our implementation, the
-chemo-thermal state of the system will remain constant as the rays are
+chemo-thermal state of the system remains constant as the rays are
 traced through the cells.  Thus in the case of a single \ion{H}{2}
 region, the speed of the ionization front is limited to approximately
-the $\lambda_{\rm mfp} / dt_P$.  We can investigate this further by
-evaluating the ionization front velocity in a growing Str\"{o}mgren
-sphere, where $\dot{N}_\gamma = 4 \pi R^2 n_{\rm H} v_{\rm IF}$.
-Using $\kph \propto \dot{n}_{\rm H} / n_{\rm H}$ and $\kph =
-\dot{N}_\gamma \sigma / 4\pi R^2 A_{\rm cell}$, we can make
-substitutions on both sides of the equation to arrive at the
-ionization front velocity
-%
-\begin{equation}
-  \label{eqn:vifront1}
-  v_{\rm IF} \propto \frac{n_{\rm H}}{\dot{n}_{\rm H}}.
-\end{equation}
-
-On the shortest timescale, one can safely set the timestep to the
-light-crossing time of a cell \citep{Abel99_RT, Trac07} but encounters
-the problems stated above.  Next we describe several methods to
-calculate the radiative transfer timestep.
+the $\lambda_{\rm mfp} / dt_P$.
 
@@
 fraction.  \citet{Shapiro04} found that this limited the speed of the
-ionization front for the same reasons described in Equation
-\ref{eqn:vifront1}.  We have implemented this method but we only
-consider cells within the ionization front (by experiment we choose
-$\tau > 0.5$) because we are interested in evolving ionization fronts
-at the correct speed.  In the ionized region, the absolute changes in
-neutral fraction are small and will not significantly affect the
-ionization front evolution.  In other words, $n_{\rm HI}/(dn_{\rm
-  HI}/dt)$ may be large but $(dn_{\rm HI}/dt) \sim 0$, thus we can
-safely ignore these cells when determining the timestep without
-sacrificing accuracy.
+ionization front.  We can investigate this further by evaluating the
+ionization front velocity in a growing Str\"{o}mgren sphere without
+recombinations, where $\dot{N}_\gamma = 4 \pi R^2 n_{\rm H} v_{\rm
+  IF}$.  Using $\kph \propto \dot{n}_{\rm H} / n_{\rm H}$ and $\kph =
+\dot{N}_\gamma \sigma / 4\pi R^2 A_{\rm cell}$, we can make
+substitutions on both sides of the equation to arrive at the
+ionization front velocity $v_{\rm IF} \propto n_{\rm H} /\dot{n}_{\rm
+  H}$.
+
+We have implemented this method but we only consider cells within the
+ionization front (by experiment we choose $\tau > 0.5$) because we are
+interested in evolving ionization fronts at the correct speed.  In the
+ionized region, the absolute changes in neutral fraction are small and
+will not significantly affect the ionization front evolution.  In
+other words, $n_{\rm HI}/(dn_{\rm HI}/dt)$ may be large but $(dn_{\rm
+  HI}/dt) \sim 0$, thus we can safely ignore these cells when
+determining the timestep without sacrificing accuracy.
 
@@
 spherically symmetric case without recombinations.  Thus all photons
-emitted from the source result in an ionization (see
-Eq. \ref{eqn:vifront1} and its derivation).  Ultimately in any
-approach, we are focused on accurately following the time evolution of
-the radiation field.  In this method, we base the timestep directly on
-the change in radiation field, the specific intensity, $I/\dot{I}$.
-We consider the field after propagating through the cell, so $I = I_0
-\exp(-\tau)$, where $\tau = n_{\rm H} \sigma dl$ is the optical depth
-through the cell.  The change in specific intensity is
+emitted from the source result in an ionization (also see
+\S\ref{sec:dt_hi}).  Ultimately in any approach, we are focused on
+accurately following the time evolution of the radiation field.  In
+this method, we base the timestep directly on the change in radiation
+field, the specific intensity, $I/\dot{I}$.  We consider the field
+after propagating through the cell, so $I = I_0 \exp(-\tau)$, where
+$\tau = n_{\rm H} \sigma dl$ is the optical depth through the cell.
+The change in specific intensity is
 %

### 2010-08-12 ms.tex
Updated Test 9 opt. thin figures.  Wrote description of Test 9.

@@
     instability; optically thick case).  Slices at $y=0$ of density
-    (top), temperature (middle), and electron fraction (bottom).}
+    (top), temperature (middle), and electron fraction (bottom).  The
+    source turns on at $t=0$.}
   \epsscale{1}
@@
   \plotone{fig/test9thin_efrac}
-  \caption{\label{fig:test9_thin} Test 9. (Irradiated Rayleigh-Taylor
-    instability; optically thin case).  Slices at $y=0$ of density
-    (top), temperature (middle), and electron fraction (bottom).}
+  \caption{\label{fig:test9_thin} Same as Figure \ref{fig:test9_thick}
+    but for the optically thin case.}
   \epsscale{1}
@@
 the perturbation grows considerably and then turn on the radiation
-source.
+source.  These tests demonstrate that Enzo+Moray can follow a highly
+dynamic system and resolve fine density structures.
 
@@
 changes---(1) a density constrast of 10, (2) a luminosity of $10^{43}$
-ph s$^{-1}$, and (3) the source is born at 6.5 Myr. The time units are
-decreased to 200 kyr so that $(T_0, T_1) = (1.8 \times 10^3, 1.8
+ph s$^{-1}$, and (3) the source is born at 6.5 Myr.  The time units
+are decreased to 200 kyr so that $(T_0, T_1) = (1.8 \times 10^3, 1.8
 \times 10^4)$ K.  Note that in code units, pressure is unchanged.  We
 adjust the physical unit scaling, so the light fluid has $T > 10^4$ K,
-$x_e \sim 1$, and thus optically-thin.  A possible physical analogue
-could be a radiation source heating and rarefying the medium below.
+$x_e \sim 1$, and thus optically-thin.  Furthermore, the ionization
+front remains R-type before interacting with the instability.  A
+possible physical analogue could be a radiation source heating and
+rarefying the medium below.
 
 The $x$ and $y$-boundaries are periodic, and the $z$-boundaries are
-reflecting.  The radiation source is turned on at $t = 7.5$ of
-evolution and placed at the center of lower $z$-boundary face.  The
-periodic boundaries will cause features that are non-physical,
-considering a more realistic plane-parallel case.  Nevertheless, these
-tests provide a good check on a radiation hydrodynamics solver.
+reflecting.  The radiation source is placed at the center of lower
+$z$-boundary face.  The periodic boundaries will cause features that
+are non-physical, considering a more realistic plane-parallel case.
+Nevertheless, these tests provide a good check on a radiation
+hydrodynamics solver.  We show the evolution of the density,
+temperature, and ionized fraction of the optically thick and optically
+thin cases in Figures \ref{fig:test9_thick} and \ref{fig:test9_thin}.
+The initial state of the Rayleigh-Taylor instability is shown in the
+left panels.
+
+In the optically thick case, a D-type front is created, which is
+clearly illustrated by the spherical density enhancement at 0.02 Myr.
+The shock then passes through the instability at $\sim$0.25 Myr and
+reflects off the upper $z$-boundary.  This and complex shock
+reflections create a Richtmeyer-Meshkov instability, driving a chaotic
+jet-like structure downwards.  The radiation source photo-evaporates
+the outer parts of this structure.  The interaction between the dense
+cool ``jet'' and the hot medium further drives instabilities along the
+surface, which can be seen when comparing $t = 0.59$ Myr and $t =
+0.91$ Myr slices.  At the latter time, the jet cannot reach the bottom
+of the domain before being photo-evaporated.  Eventually this
+structure is completely destroyed, leaving behind a turbulent medium
+between the hot and cold regions.
+
+The optically thin problem is less violent than the optically thick
+case because the R-type front does not interact with the initial
+instability as strongly.  The radiation source provides further
+buoyance in the already $T=10^4$ K gas.  The gas first to be ionized
+and photo-evaporates is the outer regions of the instability.  The
+enhanced heating also drives the upper regions of the instability,
+making the top interface turbulent.  It then reflects off the upper
+$z$-boundary and creates a warm $T = 5 \times 10^3$ K, partially
+ionized ($x_e \sim 10^{-2}$), turbulent medium, seen in the slices $t
+\ge 0.67$ Myr.  The slices of electron fraction also show that the
+dense gas is optically thick.
 
@@
 still heats the gas to $10^4$ K.  The ambient medium has a density of
-$10^{-3} \cubecm$ and an initial temperature of 100 K.  A point source
+$10^{-3}~\cubecm$ and an initial temperature of 100 K.  A point source
 of gravity also resides at the origin.  To have an equal gravitational

### 2010-08-12 ms.tex
Added description and figure for Test 11.  Added 1/dt factor for rad. pressure.  Removed Test 12.

@@
   machines and can include radiation pressure and secondary
-  ionizations from X-ray radiation.  Our implementation is included in
-  the newest public release of Enzo.
+  ionizations from X-ray radiation.  It is included in the newest
+  public release of Enzo.
 
@@
 \begin{enumerate}
+\item the photon has travelled $c \times dt_P$, where $dt_P$ is the
+  radiative transfer timestep,
 \item its photon flux is almost fully absorbed ($>99.9\%$) in a single
@@
   radiation volume filling fraction is small,
-\item the photon has travelled $c \times dt_P$, where $dt_P$ is the
-  radiative transfer timestep,
 \item the photon leaves the computational domain with isolated
@@
 \begin{equation}
-  d\mathbf{p}_\gamma = \frac{dP \; E_{\rm ph}}{c} \; \hat{r}
+  d\mathbf{p}_\gamma = \frac{dP \; E_{\rm ph}}{c\;dt} \; \hat{r}
 \end{equation}
 of the absorbed radiation from the incoming ray, where $\hat{r}$ is
-the normal direction of the ray.  The resulting acceleration of the
-gas due to radiation pressure is 
+the normal direction of the ray and $dt$ is the radiative transfer
+timestep.  The resulting acceleration of the gas due to radiation
+pressure is
 \begin{equation}
@@
 
+\begin{figure}[t]
+  \epsscale{1}
+  \plotone{fig/test11_slices}
+  \caption{\label{fig:test11} Test 11 (Collimated radiation from a
+    dense clump).  Slices of density (top) and temperature (bottom) at
+    $t = 0.1, 3.25, 10.75, 23.25$ Myr.  The conical \ion{H}{2} region
+    drives shocks transversely into the overdense sphere and creates
+    polar champange flows.  The ambient medium is heated to $T \sim 3
+    \times 10^4$ K as the ionization front passes the
+    constant-pressure cloud surface.  The ionization front changes
+    from D-type to R-type after it enters the ambient medium.}
+  \epsscale{1}
+\end{figure}
+
 Some astrophysical systems produce collimated radiation either
@@
 of the sphere.  The base grid has a resolution of 64$^3$, and it is
-refined with the same overdensity criterion as Test 8.
+refined with the same overdensity criterion as Test 8.  We run this
+test for 25 Myr.
+
+We illustrate the expansion of the \ion{H}{2} region created by the
+beamed radiation in Figure \ref{fig:test11}.  Before 3 Myr, the
+\ion{H}{2} region is conical and contained within the dense clump,
+depicted in the $t = 0.1$ Myr snapshot of the system.  At this time,
+the ionization front is transitioning from R-type to D-type in the
+transverse direction of the cone.  This can be seen in the minute
+overdensities on the \ion{H}{2} transverse surface.  When it breaks
+out of the overdensity, it creates a champange flow, where the
+ionization front transitions back to a weak R-type front.  The cloud
+surface is a constant-pressure contact discontinuity (CD) with a
+density jump of 100.  After the front heats the gas at the CD, there
+exists a pressure difference of $\sim 100$.  In response, the high
+density gas accelerates into the ambient medium and heats it to $3
+\times 10^4$ K.  Additionally a rarefaction wave travels towards the
+clump center.  At later times, the transverse D-type front continues
+through the clump, eventually creating a disk-like structure at the
+final time.  The polar champange flows proceed to flow outwards,
+creating a density shell with a diffuse ($10^{-28}$ \cubecm) and warm
+(5000 K) medium in its wake.
 
@@
 
-\subsection{Test 12: \ion{H}{2} region in a static potential}
-
-Next we construct a problem that is similar to the Rayleigh-Taylor
-test problem (Test 9) in nature but is spherically symmetric.  We use
-the same physical setup as Test 5 with a uniform medium and the
-radiation source at the origin.  It has a luminosity of $5 \times
-10^{48}$ ph s$^{-1}$ and a mono-chromatic spectrum of 14.6 eV.  We
-choose this energy so the ionization front is relatively sharp but
-still heats the gas to $10^4$ K.  The ambient medium has a density of
-$10^{-3}~\cubecm$ and an initial temperature of 100 K.  A point source
-of gravity also resides at the origin.  To have an equal gravitational
-acceleration $g(r) = g_0 / r^3$ at the Str\"{o}mgren radius $R_s =
-5.4$ kpc ($r = 0.36$) as Test 9, we set the strength of the point
-source $g_0 = 4.67 \times 10^{-3}$.  The gravity point source has the
-same effect on any pertubations as the constant gravitational force in
-Rayleigh-Taylor instability test.
-
-\subsection{Test 13: Time variations of the source luminosity}
+% \subsection{Test 12: \ion{H}{2} region in a static potential}
+
+% Next we construct a problem that is similar to the Rayleigh-Taylor
+% test problem (Test 9) in nature but is spherically symmetric.  We use
+% the same physical setup as Test 5 with a uniform medium and the
+% radiation source at the origin.  It has a luminosity of $5 \times
+% 10^{48}$ ph s$^{-1}$ and a mono-chromatic spectrum of 14.6 eV.  We
+% choose this energy so the ionization front is relatively sharp but
+% still heats the gas to $10^4$ K.  The ambient medium has a density of
+% $10^{-3}~\cubecm$ and an initial temperature of 100 K.  A point source
+% of gravity also resides at the origin.  To have an equal gravitational
+% acceleration $g(r) = g_0 / r^3$ at the Str\"{o}mgren radius $R_s =
+% 5.4$ kpc ($r = 0.36$) as Test 9, we set the strength of the point
+% source $g_0 = 4.67 \times 10^{-3}$.  The gravity point source has the
+% same effect on any pertubations as the constant gravitational force in
+% Rayleigh-Taylor instability test.
+
+\subsection{Test 12: Time variations of the source luminosity}
 

### 2010-08-14 ms.tex
Added missing references.
Adding Test 12 figure of kph and description of the radiation pulses.

@@
 \begin{equation}
-  d\mathbf{p}_\gamma = \frac{dP \; E_{\rm ph}}{c\;dt} \; \hat{r}
+  d\mathbf{p}_\gamma = \frac{dP \; E_{\rm ph}}{c} \; \hat{r}
 \end{equation}
 of the absorbed radiation from the incoming ray, where $\hat{r}$ is
-the normal direction of the ray and $dt$ is the radiative transfer
-timestep.  The resulting acceleration of the gas due to radiation
-pressure is
-\begin{equation}
-  d\mathbf{a} = d\mathbf{p}_\gamma / (\rho \; V_{\rm cell}),
-\end{equation}
-where $\rho$ is the gas density inside the cell.  This acceleration is
-then added to the other forces, e.g. gravity and gas pressure, in the
-calculation.
+the normal direction of the ray.  We do not include radiation pressure
+on dust, and thus our treatment underestimates its effects in
+applicable environments.  The resulting acceleration of the gas due to
+radiation pressure is
+\begin{equation}
+  d\mathbf{a} = \frac{d\mathbf{p}_\gamma} {dt\; \rho \; V_{\rm cell}},
+\end{equation}
+where $\rho$ is the gas density inside the cell and $dt$ is the
+radiative transfer timestep.  This acceleration is then added to the
+other forces, e.g. gravity and gas pressure, in the calculation.
 
@@
 
+\begin{figure}[t]
+  \epsscale{0.6}
+  \plotone{fig/test12_kph}
+  \caption{\label{fig:test12_kph} Test 12 (Time variations of the
+    source luminosity).  Slice of the photo-ionization rate
+    \kph~through the origin.  The source has a duty cycle of 0.5 Myr,
+    and the box has a light crossing time of 3.3 Myr.  The shells of
+    high \kph~originate from radiation that was emitted when the
+    source was at its peak luminosity, illustrating the
+    time-dependence of the radiative transfer equation.}
+  \epsscale{1}
+\end{figure}
+
 Our implementation retains the time derivative of the radiative
@@
   \label{eqn:test13}
-  L(t) = L_{\rm max} \times \exp(t_f/t_0 - 1),
-\end{equation}
-%
-where $t_f = \mathrm{mod}(t,t_0)$ and $t_0$ is the duty cycle.  To
-illustrate the variations in the photo-ionization rates due to a
-varying source, we remove any dependence on the medium by considering
-an optically-thin uniform density.  We take $L_{\rm box} = 1$ Mpc,
-which has a light crossing time of 3.3 Myr.  Thus we consider a source
-at the origin with $L_{\rm max} = 10^{50}$ ph s$^{-1}$ and $t_0 = 0.5$
+  L(t) = L_{\rm max} \times \exp[A(t_f/t_0 - 1)]
+\end{equation}
+%
+where $t_f = 2 \times |t - t_0 \times \mathrm{round}(t/t_0)|$, $t_0$
+is the duty cycle, and $A=4$ controls the width of the radiation
+pulse.  To illustrate the variations in the photo-ionization rates,
+shown in Figure \ref{fig:test12_kph}, due to a varying source, we
+remove any dependence on the medium by considering an optically-thin
+uniform density $\rho 10^{-4}~\cubecm$.  We take $L_{\rm box} = 1$
+Mpc, which has a light crossing time of 3.3 Myr.  A source is placed
+at the origin with $L_{\rm max} = 10^{55}$ ph s$^{-1}$ and $t_0 = 0.5$
 Myr.  We use a radiative transfer timestep of 50 kyr to resolve the

### 2010-08-16 ms.tex
Adding radial profile of kph for the variable source.  Adding descriptions of Test 12, the X-ray test, and the radiation pressure test.

@@
 expansion creates a photo-evaporative flow, seen in many star forming
-regions \citep[e.g. the Carina Nebula][]{Ref?} as stars irradiate
+regions \citep[e.g. M16][]{Hester96} as stars irradiate
 nearby cold, dense overdensities.  These flows become evident in the
@@
 absorbing radiation in the equatorial plane.  The latter case would be
-applicable in a subgrid model of an AGN or a protostar, for example.
-Simulating collimated radiation with ray tracing is trivially
-accomplished by only initializing rays that are within some opening
-angle $\theta_c$.
+applicable in a subgrid model of active galactic nuclei (AGN) or
+protostars, for example.  Simulating collimated radiation with ray
+tracing is trivially accomplished by only initializing rays that are
+within some opening angle $\theta_c$.
 
@@
 We illustrate the expansion of the \ion{H}{2} region created by the
-beamed radiation in Figure \ref{fig:test11}.  Before 3 Myr, the
+beamed radiation in Figure \ref{fig:test11}.  Before $t = 3$ Myr, the
 \ion{H}{2} region is conical and contained within the dense clump,
@@
 \begin{figure}[t]
-  \epsscale{0.6}
-  \plotone{fig/test12_kph}
+  \epsscale{1.15}
+  \plottwo{fig/test12_kph}{fig/test12_radial}
   \caption{\label{fig:test12_kph} Test 12 (Time variations of the
-    source luminosity).  Slice of the photo-ionization rate
+    source luminosity).  Left: Slice of the photo-ionization rate
     \kph~through the origin.  The source has a duty cycle of 0.5 Myr,
@@
     source was at its peak luminosity, illustrating the
-    time-dependence of the radiative transfer equation.}
+    time-dependence of the radiative transfer equation.  Right: Radial
+    profile \kph~with the inverse square law overplotted.}
   \epsscale{1}
@@
 light crossing time of the simulation.  Furthermore, the timestep
-should resolve the variation timescale by a few times.  To test this,
-we can use an exponentially varying source with some duty cycle.  In a
-functional form, this can be described as
+should resolve the variation timescale by a few times.  This property
+might be important in large box simulations with variable sources,
+e.g. AGN radiative feedback.  To test this, we can use an
+exponentially varying source with some duty cycle.  In a functional
+form, this can be described as
 %
@@
 is the duty cycle, and $A=4$ controls the width of the radiation
-pulse.  To illustrate the variations in the photo-ionization rates,
-shown in Figure \ref{fig:test12_kph}, due to a varying source, we
-remove any dependence on the medium by considering an optically-thin
-uniform density $\rho 10^{-4}~\cubecm$.  We take $L_{\rm box} = 1$
-Mpc, which has a light crossing time of 3.3 Myr.  A source is placed
-at the origin with $L_{\rm max} = 10^{55}$ ph s$^{-1}$ and $t_0 = 0.5$
-Myr.  We use a radiative transfer timestep of 50 kyr to resolve the
-duty cycle by 10 timesteps.
+pulse.  To illustrate the effects of source varability, we remove any
+dependence on the medium by considering an optically-thin uniform
+density $\rho 10^{-4}~\cubecm$.  We take $L_{\rm box} = 1$ Mpc, which
+has a light crossing time of 3.3 Myr.  A source is placed at the
+origin with $L_{\rm max} = 10^{55}$ ph s$^{-1}$ and $t_0 = 0.5$ Myr.
+We use a radiative transfer timestep of 50 kyr to resolve the duty
+cycle by 10 timesteps.  The simulation is run for 6 Myr, so the
+radiation propagates throughout the box.
+
+The variability of the source is clearly illustrated in the
+photo-ionization rates, shown in Figure \ref{fig:test12_kph}.  The
+shells of relative maximum \kph~corresponds to radiation that was
+emitted when the source was at its peak luminosity.  They are
+separated by $ct_0$ Mpc and are geometrically diluted with increasing
+radius.  Averaged over shells of the same width, photo-ionization
+rates decrease as $1/r^2$.
+
+Next we test the hydrodynamical response to a varying source by
+repeating Test 5.  We set the peak luminosity $L_{\rm max} = 2 \times
+10^{49}$ erg s$^{-1}$ that is a factor of 4 more luminous than Test
+5, so the average luminosity is $\sim 5 \times 10^{48}$ erg s$^{-1}$.
 
@@
 more diffusive choice of the HLL Riemann solver when compared to Roe's
-Riemann solver used in \citet{Krumholz07_ART}, which also uses PLM as
-a reconstruction method.  The evolution of the magnetic field lines
+Riemann solver used in \citet{Krumholz07_ART}, who also use PLM as a
+reconstruction method.  The evolution of the magnetic field lines
 evolve in a similar manner as their results.
@@
     ionized fraction showing the effects of secondary ionizations from
-    a mono-chromatic 1 keV spectrum.  The high energy photons can
-    ionize multiple hydrogen atoms, increasing the ionized fraction.
-    In part, less radiation goes into thermal energy, lowering the
-    temperature.}
+    a mono-chromatic 1 keV spectrum.  The discontinuity at $r \sim
+    0.4$ is caused by artifacts in the ray tracing, which is described
+    in Test 1.  The high energy photons can ionize multiple hydrogen
+    atoms, increasing the ionized fraction.  In part, less radiation
+    goes into thermal energy, lowering the temperature.}
   \epsscale{1}
@@
 
+Figure \ref{fig:xray_fig} shows the main effects of secondary
+ionizations from the 1 keV spectrum on the ionization and thermal
+state of the system.  Without secondary ionizations, each absorption
+results in one ionization with the remaining energy transferred into
+thermal energy.  But with secondary ionizations, recall that most of
+the radiation energy goes into hydrogen and helium ionizations in
+neutral gas; whereas in ionized gas, most of the energy is
+thermalized.  In this test, only the inner 300 pc is completely
+ionized because of the small cross-section of hydrogen at $E_{\rm ph}
+= 1$ keV.  Beyond this core, the medium is only partially ionized.
+This process expands the hot $T = 10^5$ K core by a factor of 2.  In
+the outer neutral regions, the ionization fraction is larger by a
+factor of $\sim 10$, which in turn results in less photo-heating,
+lowering the temperature by a factor 2--3.
+
 \subsection{Radiation pressure}
@@
 \begin{figure}[t]
+  \epsscale{1.075}
   \plottwo{fig/noRP_profiles.eps}{fig/RP_profiles.eps}
-  \caption{\label{fig:rp_profile150} (a) No radiation pressure.
+  \caption{\label{fig:rp_profiles} (a) No radiation pressure.
     Radial profiles of (clockwise from top left) density, temperature,
@@
     to 50 km/s.}
+  \epsscale{1}
 \end{figure}
@@
 $\mathbf{a}_{\rm rp} = E_{\rm ph}/c$.  This is especially important
-when the ionization front is in its initial R-type phase.  Thus we
-construct a test that focuses on a small scales, compared to the
-Str\"{o}mgren radius.  The domain has a size of 8 pc with a uniform
-density $\rho = 2900 \cubecm$ and initial temperature $T = 10^3$ K.
-The source is located at the origin with a luminosity $L = 10^{50}$ ph
-s$^{-1}$ and a $T=10^5$ K blackbody spectrum.  We use one energy group
-$E_{\rm ph} = 29.6$ eV.  The grid is adaptively refined on overdensity
-with the same criteron as Test 8.  The simulation is run for 150 kyr.
+when the ionization front is in its initial R-type phase, where the
+gas has not reacted to the thermal pressure yet.  Thus we construct a
+test that focuses on a small scales, compared to the Str\"{o}mgren
+radius.  The domain has a size of 8 pc with a uniform density $\rho =
+2900 \cubecm$ and initial temperature $T = 10^3$ K.  The source is
+located at the origin with a luminosity $L = 10^{50}$ ph s$^{-1}$ and
+a $T=10^5$ K blackbody spectrum.  We use one energy group $E_{\rm ph}
+= 29.6$ eV.  The grid is adaptively refined on overdensity with the
+same criteron as Test 8.  The simulation is run for 140 kyr.
+
+We compare nearly identical simulations but one with radiation
+pressure and one without radiation pressure to quantify its effects.
+Radial profiles of density, temperature, neutral fraction, and radial
+velocity are shown in Figure \ref{fig:rp_profiles} for both
+simulations.  Without radiation pressure, the evolution of the
+\ion{H}{2} is matches the analytical expectations described in
+\S\ref{sec:test5}.  At $t=140$ kyr, the ionization front radius is
+increased by $\sim5\% = 0.16$ pc.  However radiation pressure impacts
+the system the greatest inside the ionization front.  At $t = 40$ kyr,
+the central density is smaller by a factor of 20 with radiation
+pressure, but the temperatures are almost equal.  A rarefaction wave
+thus propagates toward the center, depicted by the negative radial
+velocities at $t = 60$ kyr.  This raises the central density to
+$10^{-21}$ g \cubecm~at $t = 80$ kyr.  Afterwards, the radiation
+continues to force gas outwards.  From $t = 100$ kyr to $t = 140$ kyr,
+the maximum radial velocity of the ionized gas increases from 10
+\kms~to 50 \kms.  This leaves behind an even more diffuse medium,
+lowering the gas density by a factor of 10 at $t = 140$ kyr.  Thus the
+recombination rates are lower, resulting in increased ionization
+fractions and temperatures in the \ion{H}{2} region.
 

### 2010-08-16 ms.tex
Started introduction with some history.  Added appropriate refs.

@@
 encompassing topics such as stellar atmospheres, the interstellar
-medium (ISM), galaxy formation, and cosmology.  Thus it is a
-well-studied problem \citep[e.g.][and more!]{Rybicki}; however, its
+medium (ISM), star formation, galaxy formation, supernovae (SNe) and
+cosmology.  Thus it is a well-studied problem
+\citep[e.g.][]{Mathews65, Rybicki, Mihalas84, Yorke86}; however, its
 treatment in multi-dimensional calculations is difficult because of
@@
 difficulty.  In the general case, one must consider all radiation
-sources at every point in calculation.  (add: simplify by symmetries
-and special cases)
+sources at every point in calculation.  Fortunately problems can be
+simplified by exploiting symmetries and special cases.  The most basic
+case was first considered by \citet{Stroemgren39} for a radiation
+source ionizing a static uniform neutral medium.  He found that the
+delineation between the neutral and ionized medium was found to be
+approximately the mean free path of the ionizing radiation.  His
+seminar work was expanded upon by \citet{Spitzer48, Spitzer49,
+  Spitzer54} and \citet{Spitzer50}, who showed that the ionizing
+radiation heated the medium to $T \sim 10^4$ K.  If the density is
+equal on both sides of the ionization front, then this
+over-pressurized region would expand and drive a shock outwards
+\citep[e.g.][]{Oort54, Schatzman55}.  These early works provided the
+basis for the modern topic of radiation hydrodynamics.  A decade
+later, radiation hydrodynamical numerical models of \ion{H}{2} regions
+in spherical symmetry were developed that described the expansion of
+the ionization front and the evolution of its associated shock wave
+that carries most of the gas outwards \citep[e.g.][]{Mathews65,
+  Lasker66, Hjellming66}.  At the same time, theoretical models of
+ionization fronts matured and were classified by \citet{Kahn54} and
+\citet{Axford61} as either R-type (rare) or D-type (dense).  R-type
+fronts travel supersonically with respect to the neutral gas, whereas
+D-type front are subsonic.  Furthermore ``weak'' and ``strong'' R-type
+fronts move subsonically and supersonically with respect to the
+ionized gas.  The same terminology conversely applies to D-type
+fronts.
 
@@
 velocity are shown in Figure \ref{fig:rp_profiles} for both
-simulations.  Without radiation pressure, the evolution of the
-\ion{H}{2} is matches the analytical expectations described in
-\S\ref{sec:test5}.  At $t=140$ kyr, the ionization front radius is
-increased by $\sim5\% = 0.16$ pc.  However radiation pressure impacts
-the system the greatest inside the ionization front.  At $t = 40$ kyr,
-the central density is smaller by a factor of 20 with radiation
-pressure, but the temperatures are almost equal.  A rarefaction wave
-thus propagates toward the center, depicted by the negative radial
-velocities at $t = 60$ kyr.  This raises the central density to
-$10^{-21}$ g \cubecm~at $t = 80$ kyr.  Afterwards, the radiation
-continues to force gas outwards.  From $t = 100$ kyr to $t = 140$ kyr,
-the maximum radial velocity of the ionized gas increases from 10
-\kms~to 50 \kms.  This leaves behind an even more diffuse medium,
-lowering the gas density by a factor of 10 at $t = 140$ kyr.  Thus the
-recombination rates are lower, resulting in increased ionization
-fractions and temperatures in the \ion{H}{2} region.
+simulations at several times.  Without radiation pressure, the
+evolution of the \ion{H}{2} is matches the analytical expectations
+described in \S\ref{sec:test5}.  At $t=140$ kyr, the ionization front
+radius is increased by $\sim5\% = 0.16$ pc.  However radiation
+pressure impacts the system the greatest inside the ionization front.
+At $t = 40$ kyr, the central density is smaller by a factor of 20 with
+radiation pressure, but the temperatures are almost equal.  A
+rarefaction wave thus propagates toward the center, depicted by the
+negative radial velocities at $t = 60$ kyr.  This raises the central
+density to $10^{-21}$ g \cubecm~at $t = 80$ kyr.  Afterwards, the
+radiation continues to force gas outwards.  From $t = 100$ kyr to $t =
+140$ kyr, the maximum radial velocity of the ionized gas increases
+from 10 \kms~to 50 \kms.  This leaves behind an even more diffuse
+medium, lowering the gas density by a factor of 10 at $t = 140$ kyr.
+Thus the recombination rates are lower, resulting in increased
+ionization fractions and temperatures in the \ion{H}{2} region.
 
@@
 density of $10^{-3}$ \cubecm and $T = 10^4$ K.  This setup is similar
-to Test 1.  The domain has a resolution of $128^3$ and is 20 kpc in
-width, and the problem is run for 500 Myr.
+to Test 1.  The domain has a resolution of $128 \times 64 \times 64$
+It is 20 kpc in width and is 10 kpc in height and depth.  The problem
+is run for 500 Myr.
 

### 2010-08-17 ms.tex
Finished the first draft of the intro.

@@
-%\documentclass[apj]{emulateapj}
+%\documentclass[apj,onecolumn]{emulateapj}
 \documentclass[12pt,preprint]{aastex}
@@
 difficulty.  In the general case, one must consider all radiation
-sources at every point in calculation.  Fortunately problems can be
-simplified by exploiting symmetries and special cases.  The most basic
-case was first considered by \citet{Stroemgren39} for a radiation
-source ionizing a static uniform neutral medium.  He found that the
-delineation between the neutral and ionized medium was found to be
-approximately the mean free path of the ionizing radiation.  His
-seminar work was expanded upon by \citet{Spitzer48, Spitzer49,
-  Spitzer54} and \citet{Spitzer50}, who showed that the ionizing
-radiation heated the medium to $T \sim 10^4$ K.  If the density is
-equal on both sides of the ionization front, then this
-over-pressurized region would expand and drive a shock outwards
-\citep[e.g.][]{Oort54, Schatzman55}.  These early works provided the
-basis for the modern topic of radiation hydrodynamics.  A decade
-later, radiation hydrodynamical numerical models of \ion{H}{2} regions
-in spherical symmetry were developed that described the expansion of
-the ionization front and the evolution of its associated shock wave
-that carries most of the gas outwards \citep[e.g.][]{Mathews65,
-  Lasker66, Hjellming66}.  At the same time, theoretical models of
+sources at every point in calculation.
+
+Fortunately problems can be simplified by exploiting symmetries and
+special cases.  The most basic case was first considered by
+\citet{Stroemgren39} for a radiation source ionizing a static uniform
+neutral medium.  He found that the delineation between the neutral and
+ionized medium was found to be approximately the mean free path of the
+ionizing radiation.  His seminar work was expanded upon by
+\citet{Spitzer48, Spitzer49, Spitzer54} and \citet{Spitzer50}, who
+showed that the ionizing radiation heated the medium to $T \sim 10^4$
+K.  If the density is equal on both sides of the ionization front,
+then this over-pressurized region would expand and drive a shock
+outwards \citep[e.g.][]{Oort54, Schatzman55}.  These early works
+provided the basis for the modern topic of radiation hydrodynamics.  A
+decade later, the first radiation hydrodynamical numerical models of
+\ion{H}{2} regions in spherical symmetry and plane-parallel ionization
+fronts were developed \citep[e.g.][]{Mathews65, Lasker66,
+  Hjellming66}.  They described the expansion of the ionization front
+and the evolution of its associated shock wave that carries most of
+the gas away from the source.  At the same time, theoretical models of
 ionization fronts matured and were classified by \citet{Kahn54} and
@@
 ionized gas.  The same terminology conversely applies to D-type
-fronts.
-
-There are several methods to solve the radiative transfer.
+fronts. (add evolution of an \ion{H}{2} region)
+
+In the 1970's and 1980's, algorithmic and computational advances
+allowed numerical models to be expanded to two dimensions, mainly
+using axi-symmetric to simplify the problem
+\citep[e.g.][]{Bodenheimer79, Sandford82, Yorke83}.  One topic that was
+studied extensively were champange flows.  Here the source is embedded
+in an overdense region, and the \ion{H}{2} region escapes from this
+region in one direction.  The interface between the ambient and dense
+medium was usually set up to be a constant pressure boundary.  When
+the ionization front passes this boundary, the dense, ionized gas is
+orders of magnitude out of pressure equilibrium as the temperatures on
+both sides of initial boundary are within a factor of a few.  In
+response, the gas is accelerated outwards in this direction, creating
+a fan-shaped outflow.
+
+Only in the past 15 years, computational resources have become large
+enough, along with further algorithmic advances, to cope with the
+requirements of three-dimensional calculations.  There are two popular
+methods to solve the radiative transfer equation in three-dimensions:
+%
+\begin{enumerate}
+\item Moment methods---The angular moments of the radiation field can
+  describe its angular structure, which are related to the energy
+  energy, flux, and radiation pressure \citep{Auer70, Norman98}.
+  These have been implemented in conjunction with short
+  characteristics \citep{Stone92_RT}, with long characteristics
+  \citep{Finlator08}, and with a variable Eddington tensor in the
+  optically thin limit \citep[OTVET;][]{Gnedin01_OTVET, Petkova09}.
+  Moment methods have the advantage of being fast, being independent
+  of the number of radiation point sources.  However, they are
+  diffusive and result in incorrect shadows in some situations.
+\item Ray tracing---Radiation can be propagated along rays that extend
+  through the compuational grid \citep[e.g.][]{Mellema98, Razoumov99,
+    Abel99, Ciardi00, Ritzerveld03, Whalen05, Rijkhorst05, Mellema06,
+    Alvarez06, Trac07, Krumholz07_ART, Paardekooper10} or particle set
+  \citep[e.g.][]{Susa06, Johnson07, Pawlik08, Altay08, Hasegawa09,
+    Pawlik10}.  In general, these methods are very accurate but
+  computationally expensive because the radiation field must be well
+  sampled by the rays with respect to the spatial resolution of the
+  grid or particles.
+\end{enumerate}
+%
+Until the mid-2000's the vast majority of the three-dimensional
+calculations were performed with static density distributions.  One
+example is calculating cosmological reionization by post-processing of
+density fields from N-body simulations \citep{Ciardi01, Sokasian01,
+  McQuinn05, Iliev07}.  Any hydrodynamical response to the radiation
+field was thus ignored.  Several radiative transfer codes were
+compared in four purely radiative transfer tests in \citet[hereafter
+RT06]{RT06}.  Only recently has the radiative transfer equation been
+coupled to the hydrodynamics in three-dimensions.  In the second
+comparision paper \citep[hereafter RT09]{Iliev09}, results from these
+radiation hydrodynamics codes were compared.  Even more rare are ones
+that couple it with magneto-hydrodynamics
+\citep[e.g.][]{Krumholz07_ART}.  The tests in RT06 and RT09 were kept
+relatively simple to ease the comparison.
+
+In this paper, we present our implementation, Enzo+Moray, of adaptive
+ray tracing \citep{Abel02_RT} in the cosmological hydrodynamics
+adaptive mesh refinement (AMR) code, \enzo~\citep{BryanNorman1997,
+  OShea2004}.  The radiation field is coupled to the hydrodynamics
+solver at small timescales, enabling it to study radiation
+hydrodynamical problems.  We have used this code to investigate the
+growth of an \ion{H}{2} region from a 100\Ms~Population III (Pop III)
+star \citep{Abel07}, radiative feedback on the formation of high
+redshift dwarf galaxies \citep{Wise08_Gal}, the early stages of
+reionization from Pop III stars \citep{Wise08_Reion}, ultraviolet
+radiation escape fractions from dwarf galaxies before reionization
+\citep{Wise09}, radiative negative feedback from accreting Pop III
+seed black holes \citep{Alvarez09}, and radiative feedback in
+accreting supermassive black holes \citep{Kim11}.  We have included
+Enzo+Moray in the latest public release of
+\enzo\footnote{http://lca.ucsd.edu/enzo}, and it is also coupled with
+the newly added MHD solver in \enzo~\citep{Wang09}.
+
+We have structured this paper as follows.  In Section 2, we describe
+the connections between adaptive ray tracing and the radiative
+transfer equation.  Furthermore, we detail how physics other than
+photo-ionization and photo-heated are included.  We then derive a
+geometric correction factor to any ray tracing method to improve
+accuracy.  We end the section by describing a new computational
+technique to approximate an optically-thin radiation field with ray
+tracing and multiple sources.  In Section 3, we cover the details of
+our radiation hydrodynamics implementation in \enzo, specifically (1)
+the ray tracing algorithms, (2) coupling with the hydrodynamics
+solver, (3) several methods to calculate the radiative transfer
+timestep, and (4) our parallelization strategy.  We present our
+results from the RT06 radiative transfer tests in Section 4.
+Afterwards in Section 5, we show the results from the RT09 radiation
+hydrodynamics tests.  We expand on these tests to include more
+dynamical and complex setups to demonstrate the flexibility and high
+fidelity of Enzo+Moray.  Section 6 reports the results from spatial,
+angular, frequency, and temporal resolution tests.  In Section 7, we
+illustrate the improvements from the geometric correction factor and
+our optically-thin approximation.  We also show the effects of X-ray
+radiation and radiation pressure in this section.  Finally in Section
+8, we demonstrate the parallel scalability of Enzo+Moray.  Last
+Section 9 summarizes our method and results.
 
@@
 \enzo~is a parallel block-structured AMR \citep{BergerAMR} code that
-is publicly available\footnote{http://lca.ucsd.edu/enzo}
-\citep{BryanNorman1997, OShea2004}.  In this section, we describe our
-parallel implementation of the adaptive ray tracing method into \enzo.
-First we explain the programming design of handling the ``photon
-packages'' that are traced along the adaptive rays.  We use the terms
-photon packages and rays interchangably.  Next we focus on the details
-of the radiation hydrodynamics and then the importance of correct
-timestepping.  Last we give our parallelization strategy of tracing
-rays through an AMR hierarchy.  This implementation is included in the
-\texttt{v2.0} public version of \enzo.
+is publicly available \citep{BryanNorman1997, OShea2004}.  In this
+section, we describe our parallel implementation of the adaptive ray
+tracing method into \enzo.  First we explain the programming design of
+handling the ``photon packages'' that are traced along the adaptive
+rays.  We use the terms photon packages and rays interchangably.  Next
+we focus on the details of the radiation hydrodynamics and then the
+importance of correct timestepping.  Last we give our parallelization
+strategy of tracing rays through an AMR hierarchy.  This
+implementation is included in the \texttt{v2.0} public version of
+\enzo.
 
@@
 
-In our implementation, photon packages are mono-chromatic and are
-assigned a photon type that corresponds whether it is a photon that
-(1) ionizes hydrogen, (2) singly ionizes helium, (3) doubly ionizes
-helium, (4) has an X-ray energy, or (5) dissociates molecular hydrogen
-(Lyman-Werner radiation).  One disadvantage of mono-chromatic rays is
-the number of rays increase with the number of frequency bins.
-However this allows for early termination of rays that are fully
-absorbed, which are likely to have high absorption cross-sections
-(e.g. \ion{H}{1} ionizations near 13.6 eV) or a low initial intensity
-(e.g. \ion{He}{2} ionizing photons in typical stellar populations).
-The other approach used by some groups \citep[e.g.][]{Trac07} is to
-store all energy groups in a single ray.  This reduces the number of
-the rays generated and the computation associated with the ray
-tracing.  Unless the ray dynamically adjusts its memory allocation for
-the energy groups as they become depleted, this method is also memory
-intensive in the situation where most of the energy groups are
-completely absorbed but a few groups still have significant flux.
+In our implementation, photon packages are mono-chromatic, i.e. energy
+groups \citep[][Ch. 6]{Mihalas84}, and are assigned a photon type that
+corresponds whether it is a photon that (1) ionizes hydrogen, (2)
+singly ionizes helium, (3) doubly ionizes helium, (4) has an X-ray
+energy, or (5) dissociates molecular hydrogen (Lyman-Werner
+radiation).  One disadvantage of mono-chromatic rays is the number of
+rays increase with the number of frequency bins.  However this allows
+for early termination of rays that are fully absorbed, which are
+likely to have high absorption cross-sections (e.g. \ion{H}{1}
+ionizations near 13.6 eV) or a low initial intensity (e.g. \ion{He}{2}
+ionizing photons in typical stellar populations).  The other approach
+used by some groups \citep[e.g.][]{Trac07} is to store all energy
+groups in a single ray.  This reduces the number of the rays generated
+and the computation associated with the ray tracing.  Unless the ray
+dynamically adjusts its memory allocation for the energy groups as
+they become depleted, this method is also memory intensive in the
+situation where most of the energy groups are completely absorbed but
+a few groups still have significant flux.
 
@@
 modeling Population III stellar radiation \citep[e.g.][for hydrogen
-  ionizing radiation only]{Abel07, Wise08b}, we have 3 energy
+  ionizing radiation only]{Abel07, Wise08_Gal}, we have 3 energy
 groups---\ion{H}{1}, \ion{He}{1}, \ion{He}{2}---each with an energy
@@
 conservative, one may choose the sound-crossing time of a cell
-\citep[e.g.][]{Abel07, Wise08b}.  Alternatively, the diameter of the
+\citep[e.g.][]{Abel07, Wise08_Gal}.  Alternatively, the diameter of the
 smallest relevant system (e.g., an accretion radius, transition radius
@@
 computational tools.  In this section, we present tests drawn from the
-Cosmological Radiative Transfer Codes Comparison Project
-\citep[][hereafter RT06]{RT06}, where results from 11 different
-radiative transfer codes compared results in four test problems.  The
-codes use various methods for radiation transport: ray tracing with
-short, long, and hybrid characteristics, Monte Carlo casting;
-ionization front tracking \citep{Alvarez06_IFT}; variable Eddington
-Tensor formalism \citep{Gnedin01_OTVET}.  They conducted tests that
-investigated (1) the growth of a single Str\"{o}mgren sphere enforcing
-isothermal conditions, (2) the same test with an evolving temperature
-field, (3) shadowing created by a dense, opticlally thick clump, and
-(4) multiple \ion{H}{2} regions in a cosmological density field.  In
-all of the tests presented here, we use the method of restricted
-neutral fraction changes (\S\ref{sec:dt_hi}) for choosing a radiative
-transfer timestep.  We cast 48 rays (HEALPix level 1) from the point
-source and require a sampling of at least $\Phi_c = 5.1$ rays per
-cell.
+Cosmological Radiative Transfer Codes Comparison Project \citep{RT06},
+where results from 11 different radiative transfer codes compared
+results in four test problems.  The codes use various methods for
+radiation transport: ray tracing with short, long, and hybrid
+characteristics, Monte Carlo casting; ionization front tracking
+\citep{Alvarez06_IFT}; variable Eddington Tensor formalism
+\citep{Gnedin01_OTVET}.  They conducted tests that investigated (1)
+the growth of a single Str\"{o}mgren sphere enforcing isothermal
+conditions, (2) the same test with an evolving temperature field, (3)
+shadowing created by a dense, opticlally thick clump, and (4) multiple
+\ion{H}{2} regions in a cosmological density field.  In all of the
+tests presented here, we use the method of restricted neutral fraction
+changes (\S\ref{sec:dt_hi}) for choosing a radiative transfer
+timestep.  We cast 48 rays (HEALPix level 1) from the point source and
+require a sampling of at least $\Phi_c = 5.1$ rays per cell.
 

### 2010-08-17 ms.tex
Adding figure for the two-source test problem.

@@
   characteristics \citep{Stone92_RT}, with long characteristics
-  \citep{Finlator08}, and with a variable Eddington tensor in the
-  optically thin limit \citep[OTVET;][]{Gnedin01_OTVET, Petkova09}.
-  Moment methods have the advantage of being fast, being independent
-  of the number of radiation point sources.  However, they are
-  diffusive and result in incorrect shadows in some situations.
+  \citep{Finlator08}, with a variable Eddington tensor in the
+  optically thin limit \citep[OTVET;][]{Gnedin01_OTVET, Petkova09},
+  and with an M1 closer relation \citep{Gonzalez07, Aubert08}.  Moment
+  methods have the advantage of being fast, being independent of the
+  number of radiation point sources.  However, they are diffusive and
+  result in incorrect shadows in some situations.
 \item Ray tracing---Radiation can be propagated along rays that extend
@@
 Test 5 with two changes --- (1) the domain has been decreased to
-$L_{\rm box} = 1.5$ kpc; and (2) a mild blastwave is initialized in
-the center of the domain.  We use 3 levels of AMR with a base grid of
+$L_{\rm box} = 1.5$ kpc; and (2) a blastwave is initialized in the
+center of the domain.  We use 3 levels of AMR with a base grid of
 64$^3$, which is refined if the density slope is greater than 0.4.
@@
 
+\begin{figure}[t]
+  \epsscale{0.6}
+  \plotone{fig/two_sources.eps}
+  \caption{\label{fig:twosrc} Slice of neutral fraction at $t = 500$
+    Myr through the sources in the consolidated \ion{H}{2} test.
+    There are no artifacts associated with rays being emitted from two
+    sources.  Both of the ionized regions are spherically symmetric
+    before they overlap.}
+  \epsscale{1}
+\end{figure}
+
 Here we test for any inaccuracies in the case of multiple sources.  We
@@
 the two sources are enveloped in a common, elongated \ion{H}{2}
-region.
+region.  To illustrate this, we show the neutral fraction in Figure
+\ref{fig:twosrc}.  Our method keeps spherical symmetry close to the
+individual sources, and there are no perceptible artifacts from having
+multiple sources.
 

### 2010-08-17 ms.tex
Adding many references for the introduction.

@@
   These have been implemented in conjunction with short
-  characteristics \citep{Stone92_RT}, with long characteristics
-  \citep{Finlator08}, with a variable Eddington tensor in the
+  characteristics \citep[2D]{Stone92_RHD}, with long characteristics
+  \citep{Finlator09}, with a variable Eddington tensor in the
   optically thin limit \citep[OTVET;][]{Gnedin01_OTVET, Petkova09},
@@
 \item Ray tracing---Radiation can be propagated along rays that extend
-  through the compuational grid \citep[e.g.][]{Mellema98, Razoumov99,
-    Abel99, Ciardi00, Ritzerveld03, Whalen05, Rijkhorst05, Mellema06,
-    Alvarez06, Trac07, Krumholz07_ART, Paardekooper10} or particle set
+  through the compuational grid \citep[e.g.][]{Razoumov99, Abel99_RT,
+    Ciardi01, Sokasian01, Whalen06, Rijkhorst06, Mellema06, Alvarez06,
+    Trac07, Krumholz07_ART, Paardekooper10} or particle set
   \citep[e.g.][]{Susa06, Johnson07, Pawlik08, Altay08, Hasegawa09,
@@
 density fields from N-body simulations \citep{Ciardi01, Sokasian01,
-  McQuinn05, Iliev07}.  Any hydrodynamical response to the radiation
-field was thus ignored.  Several radiative transfer codes were
-compared in four purely radiative transfer tests in \citet[hereafter
-RT06]{RT06}.  Only recently has the radiative transfer equation been
-coupled to the hydrodynamics in three-dimensions.  In the second
-comparision paper \citep[hereafter RT09]{Iliev09}, results from these
-radiation hydrodynamics codes were compared.  Even more rare are ones
-that couple it with magneto-hydrodynamics
-\citep[e.g.][]{Krumholz07_ART}.  The tests in RT06 and RT09 were kept
-relatively simple to ease the comparison.
+  McQuinn07, Iliev06, Iliev07}.  Any hydrodynamical response to the
+radiation field was thus ignored.  Several radiative transfer codes
+were compared in four purely radiative transfer tests in
+\citet[hereafter RT06]{RT06}.  Only recently has the radiative
+transfer equation been coupled to the hydrodynamics in
+three-dimensions.  In the second comparision paper \citep[hereafter
+  RT09]{Iliev09}, results from these radiation hydrodynamics codes
+were compared.  Even more rare are ones that couple it with
+magneto-hydrodynamics \citep[e.g.][]{Krumholz07_ART}.  The tests in
+RT06 and RT09 were kept relatively simple to ease the comparison.
 

### 2010-08-17 ms.tex
Added figure and caption for frequency resolution tests.

@@
 Fortunately problems can be simplified by exploiting symmetries and
-special cases.  The most basic case was first considered by
-\citet{Stroemgren39} for a radiation source ionizing a static uniform
-neutral medium.  He found that the delineation between the neutral and
-ionized medium was found to be approximately the mean free path of the
-ionizing radiation.  His seminar work was expanded upon by
+special cases.  The first case was considered by \citet{Stroemgren39}
+for a radiation source ionizing a static uniform neutral medium, where
+recombinations balnace photo-ionizations.  He derived a radius of an
+\ion{H}{2} region,
+%
+\begin{equation}
+  \label{eqn:Rstr}
+  R_s = \left(\frac{3\dot{N}_\gamma}{4\pi \alpha_{\rm B} n_H^2}\right)^{1/3},
+\end{equation}
+where $\dot{N}_\gamma$ is the ionizing photon luminosity, $\alpha_{\rm
+  B}$ is the recombination rate, and $n_H$ is the ambient hydrogen
+number density.  Furthermore he found that the delineation between the
+neutral and ionized medium to be approximately the mean free path of
+the ionizing radiation.  His seminar work was expanded upon by
 \citet{Spitzer48, Spitzer49, Spitzer54} and \citet{Spitzer50}, who
@@
 ionization fronts matured and were classified by \citet{Kahn54} and
-\citet{Axford61} as either R-type (rare) or D-type (dense).  R-type
-fronts travel supersonically with respect to the neutral gas, whereas
-D-type front are subsonic.  Furthermore ``weak'' and ``strong'' R-type
-fronts move subsonically and supersonically with respect to the
-ionized gas.  The same terminology conversely applies to D-type
-fronts. (add evolution of an \ion{H}{2} region)
+\citet{Axford61} as either R-type (rare) or D-type (dense).  In R-type
+fronts, the ionized gas density is higher than the neutral gas
+density, and in D-type fronts, the opposite is true.  R-type fronts
+travel supersonically with respect to the neutral gas, whereas D-type
+front are subsonic.  Furthermore ``weak'' and ``strong'' R-type fronts
+move supersonically and subsonically with respect to the ionized gas,
+respectively.  The same terminology conversely applies to D-type
+fronts.  ``Critical'' fronts are defined as moving exactly at the
+sound speed.  These works established the evolutionary track of an
+expanding \ion{H}{2} illuminated by a massive star in a uniform
+medium:
+%
+\begin{enumerate}
+\item Weak R-type---When the star (gradually) starts to shine, the
+  ionization front will move supersonically through the ambient
+  medium.  The gas is heated and ionized, but otherwise left
+  undisturbed.  This stage continues until $r \sim 0.02R_s$.
+\item Critical R-type---As the ionization front moves outwards, it
+  begins to slow because of the geometric dilution of the radiation.
+  It becomes a critical R-type front, which is equivalent to an
+  isothermal shock in the neutral gas.
+\item Strong and weak D-type---The front continues to slow, becoming a
+  strong D-type front, and then a critical D-type front.  From this
+  point forward, it is moving subsonically with respect to the ionized
+  gas, i.e. a weak D-type front.  Thus sound waves can travel across
+  the ionization front and form a shock.  The ionization front
+  detaches from the shock, putting the shock ahead of the ionization
+  front.
+\item Expansion phase---After the shock forms, the \ion{H}{2} region
+  starts to expand, lowering the interior density and thus the
+  recombination rates.  This increases the number of photons available
+  for ionizing the gas.  The sphere expands until it reaches pressure
+  equilibrium with the ambient medium at $r \sim 5R_s$.
+\end{enumerate}
+%
 
@@
 %
-\begin{enumerate}
+\begin{itemize}
 \item Moment methods---The angular moments of the radiation field can
@@
     Trac07, Krumholz07_ART, Paardekooper10} or particle set
-  \citep[e.g.][]{Susa06, Johnson07, Pawlik08, Altay08, Hasegawa09,
-    Pawlik10}.  In general, these methods are very accurate but
+  \citep[e.g.][]{Susa06, Johnson07, Pawlik08, Pawlik10, Altay08,
+    Hasegawa09}.  In general, these methods are very accurate but
   computationally expensive because the radiation field must be well
@@
   grid or particles.
-\end{enumerate}
+\end{itemize}
 %
@@
 seed black holes \citep{Alvarez09}, and radiative feedback in
-accreting supermassive black holes \citep{Kim11}.  We have included
-Enzo+Moray in the latest public release of
+accreting supermassive black holes \citep[][in prep.]{Kim11}.  We have
+included Enzo+Moray in the latest public release of
 \enzo\footnote{http://lca.ucsd.edu/enzo}, and it is also coupled with
@@
 bugs in the development process.  In this problem, the ionized region
-grows until recombinations balance photo-ionizations, which happens at
-a radius of
-%
-\begin{equation}
-  \label{eqn:Rstr}
-  R_s = \left(\frac{3\dot{N}_\gamma}{4\pi \alpha_{\rm B} n_H^2}\right)^{1/3},
-\end{equation}
-where $\dot{N}_\gamma$ is the ionizing photon luminosity, $\alpha_{\rm
-  B}$ is the recombination rate, and $n_H$ is the ambient hydrogen
-number density.  The evolution of the radius $r_s$ and velocity $v_s$
-of the ionization front has an exact solution of
+grows until recombinations balance photo-ionizations
+(Eq. \ref{eqn:Rstr}).  The evolution of the radius $r_s$ and velocity
+$v_s$ of the ionization front has an exact solution of
 %
@@
 
+\begin{figure}[t]
+  \epsscale{1.05}
+  \plottwo{fig/nures040}{fig/nures100}
+  \caption{\label{fig:nu_dep} Radial profiles of (clockwise from the
+    upper left) density, temperature, radial velocity, and ionized
+    fraction for Test 5 with $n_\nu = 1$, 2, 4, 8, and 16 frequency
+    bins sampling the $T=10^5$ K blackbody spectrum.  The data are
+    shown at $t = 200$ Myr (left) and $t = 500$ Myr (right).  The
+    double-peaked structure in the shock only appears with a
+    multi-frequency spectrum.  The solution converges at $n_\nu \ge
+    4$.}  
+  \epsscale{1}
+\end{figure}
+
 In practice, we find good agreement within 5--10\% of analytical

### 2010-08-19 ms.tex
Added timestep tests and figures.  Increased linewidth in dx-test figure.

@@
 
-\subsection{Test 5: Classical \ion{H}{2} region expansion}
+\subsection{Test 5. Classical \ion{H}{2} region expansion}
 \label{sec:test5}
@@
 
-\subsection{Test 6: \ion{H}{2} region expansion in an isothermal
+\subsection{Test 6. \ion{H}{2} region expansion in an isothermal
   sphere}
@@
 
-\subsection{Test 7: Photo-evaporation of a dense clump}
+\subsection{Test 7. Photo-evaporation of a dense clump}
 
@@
 
-\subsection{Test 8: Champange flow from a dense clump}
+\subsection{Test 8. Champange flow from a dense clump}
 
@@
 
-\subsection{Test 9: Irradiated Rayleigh-Taylor instability}
+\subsection{Test 9. Irradiated Rayleigh-Taylor instability}
 
@@
 
-\subsection{Test 10: Photo-evaporation of a blastwave}
+\subsection{Test 10. Photo-evaporation of a blastwave}
 
@@
 
-\subsection{Test 11: Collimated radiation from a dense clump}
+\subsection{Test 11. Collimated radiation from a dense clump}
 
@@
 
-% \subsection{Test 12: \ion{H}{2} region in a rotating medium}
+% \subsection{Test 12. \ion{H}{2} region in a rotating medium}
 % 
@@
 
-% \subsection{Test 12: \ion{H}{2} region in a static potential}
+% \subsection{Test 12. \ion{H}{2} region in a static potential}
 
@@
 
-\subsection{Test 12: Time variations of the source luminosity}
+\subsection{Test 12. Time variations of the source luminosity}
 
@@
 
-\subsection{Test 14: \ion{H}{2} region with MHD}
+\subsection{Test 14. \ion{H}{2} region with MHD}
 
@@
 
-In practice, we find good agreement within 5--10\% of analytical
-solutions in Tests 1, 2, and 5 with only one energy group.  We use
-Test 5 (\S\ref{sec:test5}; an expanding \ion{H}{2} region with
-hydrodynamics) to probe any differences in the solution when varying
-the resolution of the spectrum.  In RT09, ZEUS-MP was used to
-demonstrate the effect of a multi-frequency spectrum on the dynamics
-of the ionization front in this test.  Instead of a single shock seen
-in the mono-chromatic spectrum, a the shock obtained a double-peaked
-structure in density and radial velocity.  We rerun Test 5 with a
-$T=10^5$ K blackbody spectrum sampled by 1, 2, 4, 8, and 16 frequency
-bins.
+The ionization front radius is within 5--10\% of analytical solutions
+in Tests 1, 2, and 5 with only one energy group; however a
+multi-frequency spectrum can create differences in the reactive
+flows.  We use Test 5 (\S\ref{sec:test5}; an expanding \ion{H}{2}
+region with hydrodynamics) to probe any differences in the solution
+when varying the resolution of the spectrum.  In RT09, ZEUS-MP was
+used to demonstrate the effect of a multi-frequency spectrum on the
+dynamics of the ionization front in this test.  Instead of a single
+shock seen in the mono-chromatic spectrum, a the shock obtained a
+double-peaked structure in density and radial velocity.  We rerun Test
+5 with a $T=10^5$ K blackbody spectrum sampled by $n_\nu = 1$, 2, 4,
+8, and 16 frequency bins.  We use the following energies:
+%
+\begin{itemize}
+\item $n_\nu = 1$: Mean energy of 29.6 eV
+\item $n_\nu = 2$: Mean energies in bins 13.6--30 and $>$30 eV---21.1,
+  43.0 eV
+\item $n_\nu = 4$: Mean energies in bins 13.6--20, 20--30, 30--40, and
+  $>$40 eV---16.7, 24.6, 34.5, 52.1 eV
+\item $n_\nu = 8, 16$: Logarithmically spaced between 13.6 and 50 eV
+  for the first $n_\nu-1$ bins, and the last bin is the mean energy
+  above 50 eV.
+\end{itemize}
+
+Figure \ref{fig:nu_dep} shows the radial profiles of density,
+temperature, ionized fraction, and radial velocity at $t = 200$ Myr
+and $t = 500$ Myr.  All of the runs with $n_\nu > 1$ show the double
+peaked features in density and radial velocities.  The mono-chromatic
+spectrum misses this feature completely because all of the radiation
+is absorbed at a characteristic column density.  In the
+multi-frequency spectra, the higher energy photons are absorbed at
+larger column densities and photo-heated this gas.  This heated gas
+creates a photo-evaporative flow that collides with the innermost
+shock, forming the double peaked density profile.  The $n_\nu \ge 4$
+runs are indistinguishable, and the $n_\nu = 2$ spectrum only leads to
+a marginally higher density in the outer shock and lower ionized
+fractions and tempeatures in the ambient medium.  In effect, a
+mono-chromatic spectrum can be sufficient if the problem focuses on
+large-scale quantities, e.g. ionized filling fractions in reionization
+calculations.  Conversely these effects may be important when studying
+small-scale, e.g. photo-evaporation.
 
@@
 
+\begin{figure}[t]
+  \epsscale{0.75}
+  \plotone{fig/ifront_dt}
+  \caption{\label{fig:dt_dep1} Growth of the ionization front radius,
+    compared to the analytical radius, in Test 1 with varying
+    radiative transfer timesteps.  The $dn_{\rm H}/dt$ and $dI/dt$
+    based timesteps provide the best accuracy, combined with
+    computational efficiency because they take short timesteps when
+    the \ion{H}{2} is expanding rapidly but take long timesteps when
+    the photon gradients are small when $r_{\rm IF}$ is large.  At the
+    final time, all but the $t = 5$ Myr constant timestep produce
+    identical ionization front radii.}
+  \epsscale{1}
+\end{figure}
+\begin{figure}[t]
+  \epsscale{0.75}
+  \plotone{fig/vary_dt}
+  \caption{\label{fig:dt_dep2} Variable timestepping for the methods
+    that limit change in neutral fraction (solid) and specific
+    intensity (dotted).  The horizontal lines show the constant
+    timesteps that were used in the tests.  The crossing time of a
+    mean free path by the ionization front is plotted for reference.}
+  \epsscale{1}
+\end{figure}
+
 The previous three dependencies did not affect the propagation of the
 ionization front greatly.  However in our and others' past experience
-\citep[e.g.][\bf{+others!}]{Petkova09}, the timestep, especially too
-small of one, can drastically affect the ionization front velocity.
-Here we use Test 1 but with $64^3$ resolution to compare different
-timestepping methods --- restricted changes in \ion{H}{2}
-(\S\ref{sec:dt_hi}), constant timesteps (\S\ref{sec:dt_const}), and
-based on incident radiation (\S\ref{sec:dt_tau}).
+\citep[e.g.]{Shapiro04, Mellema06, Petkova09}, the timestep,
+especially too small of one, can drastically underestimate the
+ionization front velocity.  Here we use Test 1 but with $64^3$
+resolution to compare different timestepping methods --- restricted
+changes in \ion{H}{2} ($dn_{\rm H}/dt$ based; \S\ref{sec:dt_hi}),
+constant timesteps (\S\ref{sec:dt_const}), and based on incident
+radiation ($dI/dt$ based; \S\ref{sec:dt_tau}).  The growth of the
+ionization front radius is shown in Figure \ref{fig:dt_dep1}.  Both
+the \ion{H}{2} restricted and incident radiation variable timestepping
+methods agree within a few percent throughout the entire simulation,
+as does the run with constant $dt = 0.1$ Myr timesteps.  With the
+larger constant timesteps, the numerical solution lags behind the
+analytical one, but they converge to an accurate \ion{H}{2} radii at
+late times.  Even $dt = 5$ Myr timestep, which underestimated it by
+35\% at 50 Myr, is within a percent of the analytical solution.
+
+The larger constant timesteps deviate from these more accurate
+solutions at early times because the photon energy gradient is large,
+and thus so is the ionization front velocity.  To understand this, the
+ionization front can be considered static in a given timestep.  Here
+the ionizing radiation can only penetrate into the neutral gas by
+roughly a photon mean path $\lambda_{\rm mfp}$.  Only in the next
+timestep, the ionization front can advance.  If the timestep is larger
+than $\lambda_{\rm mfp} / v_{\rm IF, anyl}$, then the numerical
+solution may fall behind.
+
+The variable timestepping of the $dn_{\rm H}/dt$ and $dI/dt$ methods
+adjust accordingly to the physical situation, as seen in the plot of
+timestep versus time (Figure \ref{fig:dt_dep2}).  They provide high
+accuracy when the source first starts to shine.  At later times, the
+ionization front slows as it approaches the Str\"{o}mgren radius, and
+large timesteps are no longer necessary.  The $dI/dt$ method has a
+similar timestep as the $dn_{\rm H}/dt$ method.  It is larger by a
+factor of $\sim 2$ because of our choice of the safety factor $C_{\rm
+  RT, cfl} = 0.5$.  This causes its calculated radius to be smaller by
+1\% at $t < t_{\rm rec}$, which is still in good agreement with the
+analytical value.
 

### 2010-08-20 ms.tex
Fixed a couple of typos.
Added optically-thin approx. figure of kph.

@@
 neutral and ionized medium to be approximately the mean free path of
-the ionizing radiation.  His seminar work was expanded upon by
+the ionizing radiation.  His seminal work was expanded upon by
 \citet{Spitzer48, Spitzer49, Spitzer54} and \citet{Spitzer50}, who
@@
 calculations.  Conversely these effects may be important when studying
-small-scale, e.g. photo-evaporation.
+the details of small-scale processes, e.g. photo-evaporation.
 
@@
 \subsection{Optically-thin approximation}
+
+\begin{figure}[t]
+  \epsscale{0.6}
+  \plotone{fig/rayopt}
+  \caption{\label{fig:rayopt} Optically-thin approximation to the
+    radiation field with one ray per cell in optically thin regions.
+    The angular artifacts result from the transition to optically
+    thick (white line) at an optical depth $\tau = 0.1$.}
+  \epsscale{1}
+\end{figure}
 

### 2010-08-20 ms.tex
Added description of optically-thin approximation artifacts.

--- 2010-08-19 ms.tex
@@
 optically-thin approximation to the optically-thick regime without
-producing artifacts in the photo-ionization rate \kph.  The artifacts
-exist in cells that intersect the $\tau_{\rm thin} \equiv 0.1$
-surface.  These cells are split into the optically thin and thick
-definitions, and we have not determined a good technique to avoid any
-artifacts.  We use the optically thin problem used in the angular
-resolution test (\S\ref{sec:ang_dep}) to show these artifacts in \kph.
+producing artifacts in the photo-ionization rate \kph.  We use the
+optically thin problem used in the angular resolution test
+(\S\ref{sec:ang_dep}) with $\Phi_c = 5.1$ to show these artifacts in
+\kph~in Figure \ref{fig:rayopt}.  The radiation field strictly follows
+a $1/r^2$ profile until it reaches $\tau_{\rm thin} \equiv 0.1$, which
+is denoted by the white quarter circle in the figure.  At this radius,
+the rays are then split until a sampling of $\Phi_c$ is satisfied.
+Angular spike artifacts beyond this radius arise because of the
+interface between the optically-thin approximation and full ray
+tracing treatment.  They originate in cells that intersect the
+$\tau_{\rm thin}$ surface, which are split into the optically thin and
+thick definitions.  Unfortunately we have not determined a good
+technique to avoid such artifacts.  They occur because of the
+following reason.  When the first ray with $\tau < 0.1$ exits such a
+cell, it applies the optically-thin approximation and marks the cell
+so no other ray from the same source contributes to its \kph~and
+$\Gamma$ field.  However other rays may exit the cell with $\tau >
+0.1$ because the maximum distance between the far cell faces and the
+source is not always $\tau < 0.1$.  Then these rays will split in this
+cell and add to \kph~and become attenuated, reducing its photon
+fluxes.  When the rays continue to the next cell after this
+transition, the photon fluxes are not necessarily equal to each other,
+creating the angular artifacts seen in Figure \ref{fig:rayopt}.  We
+are continuing to formulate a scheme that avoids these artifacts
+because this approximation will be very advantageous in simulations
+with large ionized filling factors.
 

### 2010-08-20 ms.tex
Wrote the summary.

@@
 
+\begin{figure}[t]
+  \epsscale{0.6}
+  \plotone{fig/rayopt}
+  \caption{\label{fig:rayopt} Optically-thin approximation to the
+    radiation field with one ray per cell in optically thin regions.
+    The angular artifacts result from the transition to optically
+    thick (white line) at an optical depth $\tau = 0.1$.}
+  \epsscale{1}
+\end{figure}
+
 In practice, we have found it difficult to transition from this
@@
 
+In this paper, we have presented our implementation of adaptive ray
+tracing \citep{Abel02_RT} and its coupling to the hydrodynamics in the
+cosmology AMR code \enzo, making it a fully functional radiation
+hydrodynamics code.  As this method is photon conserving, accurate
+solutions are possible with coarse spatial resolution.  A new
+geometric correction factor to ray tracing on a Cartesian grid was
+described, and it is general to any implementation.  We have
+exhaustively tested the code to problems with known analytical
+solutions and the problems presented in the RT06 and RT09 radiative
+transfer comparison papers.  Additionally we have tested our code with
+more dynamical problems---champange flows, Rayleigh-Taylor
+instabilities, photo-evaporation of a blastwave, beamed radiation, a
+time-varying source, and an \ion{H}{2} region with MHD---to
+demonstrate the flexibility and fidelity of Enzo+Moray.  Because
+production simulations may not have the resolution afforded in these
+test problems, we have tested the dependence on spatial, angular,
+frequency, and temporal resolution.  It provides accurate solutions
+even at low resolution, except for the large constant timesteps.
+However, we have described two methods to determine the radiative
+transfer timestep that are based on the variations in specific
+intensity or changes in neutral fraction inside the ionization front.
+Both methods give very accurate results and provide the largest
+timestep to obtain an accurate solution, ultimately leading to higher
+computational efficiency.  On the same topic, we have described a
+method to calculate the radiation field in the optically-thin limit
+with ray tracing.
+
+Being a ray tracing code, it scales with the number of radiation
+sources, albeit lessened with ray merging; nevertheless, it scales
+well to O($10^3$) processors for problems with $\sim10^9$
+computational cells and $\sim10^4$ sources, such as reionization
+calculations.  We have also shown that the code shows good strong
+scaling in AMR calculations, given a large enough problem.  The
+combination of the AMR and adaptive ray tracing allows for
+high-resolution and high-dynamical range problems, e.g. molecular
+cloud resolving galaxy formation simulations and \ion{H}{2} regions of
+Population III stars.  Furthermore, we have included Lyman-Werner
+absorption, secondary ionizations from X-ray radiation, Compton
+heating from photon scattering, and radiation pressure, into the code,
+which extends the reach of Enzo+Moray to study AGN feedback, stellar
+winds, and local star formation.  Coupling the radiative transfer with
+MHD further broadens the applicability of our code.  The full
+implementation is included in the latest public version of
+\enzo\footnote{http://lca.ucsd.edu/enzo}, providing the community with
+a full-featured radiation hydrodynamics AMR code.
+
 \acknowledgments

### 2010-08-21 ms.tex
Cleared some ambiguities in the constant dt section.

@@
 shock front progress jointly at the sound speed of the ionized region.
-A moderately large (\textbf{show how large!}) timestep can accurately
-follow its evolution.  However after the I-front passes a critical
-radius \citep[show this!][]{Franco90}, the I-front detaches from the
-shock front and accelerates.  The I-front velocities in these two
-stages differ up to a factor of $\sim100$ (\textbf{check this!}).
-Although the solution is accurate with a large timestep in the D-type
-phase, the I-front may lag behind because of the constant timestep.
-After a few recombination times, the numerical solution evenutally
-approaches the analytical solution.  If such a simulation focuses on
-the density core expansion and any small scale structures, such as
-cometary structures and photo-dissociation regions, one can cautiously
-sacrifice temporal accuracy at large scales for computational savings.
+A moderately large (0.1 Myr) timestep can accurately follow its
+evolution.  However after the I-front passes a critical radius
+\citep{Franco90}, the I-front detaches from the shock front,
+accelerates, and transitions back to an R-type front.  This can also
+occur in champange flows when the ionization front passes a density
+discontinuity.  The I-front velocities in these two stages differ up
+to a factor of $\sim10$.  Although the solution is accurate with a
+large timestep in the D-type phase, the I-front may lag behind because
+of the constant timestep.  After a few recombination times, the
+numerical solution evenutally approaches the analytical solution.  If
+such a simulation focuses on the density core expansion and any small
+scale structures, such as cometary structures and photo-dissociation
+regions, one can cautiously sacrifice temporal accuracy at large
+scales for computational savings.
 

### 2010-08-31 ms.tex
Adding results and figures for Test 10 and Test 12 (hydro).  Adding weak scaling figure and description.

@@
   feedback.  Inaccuracies can arise from large timesteps and poor
-  sampling, therefore we devised an adaptive timestepping scheme and a
+  sampling, therefore we devised an adaptive time-stepping scheme and a
   fast approximation of the optically-thin radiation field with
@@
 for a radiation source ionizing a static uniform neutral medium, where
-recombinations balnace photo-ionizations.  He derived a radius of an
+recombinations balance photo-ionizations.  He derived a radius of an
 \ion{H}{2} region,
@@
 \citep[e.g.][]{Bodenheimer79, Sandford82, Yorke83}.  One topic that was
-studied extensively were champange flows.  Here the source is embedded
+studied extensively were champagne flows.  Here the source is embedded
 in an overdense region, and the \ion{H}{2} region escapes from this
@@
 \item Ray tracing---Radiation can be propagated along rays that extend
-  through the compuational grid \citep[e.g.][]{Razoumov99, Abel99_RT,
+  through the computational grid \citep[e.g.][]{Razoumov99, Abel99_RT,
     Ciardi01, Sokasian01, Whalen06, Rijkhorst06, Mellema06, Alvarez06,
@@
 transfer equation been coupled to the hydrodynamics in
-three-dimensions.  In the second comparision paper \citep[hereafter
+three-dimensions.  In the second comparison paper \citep[hereafter
   RT09]{Iliev09}, results from these radiation hydrodynamics codes
@@
 
-Radiation trnasport is a well-studied topic, and we begin by
+Radiation transport is a well-studied topic, and we begin by
 describing our approach in solving the radiative transfer equation,
@@
 I_\nu/\partial \mathbf{x}$.  To determine the importance of the third
-term, we evaluate the ratio of the third term ot the second term.
+term, we evaluate the ratio of the third term to the second term.
 This is $HL/c$, where $L$ is the simulation box length.  If this ratio
@@
 radiation (e.g. stars, quasars) that emit radial rays that are
-propaged along the direction $\hat{n}$.  Next we describe this
+propagated along the direction $\hat{n}$.  Next we describe this
 discretization and its contribution to the radiation field.
@@
 where $\alpha_B = 2.59 \times 10^{-13} \mathrm{cm}^3 \mathrm{s}^{-1}$
-is the recombination coefficent at 10$^4$ K in the Case B on-the-spot
+is the recombination coefficient at 10$^4$ K in the Case B on-the-spot
 approximation, in which all recombinations are locally reabsorbed,
@@
 Other radiative processes can also be important in some situations,
-such as attentuation of radiation in the Lyman-Werner bands, secondary
+such as attenuation of radiation in the Lyman-Werner bands, secondary
 ionizations from X-ray radiation, Compton heating of from scattered
@@
 Molecular hydrogen can absorb photons in the Lyman-Werner bands that
-are composed of 76 absoprtion lines ranging from 10.2 to 13.6 eV.
+are composed of 76 absorption lines ranging from 10.2 to 13.6 eV.
 Each of these spectral lines can be modelled with a typical
@@
 effective cross-section of \hh~\citep{Abel97}.  To account for any
-absorption in each photon package, we attentuate the photon number
+absorption in each photon package, we attenuate the photon number
 flux by
@@
 associated with a single ray, and assume the flux is constant across
-$\Omega_{\rm ray}$.  There exists a discrenpancy between the geometry
+$\Omega_{\rm ray}$.  There exists a discrepancy between the geometry
 cell face and HEALPix pixel when the pixel does not cover the entire
@@
 When the medium is optically thin to the radiation, radiation is only
-attentuated by geometric dilution in the local approximation to
+attenuated by geometric dilution in the local approximation to
 Eq. (\ref{eqn:rteqn}), i.e. the inverse square law.  We can minimize
@@
 handling the ``photon packages'' that are traced along the adaptive
-rays.  We use the terms photon packages and rays interchangably.  Next
+rays.  We use the terms photon packages and rays interchangeably.  Next
 we focus on the details of the radiation hydrodynamics and then the
-importance of correct timestepping.  Last we give our parallelization
+importance of correct time-stepping.  Last we give our parallelization
 strategy of tracing rays through an AMR hierarchy.  This
@@
 cell or the child pointer that exists under the current cell.  This
-provides a significant speedup when compared to a simple comparision
+provides a significant speedup when compared to a simple comparison
 of a photon package position and all of the child grid boundaries.
@@
 In practice, we have found that one energy group per photon type is
-sufficent to match expected analytical tests.  For example when
+sufficient to match expected analytical tests.  For example when
 modeling Population III stellar radiation \citep[e.g.][for hydrogen
@@
 such that it can react to the radiative heating, i.e. sound-crossing
-time.  The frequency of its evaulation will be discussed in the next
+time.  The frequency of its evaluation will be discussed in the next
 section.
@@
 timestep, the solution is guaranteed to avoid any inaccuracies
-(ignoring any systematic ones) due to timestepping, but the solver
-must be called many times.  These frequent calls may be unneccesary
+(ignoring any systematic ones) due to time-stepping, but the solver
+must be called many times.  These frequent calls may be unnecessary
 because the same solution may be accomplished with a longer timestep.
@@
 
-\subsubsection{Time averaged quantites within a timestep}
+\subsubsection{Time averaged quantities within a timestep}
 
@@
 If the timestep is too large, the ionization front will propagate too
-slowly, but it evenutually approaches the correct radius at late times
+slowly, but it eventually approaches the correct radius at late times
 (see \S\ref{sec:dt_dep}).  This does not prevent one from using a
@@
 accelerates, and transitions back to an R-type front.  This can also
-occur in champange flows when the ionization front passes a density
+occur in champagne flows when the ionization front passes a density
 discontinuity.  The I-front velocities in these two stages differ up
@@
 of the constant timestep.  After a few recombination times, the
-numerical solution evenutally approaches the analytical solution.  If
+numerical solution eventually approaches the analytical solution.  If
 such a simulation focuses on the density core expansion and any small
@@
 
-\step{2} Pack the photon packages into a contigious array for MPI
+\step{2} Pack the photon packages into a contiguous array for MPI
 communication while the messages from Step 1 completes.
@@
 conditions, (2) the same test with an evolving temperature field, (3)
-shadowing created by a dense, opticlally thick clump, and (4) multiple
+shadowing created by a dense, optically thick clump, and (4) multiple
 \ion{H}{2} regions in a cosmological density field.  In all of the
@@
 ionization front radius exceeds $R_s$ by a few percent for most of the
-calcuation.  This difference happens because the analytical solution
+calculation.  This difference happens because the analytical solution
 (Eq. \ref{eqn:rstr}) assumes the \ion{H}{2} region has a constant
@@
 threshold in Test 1.  Thus the ionization front is thicker as the
-photons can penerate deeper into the neutral medium.  Here we use 4
+photons can penetrate deeper into the neutral medium.  Here we use 4
 energy groups with the following mean energies and relative
@@
 where this ratio varies between 1 and 1.1, and the early evolution of
-$r_{\rm IF}$ is underpredicted by almost all of the codes.  If we use
+$r_{\rm IF}$ is under-predicted by almost all of the codes.  If we use
 one energy group with the mean energy (29.6 eV) of a $T=10^5$ K
@@
 expand on this test suite to include more complex situations, such as
-a Rayleigh-Taylor problem illuminated by a radiation source, champange
-flows, collimated radiation, an irradidated blast wave, and an
+a Rayleigh-Taylor problem illuminated by a radiation source, champagne
+flows, collimated radiation, an irradiated blast wave, and an
 \ion{H}{2} region in a rotating sphere.  For the \citeauthor{Iliev09}
@@
 The simulation setup is similar to Test 2 with the exception of the
-domain size $L = 15$ kpc.  Here pressure equilbrium occurs at $r_f =
+domain size $L = 15$ kpc.  Here pressure equilibrium occurs at $r_f =
 185$ kpc, which is not captured by this test.  However more
@@
 times, it provides a good match to the $t^{4/7}$ growth at late times.
-With the $x_e = 0.5$ criteron for the ionization front, the radius is
+With the $x_e = 0.5$ criterion for the ionization front, the radius is
 always underestimated by $\sim20\%$.  This behavior was also seen in
@@
 temperature, pressure, and ionized fraction.  The initial \ion{H}{2}
-region is overpressurized and creates an outward shock wave.  The
-high-energy photons can penerate through the shock and partially
+region is over-pressurized and creates an outward shock wave.  The
+high-energy photons can penetrate through the shock and partially
 ionizes and heats the exterior gas, clearly seen in the profiles.  As
@@
 a static density field.  The ionization front first proceeds as a very
-fast R-type front, then it slows to a D-type front when it encounts
+fast R-type front, then it slows to a D-type front when it encounters
 the dense clump.  As the clump is gradually photoionized and heated,
@@
 propagated through the left-most 500 pc of the clump.  This heated gas
-is now overpressurized, as seen in the pressure plot in Figure
+is now over-pressurized, as seen in the pressure plot in Figure
 \ref{fig:test7_1}, and then expands into the ambient medium.  This
@@
 
-\subsection{Test 8. Champange flow from a dense clump}
+\subsection{Test 8. Champagne flow from a dense clump}
 
@@
   \plotone{fig/test8_slices}
-  \caption{\label{fig:test8_1} Test 8. (Champange flow from a dense
+  \caption{\label{fig:test8_1} Test 8. (Champagne flow from a dense
     clump).  Slices of density through the initial clump center in the
@@
 
-Radiation-driven outflows from overdensities, known as champange
+Radiation-driven outflows from overdensities, known as champagne
 flows, is a long studied problem \citep[e.g.][\S3.3]{Yorke86}.  We set
@@
 contained within the overdensity.  In the x-z plane, there are density
-perturbuations only above a latitude of 45 degrees.  We believe that
+perturbations only above a latitude of 45 degrees.  We believe that
 these are caused by the mismatch between HEALPix pixels and the
@@
 nearly constant velocity, as seen in Test 6.  Thus these perturbations
-are not as vunerable to Rayleigh-Taylor instabilities at this point.
+are not as vulnerable to Rayleigh-Taylor instabilities at this point.
 The ambient medium and shock are always optically thick, even in the
@@
 
-We set the accleration field $g_z = 0.1$ and the adiabatic index
+We set the acceleration field $g_z = 0.1$ and the adiabatic index
 $\gamma = 1.4$.  We use a domain size of $(L_x, L_y, L_z) = (0.5, 0.5,
-1.5)$ with a resolution of (64, 64, 192).  For hydrostatic equilbrium,
+1.5)$ with a resolution of (64, 64, 192).  For hydrostatic equilibrium,
 we set $P = P_0 - g \rho(z) z$ with $P_0 = 2.5$.  In order to consider
@@
 The optically-thin case is set up similarly but with three
-changes---(1) a density constrast of 10, (2) a luminosity of $10^{43}$
+changes---(1) a density contrast of 10, (2) a luminosity of $10^{43}$
 ph s$^{-1}$, and (3) the source is born at 6.5 Myr.  The time units
@@
 instability as strongly.  The radiation source provides further
-buoyance in the already $T=10^4$ K gas.  The gas first to be ionized
+buoyancy in the already $T=10^4$ K gas.  The gas first to be ionized
 and photo-evaporates is the outer regions of the instability.  The
@@
 
+\begin{figure}[t]
+  \epsscale{1}
+  \plotone{fig/test10_slices}
+  \caption{\label{fig:test10} Test 10 (Photo-evaporation of a
+    blastwave).  Slices of density (top) and temperature (bottom) at
+    $t = 2.5, 3, 5, 7.5$ Myr in the $x-z$ plane.  As the R-type
+    ionization front propagates through the blastwave center,
+    instabilities grow from the slightly inhomogeneous hot and rarefied
+    medium.  Note that the dense shell of the blastwave also creates
+    dense inward fingers in the ionization front shock.}
+  \epsscale{1}
+\end{figure}
+
 A supernova blastwave being irradiated by a nearby star is a likely
-occurence in massive-star forming regions.  In this test, we set up an
-idealized test that mimics this scenario.  The problem is similar to
-Test 5 with two changes --- (1) the domain has been decreased to
-$L_{\rm box} = 1.5$ kpc; and (2) a blastwave is initialized in the
-center of the domain.  We use 3 levels of AMR with a base grid of
-64$^3$, which is refined if the density slope is greater than 0.4.
-The blastwave is initially in the free expansion phase with a total
-energy of $10^{50}$ erg and total mass of $100 \Ms$, corresponding to
-$E = 315$ eV per particle or $E/k_b = 3.66 \times 10^6$ K.  The
-blastwave is setup with a linearly increasing velocity profile
-according to \citet{Truelove99} with $v_{\rm max} = 130$ km s$^{-1}$
-and a radius of $L_{\rm box}/50 = 30$ pc.  The blastwave initially has
-a uniform density of $\rho_0 = 0.06 \cubecm$.  The initial kinetic
-energy is converted into thermal energy as the shock propagates away,
-and the blastwave transitions into the Sedov-Taylor phase at $r \sim
-100$ pc and $t \sim 225$ kyr after it has accumulated an equal amount
-of ambient material into the shock.  The simulation is run for 25 Myr.
+occurrence in massive-star forming regions.  In this test, we set up an
+idealized test that mimics this scenario.  The ambient medium has a
+density $\rho_0 = 0.1~\cubecm$ and temperature $T_0 = 10$ K.  The
+domain size is 1 kpc.  We use 2 levels of AMR with a base grid of
+64$^3$ that is refined if the density or total energy slope is greater
+than 0.4.  The blastwave is initialized at the beginning of the
+Sedov-Taylor phase when the mass of the swept-up material equals the
+ejected material.  It has a radius of 21.5 pc, a total energy of
+$10^{50}$ erg, and total mass of $100 \Ms$, corresponding to $E = 315$
+eV per particle or $E/k_b = 3.66 \times 10^6$ K.  The radiation source
+is located at the center of the left $x$-boundary and has a luminosity
+of $10^{50}$ erg s$^{-1}$.  We use a $T=10^5$ K blackbody spectrum
+with 2 energy groups (16.0 and 22.8 eV).  The source turns on at 2.5
+Myr at which point the blastwave has a radius of 200 pc.  The
+simulation is run for 7.5 Myr.
+
+Figure \ref{fig:test10} shows the ionization front overtaking and
+disrupting the blastwave.  We show the blastwave before the source is
+born at 2.5 Myr.  The interior is rarefied ($\rho \sim
+10^{-3}~\cubecm$).  It is heated to $T \sim 5 \times 10^5$ K by the
+reverse shock.  At $t = 3$ Myr, the ionization front is still R-type,
+and it ionizes the blastwave's dense shell.  Because the interior is
+ionized and diffuse, the ionization front rapidly propagates through
+it until it reaches the opposite shell surface.  Shortly afterward,
+the ionization front transitions from R-type to D-type at a radius of
+0.5 kpc, seen in the formation of a shock in the 5 Myr density panel.
+This transition occurs by the construction of the problem not by the
+interaction with the blastwave.  The surfaces of the blastwave that
+are perpendicular to the ionization front have the highest column
+density and thus are last to be fully ionized.  The pressure forces
+from warm ambient medium and blastwave interior compress these
+surfaces, photo-evaporating them in the process, similar to Test 7.
+They survive until the final time $t = 7.5$ Myr.  As the R-type
+ionization front interacts with the blastwave interior, the density
+perturbations create ionization front instabilities
+\citep{Whalen08_Instab} that are seen on the \ion{H}{2} region surface
+at the coordinate $z=0.5$.  Behind the ionization front, the dense
+shell of the blastwave is photo-evaporated, and a smooth overdensity
+is left in the initial blastwave center.
 
@@
     drives shocks transversely into the overdense sphere and creates
-    polar champange flows.  The ambient medium is heated to $T \sim 3
+    polar champagne flows.  The ambient medium is heated to $T \sim 3
     \times 10^4$ K as the ionization front passes the
@@
 Some astrophysical systems produce collimated radiation either
-intrinisically by relavistic beaming or by an optically-thick torus
+intrinsically by relativistic beaming or by an optically-thick torus
 absorbing radiation in the equatorial plane.  The latter case would be
@@
 overdensities on the \ion{H}{2} transverse surface.  When it breaks
-out of the overdensity, it creates a champange flow, where the
+out of the overdensity, it creates a champagne flow, where the
 ionization front transitions back to a weak R-type front.  The cloud
@@
 through the clump, eventually creating a disk-like structure at the
-final time.  The polar champange flows proceed to flow outwards,
+final time.  The polar champagne flows proceed to flow outwards,
 creating a density shell with a diffuse ($10^{-28}$ \cubecm) and warm
@@
 
+\begin{figure}[t]
+  \epsscale{0.8}
+  \plotone{fig/test12_profiles}
+  \caption{\label{fig:test12_profiles} Test 12 (Time variations of the
+    source luminosity).  Radial profiles of (clockwise from upper
+    left) density, temperature, pressure, and ionized fraction at $t =
+    50, 100, 150, 200, 250$ Myr.  In this problem, the time variations
+    in the source have little effect on the overall \ion{H}{2} region
+    expansion.  Inside the ionization front at $t = 50$ Myr, there are
+    small density perturbations that are created by the variable
+    source that are later smoothed out over a sound crossing time.}
+  \epsscale{1}
+\end{figure}
+
 Our implementation retains the time derivative of the radiative
@@
 \begin{equation}
-  \label{eqn:test13}
+  \label{eqn:test12}
   L(t) = L_{\rm max} \times \exp[A(t_f/t_0 - 1)]
@@
 is the duty cycle, and $A=4$ controls the width of the radiation
-pulse.  To illustrate the effects of source varability, we remove any
+pulse.  To illustrate the effects of source variability, we remove any
 dependence on the medium by considering an optically-thin uniform
@@
 repeating Test 5.  We set the peak luminosity $L_{\rm max} = 2 \times
-10^{49}$ erg s$^{-1}$ that is a factor of 4 more luminous than Test
-5, so the average luminosity is $\sim 5 \times 10^{48}$ erg s$^{-1}$.
+10^{49}$ erg s$^{-1}$ that is a factor of 4 more luminous than Test 5,
+so the average luminosity is $\sim 5 \times 10^{48}$ erg s$^{-1}$.
+The spectrum is mono-chromatic with an energy of 29.6 eV.  We set the
+variation timescale $t_f = cL_{\rm box}/3 = 16.3$ kyr and use a
+constant radiative transfer timestep $t_P = t_f/4 = 4.07$ kyr.  The
+simulation is run for 200 Myr.  We show the radial profiles of
+density, temperature, ionized fraction, and pressure in Figure
+\ref{fig:test12_profiles}.  The variable source has little effect on
+the overall growth of the \ion{H}{2} region.  It has the approximately
+the same radius as Test 5 at $t = 200$ Myr when run with a
+mono-chromatic spectrum (see \S\ref{sec:nu_dep}).  At early times, the
+variable source creates density perturbations with an average size of
+500 pc inside the ionized region, seen in the $t = 50$ Myr profiles.
+They do not create any instabilities and are smoothed out over its
+sound crossing time of $\sim 50$ Myr.
 
@@
 
-Another prevelant physical component in astrophysics is a magnetic
+Another prevalent physical component in astrophysics is a magnetic
 field.  We utilize the new magnetohydrodynamics (MHD) framework
@@
 spherical to oblate as it is magnetically confined in directions
-perperdicular to the magnetic field.  This occurs at $t > 0.5$ Myr
+perpendicular to the magnetic field.  This occurs at $t > 0.5$ Myr
 because the magnetic pressure exceeds the thermal pressure, and the
@@
     rates for different ray-to-cell samplings $\Phi_c$.  The colormap
-    only spans a factor of 3 to enhance the contrast.  In comparision,
+    only spans a factor of 3 to enhance the contrast.  In comparison,
     the photo-ionization rate actually spans 4 orders of magnitude in
@@
 \subsection{Frequency resolution}
+\label{sec:nu_dep}
 
@@
 a marginally higher density in the outer shock and lower ionized
-fractions and tempeatures in the ambient medium.  In effect, a
+fractions and temperatures in the ambient medium.  In effect, a
 mono-chromatic spectrum can be sufficient if the problem focuses on
@@
   \plotone{fig/vary_dt}
-  \caption{\label{fig:dt_dep2} Variable timestepping for the methods
+  \caption{\label{fig:dt_dep2} Variable time-stepping for the methods
     that limit change in neutral fraction (solid) and specific
@@
 ionization front velocity.  Here we use Test 1 but with $64^3$
-resolution to compare different timestepping methods --- restricted
+resolution to compare different time-stepping methods --- restricted
 changes in \ion{H}{2} ($dn_{\rm H}/dt$ based; \S\ref{sec:dt_hi}),
@@
 ionization front radius is shown in Figure \ref{fig:dt_dep1}.  Both
-the \ion{H}{2} restricted and incident radiation variable timestepping
+the \ion{H}{2} restricted and incident radiation variable time-stepping
 methods agree within a few percent throughout the entire simulation,
@@
 
-The variable timestepping of the $dn_{\rm H}/dt$ and $dI/dt$ methods
+The variable time-stepping of the $dn_{\rm H}/dt$ and $dI/dt$ methods
 adjust accordingly to the physical situation, as seen in the plot of
@@
     shell artifacts.  In the x-z plane, it reduces the severity of a
-    non-spherical artifact delinated at a 45 degree angle, where the
+    non-spherical artifact delineated at a 45 degree angle, where the
     HEALPix scheme switches from polar to equatorial type pixels.}
@@
 x-z plane without the correction, there is a non-spherical artifact
-delinated at a 45 degree angle.  In the lower region, the rays are
-assoicated with equatorial HEALPix pixels, and in the upper region,
+delineated at a 45 degree angle.  In the lower region, the rays are
+associated with equatorial HEALPix pixels, and in the upper region,
 they are polar HEALPix pixels.  This artifact is not seen in the x-y
@@
     Radial profiles of (clockwise from top left) density, temperature,
-    radial velocity, and neutral fraction.  Time units in the legned
+    radial velocity, and neutral fraction.  Time units in the legend
     are in kyr.  (b) Radial profiles with radiation pressure.  The
@@
     velocities than without radiation pressure.  Afterwards the
-    central region is underpressurized, and the gas infalls toward the
+    central region is under-pressurized, and the gas infalls toward the
     center, as seen at t = 60 kyr.  Then the radiation pressure
-    continues to force the gas outwards, increasing gas velocites up
+    continues to force the gas outwards, increasing gas velocities up
     to 50 km/s.}
@@
 = 29.6$ eV.  The grid is adaptively refined on overdensity with the
-same criteron as Test 8.  The simulation is run for 140 kyr.
+same criterion as Test 8.  The simulation is run for 140 kyr.
 
@@
 
+\begin{figure}[t]
+  \epsscale{0.8}
+  \plotone{fig/weak_v1.eps}
+  \caption{\label{fig:weak} Weak scaling test with one $64^3$ block
+    per process.  Each block has one source and is set up similar to
+    the radiation hydrodynamics Test 5.  Above 8 processes, all parts
+    of the code exhibit good weak scaling except for the
+    inter-processor ray communication.  The radiation module timing
+    include the ray tracing, communication, chemistry and energy
+    solver, and all other overheads associated with the radiation
+    transport.  Cache locality of the data causes the decrease in
+    performance from 1 to 8 processes.}
+  \epsscale{1}
+\end{figure}
+
 Weak scaling tests demonstrates how the code scales with the number of
 processors with a constant amount of work per processor.  Here we
-construct a test problem with a $64^3$ block per processor.  The grid
-is not adaptively refined.  The physical setup of the problem is the
-same as Test 5 with a uniform density $\rho = 10^{-3} \cubecm$ and
-initial temperature $T = 100$ K.  Each block has the same size of 15
-kpc as Test 5.  At the center of each grid, there exists a radiation
-source with a luminosity $L = 5 \times 10^{48}$ ph s$^{-1}$ and a 17
-eV mono-chromatic spectrum.  The problem is run for 100 Myr.  We run
-this test with $N_p = 2^n$ processors with $n = [0,1 \dots 11,12]$.
-The domain has $(N_x, N_y, N_z)$ blocks that is determined with the
-MPI routine \texttt{MPI\_Dims\_create}.  For example with $n = 7$, the
-problem is decomposed into $(N_x, N_y, N_z) = (4,4,8)$ blocks,
-producing a $256 \times 256 \times 512$ grid.
+construct a test problem with a $64^3$ block per core.  The grid is
+not adaptively refined.  The physical setup of the problem is the same
+as Test 5 with a uniform density $\rho = 10^{-3} \cubecm$ and initial
+temperature $T = 100$ K.  Each block has the same size of 15 kpc as
+Test 5.  At the center of each grid, there exists a radiation source
+with a luminosity $L = 5 \times 10^{48}$ ph s$^{-1}$ and a 17 eV
+mono-chromatic spectrum.  The problem is run for 250 Myr.  We run this
+test with $N_p = 2^n$ cores with $n = [0,1 \dots 10,11]$.  The domain
+has $(N_x, N_y, N_z)$ blocks that is determined with the MPI routine
+\texttt{MPI\_Dims\_create}.  For example with $n = 7$, the problem is
+decomposed into $(N_x, N_y, N_z) = (4,4,8)$ blocks, producing a $256
+\times 256 \times 512$ grid.  We have run these on the original
+(Harpertown CPUs) nodes of the NASA NAS machine, Pleiades, with 8
+cores per node.  Figure \ref{fig:weak} shows the performance timings
+of various parts of the code.  From one to two cores, the total time
+only increases by $\sim$1\% due to the overhead associated with the
+inter-processor message passing.  From two to eight cores, the
+performance decreases in the hydrodynamics solver, chemistry and
+energy solver, and obtaining the hydrodynamic boundary conditions
+because of cache locality problems of the data being passed to the
+CPU.  This occurs because of the CPU architecture, specifically the L1
+cache and core connectivity.  We see less of a penalty in newer
+processors, e.g. Intel Nehalam and Westmere CPUs.  Unfortunately there
+exists a $N_p^{1.5}$ dependence in the ray communication routines.  It
+becomes the dominant process above 512 processes.  We are actively
+pursing a solution to this scaling problem.  The other parts of the
+code exhibit excellent weak scaling.  Overall it scales well to 512
+processes, and we plan to enhance the weak scalability of Enzo+Moray
+in the near future to larger processor counts.
 
@@
 processors for the same problem.  The overhead associated with the
-structured AMR framework in \enzo~can limit the strong scalibility.
+structured AMR framework in \enzo~can limit the strong scalability.
 One key property of strong scaling is that each processor must have
@@
 measure the time spent on the hydrodynamics, non-equilibrium
-chemistry, the rebuilding of the AMR hierarhcy, and ray tracing in a
-single level-0 timestep, lasting 5 Myr, at $z=8$.  There are ??? point
-sources in this calculation at this redshift.
+chemistry, the rebuilding of the AMR hierarchy, and ray tracing in a
+single level-0 timestep, lasting 5 Myr, at $z=9.5$.  There are ??? point
+sources in this calculation at this redshift.  The ionized volume
+fraction is ???.
 
@@
 transfer comparison papers.  Additionally we have tested our code with
-more dynamical problems---champange flows, Rayleigh-Taylor
+more dynamical problems---champagne flows, Rayleigh-Taylor
 instabilities, photo-evaporation of a blastwave, beamed radiation, a
@@
 
-\clearpage
+%\clearpage
 %\input biblio.tex

### 2010-09-01 ms.tex
Added acknowledgments.  Added Whalen08_Instab to bib.

@@
 
-J.H.W. is supported by the Hubble Fellowship etc.  The majority of the
-analysis and plots were done with \texttt{yt} \citep{yt}.
+Support for this work was provided by NASA through Hubble Fellowship
+grant \#120-6370 awarded by the Space Telescope Science Institute,
+which is operated by the Association of Universities for Research in
+Astronomy, Inc., for NASA, under contract NAS 5-26555.  J.K. was
+supported by the William R. and Sara Hart Kimball Stanford Graduate
+Fellowship.  Computational resources were provided by NASA/NCCS award
+SMD-09-1439.  The majority of the analysis and plots were done with
+\texttt{yt} \citep{yt}.
 

### 2010-09-08 ms.tex
Finished strong scaling section and added figure.  Need to add results without ray merging.

@@
 \subsection{Parallelization Strategy}
+\label{sec:parallel}
 
@@
 
+\begin{figure}[t]
+  \epsscale{0.8}
+  \plotone{fig/strong_v1.eps}
+  \caption{\label{fig:strong} Strong scaling test with a $256^3$ AMR
+    calculation of cosmological reionization.  The error bars
+    represent the minimum and maximum time spent on a single core and
+    measures load balancing.  The hydrodynamics and non-equilibrium
+    chemistry solvers scale well.  Unfortunately the communication of
+    rays does not scale in this problem, where as the ray tracing
+    scales relatively well.}
+  \epsscale{1}
+\end{figure}
+
 Strong scaling tests shows how the problem scales with the number of
@@
 Here we use a small-box reionization calculation with $L_{\rm box} =
-3$ Mpc/h, a resolution of $256^3$, and 6 levels of refinement.  We
+3$ Mpc/h, a resolution of $256^3$, and six levels of refinement.  We
 measure the time spent on the hydrodynamics, non-equilibrium
-chemistry, the rebuilding of the AMR hierarchy, and ray tracing in a
-single level-0 timestep, lasting 5 Myr, at $z=9.5$.  There are ??? point
-sources in this calculation at this redshift.  The ionized volume
-fraction is ???.
+chemistry, ray tracing, and radiation transport communication in a
+timestep lasting 1 Myr, at $z=10$.  There are nine radiative transfer
+timesteps in this period.  The box has 675 point sources, ??? AMR
+grids, and ??? computational cells in this calculation at this
+redshift.  In the first radiative transfer timestep, ??? and ??? ray
+segments are traced with and without ray merging.  The ionized volume
+fraction is ???.  The calculations are performed on the Nehalam nodes
+on Pleiades on 2$^n$ cores, where $n = [2,...,8]$.
+
+Figure \ref{fig:strong} shows the strong scaling results of this
+calculation.  The hydrodynamics and non-equilbrium chemistry routines
+scale very well in this range because they depend on local phenomena.
+Note that the dominant process is the radiation transport instead of
+the hydrodynamics when compared to the weak scaling tests.  The error
+bars in the figure represent the deviations across all cores, and it
+shows that load balancing becomes an issue at 128 and 256 cores.  This
+is an even larger problem for the ray tracing because the grids that
+host multiple radiation sources will have significantly more work than
+a distant grid.  For example if a few central grids host several point
+sources, the exterior grids must wait until those grids are finished
+ray tracing in order to receive the rays.  This idle time constitutes
+the majority of the time spent in the ray communication routines
+despite our efforts (see \S\ref{sec:parallel}) to minimize idle time.
+For this reason, the communication of rays does not scale in this
+problem.  One solution is to split the AMR grids into smaller blocks
+based on the ray tracing work.  This could impact the performance of
+the rest of Enzo by increasing the number of boundaries and thus
+communication.  Nevertheless in simulations that are dominated by
+radiation transport, it will be advantageous to construct such a
+scheme to increase the feasbility of running larger problems with the
+continually increasing computational resources.
 

### 2010-09-08 ms.tex
Offset error bars in strong scaling figure.  Added a few sentences to the section.

@@
     represent the minimum and maximum time spent on a single core and
-    measures load balancing.  The hydrodynamics and non-equilibrium
-    chemistry solvers scale well.  Unfortunately the communication of
-    rays does not scale in this problem, where as the ray tracing
-    scales relatively well.}
+    measures load balancing.  Each point has been slightly offset to
+    make the error bars distinguishable.  The hydrodynamics and
+    non-equilibrium chemistry solvers scale well.  Unfortunately the
+    communication of rays does not scale in this problem, where as the
+    ray tracing scales relatively well.}
   \epsscale{1}
@@
 sufficient work to compute, compared to the communication involved.
-Here we use a small-box reionization calculation with $L_{\rm box} =
-3$ Mpc/h, a resolution of $256^3$, and six levels of refinement.  We
-measure the time spent on the hydrodynamics, non-equilibrium
-chemistry, ray tracing, and radiation transport communication in a
-timestep lasting 1 Myr, at $z=10$.  There are nine radiative transfer
-timesteps in this period.  The box has 675 point sources, ??? AMR
-grids, and ??? computational cells in this calculation at this
-redshift.  In the first radiative transfer timestep, ??? and ??? ray
-segments are traced with and without ray merging.  The ionized volume
-fraction is ???.  The calculations are performed on the Nehalam nodes
-on Pleiades on 2$^n$ cores, where $n = [2,...,8]$.
+In our experience, non-AMR calculations exhibit much better strong
+scaling than AMR ones because of reduced inter-processor
+communication.  We use an AMR simulation to demonstrate the scability
+of Enzo+Moray in a demanding, real-world calculation.  Here we use a
+small-box reionization calculation with $L_{\rm box} = 3$ Mpc/h, a
+resolution of $256^3$, and six levels of refinement.  We measure the
+time spent on the hydrodynamics, non-equilibrium chemistry, ray
+tracing, and radiation transport communication in a timestep lasting 1
+Myr, at $z=10$.  There are nine radiative transfer timesteps in this
+period.  The box has 675 point sources, ??? AMR grids, and ???
+computational cells in this calculation at this redshift.  In the
+first radiative transfer timestep, ??? and ??? ray segments are traced
+with and without ray merging.  The ionized volume fraction is ???.
+The calculations are performed on the Nehalam nodes on Pleiades on
+2$^n$ cores, where $n = [2,...,8]$.
 

### 2010-09-11 ms.tex
Changing to emulateapj
Updated strong scaling figure.  Included simulation stats for strong scaling.

@@
-%\documentclass[apj,onecolumn]{emulateapj}
-\documentclass[12pt,preprint]{aastex}
+\documentclass[apj,onecolumn]{emulateapj}
+%\documentclass[12pt,preprint]{aastex}
 
@@
 \begin{figure}[t]
+  \epsscale{1.1}
   \plotone{fig/RTalgorithm.eps}
@@
     remainder is a typical ray tracing method.}
+  \epsscale{1}
 \end{figure}
@@
 \begin{figure}[t]
+  \epsscale{0.85}
   \plotone{fig/test3_clump.eps}
@@
     (top) and temperature (bottom) of the overdense clump.}
+  \epsscale{1}
 \end{figure}
@@
 \begin{figure}[t]
-  \epsscale{0.75}
+  \epsscale{0.8}
   \plotone{fig/test5_ifront}
@@
 \begin{figure}[t]
-  \epsscale{0.75}
+  \epsscale{0.8}
   \plotone{fig/test6_ifront}
@@
 \begin{figure}[t]
+  \epsscale{0.9}
   \plotone{fig/test7_lines}
@@
     left) density, temperature, pressure, and neutral fraction.}
+  \epsscale{1}
 \end{figure}
@@
 \begin{figure}[t]
-  \epsscale{0.5}
+  \epsscale{0.75}
   \plotone{fig/test9thick_rho}
@@
 \begin{figure}[t]
-  \epsscale{0.5}
+  \epsscale{0.75}
   \plotone{fig/test9thin_rho}
@@
 Myr, at $z=10$.  There are nine radiative transfer timesteps in this
-period.  The box has 675 point sources, ??? AMR grids, and ???
-computational cells in this calculation at this redshift.  In the
-first radiative transfer timestep, ??? and ??? ray segments are traced
-with and without ray merging.  The ionized volume fraction is ???.
-The calculations are performed on the Nehalam nodes on Pleiades on
-2$^n$ cores, where $n = [2,...,8]$.
+period.  The box has 675 point sources, 15,943 AMR grids, and $6.01
+\times 10^7 \approx 392^3$ computational cells in this calculation at
+this redshift.  On average, $4.6 \times 10^8$ ray segments are traced
+each timestep.  The ionized volume fraction is 0.10.  The calculations
+are performed on the Nehalam nodes on Pleiades on 2$^n$ cores, where
+$n = [2,...,9]$.
 
@@
 radiation transport, it will be advantageous to construct such a
-scheme to increase the feasbility of running larger problems with the
-continually increasing computational resources.
+scheme to increase the feasbility of running larger problems.
 

### 2010-09-13 ms.tex
Applied many corrections after two read-throughs.

@@
   scheme, and its parallel implementation into the adaptive mesh
-  refinement (AMR) code, Enzo.  Coupling the solver with the energy
+  refinement (AMR) code, Enzo.  By coupling the solver with the energy
   equation and non-equilibrium chemistry network, our radiation
@@
   feedback.  Inaccuracies can arise from large timesteps and poor
-  sampling, therefore we devised an adaptive time-stepping scheme and a
-  fast approximation of the optically-thin radiation field with
+  sampling, therefore we devised an adaptive time-stepping scheme and
+  a fast approximation of the optically-thin radiation field with
   multiple sources.  We test the method with several radiative
@@
   front through a Rayleigh-Taylor instability, time-varying
-  luminosities, and collimated radiation.  This method linearly scales
-  with the number of point sources and number of grid cells.  To
-  combat this, we use a novel method of merging rays at large radius,
-  using a tree method, which we briefly describe.  Our implementation
-  is scalable to O(10$^3$) processors on distributed and shared memory
-  machines and can include radiation pressure and secondary
-  ionizations from X-ray radiation.  It is included in the newest
-  public release of Enzo.
+  luminosities, and collimated radiation.  The test suite also
+  includes an expanding \ion{H}{2} region in a magnetized medium,
+  utilizing the newly implemented magnetohydrodynamics module in
+  \enzo.  This method linearly scales with the number of point sources
+  and number of grid cells.  To combat this, we use a novel method of
+  merging rays at large radius, using a tree method, which we briefly
+  describe.  Our implementation is scalable to 512 processors on
+  distributed memory machines and can include radiation pressure and
+  secondary ionizations from X-ray radiation.  It is included in the
+  newest public release of Enzo.
 
@@
 travel supersonically with respect to the neutral gas, whereas D-type
-front are subsonic.  Furthermore ``weak'' and ``strong'' R-type fronts
+fronts are subsonic.  Furthermore ``weak'' and ``strong'' R-type fronts
 move supersonically and subsonically with respect to the ionized gas,
@@
   optically thin limit \citep[OTVET;][]{Gnedin01_OTVET, Petkova09},
-  and with an M1 closer relation \citep{Gonzalez07, Aubert08}.  Moment
-  methods have the advantage of being fast, being independent of the
-  number of radiation point sources.  However, they are diffusive and
-  result in incorrect shadows in some situations.
+  and with an M1 closure relation \citep{Gonzalez07, Aubert08}.
+  Moment methods have the advantage of being fast, being independent
+  of the number of radiation point sources.  However, they are
+  diffusive and result in incorrect shadows in some situations.
 \item Ray tracing---Radiation can be propagated along rays that extend
@@
 growth of an \ion{H}{2} region from a 100\Ms~Population III (Pop III)
-star \citep{Abel07}, radiative feedback on the formation of high
-redshift dwarf galaxies \citep{Wise08_Gal}, the early stages of
-reionization from Pop III stars \citep{Wise08_Reion}, ultraviolet
-radiation escape fractions from dwarf galaxies before reionization
-\citep{Wise09}, radiative negative feedback from accreting Pop III
+star \citep{Abel07}, the early stages of reionization from Pop III
+stars \citep{Wise08_Reion}, radiative feedback on the formation of
+high redshift dwarf galaxies \citep{Wise08_Gal}, ultraviolet radiation
+escape fractions from dwarf galaxies before reionization
+\citep{Wise09}, negative radiative feedback from accreting Pop III
 seed black holes \citep{Alvarez09}, and radiative feedback in
@@
 We have structured this paper as follows.  In Section 2, we describe
-the connections between adaptive ray tracing and the radiative
-transfer equation.  Furthermore, we detail how physics other than
-photo-ionization and photo-heated are included.  We then derive a
+the mathematical connections between adaptive ray tracing and the
+radiative transfer equation.  Furthermore, we detail how physics other
+than photo-ionization and photo-heated are included.  We then derive a
 geometric correction factor to any ray tracing method to improve
@@
 dynamical and complex setups to demonstrate the flexibility and high
-fidelity of Enzo+Moray.  Section 6 reports the results from spatial,
+fidelity of Enzo+Moray.  Section 6 gives the results from spatial,
 angular, frequency, and temporal resolution tests.  In Section 7, we
@@
 second term represents the propagation of radiation, where the factor
-$1/a$ accounts for cosmic expansion.  The third term describes both
-the cosmological redshift and dilution of radiation.  On the right
-hand side, the first term considers the absorption coefficient
+$1/\bar{a}$ accounts for cosmic expansion.  The third term describes
+both the cosmological redshift and dilution of radiation.  On the
+right hand side, the first term considers the absorption coefficient
 $\kappa_\nu \equiv \kappa_\nu(\mathbf{x},\nu,t)$, and the second term
@@
 it could be important to consider cosmological redshifting and
-dilution of the radiation, which we will describe later in
-\S\ref{sec:ART}.  Thus equation (\ref{eqn:rteqn}) reduces to the
-non-cosmological form in this local approximation,
+dilution of the radiation.  Thus equation (\ref{eqn:rteqn}) reduces to
+the non-cosmological form in this local approximation,
 %
@@
 Ray tracing is an accurate method to propagate radiation from point
-sources on a computational grid, given that there are rays passing
-through each cell.  Along a ray, the radiative transfer equation reads
+sources on a computational grid, given that there are a sufficient
+number of rays passing through each cell.  Along a ray, the radiative
+transfer equation reads
 %
@@
 initial HEALPix level.  We usually find $l$ = 0 or 1 is sufficient
-because these coarse rays will be usually be split before traversing
+because these coarse rays will usually be split before traversing
 the first cell.
@@
   src,i}$ are the initial distance travelled by the ray, normal
-direction of the ray, the next cell boundary crossing on the $i$-th
+direction of the ray, the next cell boundary crossing in the $i$-th
 dimension, and the position of the point source that emitted the ray,
@@
 %
-If $\Phi_c$ is less than a pre-determined value (usually $>2$), the
+If $\Phi_c$ is less than a pre-determined value (usually $>3$), the
 ray is split into 4 child rays.  We investigate the variations in
@@
 %
-In the second case, the photon is halted at that position and saved,
+In the first case, the photon is halted at that position and saved,
 where it will be considered in the solution of $I_\nu$ at the next
@@
 a hierarchical binary tree, which is analogous to the gravity tree
-solvers.  We show the performance improvements in the strong scaling
-tests (\S\ref{sec:strong_sc}).  However we leave its full details for
-a later paper.
+solvers.  In principle, this should increase the efficiency of the
+solver, but currently in most problems the overhead is greater than
+the compuational savings.  Nevertheless the biggest advantage of this
+method is the memory savings in simulations with clustered sources.
+We leave its full details for a later paper and now describe our
+photon-conserving transport method.
 
@@
 The radiation field is calculated by integrating equation
-\ref{eqn:rtray} along each ray, which is done by considering the
+(\ref{eqn:rtray}) along each ray, which is done by considering the
 discretization of the ray into segments.  In the following section, we
 assume the rays are monochromatic.  For convenience, we express the
-integration in terms of optical depth $\tau = \int \kappa(r,t) \;
-dr$, and for a ray segment,
+integration in terms of optical depth $\tau = \int \kappa(r,t) \; dr$,
+and for a ray segment,
 %
@@
 cell-centered density in our calculations but have experimented with
-trilinearly interpolated densities \citep[see][]{Mellema06} without
-producing considerable artifacts.  Equation (\ref{eqn:rtray}) has a
-simple exponential analytic solution, and the photon flux of a ray is
-reduced by
+trilinearly interpolated densities \citep[see][]{Mellema06} but could
+not devise a method that did not produce considerable artifacts.
+Equation (\ref{eqn:rtray}) has a simple exponential analytic solution,
+and the photon flux of a ray is reduced by
 %
@@
 \end{equation}
-where $\alpha_B = 2.59 \times 10^{-13} \mathrm{cm}^3 \mathrm{s}^{-1}$
-is the recombination coefficient at 10$^4$ K in the Case B on-the-spot
-approximation, in which all recombinations are locally reabsorbed,
-\citep{Spitzer78}, and $C_{\rm H}$ is the collisional ionization rate.
-However for more accurate solutions in calculations that consider
-several chemical species, the photo-ionization rates are better
-utilized in solvers that consider chemical networks
-\citep[e.g.][]{Abel97}.
-
-\subsection{Additional Physics}
-\label{sec:addphysics}
-
-Other radiative processes can also be important in some situations,
-such as attenuation of radiation in the Lyman-Werner bands, secondary
-ionizations from X-ray radiation, Compton heating of from scattered
-photons, and radiation pressure.
-
-\subsubsection{Absorption of Lyman-Werner Radiation}
-
-Molecular hydrogen can absorb photons in the Lyman-Werner bands that
-are composed of 76 absorption lines ranging from 10.2 to 13.6 eV.
-Each of these spectral lines can be modelled with a typical
-exponential attenuation equation \citep{Ricotti01}, but
-\citet{Draine96} showed that this self-shielding is well modeled with
-the following relation to total \hh~column density
-%
-\begin{equation}
-  \label{eqn:lwband}
-  f_{\rm shield}(N_{\rm H2}) = \left\{ \begin{array}{l@{\quad}l}
-      1 & (N_{\rm H2} \le 10^{14} \; \mathrm{cm}^{-2})\\
-      (N_{\rm H2}/10^{14} \; \mathrm{cm}^{-2})^{-0.75} & (N_{\rm H2} >
-        10^{14} \; \mathrm{cm}^{-2})
-    \end{array} \right. .
-\end{equation}
-To incorporate this shielding function into the ray tracer, we store
-the total \hh~column density and calculate the \hh~dissociation rate
-by summing the contribution of all rays,
-%
-\begin{equation}
-  \label{eqn:lwRT}
-  k_{\rm diss} = \sum_{\rm rays} \frac{P \; \sigma_{\rm LW} \;
-    \Omega_{\rm ray} \; r^2 \; dr}{A_{\rm cell} \; dV \; dt_P},
-\end{equation}
-where $\sigma_{\rm LW} = 3.71 \times 10^{18} \mathrm{cm}^2$ is the
-effective cross-section of \hh~\citep{Abel97}.  To account for any
-absorption in each photon package, we attenuate the photon number
-flux by
-%
-\begin{equation}
-  \label{eqn:LWdP}
-  dP = P [f_{\rm shield}(N_{\rm H2} + dN_{\rm H2}) - f_{\rm shield}(N_{\rm H2})],
-\end{equation}
-where $dN_{\rm H2}$ is the \hh~column density in the current cell.
-
-\subsubsection{Secondary Ionizations from X-rays}
-\label{sec:xrays}
-
-A high-energy ($E_{\rm ph} \gsim 100$ eV) photon can ionize multiple
-neutral hydrogen and helium atoms, and this should be considered in
-such radiation fields.  \citet{Shull85} studied this effect with Monte
-Carlo calculations over varying electron fractions and photon energies
-up to 3 keV.  They find that the excitation of hydrogen and helium and
-the ionization of \ion{He}{2} is negligible.  The number of secondary
-ionizations of H and He is reduced from the ratio of the photon and
-ionization energies ($E_{\rm ph} / E_i$) by a factor of
-%
-\begin{equation}
-  Y_{\rm k,H} = 0.3908 (1 - x^{0.4092})^{1.7592},
-\end{equation}
-\begin{equation}
-  Y_{\rm k,He} = 0.0554 (1 - x^{0.4614})^{1.6660},
-\end{equation}
-where $x$ is the electron fraction.  The remainder of the photon
-energy is deposited into thermal energy that is approximated by
-%
-\begin{equation}
-  Y_{\rm \Gamma} = 0.9971 [ 1 - (1 - x^{0.2663})^{1.3163} ]
-\end{equation}
-and approaches one as $x \rightarrow 1$.  Thus in gas with low
-electron fractions, most of the energy results in ionizations of
-hydrogen and helium, and in nearly ionized gas, the energy goes into
-photo-heating.
-
-\subsubsection{Compton Heating from Photon Scattering}
-
-High energy photons can also cause Compton heating by scattering off
-free electrons.  During a scattering, a photon loses $\Delta E(T_e) =
-4kT_e \times (E_{ph} / m_e c^2)$ of energy, where $T_e$ is the
-electron temperature.  For the case of monochromatic energy groups, we
-model this process by considering that the photons are absorbed by a
-factor of 
-\begin{equation}
-  \frac{dP_C}{P} = (1 - e^{-\tau_e}) \frac{\Delta(T_e)}{E_{ph}},
-\end{equation}
-which is the equivalent of the photon energy decreasing.  Here $\tau_e
-= n_e \sigma_{KN} dl$ is the optical depth to Compton scattering, and
-$\sigma_{KN}$ is the non-relativistic Klein-Nishina cross section
-\citep{Rybicki}.  The Compton heating rate is thus
-\begin{equation}
-  \Gamma_{\rm ph,C} = \frac{dP_C}{n_e \; V_{\rm cell} \; dt}.
-\end{equation}
-
-\subsubsection{Radiation Pressure}
-
-The absorption of radiation transfers momentum from photons to the
-absorbing medium, i.e. radiation pressure.  This is easily computed by
-considering the momentum
-\begin{equation}
-  d\mathbf{p}_\gamma = \frac{dP \; E_{\rm ph}}{c} \; \hat{r}
-\end{equation}
-of the absorbed radiation from the incoming ray, where $\hat{r}$ is
-the normal direction of the ray.  We do not include radiation pressure
-on dust, and thus our treatment underestimates its effects in
-applicable environments.  The resulting acceleration of the gas due to
-radiation pressure is
-\begin{equation}
-  d\mathbf{a} = \frac{d\mathbf{p}_\gamma} {dt\; \rho \; V_{\rm cell}},
-\end{equation}
-where $\rho$ is the gas density inside the cell and $dt$ is the
-radiative transfer timestep.  This acceleration is then added to the
-other forces, e.g. gravity and gas pressure, in the calculation.
+where $\alpha_B = 2.59 \times 10^{-13} \mathrm{cm}^3 \;
+\mathrm{s}^{-1}$ is the recombination coefficient at 10$^4$ K in the
+Case B on-the-spot approximation in which all recombinations are
+locally reabsorbed, \citep{Spitzer78}, and $C_{\rm H}$ is the
+collisional ionization rate.  However for more accurate solutions in
+calculations that consider several chemical species, the
+photo-ionization rates are better utilized in solvers that consider
+chemical networks \citep[e.g.][]{Abel97}.
 
@@
 
-Consider the solid angle $\Omega_{\rm ray}$ and photon flux $P$
-associated with a single ray, and assume the flux is constant across
-$\Omega_{\rm ray}$.  There exists a discrepancy between the geometry
-cell face and HEALPix pixel when the pixel does not cover the entire
-cell face, which is illustrated in Figure \ref{fig:covering}.  This
-mismatch causes non-spherical artifacts and is most apparent in the
-optically thin case, where the area of the pixel is dominant over $(1
-- e^\tau)$ when calculating $k_{\rm ph}$.  One can avoid these
-artifacts by increasing the sampling $\Phi_c$ to high values,
-e.g. $>10$, but we have formulated a simple geometric correction to
-the calculation of the radiation field.  This correction is not unique
-to the HEALPix formalism but can be applied to any type of
-pixelization.
+For a ray tracing method to accurately, i.e. without non-spherical
+artifacts, compute the radiation field, the computational grid must be
+well-sampled by the rays.  The main source of these artifacts is the
+geometrical difference between the cell and the HEALPix pixel.  In
+this section, we devise a correction scheme to account for these
+differences.  Consider the solid angle $\Omega_{\rm ray}$ and photon
+flux $P$ associated with a single ray, and assume the flux is constant
+across $\Omega_{\rm ray}$.  There exists a discrepancy between the
+geometry cell face and HEALPix pixel when the pixel does not cover the
+entire cell face, which is illustrated in Figure \ref{fig:covering}.
+This mismatch causes non-spherical artifacts and is most apparent in
+the optically thin case, where the area of the pixel is dominant over
+$(1 - e^\tau)$ when calculating $k_{\rm ph}$.  One can avoid these
+artifacts by increasing the sampling $\Phi_c$ to high values ($>10$)
+but we have formulated a simple geometric correction to the
+calculation of the radiation field.  This correction is not unique to
+the HEALPix formalism but can be applied to any type of pixelization.
 
 The contribution to $k_{\rm ph}$ and $\Gamma_{\rm ph}$ must be
-corrected by a covering factor $f_c$.  When the pixel is fully
-contained within the cell face, $f_c \equiv 1$.  Because the geometry
-of the pixel can be complex, i.e. curved edges, we approximate $f_c$
-by assuming the pixel is square.  The covering factor is thus related
-to the width of a pixel, $L_{\rm pix} = R_0 \, \theta_{\rm pix}$, and
-the distance from the ray segment midpoint to the closest cell
-boundary, which is depicted in Figure \ref{fig:covering}.  To estimate
-$f_c$, we first find the distance $d_{\rm center,i}$ from the midpoint
-of the ray segment to the cell center $x_{\rm 0,i}$ in orthogonal
-directions,
+corrected by the covering factor $f_c$ of the pixel with respect to
+the cell.  When the pixel is fully contained within the cell face,
+$f_c \equiv 1$.  Because the geometry of the pixel can be complex with
+curved edges, we approximate $f_c$ by assuming the pixel is square.
+The covering factor is thus related to the width of a pixel, $L_{\rm
+  pix} = R_0 \, \theta_{\rm pix}$, and the distance from the ray
+segment midpoint to the closest cell boundary $D_{\rm c,i}$, which is
+depicted in Figure \ref{fig:covering}.  To estimate $f_c$, we first
+find the distance $d_{\rm center,i}$ from the midpoint of the ray
+segment to the cell center $x_{\rm 0,i}$ in orthogonal directions,
 %
@@
   D_{\rm c,i} = \left| R_{\rm 0,i} + \hat{n}_i\,\frac{dr}{2} - x_{\rm
-      0,i} \right|.
-\end{equation}
-The distance to the closest cell boundary is $D_{\rm edge} = dx/2 -
-\min_{i=1 \rightarrow 3} (D_{\rm c,i})$.  Thus the covering
-factor is related to the square of the ratio between the $L_{\rm pix}$
-and $d_{\rm mid}$ by
+      0,i} \right|,
+\end{equation}
+where $R_{\rm 0,i}$ is the distance travelled by the ray in each
+orthogonal direction.  The distance to the closest cell boundary is
+$D_{\rm edge} = dx/2 - \min_{i=1 \rightarrow 3} (D_{\rm c,i})$.  Thus
+the covering factor is related to the square of the ratio between the
+$L_{\rm pix}$ and $D_{\rm edge}$ by
 %
@@
 spherical symmetry obtained outweighed the loss of photon
-conservation.  We show the deviations from fully conservative in
-\S\ref{sec:test_fc}.
+conservation.  However we show that there are no perceptible
+deviations from photon conservation in \S\ref{sec:test1} and
+\S\ref{sec:dx_dep}.
 
@@
 would consider the distance between the cell boundary and ray segment
-midpoint in the direction of $\mathbf{x}_{\rm mid} - \mathbf{x}_{\rm
-  center}$.  However we find that the method outlined here provides a
-sufficient correction factor to avoid any non-spherical artifacts.
+midpoint in the direction between the midpoint and cell center of
+$\mathbf{x}_{\rm mid} - \mathbf{x}_0$.  We find that the method
+outlined here provides a sufficient correction factor to avoid any
+non-spherical artifacts and deviations from photon conservation.
 Furthermore in principle, the ray should also contribute to any
@@
 
-When the medium is optically thin to the radiation, radiation is only
-attenuated by geometric dilution in the local approximation to
-Eq. (\ref{eqn:rteqn}), i.e. the inverse square law.  We can minimize
-the computational work of ray tracing in the optically thin regime by
-utilizing this fact.  Here we track the total column density $N_{\rm
-  abs}$ and the equivalent total optical depth $\tau$ traversed by the
-photon.  If $\tau < \tau_{\rm thin} \sim 0.1$ after the ray exits the
-cell, we calculate the photo-ionization and photo-heating rates
-directly from the incoming ray instead of the luminosity of the
-source.  This should only be evaluated once per cell per radiation
-source.
+In an optically thin medium, radiation is only attenuated by geometric
+dilution in the local approximation to Equation (\ref{eqn:rteqn}),
+i.e. the inverse square law.  With such a simple solution, the tracing
+of rays is wasteful, however these rays must be propagated because the
+the medium farther awap can be optically thick.  Here we describe a
+method that minimizes the computational work of ray tracing in the
+optically thin regime by exploiting this fact.  Each ray tracks the
+total column density $N_{\rm abs}$ and the equivalent total optical
+depth $\tau$ traversed by the photon.  If $\tau < \tau_{\rm thin} \sim
+0.1$ after the ray exits the cell, we calculate the photo-ionization
+and photo-heating rates directly from the incoming ray instead of the
+luminosity of the source.
 \begin{equation}
@@
 photo-heating ray is calculated in the same manner as the general
-case, $\Gamma_{\rm ph} = k_{\rm ph} (E_{\rm ph} - E_i)$.  No photons
-are removed from the ray.  With this method, we only require one ray
+case, $\Gamma_{\rm ph} = k_{\rm ph} (E_{\rm ph} - E_i)$.  This should
+only be evaluated once per cell per radiation source.  No photons are
+removed from the ray.  With this method, we only require one ray
 travel through each cell where the gas is optically thin, thus
@@
 
+\subsection{Additional Physics}
+\label{sec:addphysics}
+
+Other radiative processes can also be important in some situations,
+such as attenuation of radiation in the Lyman-Werner bands, secondary
+ionizations from X-ray radiation, Compton heating of from scattered
+photons, and radiation pressure.  We describe our implementation of
+these physics next.
+
+\subsubsection{Absorption of Lyman-Werner Radiation}
+
+Molecular hydrogen can absorb photons in the Lyman-Werner bands
+through the two-step Solomon process that are composed of 76
+absorption lines ranging from 11.1 to 13.6 eV \citep{Stecher67,
+  Dalgarno70}.  Each of these spectral lines can be modelled with a
+typical exponential attenuation equation \citep{Ricotti01}, but
+\citet{Draine96} showed that this self-shielding is well modeled with
+the following relation to total \hh~column density
+%
+\begin{equation}
+  \label{eqn:lwband}
+  f_{\rm shield}(N_{\rm H2}) = \left\{ \begin{array}{l@{\quad}l}
+      1 & (N_{\rm H2} \le 10^{14} \; \mathrm{cm}^{-2})\\
+      (N_{\rm H2}/10^{14} \; \mathrm{cm}^{-2})^{-0.75} & (N_{\rm H2} >
+        10^{14} \; \mathrm{cm}^{-2})
+    \end{array} \right. .
+\end{equation}
+To incorporate this shielding function into the ray tracer, we store
+the total \hh~column density and calculate the \hh~dissociation rate
+by summing the contribution of all rays,
+%
+\begin{equation}
+  \label{eqn:lwRT}
+  k_{\rm diss} = \sum_{\rm rays} \frac{P \; \sigma_{\rm LW} \;
+    \Omega_{\rm ray} \; r^2 \; dr}{A_{\rm cell} \; dV \; dt_P},
+\end{equation}
+where $\sigma_{\rm LW} = 3.71 \times 10^{18} \mathrm{cm}^2$ is the
+effective cross-section of \hh~\citep{Abel97}.  To account for
+absorption, we attenuate the photon number flux by
+%
+\begin{equation}
+  \label{eqn:LWdP}
+  dP = P [f_{\rm shield}(N_{\rm H2} + dN_{\rm H2}) - f_{\rm shield}(N_{\rm H2})],
+\end{equation}
+where $dN_{\rm H2}$ is the \hh~column density in the current cell.
+
+\subsubsection{Secondary Ionizations from X-rays}
+\label{sec:xrays}
+
+At the other end of the spectrum, a high-energy ($E_{\rm ph} \gsim
+100$ eV) photon can ionize multiple neutral hydrogen and helium atoms,
+and this should be considered in such radiation fields.
+\citet{Shull85} studied this effect with Monte Carlo calculations over
+varying electron fractions and photon energies up to 3 keV.  They find
+that the excitation of hydrogen and helium and the ionization of
+\ion{He}{2} is negligible.  The number of secondary ionizations of H
+and He is reduced from the ratio of the photon and ionization energies
+($E_{\rm ph} / E_i$) by a factor of
+%
+\begin{equation}
+  Y_{\rm k,H} = 0.3908 (1 - x^{0.4092})^{1.7592},
+\end{equation}
+\begin{equation}
+  Y_{\rm k,He} = 0.0554 (1 - x^{0.4614})^{1.6660},
+\end{equation}
+where $x$ is the electron fraction.  The remainder of the photon
+energy is deposited into thermal energy that is approximated by
+%
+\begin{equation}
+  Y_{\rm \Gamma} = 0.9971 [ 1 - (1 - x^{0.2663})^{1.3163} ]
+\end{equation}
+and approaches one as $x \rightarrow 1$.  Thus in gas with low
+electron fractions, most of the energy results in ionizations of
+hydrogen and helium, and in nearly ionized gas, the energy goes into
+photo-heating.
+
+\subsubsection{Compton Heating from Photon Scattering}
+
+High energy photons can also cause Compton heating by scattering off
+free electrons.  During a scattering, a photon loses $\Delta E(T_e) =
+4kT_e \times (E_{ph} / m_e c^2)$ of energy, where $T_e$ is the
+electron temperature.  For the case of monochromatic energy groups, we
+model this process by considering that the photons are absorbed by a
+factor of 
+\begin{equation}
+  \frac{dP_C}{P} = (1 - e^{-\tau_e}) \frac{\Delta(T_e)}{E_{ph}},
+\end{equation}
+which is the equivalent of the photon energy decreasing.  Here $\tau_e
+= n_e \sigma_{\rm KN} dl$ is the optical depth to Compton scattering,
+and $\sigma_{\rm KN}$ is the non-relativistic Klein-Nishina cross
+section \citep{Rybicki}.  The Compton heating rate is thus
+\begin{equation}
+  \Gamma_{\rm ph,C} = \frac{dP_C}{n_e \; V_{\rm cell} \; dt_P}.
+\end{equation}
+
+\subsubsection{Radiation Pressure}
+
+Another relevant process is radiation pressure, where the absorption
+of radiation transfers momentum from photons to the absorbing medium.
+This is easily computed by considering the momentum
+\begin{equation}
+  d\mathbf{p}_\gamma = \frac{dP \; E_{\rm ph}}{c} \; \hat{r}
+\end{equation}
+of the absorbed radiation from the incoming ray, where $\hat{r}$ is
+the normal direction of the ray.  We do not include radiation pressure
+on dust, and thus our treatment underestimates its effects in
+applicable environments.  The resulting acceleration of the gas due to
+radiation pressure is
+\begin{equation}
+  d\mathbf{a} = \frac{d\mathbf{p}_\gamma} {dt_P\; \rho \; V_{\rm cell}},
+\end{equation}
+where $\rho$ is the gas density inside the cell.  This acceleration is
+then added to the other forces, e.g. gravity, in the calculation.
+
 \section{Numerical Implementation in Enzo}
 
-\enzo~is a parallel block-structured AMR \citep{BergerAMR} code that
-is publicly available \citep{BryanNorman1997, OShea2004}.  In this
-section, we describe our parallel implementation of the adaptive ray
-tracing method into \enzo.  First we explain the programming design of
-handling the ``photon packages'' that are traced along the adaptive
-rays.  We use the terms photon packages and rays interchangeably.  Next
-we focus on the details of the radiation hydrodynamics and then the
-importance of correct time-stepping.  Last we give our parallelization
-strategy of tracing rays through an AMR hierarchy.  This
-implementation is included in the \texttt{v2.0} public version of
-\enzo.
+In this section, we describe our parallel implementation of the
+adaptive ray tracing method into \enzo.  \enzo~is a parallel
+block-structured AMR \citep{BergerAMR} code that is publicly available
+\citep{BryanNorman1997, OShea2004}.  First we explain the programming
+design of handling the ``photon packages'' that are traced along the
+adaptive rays.  We use the terms photon packages and rays
+interchangeably.  Next we focus on the details of the radiation
+hydrodynamics and then the importance of correct time-stepping.  Last
+we give our parallelization strategy of tracing rays through an AMR
+hierarchy.  This implementation is included in the \texttt{v2.0}
+public version of \enzo.
 
@@
 pointer of the current grid if no subgrid exists under the current
-cell or the child pointer that exists under the current cell.  This
-provides a significant speedup when compared to a simple comparison
-of a photon package position and all of the child grid boundaries.
-Note that this is the same algorithm used in \enzo~when moving
-collisionless particles to child grids.
+cell or the child grid pointer that exists under the current cell.
+This provides a significant speedup when compared to a simple
+comparison of a photon package position and all of the child grid
+boundaries.  Note that this is the same algorithm used in \enzo~when
+moving collisionless particles to child grids.
 
@@
 \step{3k} Check if the ray has exited the current grid.  If false,
-continue to the next ray (step 3a).  If true, move the ray to the
+continue to the next cell (step 3b).  If true, move the ray to the
 linked list \texttt{PhotonMoveList}, similar to step 3c.  If the ray
@@
 In practice, we have found that one energy group per photon type is
-sufficient to match expected analytical tests.  For example when
-modeling Population III stellar radiation \citep[e.g.][for hydrogen
-  ionizing radiation only]{Abel07, Wise08_Gal}, we have 3 energy
-groups---\ion{H}{1}, \ion{He}{1}, \ion{He}{2}---each with an energy
-that equals the average photon energy above the ionization threshold.
+sufficient to match expected analytical tests (\S\ref{sec:nu_dep}).
+For example when modeling Population III stellar radiation
+\citep[e.g.][for hydrogen ionizing radiation only]{Abel07,
+  Wise08_Gal}, we have 3 energy groups---\ion{H}{1}, \ion{He}{1},
+\ion{He}{2}---each with an energy that equals the average photon
+energy above the ionization threshold.
 
@@
 boundary.  Then radiation permeates the grid in the time between
-$t_{\rm L=1} \rightarrow t_{\rm L=1}+dt_{\rm L=1}$, and the energy and
-chemical state of the cells must be updated again to advance the
-ionization front accurately.  If one does not update these cells, it
-will appear that the ionization front does not enter the grid until
-the next hydrodynamical timestep!  Visually this appears as
-discontinuities in the temperature and electron fraction on grid
-boundaries.  One may avert this problem by solving the chemistry and
-energy equations for every cell on every radiative transfer timestep,
-but this is very time consuming and unnecessary, especially if the
-radiation filling factor is small.
+$t_{\rm L} \rightarrow t_{\rm L}+dt_{\rm L}$, and the energy and
+chemical state of the cells must be updated with each radiation update
+to advance the ionization front accurately.  If one does not update
+these cells, it will appear that the ionization front does not enter
+the grid until the next hydrodynamical timestep!  Visually this
+appears as discontinuities in the temperature and electron fraction on
+grid boundaries.  One may avert this problem by solving the chemistry
+and energy equations for every cell on every radiative transfer
+timestep, but this is very time consuming and unnecessary, especially
+if the radiation filling factor is small.
 
@@
 chemo-thermal state of the system remains constant as the rays are
-traced through the cells.  Thus in the case of a single \ion{H}{2}
-region, the speed of the ionization front is limited to approximately
-the $\lambda_{\rm mfp} / dt_P$.
+traced through the cells.  In the case of a single \ion{H}{2} region,
+the speed of the ionization front is limited to approximately
+$\lambda_{\rm mfp} / dt_P$.
 
@@
 
-Another strategy is only allowing the neutral fraction of the ionized
-gas to change a small amount, i.e. for a single cell,
+Another strategy is restricting the neutral fraction to change a small
+amount, i.e. for a single cell,
 %
@@
 ionization front velocity in a growing Str\"{o}mgren sphere without
-recombinations, where $\dot{N}_\gamma = 4 \pi R^2 n_{\rm H} v_{\rm
-  IF}$.  Using $\kph \propto \dot{n}_{\rm H} / n_{\rm H}$ and $\kph =
-\dot{N}_\gamma \sigma / 4\pi R^2 A_{\rm cell}$, we can make
-substitutions on both sides of the equation to arrive at the
-ionization front velocity $v_{\rm IF} \propto n_{\rm H} /\dot{n}_{\rm
-  H}$.
+recombinations, 
+\begin{equation}
+  \label{eqn:ndot}
+  \dot{N}_\gamma = 4 \pi R^2 n_{\rm H} v_{\rm IF}.
+\end{equation}
+Using $\kph = \dot{N}_\gamma \sigma / 4\pi R^2 A_{\rm cell}$ and $\kph
+\propto \dot{n}_{\rm H} / n_{\rm H}$, we can make substitutions
+respectively on both sides of Equation (\ref{eqn:ndot}) to arrive at
+the ionization front velocity $v_{\rm IF} \propto n_{\rm H}
+/\dot{n}_{\rm H}$.
 
@@
 modifications as the timestep, but there is considerable noise both
-spatially and temporally.  In order to make this technique stable, we
+spatially and temporally.  In order to stabilize this technique, we
 first spatially smooth the values of $dt_{\rm P,cell}$ with a Gaussian
@@
 smoothed $dt_{\rm P,cell}$, we select the minimum value as $dt_P$.
-Significant noise in $dt_P$ can exist between time discretizations.
+Significant noise in $dt_P$ can exist between time steps as well.
 Because the solution can become inaccurate if the timestep is allowed
@@
 \end{equation}
-Otherwise, we still restrict the change in timestep by setting the
-next timestep to be the average of the previous timestep $dt_{\rm
-  P,0}$ and $\min(dt_{\rm P,cell})$.  Figure \ref{fig:dtsmooth} shows
-the smooth evolution of $dt_{\rm P}$ in a growing Str\"{o}mgren sphere when
-compared to the values of $\min(dt_{\rm P,cell})$.
+Figure \ref{fig:dtsmooth} shows the smooth evolution of $dt_{\rm P}$
+in a growing Str\"{o}mgren sphere when compared to the values of
+$\min(dt_{\rm P,cell})$.
 
@@
 
-In our implementation, a constant timestep is necessary when solving
-the time-dependent radiative transfer equation.  It should be small
-enough to evolve ionization fronts accurately, as discussed earlier.
-The timestep can be based on physical arguments, for example, the
+A constant timestep is necessary when solving the time-dependent
+radiative transfer equation in Enzo+Moray.  It should be small enough
+to evolve ionization fronts accurately, as discussed earlier.  The
+timestep can be based on physical arguments, for example, the
 sound-crossing time of an ionized region at $T > 10^4$ K.  To be
 conservative, one may choose the sound-crossing time of a cell
-\citep[e.g.][]{Abel07, Wise08_Gal}.  Alternatively, the diameter of the
-smallest relevant system (e.g., an accretion radius, transition radius
-to a D-type ionization front, etc.) in the simulation may be chosen to
-calculate the sound-crossing time.
+\citep[e.g.][]{Abel07, Wise08_Gal}.  Alternatively, the diameter of
+the smallest relevant system (e.g., an accretion radius, transition
+radius to a D-type ionization front, etc.) in the simulation may be
+chosen to calculate the sound-crossing time.
 
@@
 
+\textbf{Reorganize to be more clear!}
+
 Ionization front velocities can approach significant fractions of the
@@
 processors and send them in groups.  We also send the destination grid
-level and ID number along with the ray information, which is listed at
+level and ID number along with the ray information that is listed at
 the beginning of \S\ref{sec:design}.
@@
   \label{eqn:rstr}
-  r_s(t) = R_s [ 1 - \exp(-t/t_{\rm rec}) ]^{1/3}
+  r_s(t) = R_s [ 1 - \exp(-t/t_{\rm rec}) ]^{1/3},
 \end{equation}
@@
 kpc.  The ambient medium is initially set at $T=10^4$ K, $n_H =
-10^{-3} \cubecm$, $x = 1.2 \times 10^{-3}$, resulting in $R_s = 5.4$
+10^{-3}\;\cubecm$, $x = 1.2 \times 10^{-3}$, resulting in $R_s = 5.4$
 kpc and $t_{\rm rec} = 122.4$ Myr.  The problem is run for 500 Myr.
@@
 
-This test is similar Test 1, but the temperature is allowed to evolve
-The radiation source now has a blackbody spectrum with a $T = 10^5$ K.
-The initial temperature is set at 100 K.  The higher energy photons
-have a longer mean free path than the photons at the ionization
-threshold in Test 1.  Thus the ionization front is thicker as the
-photons can penetrate deeper into the neutral medium.  Here we use 4
-energy groups with the following mean energies and relative
+This test is similar to Test 1, but the temperature is allowed to
+evolve.  The radiation source now has a blackbody spectrum with a $T =
+10^5$ K.  The initial temperature is set at 100 K.  The higher energy
+photons have a longer mean free path than the photons at the
+ionization threshold in Test 1.  Thus the ionization front is thicker
+as the photons can penetrate deeper into the neutral medium.  Here we
+use 4 energy groups with the following mean energies and relative
 luminosities: $E_i = (16.74, 24.65, 34.49, 52.06)$, $L_i/L = (0.277,
@@
 
-In Figure \ref{fig:test2_1}, we show the neutral and ionized fraction
-as a function of radius at $t = $ 10, 30, 100, and 500 Myr, and the
-total neutral fraction of the domain.  Compared with Test 1, the
-ionization front is thicker, as expected with the harder spectrum.
-The total neutral fraction decreases to 0.67 over 4$t_{\rm rec} = 500$
-Myr, which is in agreement with the analytical expectation and other
-codes in RT06.  In Figure \ref{fig:test2_2}, we show the ratio of the
+In Figure \ref{fig:test2_1}, we show the radially averaged neutral and
+ionized fraction at $t = $ 10, 30, 100, and 500 Myr, and the total
+neutral fraction of the domain.  Compared with Test 1, the ionization
+front is thicker, as expected with the harder spectrum.  The total
+neutral fraction decreases to 0.67 over 4$t_{\rm rec} = 500$ Myr,
+which is in agreement with the analytical expectation and other codes
+in RT06.  In Figure \ref{fig:test2_2}, we show the ratio of the
 ionization front radius $r_{\rm IF}$ in our simulation and $R_s$.
@@
 asymptotes to a solution that is 4\% greater than $R_s$.  This
-behavior puts our code is approximately the median result in RT06,
-where this ratio varies between 1 and 1.1, and the early evolution of
-$r_{\rm IF}$ is under-predicted by almost all of the codes.  If we use
-one energy group with the mean energy (29.6 eV) of a $T=10^5$ K
-blackbody, we find that $r_{\rm IF}/R_s$ = 1.08, which is
-representative of the codes in the upper range of RT06.  In Figure
-\ref{fig:test2_3}, we show slices of neutral fraction and temperature
-through the origin at $t = $ 10 and 100 Myr.  Here one sees the
-spherically symmetric \ion{H}{2} regions and a smooth temperature
-transition to the neutral ambient medium.
+behavior is approximately the median result in RT06, where this ratio
+varies between 1 and 1.1, and the early evolution of $r_{\rm IF}$ is
+under-predicted by almost all of the codes.  If we use one energy
+group with the mean energy (29.6 eV) of a $T=10^5$ K blackbody, we
+find that $r_{\rm IF}/R_s$ = 1.08, which is representative of the
+codes in the upper range of RT06.  In Figure \ref{fig:test2_3}, we
+show slices of neutral fraction and temperature through the origin at
+$t = $ 10 and 100 Myr.  Here one sees the spherically symmetric
+\ion{H}{2} regions and a smooth temperature transition to the neutral
+ambient medium.
 
@@
 The problem for this test is contained in a 6.6 kpc box with an
-ambient medium of $n_H = 2 \times 10^{-4} \cubecm$ and $T = 8000$ K.
-The clump is in pressure equilibrium with $n_H = 0.04 \cubecm$ and $T
-= 40$ K.  It has a radius of $r_c = 0.8$ kpc and is centered at
+ambient medium of $n_H = 2 \times 10^{-4}\;\cubecm$ and $T = 8000$ K.
+The clump is in pressure equilibrium with $n_H = 0.04\; \cubecm$ and
+$T = 40$ K.  It has a radius of $r_c = 0.8$ kpc and is centered at
 $(x,y,z) = (5, 3.3, 3.3)$ kpc.  In RT06, the test considered a plane
@@
 the center of the $y=0$ boundary.  The luminosity of $\dot{N}_\gamma =
-3 \times 10^{51}$ ph s$^{-1}$ corresponds to the same flux $F_0$.  The
-location where the ionization front trapping can be calculated
-analytically \citep{Shapiro04}, and with these parameters, it should
-halt at approximately the center of the clump.  We use the same four
-energy groups as in Test 2.
+3 \times 10^{51}$ ph s$^{-1}$ corresponds to the same flux $F_0$ at 5
+kpc.  The location where the ionization front trapping can be
+calculated analytically \citep{Shapiro04}, and with these parameters,
+it should halt at approximately the center of the clump.  We use the
+same four energy groups as in Test 2.
 
@@
 the analytical expectation.  The hardness of the $T = 10^5$ K
-blackbody spectrum allows the gas outside of the ionization front.
-Where the gas is ionized, the temperature is between 10,000 and 20,000
-K, but decreases sharply with the ionized fraction.  Figure
-\ref{fig:test3_2} depicts the average ionized fraction and temperature
-inside the dense clump, which both gradually increase as the
-ionization front propagates through the overdensity.  Our results are
-consistent with RT06.  Finally we show slices of neutral fraction and
-temperature in the $z = 0.5$ plane in Figure \ref{fig:test3_3}.  The
-neutral fraction slices prominently show the sharp shadows created by
-the clump and demonstrates the non-diffusivity behavior of ray
+blackbody spectrum allows the gas outside of the ionization front to
+be photo-heated.  Where the gas is ionized, the temperature is between
+10,000 and 20,000 K, but decreases sharply with the ionized fraction.
+Figure \ref{fig:test3_2} depicts the average ionized fraction and
+temperature inside the dense clump, which both gradually increase as
+the ionization front propagates through the overdensity.  Our results
+are consistent with RT06.  Finally we show slices of neutral fraction
+and temperature in the $z = 0.5$ plane in Figure \ref{fig:test3_3}.
+The neutral fraction slices prominently show the sharp shadows created
+by the clump and demonstrates the non-diffusivity behavior of ray
 tracing.  The discretization of the sphere creates one neutral cell on
@@
   Sokasian03}, where the dense regions around halos are ionized first,
-then the voids are ionized last.  At the end of the simulation, $x_v =
-0.65$, which is lower than all of the codes in RT06.  However by
-visual inspection in the slices of electron fraction
-(Fig. \ref{fig:test4_2}), there appears to be very good agreement with
-C$^2$-ray and FTTE.  By first glance, our result appears to be
-different than the RT06 because of the color-mapping.  Our results are
-also in good agreement with the multi-frequency version of TRAPHIC
-\citep[][see also for better representations of the electron fraction
-  slices]{Pawlik10}.  In the slices of electron fraction and
-temperature, Figure \ref{fig:test4_2}, the photo-heated regions are
-larger than the ionized regions by a factor of 2--3 because of the
-hardness of the $T = 10^5$ K blackbody spectrum.
+then the voids are ionized last.  At the end of the simulation, 65\%
+of the simulation is ionized.  However by visual inspection in the
+slices of electron fraction (Fig. \ref{fig:test4_2}), there appears to
+be very good agreement with C$^2$-ray and FTTE.  By first glance, our
+result appears to be different than the RT06 because of the
+color-mapping.  Our results are also in good agreement with the
+multi-frequency version of TRAPHIC \citep[][see also for better
+representations of the electron fraction slices]{Pawlik10}.  In the
+slices of electron fraction and temperature, Figure \ref{fig:test4_2},
+the photo-heated regions are larger than the ionized regions by a
+factor of 2--3 because of the hardness of the $T = 10^5$ K blackbody
+spectrum.
 
@@
 
-In this section, we show results from radiation hydrodynamics test
-problems presented in \citet[][hereafter RT09]{Iliev09}.  They involve
-(1) the expansion of an \ion{H}{2} region in a uniform medium, similar
-to Test 2, (2) an \ion{H}{2} region in an isothermal sphere, and (3)
-the photo-evaporation of a dense, cold clump, similar to Test 3.  We
+We next show results from radiation hydrodynamics test problems
+presented in \citet[][hereafter RT09]{Iliev09}.  They involve (1) the
+expansion of an \ion{H}{2} region in a uniform medium, similar to Test
+2, (2) an \ion{H}{2} region in an isothermal sphere, and (3) the
+photo-evaporation of a dense, cold clump, similar to Test 3.  We
 expand on this test suite to include more complex situations, such as
 a Rayleigh-Taylor problem illuminated by a radiation source, champagne
-flows, collimated radiation, an irradiated blast wave, and an
-\ion{H}{2} region in a rotating sphere.  For the \citeauthor{Iliev09}
+flows, an irradiated blast wave, collimated radiation, and an
+\ion{H}{2} with a variable source.  For the \citeauthor{Iliev09}
 tests, we turn off self-gravity and AMR in accordance with them.  In
 the latter tests, we will indicate whether we use those capabilities
-of \enzo.  Lastly, we use the new MHD implementation in \enzo~v2.0 in
-the problem of a growing \ion{H}{2} region in a magnetic field.
+of \enzo.  Last we use the new MHD implementation in \enzo~v2.0 in the
+problem of a growing \ion{H}{2} region in a magnetic field.
 
@@
 
-The growth of the \ion{H}{2} region is shown in Figure
+The growth of the ionization front radius is shown in Figure
 \ref{fig:test5_1}, using both $T = 10^4$ K and $x_e = 0.5$ as
@@
 temperature, pressure, and ionized fraction.  The initial \ion{H}{2}
-region is over-pressurized and creates an outward shock wave.  The
+region is over-pressurized and creates an forward shock wave.  The
 high-energy photons can penetrate through the shock and partially
@@
 expansion creates a photo-evaporative flow, seen in many star forming
-regions \citep[e.g. M16][]{Hester96} as stars irradiate
-nearby cold, dense overdensities.  These flows become evident in the
-density at 10 Myr, seen both in the line cuts and slices (Figure
-\ref{fig:test7_2}).  These outflows have temperatures up to 50,000 K.
-At this time, the front has progressed about halfway through the
-clump, if one inspects the neutral fraction.  However the high energy
-photons have heated all but the rear surface of the clump.  At the end
-of the test ($t = 50$ Myr), only the core and its associated shadow is
-neutral, as seen in Figure \ref{fig:test7_3}.  The core has been
-compressed by the surrounding warm medium, thus causing the higher
-densities seen at $t = 50$ Myr.  The non-spherical artifacts on the
-inner boundary of the warm outermost shell are caused by the initial
-discretization of the sphere, as discussed in \S\ref{sec:test3}.
+regions \citep[e.g. M16;][]{Hester96} as stars irradiate nearby cold,
+dense overdensities.  These flows become evident in the density at 10
+Myr, seen both in the line cuts and slices (Figure \ref{fig:test7_2}).
+They have temperatures up to 50,000 K.  At this time, the front has
+progressed about halfway through the clump, if one inspects the
+neutral fraction.  However the high energy photons have heated all but
+the rear surface of the clump.  At the end of the test ($t = 50$ Myr),
+only the core and its associated shadow is neutral, seen in Figure
+\ref{fig:test7_3}.  The core has been compressed by the surrounding
+warm medium, thus causing the higher densities seen at $t = 50$ Myr.
+The non-spherical artifacts on the inner boundary of the warm
+outermost shell are caused by the initial discretization of the
+sphere, as discussed in \S\ref{sec:test3}.
+
+We have completed presenting results from the RT06 and RT09 test
+suites.  Next we test Enzo+Moray with five additional tests that
+further demonstrate its capabilities and accuracy.
 
@@
 Radiation-driven outflows from overdensities, known as champagne
-flows, is a long studied problem \citep[e.g.][\S3.3]{Yorke86}.  We set
-up a spherical tophat with an overdensity of 10 and radius of 1 pc in
-a simulation box of 8 pc.  The ambient medium is 290 \cubecm~and 100
-K.  The radiation source is offset from the overdensity center by 0.4
-pc.  It has a luminosity of \tento{49} ph s$^{-1}$ and a $T=10^5$ K
-blackbody spectrum.  The resulting Str\"{o}mgren radius is 0.33 pc,
+flows, is a long studied problem \citep[e.g.][\S3.3]{Yorke86}.  To
+study this, we use the same setup as \citet{Bisbas09} --- a spherical
+tophat with an overdensity of 10 and radius of 1 pc in a simulation
+box of 8 pc.  The ambient medium has $\rho = 290$ \cubecm~and $T =
+100$ K.  The radiation source is offset from the overdensity center by
+0.4 pc.  It has a luminosity of \tento{49} ph s$^{-1}$ and a $T=10^5$
+K blackbody spectrum.  The resulting Str\"{o}mgren radius is 0.33 pc,
 just inside of the overdense clump.  These parameters are the same
@@
 \ref{fig:test8_1} at $t = 10, 40, 100, 150$ kyr.  In the direction of
-the clump center, the ionization front transitions from spherical to
-parabolic after it escapes from the clump in the opposite direction.
-At $t = 10$ kyr, the surface of the \ion{H}{2} region is just
-contained within the overdensity.  In the x-z plane, there are density
-perturbations only above a latitude of 45 degrees.  We believe that
-these are caused by the mismatch between HEALPix pixels and the
+the clump center, the ionization front shape transitions from
+spherical to parabolic after it escapes from the clump in the opposite
+direction.  At $t = 10$ kyr, the surface of the \ion{H}{2} region is
+just contained within the overdensity.  In the x-z plane, there are
+density perturbations only above a latitude of 45 degrees.  We believe
+that these are caused by the mismatch between HEALPix pixels and the
 Cartesian grid, even with our geometric correction.  After the
@@
 perturbations evolve.  We consider the case of a single-mode
-perturbation.  We let the system evolve without any radiation until
-the perturbation grows considerably and then turn on the radiation
-source.  These tests demonstrate that Enzo+Moray can follow a highly
-dynamic system and resolve fine density structures.
+perturbation.  The system evolves without any radiation until the
+perturbation grows considerably and then turn on the radiation source.
+These tests demonstrate that Enzo+Moray can follow a highly dynamic
+system and resolve fine density structures.
 
@@
 $\gamma = 1.4$.  We use a domain size of $(L_x, L_y, L_z) = (0.5, 0.5,
-1.5)$ with a resolution of (64, 64, 192).  For hydrostatic equilibrium,
-we set $P = P_0 - g \rho(z) z$ with $P_0 = 2.5$.  In order to consider
-a radiation source with a ionizing photon luminosity of $10^{42}$ ph
-s$^{-1}$, we scale the domain to a physical size of (0.5, 0.5, 1.5)
-pc; time is in units of Myr; density is in units of $m_h$, resulting
-in an initial temperature of $(T_0, T_1) = (363, 726)$ K.  The
-radiation source starts to shine at $t = 10$ Myr.
+1.5)$ with a resolution of (64, 64, 192).  For hydrostatic
+equilibrium, we set $P = P_0 - g \rho(z) z$ with $P_0 = 2.5$.  In
+order to consider a radiation source with a ionizing photon luminosity
+of $10^{42}$ ph s$^{-1}$, we scale the domain to a physical size of
+(0.5, 0.5, 1.5) pc; time is in units of Myr; density is in units of
+$m_h$, resulting in an initial temperature of $(T_0, T_1) = (363,
+726)$ K.  The radiation source is placed at the center of lower
+$z$-boundary face and starts to shine at $t = 10$ Myr.
 
@@
 \times 10^4)$ K.  Note that in code units, pressure is unchanged.  We
-adjust the physical unit scaling, so the light fluid has $T > 10^4$ K,
-$x_e \sim 1$, and thus optically-thin.  Furthermore, the ionization
-front remains R-type before interacting with the instability.  A
-possible physical analogue could be a radiation source heating and
-rarefying the medium below.
+adjust the physical unit scaling because we desire an optically thin
+bottom medium with $T > 10^4$ K and $x_e \sim 1$.  Furthermore, the
+ionization front remains R-type before interacting with the
+instability.  A possible physical analogue could be a radiation source
+heating and rarefying the medium below.
 
 The $x$ and $y$-boundaries are periodic, and the $z$-boundaries are
-reflecting.  The radiation source is placed at the center of lower
-$z$-boundary face.  The periodic boundaries will cause features that
-are non-physical, considering a more realistic plane-parallel case.
-Nevertheless, these tests provide a good check on a radiation
-hydrodynamics solver.  We show the evolution of the density,
-temperature, and ionized fraction of the optically thick and optically
-thin cases in Figures \ref{fig:test9_thick} and \ref{fig:test9_thin}.
-The initial state of the Rayleigh-Taylor instability is shown in the
-left panels.
+reflecting.  These will cause features that are non-physical, in
+particular the top reflecting boundary; nevertheless, these tests
+provide a good check on a radiation hydrodynamics solver.  We show the
+evolution of the density, temperature, and ionized fraction of the
+optically thick and optically thin cases in Figures
+\ref{fig:test9_thick} and \ref{fig:test9_thin}.  The initial state of
+the Rayleigh-Taylor instability is shown in the left panels.
 
@@
 reflects off the upper $z$-boundary.  This and complex shock
-reflections create a Richtmeyer-Meshkov instability, driving a chaotic
-jet-like structure downwards.  The radiation source photo-evaporates
-the outer parts of this structure.  The interaction between the dense
-cool ``jet'' and the hot medium further drives instabilities along the
-surface, which can be seen when comparing $t = 0.59$ Myr and $t =
-0.91$ Myr slices.  At the latter time, the jet cannot reach the bottom
-of the domain before being photo-evaporated.  Eventually this
-structure is completely destroyed, leaving behind a turbulent medium
-between the hot and cold regions.
+reflections create a Richtmyer-Meshkov instability \citep[see][for a
+review]{RMI}, driving a chaotic jet-like structure downwards.  The
+radiation source photo-evaporates the outer parts of this structure.
+The interaction between the dense cool ``jet'' and the hot medium
+further drives instabilities along the surface, which can be seen when
+comparing $t = 0.59$ Myr and $t = 0.91$ Myr slices.  At the latter
+time, the jet cannot reach the bottom of the domain before being
+photo-evaporated.  Eventually this structure is completely destroyed,
+leaving behind a turbulent medium between the hot and cold regions.
 
@@
 buoyancy in the already $T=10^4$ K gas.  The gas first to be ionized
-and photo-evaporates is the outer regions of the instability.  The
+and photo-evaporated are the outer regions of the instability.  The
 enhanced heating also drives the upper regions of the instability,
@@
 dense gas is optically thick.
+
+\li Perhaps add more description?
 
@@
 born at 2.5 Myr.  The interior is rarefied ($\rho \sim
-10^{-3}~\cubecm$).  It is heated to $T \sim 5 \times 10^5$ K by the
+10^{-3}~\cubecm$) and is heated to $T \sim 5 \times 10^5$ K by the
 reverse shock.  At $t = 3$ Myr, the ionization front is still R-type,
-and it ionizes the blastwave's dense shell.  Because the interior is
-ionized and diffuse, the ionization front rapidly propagates through
-it until it reaches the opposite shell surface.  Shortly afterward,
-the ionization front transitions from R-type to D-type at a radius of
-0.5 kpc, seen in the formation of a shock in the 5 Myr density panel.
-This transition occurs by the construction of the problem not by the
-interaction with the blastwave.  The surfaces of the blastwave that
-are perpendicular to the ionization front have the highest column
-density and thus are last to be fully ionized.  The pressure forces
-from warm ambient medium and blastwave interior compress these
-surfaces, photo-evaporating them in the process, similar to Test 7.
-They survive until the final time $t = 7.5$ Myr.  As the R-type
-ionization front interacts with the blastwave interior, the density
-perturbations create ionization front instabilities
+and it ionizes the rear side of the dense shell.  Because the interior
+is ionized and diffuse, the ionization front rapidly propagates
+through it until it reaches the opposite shell surface.  Shortly
+afterward, the ionization front transitions from R-type to D-type at a
+radius of 0.5 kpc, seen in the formation of a shock in the 5 Myr
+density panel.  This transition occurs by the construction of the
+problem not by the interaction with the blastwave.  The surfaces of
+the blastwave that are perpendicular to the ionization front have the
+highest column density and thus are last to be fully ionized.  The
+pressure forces from warm ambient medium and blastwave interior
+compress these surfaces, photo-evaporating them in the process,
+similar to Test 7.  They survive until the final time $t = 7.5$ Myr.
+As the R-type ionization front interacts with the blastwave interior,
+the density perturbations create ionization front instabilities
 \citep{Whalen08_Instab} that are seen on the \ion{H}{2} region surface
@@
 and $r = 250$ pc, at the center of the box.  Radiation is emitted in
-two polar cones with $\theta_c = \pi/6$ with a total luminosity of
-$10^{49}$ erg s$^{-1}$ and a 17.6 eV mono-chromatic spectrum.  This
-results in $t_{\rm rec} = 1.22$ Myr and $R_s = 315$ pc, just outside
-of the sphere.  The base grid has a resolution of 64$^3$, and it is
-refined with the same overdensity criterion as Test 8.  We run this
-test for 25 Myr.
+two polar cones with $\theta_c = \pi/6$ with 768 (HEALPix level 3)
+initial rays, a total luminosity of $10^{49}$ erg s$^{-1}$, and a 17.6
+eV mono-chromatic spectrum.  This results in $t_{\rm rec} = 1.22$ Myr
+and $R_s = 315$ pc, just outside of the sphere.  The base grid has a
+resolution of 64$^3$, and it is refined with the same overdensity
+criterion as Test 8.  We run this test for 25 Myr.
 
@@
 overdensities on the \ion{H}{2} transverse surface.  When it breaks
-out of the overdensity, it creates a champagne flow, where the
+out of the overdensity, a champagne flow develops, where the
 ionization front transitions back to a weak R-type front.  The cloud
@@
 clump center.  At later times, the transverse D-type front continues
-through the clump, eventually creating a disk-like structure at the
-final time.  The polar champagne flows proceed to flow outwards,
-creating a density shell with a diffuse ($10^{-28}$ \cubecm) and warm
+through the clump, eventually forming a disk-like structure at the
+final time.  The polar champagne flows proceed to flow outwards and
+produces a dense shell with a diffuse ($10^{-28}$ \cubecm) and warm
 (5000 K) medium in its wake.
@@
 tracing timestep, which saves the photon packages between timesteps if
-the $c\;dt_{\rm P} < L_{\rm box}$.  This effect only becomes apparent
-when the variation timescale of the point source is smaller than the
-light crossing time of the simulation.  Furthermore, the timestep
-should resolve the variation timescale by a few times.  This property
-might be important in large box simulations with variable sources,
-e.g. AGN radiative feedback.  To test this, we can use an
-exponentially varying source with some duty cycle.  In a functional
-form, this can be described as
+$c\;dt_{\rm P} < L_{\rm box}$.  This effect only becomes apparent when
+the variation timescale of the point source is smaller than the light
+crossing time of the simulation.  Furthermore, the timestep should
+resolve the variation timescale by at least a few times.  This
+property might be important in large box simulations with variable
+sources, e.g. AGN radiative feedback.  To test this, we can use an
+exponentially varying source with some duty cycle $t_0$.  In a
+functional form, this can be described as
 %
@@
 %
-where $t_f = 2 \times |t - t_0 \times \mathrm{round}(t/t_0)|$, $t_0$
-is the duty cycle, and $A=4$ controls the width of the radiation
-pulse.  To illustrate the effects of source variability, we remove any
-dependence on the medium by considering an optically-thin uniform
-density $\rho 10^{-4}~\cubecm$.  We take $L_{\rm box} = 1$ Mpc, which
-has a light crossing time of 3.3 Myr.  A source is placed at the
-origin with $L_{\rm max} = 10^{55}$ ph s$^{-1}$ and $t_0 = 0.5$ Myr.
-We use a radiative transfer timestep of 50 kyr to resolve the duty
-cycle by 10 timesteps.  The simulation is run for 6 Myr, so the
-radiation propagates throughout the box.
+where $t_f = 2 \times |t - t_0 \times \mathrm{round}(t/t_0)|$, and
+$A=4$ controls the width of the radiation pulse.  To illustrate the
+effects of source variability, we remove any dependence on the medium
+by considering an optically-thin uniform density $\rho =
+10^{-4}~\cubecm$.  We take $L_{\rm box} = 1$ Mpc, which has a light
+crossing time of 3.3 Myr.  A source is placed at the origin with
+$L_{\rm max} = 10^{55}$ ph s$^{-1}$ and $t_0 = 0.5$ Myr.  We use a
+radiative transfer timestep of 50 kyr to resolve the duty cycle by 10
+timesteps.  The simulation is run for 6 Myr, so the radiation
+propagates throughout the box.
 
@@
 
+\li Add more description of the problem.
+
 \subsection{Test 14. \ion{H}{2} region with MHD}
@@
 \citep{Wang09} in \enzo~v2.0 that uses an unsplit conservative
-hydrodynamics solver and a hyperbolic $\nabla \cdot \mathbf{B} = 0$
+hydrodynamics solver and the hyperbolic $\nabla \cdot \mathbf{B} = 0$
 cleaning method of \citet{Dedner02}.  This marriage of radiation
@@
 
-As the \ion{H}{2} region grows the magnetized medium, shown in Figures
-\ref{fig:test14_1} and \ref{fig:test14_2}, it transforms from
+As the \ion{H}{2} region grows in the magnetized medium, shown in
+Figures \ref{fig:test14_1} and \ref{fig:test14_2}, it transforms from
 spherical to oblate as it is magnetically confined in directions
@@
 observed some carbuncle artifacts along the ionization front; whereas
-we see smooth density gradients, which is most likely caused by our
-more diffusive choice of the HLL Riemann solver when compared to Roe's
+we see smooth density gradients, which is most likely caused by both
+the geometric correction to the ray tracing (\S\ref{sec:meth_fc}) and
+the diffusivity of the HLL Riemann solver when compared to Roe's
 Riemann solver used in \citet{Krumholz07_ART}, who also use PLM as a
@@
 \subsection{Spatial resolution}
+\label{sec:dx_dep}
 
@@
 than the higher resolution cases.  This shows that our method gives
-accurate results, even in marginally resolved cases.
+accurate results, even in marginally resolved cases, which is expected
+with a photon conserving method.  Furthermore this demonstrates that
+the geometric correction does not significantly affect photon
+conservation.
 
@@
 medium has $\rho = 10^{-3}~\cubecm$, $T = 10^4$ K, and $1 - x_e =
-10^{-4}$.  The radiation source is located in the center of a 6.6 kpc
-domain.  The simulation is only run for one timestep because the
+10^{-4}$.  The simulation is only run for one timestep because the
 radiation field should be static in this optically-thin test.
@@
 in Tests 1, 2, and 5 with only one energy group; however a
-multi-frequency spectrum can create differences in the reactive
-flows.  We use Test 5 (\S\ref{sec:test5}; an expanding \ion{H}{2}
-region with hydrodynamics) to probe any differences in the solution
-when varying the resolution of the spectrum.  In RT09, ZEUS-MP was
-used to demonstrate the effect of a multi-frequency spectrum on the
-dynamics of the ionization front in this test.  Instead of a single
-shock seen in the mono-chromatic spectrum, a the shock obtained a
-double-peaked structure in density and radial velocity.  We rerun Test
-5 with a $T=10^5$ K blackbody spectrum sampled by $n_\nu = 1$, 2, 4,
-8, and 16 frequency bins.  We use the following energies:
+multi-frequency spectrum can create differences in the reactive flows.
+We use Test 5 (\S\ref{sec:test5}; an expanding \ion{H}{2} region with
+hydrodynamics) to probe any differences in the solution when varying
+the resolution of the spectrum.  In RT09, ZEUS-MP was used to
+demonstrate the effect of a multi-frequency spectrum on the dynamics
+of the ionization front in this test.  Instead of a single shock seen
+in the mono-chromatic spectrum, the shock obtains a double-peaked
+structure in density and radial velocity.  We rerun Test 5 with a
+$T=10^5$ K blackbody spectrum sampled by $n_\nu = 1$, 2, 4, 8, and 16
+frequency bins.  We use the following energies:
 %
@@
 ionization front greatly.  However in our and others' past experience
-\citep[e.g.]{Shapiro04, Mellema06, Petkova09}, the timestep,
+\citep[e.g.][]{Shapiro04, Mellema06, Petkova09}, the timestep,
 especially too small of one, can drastically underestimate the
@@
 changes in \ion{H}{2} ($dn_{\rm H}/dt$ based; \S\ref{sec:dt_hi}),
-constant timesteps (\S\ref{sec:dt_const}), and based on incident
-radiation ($dI/dt$ based; \S\ref{sec:dt_tau}).  The growth of the
-ionization front radius is shown in Figure \ref{fig:dt_dep1}.  Both
-the \ion{H}{2} restricted and incident radiation variable time-stepping
-methods agree within a few percent throughout the entire simulation,
-as does the run with constant $dt = 0.1$ Myr timesteps.  With the
-larger constant timesteps, the numerical solution lags behind the
-analytical one, but they converge to an accurate \ion{H}{2} radii at
-late times.  Even $dt = 5$ Myr timestep, which underestimated it by
-35\% at 50 Myr, is within a percent of the analytical solution.
+constant timesteps of 0.1, 0.5, 1, and 5 Myr (\S\ref{sec:dt_const}),
+and based on incident radiation ($dI/dt$ based; \S\ref{sec:dt_tau}).
+The growth of the ionization front radius is shown in Figure
+\ref{fig:dt_dep1}.  Both the \ion{H}{2} restricted and incident
+radiation variable time-stepping methods agree within a few percent
+throughout the entire simulation, as does the run with constant $dt_P
+= 0.1$ Myr timesteps.  With the larger constant timesteps, the
+numerical solution lags behind the analytical one, but they converge
+to an accurate \ion{H}{2} radii at late times.  Even $dt_P = 5$ Myr
+timestep, which underestimated it by 35\% at 50 Myr, is within a
+percent of the analytical solution.
 
@@
 $(1-e^{-\tau})$ absorption factor.  In this section, we repeat the
-angular resolution tests in \S\ref{sec:ang_dep}.  Slices of the
-photo-ionization rates through the origin are shown in Figure
-\ref{fig:fc_slices}, depicting the improvements in spherical symmetry
-and a closer agreement to a smooth $1/r^2$ profile.  Previous attempts
-to reduce these artifacts either introduced a random rotation of the
-HEALPix pixelization \citep[e.g.][]{Abel02_RT, Trac07, Krumholz07_ART}
-or by increasing the ray-to-cell sampling.
+angular resolution tests in \S\ref{sec:ang_dep} with $\Phi_c = 5.1$.
+Slices of the photo-ionization rates through the origin are shown in
+Figure \ref{fig:fc_slices}, depicting the improvements in spherical
+symmetry and a closer agreement to a smooth $1/r^2$ profile.  Previous
+attempts to reduce these artifacts either introduced a random rotation
+of the HEALPix pixelization \citep[e.g.][]{Abel02_RT, Trac07,
+  Krumholz07_ART} or by increasing the ray-to-cell sampling.
 
@@
 
-In practice, we have found it difficult to transition from this
+In practice, we have found it difficult to transition from the
 optically-thin approximation to the optically-thick regime without
@@
 a $1/r^2$ profile until it reaches $\tau_{\rm thin} \equiv 0.1$, which
-is denoted by the white quarter circle in the figure.  At this radius,
-the rays are then split until a sampling of $\Phi_c$ is satisfied.
-Angular spike artifacts beyond this radius arise because of the
-interface between the optically-thin approximation and full ray
-tracing treatment.  They originate in cells that intersect the
-$\tau_{\rm thin}$ surface, which are split into the optically thin and
-thick definitions.  Unfortunately we have not determined a good
-technique to avoid such artifacts.  They occur because of the
-following reason.  When the first ray with $\tau < 0.1$ exits such a
-cell, it applies the optically-thin approximation and marks the cell
-so no other ray from the same source contributes to its \kph~and
-$\Gamma$ field.  However other rays may exit the cell with $\tau >
-0.1$ because the maximum distance between the far cell faces and the
-source is not always $\tau < 0.1$.  Then these rays will split in this
-cell and add to \kph~and become attenuated, reducing its photon
-fluxes.  When the rays continue to the next cell after this
-transition, the photon fluxes are not necessarily equal to each other,
-creating the angular artifacts seen in Figure \ref{fig:rayopt}.  We
-are continuing to formulate a scheme that avoids these artifacts
-because this approximation will be very advantageous in simulations
-with large ionized filling factors.
+is denoted by the white quarter circle in the figure.  Within this
+radius, only $\Phi_c = 1$ is required.  Then at this radius, the rays
+are then split until a sampling of $\Phi_c$ is satisfied.  Angular
+spike artifacts beyond this radius arise because of the interface
+between the optically-thin approximation and full ray tracing
+treatment.  They originate in cells that intersect the $\tau_{\rm
+  thin}$ surface, which are split into the optically thin and thick
+definitions.  Unfortunately we have not determined a good technique to
+avoid such artifacts.  They occur because of the following reason.
+When the first ray with $\tau < 0.1$ exits such a cell, it applies the
+optically-thin approximation and marks the cell so no other ray from
+the same source contributes to its \kph~and $\Gamma$ field.  However
+other rays may exit the cell with $\tau > 0.1$ because the maximum
+distance between the far cell faces and the source is not always $\tau
+< 0.1$.  Then these rays will split in this cell and add to \kph~and
+become attenuated, reducing its photon fluxes.  When the rays continue
+to the next cell after this transition, the photon fluxes are not
+necessarily equal to each other, creating the angular artifacts seen
+in Figure \ref{fig:rayopt}.  We are continuing to formulate a scheme
+that avoids these artifacts because this approximation will be very
+advantageous in simulations with large ionized filling factors.
 
@@
 radius.  The domain has a size of 8 pc with a uniform density $\rho =
-2900 \cubecm$ and initial temperature $T = 10^3$ K.  The source is
+2900\;\cubecm$ and initial temperature $T = 10^3$ K.  The source is
 located at the origin with a luminosity $L = 10^{50}$ ph s$^{-1}$ and
@@
 evolution of the \ion{H}{2} is matches the analytical expectations
-described in \S\ref{sec:test5}.  At $t=140$ kyr, the ionization front
-radius is increased by $\sim5\% = 0.16$ pc.  However radiation
-pressure impacts the system the greatest inside the ionization front.
-At $t = 40$ kyr, the central density is smaller by a factor of 20 with
-radiation pressure, but the temperatures are almost equal.  A
-rarefaction wave thus propagates toward the center, depicted by the
-negative radial velocities at $t = 60$ kyr.  This raises the central
-density to $10^{-21}$ g \cubecm~at $t = 80$ kyr.  Afterwards, the
-radiation continues to force gas outwards.  From $t = 100$ kyr to $t =
-140$ kyr, the maximum radial velocity of the ionized gas increases
-from 10 \kms~to 50 \kms.  This leaves behind an even more diffuse
-medium, lowering the gas density by a factor of 10 at $t = 140$ kyr.
-Thus the recombination rates are lower, resulting in increased
-ionization fractions and temperatures in the \ion{H}{2} region.
+described in \S\ref{sec:test5}.  At $t=140$ kyr with radiation
+pressure, the ionization front radius is increased by $\sim5\% = 0.16$
+pc.  However radiation pressure impacts the system the greatest inside
+the ionization front.  At $t = 40$ kyr, the central density is smaller
+by a factor of 20 with radiation pressure, but the temperatures are
+almost equal.  A rarefaction wave thus propagates toward the center,
+depicted by the negative radial velocities at $t = 60$ kyr.  This
+raises the central density to $10^{-21}$ g \cubecm~at $t = 80$ kyr.
+Afterwards, the radiation continues to force gas outwards.  From $t =
+100$ kyr to $t = 140$ kyr, the maximum radial velocity of the ionized
+gas increases from 10 \kms~to 50 \kms.  This leaves behind an even
+more diffuse medium, lowering the gas density by a factor of 10 at $t
+= 140$ kyr.  Thus the recombination rates are lower, resulting in
+increased ionization fractions and temperatures in the \ion{H}{2}
+region.
 
@@
 construct a test problem with a $64^3$ block per core.  The grid is
-not adaptively refined.  The physical setup of the problem is the same
-as Test 5 with a uniform density $\rho = 10^{-3} \cubecm$ and initial
-temperature $T = 100$ K.  Each block has the same size of 15 kpc as
-Test 5.  At the center of each grid, there exists a radiation source
-with a luminosity $L = 5 \times 10^{48}$ ph s$^{-1}$ and a 17 eV
-mono-chromatic spectrum.  The problem is run for 250 Myr.  We run this
-test with $N_p = 2^n$ cores with $n = [0,1 \dots 10,11]$.  The domain
-has $(N_x, N_y, N_z)$ blocks that is determined with the MPI routine
-\texttt{MPI\_Dims\_create}.  For example with $n = 7$, the problem is
-decomposed into $(N_x, N_y, N_z) = (4,4,8)$ blocks, producing a $256
-\times 256 \times 512$ grid.  We have run these on the original
-(Harpertown CPUs) nodes of the NASA NAS machine, Pleiades, with 8
-cores per node.  Figure \ref{fig:weak} shows the performance timings
-of various parts of the code.  From one to two cores, the total time
-only increases by $\sim$1\% due to the overhead associated with the
-inter-processor message passing.  From two to eight cores, the
-performance decreases in the hydrodynamics solver, chemistry and
-energy solver, and obtaining the hydrodynamic boundary conditions
-because of cache locality problems of the data being passed to the
-CPU.  This occurs because of the CPU architecture, specifically the L1
-cache and core connectivity.  We see less of a penalty in newer
-processors, e.g. Intel Nehalam and Westmere CPUs.  Unfortunately there
-exists a $N_p^{1.5}$ dependence in the ray communication routines.  It
-becomes the dominant process above 512 processes.  We are actively
-pursing a solution to this scaling problem.  The other parts of the
-code exhibit excellent weak scaling.  Overall it scales well to 512
-processes, and we plan to enhance the weak scalability of Enzo+Moray
-in the near future to larger processor counts.
+not adaptively refined.  The physical setup of the problem is nearly
+the same as Test 5 with a uniform density $\rho = 10^{-3} \;\cubecm$
+and initial temperature $T = 100$ K.  Each block has the same size of
+15 kpc as Test 5.  At the center of each grid, there exists a
+radiation source with a luminosity $L = 5 \times 10^{48}$ ph s$^{-1}$
+and a 17 eV mono-chromatic spectrum.  The problem is run for 250 Myr.
+We run this test with $N_p = 2^n$ cores with $n = [0,1 \dots 10,11]$.
+The domain has $(N_x, N_y, N_z)$ blocks that is determined with the
+MPI routine \texttt{MPI\_Dims\_create}.  For example with $n = 7$, the
+problem is decomposed into $(N_x, N_y, N_z) = (4,4,8)$ blocks,
+producing a $256 \times 256 \times 512$ grid.  We have run these on
+the original (Harpertown CPUs) nodes of the NASA NAS machine,
+Pleiades, with 8 cores per node.  Figure \ref{fig:weak} shows the
+performance timings of various parts of the code.  From one to two
+cores, the total time only increases by $\sim$1\% due to the overhead
+associated with the inter-processor message passing.  From two to
+eight cores, the performance decreases in the hydrodynamics solver,
+chemistry and energy solver, and obtaining the hydrodynamic boundary
+conditions because of cache locality problems of the data being passed
+to the CPU.  This occurs because of the CPU architecture, specifically
+the L1 cache and core connectivity.  We see less of a penalty in newer
+processors, e.g. Intel Nehalam and Westmere CPUs.  Above eight
+processes, these routines exhibit near perfect weak scaling to 2048
+cores.  Unfortunately there exists a $N_p^{1.5}$ dependence in the ray
+communication routines.  It becomes the dominant process above 512
+processes.  We are actively pursing a solution to this scaling
+problem.  The other parts of the code exhibit excellent weak scaling.
+Overall it scales well to 512 processes, and we plan to enhance the
+weak scalability of Enzo+Moray in the near future to larger processor
+counts.
 
@@
 
-In this paper, we have presented our implementation of adaptive ray
-tracing \citep{Abel02_RT} and its coupling to the hydrodynamics in the
-cosmology AMR code \enzo, making it a fully functional radiation
-hydrodynamics code.  As this method is photon conserving, accurate
-solutions are possible with coarse spatial resolution.  A new
-geometric correction factor to ray tracing on a Cartesian grid was
-described, and it is general to any implementation.  We have
-exhaustively tested the code to problems with known analytical
+In this paper, we have presented our implementation, Enzo+Moray, of
+adaptive ray tracing \citep{Abel02_RT} and its coupling to the
+hydrodynamics in the cosmology AMR code \enzo, making it a fully
+functional radiation hydrodynamics code.  As this method is photon
+conserving, accurate solutions are possible with coarse spatial
+resolution.  A new geometric correction factor to ray tracing on a
+Cartesian grid was described, and it is general to any implementation.
+We have exhaustively tested the code to problems with known analytical
 solutions and the problems presented in the RT06 and RT09 radiative
@@
 scaling in AMR calculations, given a large enough problem.  The
-combination of the AMR and adaptive ray tracing allows for
-high-resolution and high-dynamical range problems, e.g. molecular
-cloud resolving galaxy formation simulations and \ion{H}{2} regions of
-Population III stars.  Furthermore, we have included Lyman-Werner
-absorption, secondary ionizations from X-ray radiation, Compton
-heating from photon scattering, and radiation pressure, into the code,
-which extends the reach of Enzo+Moray to study AGN feedback, stellar
-winds, and local star formation.  Coupling the radiative transfer with
-MHD further broadens the applicability of our code.  The full
-implementation is included in the latest public version of
-\enzo\footnote{http://lca.ucsd.edu/enzo}, providing the community with
-a full-featured radiation hydrodynamics AMR code.
+combination of AMR and adaptive ray tracing allows for high-resolution
+and high-dynamical range problems, e.g. present-day star formation,
+molecular cloud resolving cosmological galaxy formation, and
+\ion{H}{2} regions of Population III stars.  Furthermore, we have
+included Lyman-Werner absorption, secondary ionizations from X-ray
+radiation, Compton heating from photon scattering, and radiation
+pressure into the code, which extends the reach of Enzo+Moray to study
+AGN feedback, stellar winds, and local star formation.  Coupling the
+radiative transfer with MHD further broadens the applicability of our
+code.  The full implementation is included in the latest public
+version of \enzo\footnote{http://lca.ucsd.edu/enzo}, providing the
+community with a full-featured radiation hydrodynamics AMR code.
 

### 2010-10-26 ms.tex
Updated author list.

@@
 
-\author{John H. Wise\altaffilmark{1,2}, 
-  Tom Abel\altaffilmark{3}, 
-  Ji-hoon Kim\altaffilmark{3}, 
-  Peng Wang\altaffilmark{3,4},
-  Peter Iannucci\altaffilmark{5}}
-
-\altaffiltext{1}{Department of Astrophysical Sciences, Princeton
-  University, Peyton Hall, Ivy Lane, Princeton, NJ 08544}
-\altaffiltext{2}{Hubble Fellow}
-\altaffiltext{3}{Kavli Institute for Particle Astrophysics and
-  Cosmology, Stanford University, Menlo Park, CA 94025}
-\altaffiltext{4}{NVIDIA}
-\altaffiltext{5}{Massachusetts Institute of Technology}
+\author{John H. Wise\altaffilmark{1}} 
+\affil{Department of Astrophysical Sciences, Princeton University,
+  Peyton Hall, Ivy Lane, Princeton, NJ 08544}
+
+\author{Ji-hoon Kim and Tom Abel} 
+\affil{Kavli Institute for Particle Astrophysics and Cosmology,
+  Stanford University, Menlo Park, CA 94025}
+
+\altaffiltext{1}{Hubble Fellow}
 \email{jwise@astro.princeton.edu}

### 2010-11-13 mnras.tex
Added MNRAS version

--- 2010-10-26 ms.tex
@@
-\documentclass[apj,onecolumn]{emulateapj}
-%\documentclass[12pt,preprint]{aastex}
+\documentclass[useAMS,usenatbib]{mn2e}
 
@@
 \usepackage{natbib}
-\usepackage[section] {placeins}
-\bibliographystyle{apj}
-\citestyle{apj}
+%\usepackage[section] {placeins}
+\bibliographystyle{mn2e}
+\citestyle{mn2e}
 
@@
 
-\shorttitle{AMR SIMULATIONS WITH ADAPTIVE RAY TRACING}
-\shortauthors{WISE ET AL.}
-
-\title{Enzo+Moray: Radiation Hydrodynamics Adaptive Mesh Refinement
-  Simulations with Adaptive Ray Tracing}
-
-\author{John H. Wise\altaffilmark{1}} 
-\affil{Department of Astrophysical Sciences, Princeton University,
-  Peyton Hall, Ivy Lane, Princeton, NJ 08544}
-
-\author{Ji-hoon Kim and Tom Abel} 
-\affil{Kavli Institute for Particle Astrophysics and Cosmology,
-  Stanford University, Menlo Park, CA 94025}
-
-\altaffiltext{1}{Hubble Fellow}
-\email{jwise@astro.princeton.edu}
+\title[AMR Simulations with Adaptive Ray Tracing] {Enzo+Moray:
+  Radiation Hydrodynamics Adaptive Mesh Refinement Simulations with
+  Adaptive Ray Tracing}
+
+\author[J. H. Wise and T. Abel] {John H. Wise$^1$\thanks{Hubble
+    Fellow; e-mail: jwise@astro.princeton.edu} and Tom Abel$^2$\\
+$^{1}$ Department of Astrophysical Sciences, Princeton University,
+Peyton Hall, Ivy Lane, Princeton, NJ 08544, USA\\
+$^{2}$ Kavli Institute for Particle Astrophysics and Cosmology,
+Stanford University, Menlo Park, CA 94025, USA}
+
+\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2010}
+
+\maketitle
+\label{firstpage}
 
@@
   luminosities, and collimated radiation.  The test suite also
-  includes an expanding \ion{H}{2} region in a magnetized medium,
+  includes an expanding \hii region in a magnetized medium,
   utilizing the newly implemented magnetohydrodynamics module in
@@
 
-\keywords{cosmology --- methods: numerical --- hydrodynamics ---
-  radiative transfer}
+\begin{keywords}
+  cosmology --- methods: numerical --- hydrodynamics --- radiative
+  transfer.
+\end{keywords}
 
@@
 treatment in multi-dimensional calculations is difficult because of
-the dependence on seven variables --- three spatial, two angular,
+the dependence on seven variables -- three spatial, two angular,
 frequency, and time.  The non-local nature of the thermal and
@@
 recombinations balance photo-ionizations.  He derived a radius of an
-\ion{H}{2} region,
+\hii region,
 %
@@
 decade later, the first radiation hydrodynamical numerical models of
-\ion{H}{2} regions in spherical symmetry and plane-parallel ionization
+\hii regions in spherical symmetry and plane-parallel ionization
 fronts were developed \citep[e.g.][]{Mathews65, Lasker66,
@@
 sound speed.  These works established the evolutionary track of an
-expanding \ion{H}{2} illuminated by a massive star in a uniform
+expanding \hii illuminated by a massive star in a uniform
 medium:
@@
 \begin{enumerate}
-\item Weak R-type---When the star (gradually) starts to shine, the
+\item Weak R-type:  When the star (gradually) starts to shine, the
   ionization front will move supersonically through the ambient
@@
   undisturbed.  This stage continues until $r \sim 0.02R_s$.
-\item Critical R-type---As the ionization front moves outwards, it
+\item Critical R-type:  As the ionization front moves outwards, it
   begins to slow because of the geometric dilution of the radiation.
@@
   isothermal shock in the neutral gas.
-\item Strong and weak D-type---The front continues to slow, becoming a
+\item Strong and weak D-type:  The front continues to slow, becoming a
   strong D-type front, and then a critical D-type front.  From this
@@
   front.
-\item Expansion phase---After the shock forms, the \ion{H}{2} region
+\item Expansion phase:  After the shock forms, the \hii region
   starts to expand, lowering the interior density and thus the
@@
 studied extensively were champagne flows.  Here the source is embedded
-in an overdense region, and the \ion{H}{2} region escapes from this
+in an overdense region, and the \hii region escapes from this
 region in one direction.  The interface between the ambient and dense
@@
 \begin{itemize}
-\item Moment methods---The angular moments of the radiation field can
+\item Moment methods:  The angular moments of the radiation field can
   describe its angular structure, which are related to the energy
@@
   diffusive and result in incorrect shadows in some situations.
-\item Ray tracing---Radiation can be propagated along rays that extend
+\item Ray tracing:  Radiation can be propagated along rays that extend
   through the computational grid \citep[e.g.][]{Razoumov99, Abel99_RT,
@@
 hydrodynamical problems.  We have used this code to investigate the
-growth of an \ion{H}{2} region from a 100\Ms~Population III (Pop III)
+growth of an \hii region from a 100\Ms~Population III (Pop III)
 star \citep{Abel07}, the early stages of reionization from Pop III
@@
 
-\input table1.tex
+\input table1_mnras.tex
 
@@
 
-\begin{figure}[t]
+\begin{figure}
   \plottwo{fig/covering.eps}{fig/calc_fc.eps}
@@
 rays enter a single cell.  In the case of a single radiation source,
-the solution is simple --- only assign the cell the photo-ionization
+the solution is simple -- only assign the cell the photo-ionization
 and photo-heating rates when $k_{\rm ph} = 0$.  However in the case
@@
   \label{eqn:lwband}
-  f_{\rm shield}(N_{\rm H2}) = \left\{ \begin{array}{l@{\quad}l}
-      1 & (N_{\rm H2} \le 10^{14} \; \mathrm{cm}^{-2})\\
-      (N_{\rm H2}/10^{14} \; \mathrm{cm}^{-2})^{-0.75} & (N_{\rm H2} >
-        10^{14} \; \mathrm{cm}^{-2})
-    \end{array} \right. .
-\end{equation}
-To incorporate this shielding function into the ray tracer, we store
-the total \hh~column density and calculate the \hh~dissociation rate
-by summing the contribution of all rays,
+  f_{\rm shield} (N_{\rm H2}) =
+  \left\{ \begin{array}{l@{\quad}l}
+      1 & (N_{\rm H2} \le 10^{14})\\
+      (N_{\rm H2}/10^{14})^{-0.75} & (N_{\rm H2} >
+      10^{14})
+    \end{array} \right. ,
+\end{equation}
+where $N_{\rm H2}$ is in units of cm$^{-2}$.  To incorporate this
+shielding function into the ray tracer, we store the total \hh~column
+density and calculate the \hh~dissociation rate by summing the
+contribution of all rays,
 %
@@
 that the excitation of hydrogen and helium and the ionization of
-\ion{He}{2} is negligible.  The number of secondary ionizations of H
+He {\sc ii} is negligible.  The number of secondary ionizations of H
 and He is reduced from the ratio of the photon and ionization energies
@@
 
-\begin{figure}[t]
+\begin{figure*}
+  \epsscale{2}
   \plotone{fig/RTcoupling.eps}
+  \epsscale{1}
   \caption{\label{fig:MainAlgorithm} Flow chart for the overall
@@
     \ref{fig:RTalgorithm}.}
-\end{figure}
-
-\begin{figure}[t]
-  \epsscale{1.1}
+\end{figure*}
+
+\begin{figure*}
+  \epsscale{2}
   \plotone{fig/RTalgorithm.eps}
+  \epsscale{1}
   \caption{\label{fig:RTalgorithm} Flow chart for the ray tracing
@@
     remainder is a typical ray tracing method.}
-  \epsscale{1}
-\end{figure}
+\end{figure*}
 
@@
 \step{3g} Add the effects of any optional physics modules
-(\S\ref{sec:addphysics})---secondary ionizations from X-rays, Compton
+(\S\ref{sec:addphysics}) -- secondary ionizations from X-rays, Compton
 heating from scattering, and radiation pressure.
@@
 for early termination of rays that are fully absorbed, which are
-likely to have high absorption cross-sections (e.g. \ion{H}{1}
-ionizations near 13.6 eV) or a low initial intensity (e.g. \ion{He}{2}
-ionizing photons in typical stellar populations).  The other approach
-used by some groups \citep[e.g.][]{Trac07} is to store all energy
-groups in a single ray.  This reduces the number of the rays generated
-and the computation associated with the ray tracing.  Unless the ray
+likely to have high absorption cross-sections (e.g. \hi ionizations
+near 13.6 eV) or a low initial intensity (e.g. He {\sc ii} ionizing
+photons in typical stellar populations).  The other approach used by
+some groups \citep[e.g.][]{Trac07} is to store all energy groups in a
+single ray.  This reduces the number of the rays generated and the
+computation associated with the ray tracing.  Unless the ray
 dynamically adjusts its memory allocation for the energy groups as
@@
 \citep[e.g.][for hydrogen ionizing radiation only]{Abel07,
-  Wise08_Gal}, we have 3 energy groups---\ion{H}{1}, \ion{He}{1},
-\ion{He}{2}---each with an energy that equals the average photon
-energy above the ionization threshold.
+  Wise08_Gal}, we have 3 energy groups -- H {\sc i}, He {\sc i}, He
+{\sc ii} -- each with an energy that equals the average photon energy
+above the ionization threshold.
 
@@
 chemo-thermal state of the system remains constant as the rays are
-traced through the cells.  In the case of a single \ion{H}{2} region,
+traced through the cells.  In the case of a single \hii region,
 the speed of the ionization front is limited to approximately
@@
 
-\begin{figure}[t]
+\begin{figure*}
+  \epsscale{2}
   \plottwo{fig/dtp_test3noavg.eps}{fig/dtp_test3.eps}
+  \epsscale{1}
   \caption{\label{fig:dtsmooth} Radiative transfer adaptive timestep
@@
     into the next neutral cell in the overdensity.}
-\end{figure}
+\end{figure*}
 
@@
 large timestep, particularly if the system is not critically affected
-by a slower I-front velocity.  One example is an expanding \ion{H}{2}
+by a slower I-front velocity.  One example is an expanding \hii
 region in a power-law density gradient.  After a brief, initial R-type
@@
 speed of light in steep density gradients and in the early expansion
-of the \ion{H}{2} region.  If the ionization front position is
+of the \hii region.  If the ionization front position is
 critical to the calculation, the radiation transport timestep can be
@@
 shadowing created by a dense, optically thick clump, and (4) multiple
-\ion{H}{2} regions in a cosmological density field.  In all of the
+\hii regions in a cosmological density field.  In all of the
 tests presented here, we use the method of restricted neutral fraction
@@
 
-\subsection{Test 1. Pure hydrogen isothermal \ion{H}{2} region
+\subsection{Test 1. Pure hydrogen isothermal \hii region
   expansion}
@@
 
-\begin{figure}[t]
+\begin{figure*}
+  \epsscale{2}
   \plottwo{fig/test1_ionfrac.eps}{fig/test1_ifront.eps}
-  \caption{\label{fig:test1_ifront} Test 1 (\ion{H}{2} region
+  \epsscale{1}
+  \caption{\label{fig:test1_ifront} Test 1 (\hii region
     expansion with a monochromatic spectrum of 13.6 eV).  Left:
@@
     radius.  The ratio of these radii are plotted in the bottom panel.}
-\end{figure}
-
-\begin{figure}[t]
-  \epsscale{0.8}
+\end{figure*}
+
+\begin{figure}
+  %\epsscale{0.8}
   \plotone{fig/test1_HI500.eps}
-  \caption{\label{fig:test1_HI} Test 1 (\ion{H}{2} region expansion
+  \caption{\label{fig:test1_HI} Test 1 (\hii region expansion
     with a monochromatic spectrum of 13.6 eV). Slice of neutral
     fraction at the origin at 500 Myr.}
-  \epsscale{1.0}
+  %\epsscale{1.0}
 \end{figure}
@@
 codes presented in RT06 is the increasing neutral fraction outside of
-the \ion{H}{2}.  This occurs because the initial ionized fraction and
+the \hii.  This occurs because the initial ionized fraction and
 temperature is set to $1.3 \times 10^{-3}$ and 8000 K, which are not
@@
 calculation.  This difference happens because the analytical solution
-(Eq. \ref{eqn:rstr}) assumes the \ion{H}{2} region has a constant
+(Eq. \ref{eqn:rstr}) assumes the \hii region has a constant
 ionized fraction.  The evolution of the ionized fraction as a function
@@
 
-\subsection{Test 2. \ion{H}{2} region expansion: temperature evolution}
-
-\begin{figure}[t]
+\subsection{Test 2. \hii region expansion: temperature evolution}
+
+\begin{figure*}
+  \epsscale{2}
   \plottwo{fig/test2_ionfrac.eps}{fig/test2_neutral.eps}
-  \caption{\label{fig:test2_1} Test 2. (\ion{H}{2} region
+  \epsscale{1}
+  \caption{\label{fig:test2_1} Test 2. (\hii region
     expansion with a $T=10^5$ K blackbody spectrum).  Left:
@@
     average neutral fraction.}
-\end{figure}
-
-\begin{figure}[t]
+\end{figure*}
+
+\begin{figure}
   \plotone{fig/test2_ifront.eps}
-  \caption{\label{fig:test2_2} Test 2. (\ion{H}{2} region expansion
+  \caption{\label{fig:test2_2} Test 2. (\hii region expansion
     with a $T=10^5$ K blackbody spectrum).  Top: Evolution of the
@@
 
-\begin{figure}[]
+\begin{figure*}
+  \epsscale{2}
   \plotone{fig/test2_slices}
-  \caption{\label{fig:test2_3} Test 2. (\ion{H}{2} region expansion
+  \epsscale{1}
+  \caption{\label{fig:test2_3} Test 2. (\hii region expansion
     with a $T=10^5$ K blackbody spectrum).  Top: Slices through the
@@
     temperature at 10 and 100 Myr.}
-\end{figure}
+\end{figure*}
 
@@
 $t = $ 10 and 100 Myr.  Here one sees the spherically symmetric
-\ion{H}{2} regions and a smooth temperature transition to the neutral
+\hii regions and a smooth temperature transition to the neutral
 ambient medium.
@@
 
-\begin{figure}[t]
+\begin{figure*}
+  \epsscale{2}
   \plottwo{fig/test3_HI.eps}{fig/test3_temp.eps}
+  \epsscale{1}
   \caption{\label{fig:test3_1} Test 3. (I-front trapping in a dense
@@
     (right) of the clump.}
-\end{figure}
-
-\begin{figure}[t]
-  \epsscale{0.85}
+\end{figure*}
+
+\begin{figure}
+  %\epsscale{0.85}
   \plotone{fig/test3_clump.eps}
@@
     (top) and temperature (bottom) of the overdense clump.}
+  %\epsscale{1}
+\end{figure}
+
+\begin{figure*}
+  \epsscale{2}
+  \plotone{fig/test3_slices}
   \epsscale{1}
-\end{figure}
-
-\begin{figure}[t]
-  \plotone{fig/test3_slices}
   \caption{\label{fig:test3_3} Test 3. (I-front trapping in a dense
@@
     temperature (15 Myr), and neutral fraction (15 Myr).}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{figure}[t]
-  \epsscale{0.75}
+\begin{figure}
+  %\epsscale{0.75}
   \plotone{fig/test4_ion}
@@
     (solid) ionized fraction.}
+  %\epsscale{1}
+\end{figure}
+
+\begin{figure*}
+  %\epsscale{0.9}
+  \epsscale{2}
+  \plotone{fig/test4_slices}
   \epsscale{1}
-\end{figure}
-
-\begin{figure}[t]
-  \epsscale{0.9}
-  \plotone{fig/test4_slices}
   \caption{\label{fig:test4_2} Test 4. (Multiple cosmological
@@
     applied to the images.}
-  \epsscale{1}
-\end{figure}
+  %\epsscale{1}
+\end{figure*}
 
@@
 
-We show the growth of the \ion{H}{2} regions by computing the
+We show the growth of the \hii regions by computing the
 mass-averaged $x_m$ and volume-averaged $x_v$ ionized fraction in
@@
 presented in \citet[][hereafter RT09]{Iliev09}.  They involve (1) the
-expansion of an \ion{H}{2} region in a uniform medium, similar to Test
-2, (2) an \ion{H}{2} region in an isothermal sphere, and (3) the
+expansion of an \hii region in a uniform medium, similar to Test
+2, (2) an \hii region in an isothermal sphere, and (3) the
 photo-evaporation of a dense, cold clump, similar to Test 3.  We
@@
 flows, an irradiated blast wave, collimated radiation, and an
-\ion{H}{2} with a variable source.  For the \citeauthor{Iliev09}
+\hii with a variable source.  For the \citeauthor{Iliev09}
 tests, we turn off self-gravity and AMR in accordance with them.  In
@@
 of \enzo.  Last we use the new MHD implementation in \enzo~v2.0 in the
-problem of a growing \ion{H}{2} region in a magnetic field.
-
-\subsection{Test 5. Classical \ion{H}{2} region expansion}
+problem of a growing \hii region in a magnetic field.
+
+\subsection{Test 5. Classical \hii region expansion}
 \label{sec:test5}
 
-\begin{figure}[t]
-  \epsscale{0.8}
+\begin{figure}
+  %\epsscale{0.8}
   \plotone{fig/test5_ifront}
-  \caption{\label{fig:test5_1} Test 5. (\ion{H}{2} region in a uniform
+  \caption{\label{fig:test5_1} Test 5. (\hii region in a uniform
     medium).  Top: Growth of the computed ionization front radius at
@@
     ionization front radii to the analytical estimate.} 
-  \epsscale{1}
+  %\epsscale{1}
 \end{figure}
 
-\begin{figure}[t]
+\begin{figure}
   \plotone{fig/test5_profiles}
-  \caption{\label{fig:test5_2} Test 5. (\ion{H}{2} region in a uniform
+  \caption{\label{fig:test5_2} Test 5. (\hii region in a uniform
     medium).  Clockwise from the upper left: Radial profiles of
@@
 
-\begin{figure}[t]
+\begin{figure*}
+  \epsscale{2}
   \plotone{fig/test5_slices}
-  \caption{\label{fig:test5_3} Test 5. (\ion{H}{2} region in a uniform
+  \epsscale{1}
+  \caption{\label{fig:test5_3} Test 5. (\hii region in a uniform
     medium).  Clockwise from the upper left: Slices through the origin
@@
     time $t =$ 500 Myr.}
-\end{figure}
-
-Here we consider the expansion of an \ion{H}{2} region into a uniform
+\end{figure*}
+
+Here we consider the expansion of an \hii region into a uniform
 neutral medium including the hydrodynamical response to the heated
@@
 at times $t$ = 10, 200, and 500 Myr in radial profiles of density,
-temperature, pressure, and ionized fraction.  The initial \ion{H}{2}
+temperature, pressure, and ionized fraction.  The initial \hii
 region is over-pressurized and creates an forward shock wave.  The
@@
 
-\subsection{Test 6. \ion{H}{2} region expansion in an isothermal
+\subsection{Test 6. \hii region expansion in an isothermal
   sphere}
 
-\begin{figure}[t]
-  \epsscale{0.8}
+\begin{figure}
+  %\epsscale{0.8}
   \plotone{fig/test6_ifront}
-  \caption{\label{fig:test6_1} Test 6. (\ion{H}{2} region in a 1/$r^2$
+  \caption{\label{fig:test6_1} Test 6. (\hii region in a 1/$r^2$
     density profile).  Top: Growth of the computed ionization front
@@
       IF}$.  It is smooth within the calculation itself.}
-  \epsscale{1}
+  %\epsscale{1}
 \end{figure}
 
-\begin{figure}[t]
+\begin{figure}
   \plotone{fig/test6_profiles}
-  \caption{\label{fig:test6_2} Test 6. (\ion{H}{2} region in a 1/$r^2$
+  \caption{\label{fig:test6_2} Test 6. (\hii region in a 1/$r^2$
     density profile).  Clockwise from the upper left: Radial profiles of
@@
 
-\begin{figure}[t]
+\begin{figure*}
+  \epsscale{2}
   \plotone{fig/test6_slices}
-  \caption{\label{fig:test6_3} Test 6. (\ion{H}{2} region in a 1/$r^2$
+  \epsscale{1}
+  \caption{\label{fig:test6_3} Test 6. (\hii region in a 1/$r^2$
     density profile).  Clockwise from the upper left: Slices through the origin
@@
     time $t =$ 25 Myr.}
-\end{figure}
+\end{figure*}
 
@@
 where $r_0$ is the radius of the core.  If the Str\"{o}mgren radius is
-smaller than the core radius, then the resulting \ion{H}{2} region
+smaller than the core radius, then the resulting \hii region
 never escapes into the steep density slope.  When the ionization front
@@
 
-\begin{figure}[t]
-  \epsscale{0.9}
+\begin{figure}
+  %\epsscale{0.9}
   \plotone{fig/test7_lines}
@@
     left) density, temperature, pressure, and neutral fraction.}
+  %\epsscale{1}
+\end{figure}
+
+\begin{figure*}
+  \epsscale{2}
+  \plotone{fig/test7_slices10}
   \epsscale{1}
-\end{figure}
-
-\begin{figure}[t]
-  \plotone{fig/test7_slices10}
   \caption{\label{fig:test7_2} Test 7. (Photo-evaporation of a dense
@@
     time $t =$ 10 Myr.}
-\end{figure}
-
-\begin{figure}[t]
+\end{figure*}
+
+\begin{figure*}
+  \epsscale{2}
   \plotone{fig/test7_slices50}
+  \epsscale{1}
   \caption{\label{fig:test7_3} Test 7. (Photo-evaporation of a dense
     clump).  Same as Figure \ref{fig:test7_1} but at $t = 50$ Myr.}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{figure}[t]
+\begin{figure*}
+  \epsscale{2}
   \plotone{fig/test8_slices}
+  \epsscale{1}
   \caption{\label{fig:test8_1} Test 8. (Champagne flow from a dense
@@
     kyr.  Notice the instabilities that grow from perturbations
-    created while the \ion{H}{2} region is contained in the dense
+    created while the \hii region is contained in the dense
     clump.}
-\end{figure}
+\end{figure*}
 
@@
 flows, is a long studied problem \citep[e.g.][\S3.3]{Yorke86}.  To
-study this, we use the same setup as \citet{Bisbas09} --- a spherical
+study this, we use the same setup as \citet{Bisbas09} -- a spherical
 tophat with an overdensity of 10 and radius of 1 pc in a simulation
@@
 spherical to parabolic after it escapes from the clump in the opposite
-direction.  At $t = 10$ kyr, the surface of the \ion{H}{2} region is
+direction.  At $t = 10$ kyr, the surface of the \hii region is
 just contained within the overdensity.  In the x-z plane, there are
@@
 
-\begin{figure}[t]
-  \epsscale{0.75}
+\begin{figure}
+  %\epsscale{0.75}
   \plotone{fig/test9thick_rho}
@@
     source turns on at $t=0$.}
-  \epsscale{1}
+  %\epsscale{1}
 \end{figure}
 
-\begin{figure}[t]
-  \epsscale{0.75}
+\begin{figure}
+  %\epsscale{0.75}
   \plotone{fig/test9thin_rho}
@@
     but for the optically thin case.}
-  \epsscale{1}
+  %\epsscale{1}
 \end{figure}
@@
 Here we combine the classic case of a Rayleigh-Taylor instability and
-an expanding \ion{H}{2} region.  The Rayleigh-Taylor instability
+an expanding \hii region.  The Rayleigh-Taylor instability
 occurs when a dense fluid is being supported by a lighter fluid,
@@
 
-We run two cases --- an optically-thick and optically-thin case.  In
+We run two cases, an optically-thick and optically-thin case.  In
 the former, we take the parameter choices from past literature
@@
 by
-\begin{equation}
-  v_z(x,y,z) = 0.01 [1 + \cos(2\pi x / L_x)] \times 
-  [1 + \cos(2\pi y / L_y)] \times [1 + \cos(2\pi z / L_z)]/8.
-\end{equation}
+\begin{eqnarray}
+  v_z(x,y,z) & = & 0.01 [1 + \cos(2\pi x / L_x)] \times  \nonumber\\
+  & & [1 + \cos(2\pi y / L_y)] \times \nonumber\\
+  & & [1 + \cos(2\pi z / L_z)]/8.
+\end{eqnarray}
 
@@
 
-The optically-thin case is set up similarly but with three
-changes---(1) a density contrast of 10, (2) a luminosity of $10^{43}$
-ph s$^{-1}$, and (3) the source is born at 6.5 Myr.  The time units
-are decreased to 200 kyr so that $(T_0, T_1) = (1.8 \times 10^3, 1.8
+The optically-thin case is set up similarly but with three changes:
+(1) a density contrast of 10, (2) a luminosity of $10^{43}$ ph
+s$^{-1}$, and (3) the source is born at 6.5 Myr.  The time units are
+decreased to 200 kyr so that $(T_0, T_1) = (1.8 \times 10^3, 1.8
 \times 10^4)$ K.  Note that in code units, pressure is unchanged.  We
@@
 
-\begin{figure}[t]
+\begin{figure*}
+  \epsscale{2}
+  \plotone{fig/test10_slices}
   \epsscale{1}
-  \plotone{fig/test10_slices}
   \caption{\label{fig:test10} Test 10 (Photo-evaporation of a
@@
     dense inward fingers in the ionization front shock.}
-  \epsscale{1}
-\end{figure}
+  %\epsscale{1}
+\end{figure*}
 
@@
 the density perturbations create ionization front instabilities
-\citep{Whalen08_Instab} that are seen on the \ion{H}{2} region surface
+\citep{Whalen08_Instab} that are seen on the \hii region surface
 at the coordinate $z=0.5$.  Behind the ionization front, the dense
@@
 
-\begin{figure}[t]
+\begin{figure*}
+  %\epsscale{1}
+  \epsscale{2}
+  \plotone{fig/test11_slices}
   \epsscale{1}
-  \plotone{fig/test11_slices}
   \caption{\label{fig:test11} Test 11 (Collimated radiation from a
     dense clump).  Slices of density (top) and temperature (bottom) at
-    $t = 0.1, 3.25, 10.75, 23.25$ Myr.  The conical \ion{H}{2} region
+    $t = 0.1, 3.25, 10.75, 23.25$ Myr.  The conical \hii region
     drives shocks transversely into the overdense sphere and creates
@@
     from D-type to R-type after it enters the ambient medium.}
-  \epsscale{1}
-\end{figure}
+  %\epsscale{1}
+\end{figure*}
 
@@
 
-We illustrate the expansion of the \ion{H}{2} region created by the
+We illustrate the expansion of the \hii region created by the
 beamed radiation in Figure \ref{fig:test11}.  Before $t = 3$ Myr, the
-\ion{H}{2} region is conical and contained within the dense clump,
+\hii region is conical and contained within the dense clump,
 depicted in the $t = 0.1$ Myr snapshot of the system.  At this time,
@@
 transverse direction of the cone.  This can be seen in the minute
-overdensities on the \ion{H}{2} transverse surface.  When it breaks
+overdensities on the \hii transverse surface.  When it breaks
 out of the overdensity, a champagne flow develops, where the
@@
 
-% \subsection{Test 12. \ion{H}{2} region in a rotating medium}
+% \subsection{Test 12. \hii region in a rotating medium}
 % 
 % Angular momentum is prevalent throughout all astrophysical systems.
-% We construct a problem with an \ion{H}{2} region that is completely
+% We construct a problem with an \hii region that is completely
 % contained within a sphere with solid-body rotation.  Self-gravity is
@@
 
-% \subsection{Test 12. \ion{H}{2} region in a static potential}
+% \subsection{Test 12. \hii region in a static potential}
 
@@
 
-\begin{figure}[t]
-  \epsscale{1.15}
+\begin{figure*}
+  %\epsscale{1.15}
+  \epsscale{2}
   \plottwo{fig/test12_kph}{fig/test12_radial}
+  \epsscale{1}
   \caption{\label{fig:test12_kph} Test 12 (Time variations of the
@@
     profile \kph~with the inverse square law overplotted.}
-  \epsscale{1}
-\end{figure}
-
-\begin{figure}[t]
-  \epsscale{0.8}
+  %\epsscale{1}
+\end{figure*}
+
+\begin{figure}
+  %\epsscale{0.8}
   \plotone{fig/test12_profiles}
@@
     50, 100, 150, 200, 250$ Myr.  In this problem, the time variations
-    in the source have little effect on the overall \ion{H}{2} region
+    in the source have little effect on the overall \hii region
     expansion.  Inside the ionization front at $t = 50$ Myr, there are
@@
     source that are later smoothed out over a sound crossing time.}
-  \epsscale{1}
+  %\epsscale{1}
 \end{figure}
@@
 \ref{fig:test12_profiles}.  The variable source has little effect on
-the overall growth of the \ion{H}{2} region.  It has the approximately
+the overall growth of the \hii region.  It has the approximately
 the same radius as Test 5 at $t = 200$ Myr when run with a
@@
 
-\subsection{Test 14. \ion{H}{2} region with MHD}
-
-\begin{figure}[t]
+\subsection{Test 14. \hii region with MHD}
+
+\begin{figure*}
+  \epsscale{2}
   \plotone{fig/test14_slices_xy}
-  \caption{\label{fig:test14_1} Test 14. (\ion{H}{2} region with MHD).
+  \epsscale{1}
+  \caption{\label{fig:test14_1} Test 14. (\hii region with MHD).
     Left to right: slices of density at $t = 0.18, 0.53, 1.58$ Myr in
     the x-y plane.  The streamlines show the magnetic field.}
-\end{figure}
-
-\begin{figure}[t]
+\end{figure*}
+
+\begin{figure*}
+  \epsscale{2}
   \plotone{fig/test14_slices_yz}
-  \caption{\label{fig:test14_2} Test 14. (\ion{H}{2} region with
+  \epsscale{1}
+  \caption{\label{fig:test14_2} Test 14. (\hii region with
     MHD). Slices of density (top) and the x-component of the magnetic
@@
     (left to right).}
-\end{figure}
+\end{figure*}
 
@@
 for illustrative purposes, we show a test problem with an expanding
-\ion{H}{2} region in an initially uniform density field and constant
+\hii region in an initially uniform density field and constant
 magnetic field.  We use the same problem setup as
-\citet{Krumholz07_ART} --- $\rho = 100~\cubecm$, $T = 11$ K, $L_{\rm
+\citet{Krumholz07_ART} -- $\rho = 100~\cubecm$, $T = 11$ K, $L_{\rm
   box} = 20$ pc with a resolution of 256$^3$.  This ambient medium is
@@
 
-As the \ion{H}{2} region grows in the magnetized medium, shown in
+As the \hii region grows in the magnetized medium, shown in
 Figures \ref{fig:test14_1} and \ref{fig:test14_2}, it transforms from
@@
 
-\begin{figure}[t]
-  \epsscale{0.75}
+\begin{figure}
+  %\epsscale{0.75}
   \plotone{fig/ifront_res}
@@
     within 0.5\% of the higher resolution runs.}
-  \epsscale{1}
+  %\epsscale{1}
 \end{figure}
@@
 
-\begin{figure}[t]
+\begin{figure*}
+  %\epsscale{1}
+  \epsscale{2}
+  \plotone{fig/phic_slices}
   \epsscale{1}
-  \plotone{fig/phic_slices}
   \caption{\label{fig:ang_dep1} Variations in the photo-ionization
@@
     this test.}
-  \epsscale{1}
-\end{figure}
-
-\begin{figure}[t]
-  \epsscale{0.75}
+  %\epsscale{1}
+\end{figure*}
+
+\begin{figure}
+  %\epsscale{0.75}
   \plotone{fig/phic_dep}
@@
     \Phi_c^{-0.6}$.}
-  \epsscale{1}
+  %\epsscale{1}
 \end{figure}
@@
 
-\begin{figure}[t]
-  \epsscale{1.05}
+\begin{figure*}
+  %\epsscale{1.05}
+  \epsscale{2}
   \plottwo{fig/nures040}{fig/nures100}
+  \epsscale{1}
   \caption{\label{fig:nu_dep} Radial profiles of (clockwise from the
@@
     4$.}  
-  \epsscale{1}
-\end{figure}
+  %\epsscale{1}
+\end{figure*}
 
@@
 multi-frequency spectrum can create differences in the reactive flows.
-We use Test 5 (\S\ref{sec:test5}; an expanding \ion{H}{2} region with
+We use Test 5 (\S\ref{sec:test5}; an expanding \hii region with
 hydrodynamics) to probe any differences in the solution when varying
@@
 \item $n_\nu = 1$: Mean energy of 29.6 eV
-\item $n_\nu = 2$: Mean energies in bins 13.6--30 and $>$30 eV---21.1,
+\item $n_\nu = 2$: Mean energies in bins 13.6--30 and $>$30 eV--21.1,
   43.0 eV
 \item $n_\nu = 4$: Mean energies in bins 13.6--20, 20--30, 30--40, and
-  $>$40 eV---16.7, 24.6, 34.5, 52.1 eV
+  $>$40 eV--16.7, 24.6, 34.5, 52.1 eV
 \item $n_\nu = 8, 16$: Logarithmically spaced between 13.6 and 50 eV
@@
 
-\begin{figure}[t]
-  \epsscale{0.75}
+\begin{figure}
+  %\epsscale{0.75}
   \plotone{fig/ifront_dt}
@@
     computational efficiency because they take short timesteps when
-    the \ion{H}{2} is expanding rapidly but take long timesteps when
+    the \hii is expanding rapidly but take long timesteps when
     the photon gradients are small when $r_{\rm IF}$ is large.  At the
@@
     identical ionization front radii.}
-  \epsscale{1}
+  %\epsscale{1}
 \end{figure}
-\begin{figure}[t]
-  \epsscale{0.75}
+\begin{figure}
+  %\epsscale{0.75}
   \plotone{fig/vary_dt}
@@
     mean free path by the ionization front is plotted for reference.}
-  \epsscale{1}
+  %\epsscale{1}
 \end{figure}
@@
 ionization front velocity.  Here we use Test 1 but with $64^3$
-resolution to compare different time-stepping methods --- restricted
-changes in \ion{H}{2} ($dn_{\rm H}/dt$ based; \S\ref{sec:dt_hi}),
+resolution to compare different time-stepping methods -- restricted
+changes in \hii ($dn_{\rm H}/dt$ based; \S\ref{sec:dt_hi}),
 constant timesteps of 0.1, 0.5, 1, and 5 Myr (\S\ref{sec:dt_const}),
@@
 The growth of the ionization front radius is shown in Figure
-\ref{fig:dt_dep1}.  Both the \ion{H}{2} restricted and incident
+\ref{fig:dt_dep1}.  Both the \hii restricted and incident
 radiation variable time-stepping methods agree within a few percent
@@
 numerical solution lags behind the analytical one, but they converge
-to an accurate \ion{H}{2} radii at late times.  Even $dt_P = 5$ Myr
+to an accurate \hii radii at late times.  Even $dt_P = 5$ Myr
 timestep, which underestimated it by 35\% at 50 Myr, is within a
@@
 
-\begin{figure}[t]
-  \epsscale{0.7}
+\begin{figure}
+  %\epsscale{0.7}
   \plotone{fig/fc_slices}
@@
     HEALPix scheme switches from polar to equatorial type pixels.}
-  \epsscale{1}
+  %\epsscale{1}
 \end{figure}
@@
 
-\begin{figure}[t]
-  \epsscale{0.6}
+\begin{figure}
+  %\epsscale{0.6}
   \plotone{fig/rayopt}
@@
     thick (white line) at an optical depth $\tau = 0.1$.}
-  \epsscale{1}
+  %\epsscale{1}
 \end{figure}
@@
 
-\begin{figure}[t]
-  \epsscale{0.6}
+\begin{figure}
+  %\epsscale{0.6}
   \plotone{fig/xray_profiles.eps}
@@
     goes into thermal energy, lowering the temperature.}
-  \epsscale{1}
+  %\epsscale{1}
 \end{figure}
@@
 \ref{fig:xray_fig} compares the density, temperature, ionized
-fraction, and neutral fraction of the expanding \ion{H}{2} region
+fraction, and neutral fraction of the expanding \hii region
 considering secondary ionizations and reduced photo-heating and
@@
 
-\begin{figure}[t]
-  \epsscale{1.075}
+\begin{figure*}
+  %\epsscale{1.075}
+  \epsscale{2}
   \plottwo{fig/noRP_profiles.eps}{fig/RP_profiles.eps}
+  \epsscale{1}
   \caption{\label{fig:rp_profiles} (a) No radiation pressure.
@@
     to 50 km/s.}
-  \epsscale{1}
-\end{figure}
-
-Radiation pressure affects gas dynamics in an \ion{H}{2} region when
+  %\epsscale{1}
+\end{figure*}
+
+Radiation pressure affects gas dynamics in an \hii region when
 its force is comparable to the acceleration created by gas pressure of
@@
 simulations at several times.  Without radiation pressure, the
-evolution of the \ion{H}{2} is matches the analytical expectations
+evolution of the \hii is matches the analytical expectations
 described in \S\ref{sec:test5}.  At $t=140$ kyr with radiation
@@
 = 140$ kyr.  Thus the recombination rates are lower, resulting in
-increased ionization fractions and temperatures in the \ion{H}{2}
+increased ionization fractions and temperatures in the \hii
 region.
 
-\subsection{Consolidated \ion{H}{2} region with two sources}
-
-\begin{figure}[t]
-  \epsscale{0.6}
+\subsection{Consolidated \hii region with two sources}
+
+\begin{figure}
+  %\epsscale{0.6}
   \plotone{fig/two_sources.eps}
   \caption{\label{fig:twosrc} Slice of neutral fraction at $t = 500$
-    Myr through the sources in the consolidated \ion{H}{2} test.
+    Myr through the sources in the consolidated \hii test.
     There are no artifacts associated with rays being emitted from two
@@
     before they overlap.}
-  \epsscale{1}
+  %\epsscale{1}
 \end{figure}
@@
 
-The \ion{H}{2} regions grow to $r = 4$ kpc where they overlap.  Then
-the two sources are enveloped in a common, elongated \ion{H}{2}
+The \hii regions grow to $r = 4$ kpc where they overlap.  Then
+the two sources are enveloped in a common, elongated \hii
 region.  To illustrate this, we show the neutral fraction in Figure
@@
 
-\begin{figure}[t]
-  \epsscale{0.8}
+\begin{figure}
+  %\epsscale{0.8}
   \plotone{fig/weak_v1.eps}
@@
     performance from 1 to 8 processes.}
-  \epsscale{1}
+  %\epsscale{1}
 \end{figure}
@@
 
-\begin{figure}[t]
-  \epsscale{0.8}
+\begin{figure}
+  %\epsscale{0.8}
   \plotone{fig/strong_v1.eps}
@@
     ray tracing scales relatively well.}
-  \epsscale{1}
+  %\epsscale{1}
 \end{figure}
@@
 transfer comparison papers.  Additionally we have tested our code with
-more dynamical problems---champagne flows, Rayleigh-Taylor
+more dynamical problems -- champagne flows, Rayleigh-Taylor
 instabilities, photo-evaporation of a blastwave, beamed radiation, a
-time-varying source, and an \ion{H}{2} region with MHD---to
+time-varying source, and an \hii region with MHD -- to
 demonstrate the flexibility and fidelity of Enzo+Moray.  Because
@@
 molecular cloud resolving cosmological galaxy formation, and
-\ion{H}{2} regions of Population III stars.  Furthermore, we have
+\hii regions of Population III stars.  Furthermore, we have
 included Lyman-Werner absorption, secondary ionizations from X-ray
@@
 
-\acknowledgments
+\section*{Acknowledgments}
 
@@
 
-%\clearpage
-%\input biblio.tex
 \bibliography{ms}
 
+\bsp
+
+\label{lastpage}
+
 \end{document}

### 2010-11-15 mnras.tex

@@
 
+\begin{figure*}
+  \epsscale{2}
+  \plotone{fig/test2_slices}
+  \epsscale{1}
+  \caption{\label{fig:test2_2} Test 2. (\hii region expansion
+    with a $T=10^5$ K blackbody spectrum).  Top: Slices through the
+    origin of neutral fraction at 10 and 100 Myr.  Bottom: Slices of
+    temperature at 10 and 100 Myr.}
+\end{figure*}
+
 \begin{figure}
   \plotone{fig/test2_ifront.eps}
-  \caption{\label{fig:test2_2} Test 2. (\hii region expansion
+  \caption{\label{fig:test2_3} Test 2. (\hii region expansion
     with a $T=10^5$ K blackbody spectrum).  Top: Evolution of the
@@
 \end{figure}
-
-\begin{figure*}
-  \epsscale{2}
-  \plotone{fig/test2_slices}
-  \epsscale{1}
-  \caption{\label{fig:test2_3} Test 2. (\hii region expansion
-    with a $T=10^5$ K blackbody spectrum).  Top: Slices through the
-    origin of neutral fraction at 10 and 100 Myr.  Bottom: Slices of
-    temperature at 10 and 100 Myr.}
-\end{figure*}
 
@@
 which is in agreement with the analytical expectation and other codes
-in RT06.  In Figure \ref{fig:test2_2}, we show the ratio of the
-ionization front radius $r_{\rm IF}$ in our simulation and $R_s$.
-Before $1.5t_{\rm rec}$, $r_{\rm IF}$ lags behind $R_s$, initially by
-10\% and then increases to $R_s$; however afterwards, this ratio
-asymptotes to a solution that is 4\% greater than $R_s$.  This
-behavior is approximately the median result in RT06, where this ratio
-varies between 1 and 1.1, and the early evolution of $r_{\rm IF}$ is
-under-predicted by almost all of the codes.  If we use one energy
-group with the mean energy (29.6 eV) of a $T=10^5$ K blackbody, we
-find that $r_{\rm IF}/R_s$ = 1.08, which is representative of the
-codes in the upper range of RT06.  In Figure \ref{fig:test2_3}, we
-show slices of neutral fraction and temperature through the origin at
-$t = $ 10 and 100 Myr.  Here one sees the spherically symmetric
-\hii regions and a smooth temperature transition to the neutral
-ambient medium.
+in RT06.  In Figure \ref{fig:test2_2}, we show slices of neutral
+fraction and temperature through the origin at $t = $ 10 and 100 Myr.
+Here one sees the spherically symmetric \hii regions and a smooth
+temperature transition to the neutral ambient medium.  In Figure
+\ref{fig:test2_3}, we show the ratio of the ionization front radius
+$r_{\rm IF}$ in our simulation and $R_s$.  Before $1.5t_{\rm rec}$,
+$r_{\rm IF}$ lags behind $R_s$, initially by 10\% and then increases
+to $R_s$; however afterwards, this ratio asymptotes to a solution that
+is 4\% greater than $R_s$.  This behavior is approximately the median
+result in RT06, where this ratio varies between 1 and 1.1, and the
+early evolution of $r_{\rm IF}$ is under-predicted by almost all of
+the codes.  If we use one energy group with the mean energy (29.6 eV)
+of a $T=10^5$ K blackbody, we find that $r_{\rm IF}/R_s$ = 1.08, which
+is representative of the codes in the upper range of RT06.
 

### 2010-11-15 mnras.tex
Including Tom's revisions.

@@
 
-  We describe a photon-conserving numerical method that solves the
-  radiative transfer equation, using a spatially-adaptive ray tracing
-  scheme, and its parallel implementation into the adaptive mesh
-  refinement (AMR) code, Enzo.  By coupling the solver with the energy
+  We describe a photon-conserving radiative transfer algorithm, using
+  a spatially-adaptive ray tracing scheme, and its parallel
+  implementation into the adaptive mesh refinement (AMR) cosmological
+  hydrodynamics code, Enzo.  By coupling the solver with the energy
   equation and non-equilibrium chemistry network, our radiation
@@
   luminosities, and collimated radiation.  The test suite also
-  includes an expanding \hii region in a magnetized medium,
-  utilizing the newly implemented magnetohydrodynamics module in
-  \enzo.  This method linearly scales with the number of point sources
-  and number of grid cells.  To combat this, we use a novel method of
-  merging rays at large radius, using a tree method, which we briefly
-  describe.  Our implementation is scalable to 512 processors on
+  includes an expanding \hii region in a magnetized medium, utilizing
+  the newly implemented magnetohydrodynamics module in \enzo.  This
+  method linearly scales with the number of point sources and number
+  of grid cells.  Our implementation is scalable to 512 processors on
   distributed memory machines and can include radiation pressure and
@@
 
-Radiative transfer is ubiquitous in many astrophysical problems,
-encompassing topics such as stellar atmospheres, the interstellar
-medium (ISM), star formation, galaxy formation, supernovae (SNe) and
-cosmology.  Thus it is a well-studied problem
-\citep[e.g.][]{Mathews65, Rybicki, Mihalas84, Yorke86}; however, its
-treatment in multi-dimensional calculations is difficult because of
-the dependence on seven variables -- three spatial, two angular,
-frequency, and time.  The non-local nature of the thermal and
+Radiation from stars and black holes strongly affects their
+surroundings and plays a crucical role in topics such as stellar
+atmospheres, the interstellar medium (ISM), star formation, galaxy
+formation, supernovae (SNe) and cosmology.  It is a well-studied
+problem \citep[e.g.][]{Mathews65, Rybicki, Mihalas84, Yorke86};
+however, its treatment in multi-dimensional calculations is difficult
+because of the dependence on seven variables -- three spatial, two
+angular, frequency, and time.  The non-local nature of the thermal and
 hydrodynamical response to radiation sources further adds to the
-difficulty.  In the general case, one must consider all radiation
-sources at every point in calculation.
-
-Fortunately problems can be simplified by exploiting symmetries and
-special cases.  The first case was considered by \citet{Stroemgren39}
-for a radiation source ionizing a static uniform neutral medium, where
-recombinations balance photo-ionizations.  He derived a radius of an
-\hii region,
+difficulty.  Depending on the problem of interest some simplifying
+assumptions may be made.
+
+An important case was considered by \citet{Stroemgren39} for an
+ultraviolet (UV) radiation source photoionizing a static uniform
+neutral medium.  When recombinations balance photo-ionizations, the
+radius of a so-called \hii region,
 %
@@
 outwards \citep[e.g.][]{Oort54, Schatzman55}.  These early works
-provided the basis for the modern topic of radiation hydrodynamics.  A
-decade later, the first radiation hydrodynamical numerical models of
-\hii regions in spherical symmetry and plane-parallel ionization
-fronts were developed \citep[e.g.][]{Mathews65, Lasker66,
+provided the basis for the modern topic of radiation hydrodynamics of
+the ISM.  A decade later, the first radiation hydrodynamical numerical
+models of \hii regions in spherical symmetry and plane-parallel
+ionization fronts were developed \citep[e.g.][]{Mathews65, Lasker66,
   Hjellming66}.  They described the expansion of the ionization front
@@
 travel supersonically with respect to the neutral gas, whereas D-type
-fronts are subsonic.  Furthermore ``weak'' and ``strong'' R-type fronts
-move supersonically and subsonically with respect to the ionized gas,
-respectively.  The same terminology conversely applies to D-type
-fronts.  ``Critical'' fronts are defined as moving exactly at the
-sound speed.  These works established the evolutionary track of an
-expanding \hii illuminated by a massive star in a uniform
-medium:
+fronts are subsonic.  Furthermore ``weak'' and ``strong'' R-type
+fronts move supersonically and subsonically with respect to the
+ionized gas, respectively.  The same terminology conversely applies to
+D-type fronts.  ``Critical'' fronts are defined as moving exactly at
+the sound speed.  These works established the evolutionary track of an
+expanding \hii illuminated by a massive star in a uniform medium:
 %
@@
   and with an M1 closure relation \citep{Gonzalez07, Aubert08}.
-  Moment methods have the advantage of being fast, being independent
-  of the number of radiation point sources.  However, they are
-  diffusive and result in incorrect shadows in some situations.
+  Moment methods have the advantage of being fast and independent of
+  the number of radiation sources.  However, they are diffusive and
+  result in incorrect shadows in some situations.
 \item Ray tracing:  Radiation can be propagated along rays that extend
@@
 hydrodynamical problems.  We have used this code to investigate the
-growth of an \hii region from a 100\Ms~Population III (Pop III)
-star \citep{Abel07}, the early stages of reionization from Pop III
-stars \citep{Wise08_Reion}, radiative feedback on the formation of
-high redshift dwarf galaxies \citep{Wise08_Gal}, ultraviolet radiation
+growth of an \hii region from a 100\Ms~Population III (Pop III) star
+\citep{Abel07}, the early stages of reionization from Pop III stars
+\citep{Wise08_Reion}, radiative feedback on the formation of high
+redshift dwarf galaxies \citep{Wise08_Gal}, ultraviolet radiation
 escape fractions from dwarf galaxies before reionization
@@
 included Enzo+Moray in the latest public release of
-\enzo\footnote{http://lca.ucsd.edu/enzo}, and it is also coupled with
-the newly added MHD solver in \enzo~\citep{Wang09}.
+\enzo\footnote{http://enzo.googlecode.com}, and it is also coupled
+with the newly added MHD solver in \enzo~\citep{Wang09}.
 
@@
 where the light crossing time is comparable to the Hubble time, then
-it could be important to consider cosmological redshifting and
-dilution of the radiation.  Thus equation (\ref{eqn:rteqn}) reduces to
-the non-cosmological form in this local approximation,
+it becomes important to consider cosmological redshifting and dilution
+of the radiation.  Thus equation (\ref{eqn:rteqn}) reduces to the
+non-cosmological form in this local approximation,
 %
@@
 Furthermore any time variations of the luminosities will be retained
-in the radiation field.  In this sense, our method retains the time
+in the radiation field.  This is how this method retains the time
 derivative of the radiative transfer equation.
 
-\subsection{Ray Merging}
-
-Unfortunately the computational work of ray tracing scales with the
-number of sources.  To resolve this barrier, rays can be merged in
-cases with either nearly parallel rays from clustered sources of
-radiation, whether it be diffuse radiation or point sources, or where
-rays exit a region with high resolution into a coarsely resolved
-region.  In each case, the factor $\Phi_c$ can be much higher than the
-desired value, and it would be efficient to merge these rays.  We have
-devised a new scheme that merges rays from clustered sources based on
-a hierarchical binary tree, which is analogous to the gravity tree
-solvers.  In principle, this should increase the efficiency of the
-solver, but currently in most problems the overhead is greater than
-the compuational savings.  Nevertheless the biggest advantage of this
-method is the memory savings in simulations with clustered sources.
-We leave its full details for a later paper and now describe our
-photon-conserving transport method.
+% \subsection{Ray Merging}
+
+% Unfortunately the computational work of ray tracing scales with the
+% number of sources.  To resolve this barrier, rays can be merged in
+% cases with either nearly parallel rays from clustered sources of
+% radiation, whether it be diffuse radiation or point sources, or where
+% rays exit a region with high resolution into a coarsely resolved
+% region.  In each case, the factor $\Phi_c$ can be much higher than the
+% desired value, and it would be efficient to merge these rays.  We have
+% devised a new scheme that merges rays from clustered sources based on
+% a hierarchical binary tree, which is analogous to the gravity tree
+% solvers.  In principle, this should increase the efficiency of the
+% solver, but currently in most problems the overhead is greater than
+% the compuational savings.  Nevertheless the biggest advantage of this
+% method is the memory savings in simulations with clustered sources.
+% We leave its full details for a later paper and now describe our
+% photon-conserving transport method.
 
@@
 number density of the absorbing medium, respectively.  We use the
-cell-centered density in our calculations but have experimented with
-trilinearly interpolated densities \citep[see][]{Mellema06} but could
-not devise a method that did not produce considerable artifacts.
-Equation (\ref{eqn:rtray}) has a simple exponential analytic solution,
-and the photon flux of a ray is reduced by
+cell-centered density in our calculations.  Using trilinearly
+interpolated densities \citep[see][]{Mellema06} did not produce
+improved results.  Equation (\ref{eqn:rtray}) has a simple exponential
+analytic solution, and the photon flux of a ray is reduced by
 %
@@
 locally reabsorbed, \citep{Spitzer78}, and $C_{\rm H}$ is the
-collisional ionization rate.  However for more accurate solutions in
+collisional ionization rate.  However, for more accurate solutions in
 calculations that consider several chemical species, the
-photo-ionization rates are better utilized in solvers that consider
-chemical networks \citep[e.g.][]{Abel97}.
+photo-ionization rates are terms in the relevant chemical networks
+\citep[e.g.][]{Abel97}.
 
@@
 artifacts, compute the radiation field, the computational grid must be
-well-sampled by the rays.  The main source of these artifacts is the
-geometrical difference between the cell and the HEALPix pixel.  In
-this section, we devise a correction scheme to account for these
+well-sampled by the rays.  The main source of potential artifacts is
+the geometrical difference between the cell and the HEALPix pixel
+relevant in the angular integration of the intensity over the cell.
+In this section, we devise a correction scheme to account for these
 differences.  Consider the solid angle $\Omega_{\rm ray}$ and photon
@@
 Molecular hydrogen can absorb photons in the Lyman-Werner bands
-through the two-step Solomon process that are composed of 76
-absorption lines ranging from 11.1 to 13.6 eV \citep{Stecher67,
-  Dalgarno70}.  Each of these spectral lines can be modelled with a
-typical exponential attenuation equation \citep{Ricotti01}, but
-\citet{Draine96} showed that this self-shielding is well modeled with
-the following relation to total \hh~column density
+through the two-step Solomon process, which for the lowest
+ro-vibrational states already consists of 76 absorption lines ranging
+from 11.1 to 13.6 eV \citep{Stecher67, Dalgarno70, Haiman00}.  Each of
+these spectral lines can be modelled with a typical exponential
+attenuation equation \citep{Ricotti01}, but \citet{Draine96} showed
+that this self-shielding is well modeled with the following relation
+to total \hh~column density
 %
@@
 \begin{equation}
-  \Gamma_{\rm ph,C} = \frac{dP_C}{n_e \; V_{\rm cell} \; dt_P}.
-\end{equation}
+  \Gamma_{\rm ph,C} = \frac{dP_C}{n_e \; V_{\rm cell} \; dt_P},
+\end{equation}
+which has been used in \citet{Kim11}.
 
@@
 the normal direction of the ray.  We do not include radiation pressure
-on dust, and thus our treatment underestimates its effects in
-applicable environments.  The resulting acceleration of the gas due to
+on dust currently.  The resulting acceleration of the gas because of
 radiation pressure is
@@
 where $\rho$ is the gas density inside the cell.  This acceleration is
-then added to the other forces, e.g. gravity, in the calculation.
+then added to the other forces, e.g. gravity, in the calculation in an
+operator split fashion.
 
@@
 keep track of their (1) photon flux, (2) photon type, (3) photon
-energy, (4) the length of its emission, (5) emission time, (6) current
-time, (7) radius, (8) total column density, (9) HEALPix pixel number,
-(10) HEALPix level, and (11) position of the originating source,
-totaling 60 (88) bytes for single (double) precision.  When \enzo~uses
-double precision for grid and particle positions and time, items 4-7
-and 11 are double precision.
+energy, (4) the time interval of its emission, (5) emission time, (6)
+current time, (7) radius, (8) total column density, (9) HEALPix pixel
+number, (10) HEALPix level, and (11) position of the originating
+source, totaling 60 (88) bytes for single (double) precision.  When
+\enzo~uses double precision for grid and particle positions and time,
+items 4-7 and 11 are double precision.
 
@@
 
-There have been several methods of choosing a timestep to solve
-radiation transfer equation because an accurate yet large timestep is
-not trivial to compute.  We describe several methods to calculate the
-radiative transfer timestep in this section.  With a small enough
-timestep, the solution is guaranteed to avoid any inaccuracies
-(ignoring any systematic ones) due to time-stepping, but the solver
-must be called many times.  These frequent calls may be unnecessary
-because the same solution may be accomplished with a longer timestep.
-Furthermore with ray tracing, the photon packages only advance a short
-distance, and they will exist in every $dx/dt_P$ cells with radiation
-and are stored between timesteps, excessively consuming memory.  On
-the shortest timescale, one can safely set the timestep to the
-light-crossing time of a cell \citep{Abel99_RT, Trac07} but encounters
-the problems stated above.
+There have been several methods of choosing a maximal timestep to
+solve radiation transfer equation while retaining stability and
+accuracy.  We describe several methods to calculate the radiative
+transfer timestep in this section.  With a small enough timestep, the
+solution is accurate (ignoring any systematic ones), but the solver is
+slow.  Furthermore for very small timesteps, the photon packages only
+advance a short distance, and they will exist in every $dx/dt_P$ cells
+with radiation and are stored between timesteps, excessively consuming
+memory.  On the shortest timescale, one can safely set the timestep to
+the light-crossing time of a cell \citep{Abel99_RT, Trac07} but
+encounters the problems stated above.
 
@@
 artifacts that generate the plateaus at 1.5 and 3 kpc, one sees
-spherical symmetry in our solution.
+spherical symmetry without any noise in our solution.
 
@@
 10^{-3}$ and $T = 2000$ K out to $\sim50$ pc from the shock.  The
-reflecting boundaries in Enzo might be responsible for this artifact
-because this is not seen when the problem is centered in the domain,
-removing any boundary effects.
+reflecting boundaries are responsible for this artifact because this
+is not seen when the problem is centered in the domain, removing any
+boundary effects.
 
@@
 The $x$ and $y$-boundaries are periodic, and the $z$-boundaries are
-reflecting.  These will cause features that are non-physical, in
-particular the top reflecting boundary; nevertheless, these tests
-provide a good check on a radiation hydrodynamics solver.  We show the
-evolution of the density, temperature, and ionized fraction of the
+reflecting.  These will cause artifical features, in particular,
+because of the top reflecting boundary; nevertheless, these tests
+provide a stress test on a radiation hydrodynamics solver.  We show
+the evolution of the density, temperature, and ionized fraction of the
 optically thick and optically thin cases in Figures
@@
 hydrodynamics solver and the hyperbolic $\nabla \cdot \mathbf{B} = 0$
-cleaning method of \citet{Dedner02}.  This marriage of radiation
-transport and MHD has already been demonstrated in \citet{Wang10}, but
-for illustrative purposes, we show a test problem with an expanding
-\hii region in an initially uniform density field and constant
-magnetic field.  We use the same problem setup as
+cleaning method of \citet{Dedner02}.  We show a test problem with an
+expanding \hii region in an initially uniform density field and
+constant magnetic field.  We use the same problem setup as
 \citet{Krumholz07_ART} -- $\rho = 100~\cubecm$, $T = 11$ K, $L_{\rm
@@
 \citep[e.g.][]{Shapiro04, Mellema06, Petkova09}, the timestep,
-especially too small of one, can drastically underestimate the
+especially too small a one, can drastically underestimate the
 ionization front velocity.  Here we use Test 1 but with $64^3$
@@
 problem.  The other parts of the code exhibit excellent weak scaling.
-Overall it scales well to 512 processes, and we plan to enhance the
-weak scalability of Enzo+Moray in the near future to larger processor
-counts.
+Overall it scales already well to 512 processes, and there is room to
+enhance the weak scalability of Enzo+Moray in the near future.
 
@@
   \caption{\label{fig:strong} Strong scaling test with a $256^3$ AMR
-    calculation of cosmological reionization.  The error bars
-    represent the minimum and maximum time spent on a single core and
-    measures load balancing.  Each point has been slightly offset to
-    make the error bars distinguishable.  The hydrodynamics and
-    non-equilibrium chemistry solvers scale well.  Unfortunately the
-    communication of rays does not scale in this problem, where as the
-    ray tracing scales relatively well.}
+    calculation of cosmological reionization with $\sim329^3$ zones.
+    The error bars represent the minimum and maximum time spent on a
+    single core and measures load balancing.  Each point has been
+    slightly offset to make the error bars distinguishable.  The
+    hydrodynamics and non-equilibrium chemistry solvers scale well.
+    The communication of rays does not scale well in this problem and
+    limits the performance, where as the ray tracing scales relatively
+    well.}
   %\epsscale{1}
@@
 communication.  We use an AMR simulation to demonstrate the scability
-of Enzo+Moray in a demanding, real-world calculation.  Here we use a
+of Enzo+Moray in a demanding, research application.  Here we use a
 small-box reionization calculation with $L_{\rm box} = 3$ Mpc/h, a
@@
 Being a ray tracing code, it scales with the number of radiation
-sources, albeit lessened with ray merging; nevertheless, it scales
-well to O($10^3$) processors for problems with $\sim10^9$
-computational cells and $\sim10^4$ sources, such as reionization
-calculations.  We have also shown that the code shows good strong
-scaling in AMR calculations, given a large enough problem.  The
-combination of AMR and adaptive ray tracing allows for high-resolution
-and high-dynamical range problems, e.g. present-day star formation,
-molecular cloud resolving cosmological galaxy formation, and
-\hii regions of Population III stars.  Furthermore, we have
-included Lyman-Werner absorption, secondary ionizations from X-ray
-radiation, Compton heating from photon scattering, and radiation
+sources; nevertheless, it scales well to O($10^3$) processors for
+problems with $\sim10^9$ computational cells and $\sim10^4$ sources,
+such as reionization calculations.  We have also shown that the code
+shows good strong scaling in AMR calculations, given a large enough
+problem.  The combination of AMR and adaptive ray tracing allows for
+high-resolution and high-dynamical range problems, e.g. present-day
+star formation, molecular cloud resolving cosmological galaxy
+formation, and \hii regions of Population III stars.  Furthermore, we
+have included Lyman-Werner absorption, secondary ionizations from
+X-ray radiation, Compton heating from photon scattering, and radiation
 pressure into the code, which extends the reach of Enzo+Moray to study
@@
 code.  The full implementation is included in the latest public
-version of \enzo\footnote{http://lca.ucsd.edu/enzo}, providing the
+version of \enzo\footnote{http://enzo.googlecode.com}, providing the
 community with a full-featured radiation hydrodynamics AMR code.
@@
 which is operated by the Association of Universities for Research in
-Astronomy, Inc., for NASA, under contract NAS 5-26555.  J.K. was
-supported by the William R. and Sara Hart Kimball Stanford Graduate
-Fellowship.  Computational resources were provided by NASA/NCCS award
-SMD-09-1439.  The majority of the analysis and plots were done with
-\texttt{yt} \citep{yt}.
+Astronomy, Inc., for NASA, under contract NAS 5-26555.  Computational
+resources were provided by NASA/NCCS award SMD-09-1439.  The majority
+of the analysis and plots were done with \texttt{yt}
+\citep{yt_full_paper}.
 

### 2010-11-16 mnras.tex
Fixed margins, added SVG version of covering factor figure, clarified the "change in incident radiation" timestep method, moved resolution tests to its original position.

@@
-\documentclass[useAMS,usenatbib]{mn2e}
+\documentclass[useAMS,usenatbib,a4paper]{mn2e}
 
@@
 \usepackage{natbib}
-%\usepackage[section] {placeins}
+\usepackage[section] {placeins}
 \bibliographystyle{mn2e}
@@
 \input macros.tex
+\voffset=-2cm
 
@@
 \citep{Wise08_Reion}, radiative feedback on the formation of high
-redshift dwarf galaxies \citep{Wise08_Gal}, ultraviolet radiation
-escape fractions from dwarf galaxies before reionization
+redshift dwarf galaxies \citep{Wise08_Gal, Wise10_Gal}, ultraviolet
+radiation escape fractions from dwarf galaxies before reionization
 \citep{Wise09}, negative radiative feedback from accreting Pop III
@@
 \begin{figure}
-  \plottwo{fig/covering.eps}{fig/calc_fc.eps}
+  \plotone{fig/geo_corr.eps}
   \caption{\label{fig:covering} (a) A two-dimensional illustration of
@@
     dark and light grey.  The photo-ionization and photo-heating rates
-    should be corrected by this overlap fraction $f_c$.  (b)
-    Annotation of quantities used in this geometric correction.}
+    should be corrected by the ratio of these areas, i.e. the overlap
+    fraction $f_c$.  (b) Annotation of quantities used in this
+    geometric correction.}
 \end{figure}
@@
 orthogonal direction.  The distance to the closest cell boundary is
-$D_{\rm edge} = dx/2 - \min_{i=1 \rightarrow 3} (D_{\rm c,i})$.  Thus
+$D_{\rm edge} = dx/2 - \max_{i=1 \rightarrow 3} (D_{\rm c,i})$.  Thus
 the covering factor is related to the square of the ratio between the
@@
 
-\begin{figure*}
-  \epsscale{2}
+\begin{figure}
   \plottwo{fig/dtp_test3noavg.eps}{fig/dtp_test3.eps}
-  \epsscale{1}
   \caption{\label{fig:dtsmooth} Radiative transfer adaptive timestep
@@
     the neutral fraction change to 5\% in the ionization front.  The
-    unmodified timestep (left) is slightly more noisy and the minima
+    unmodified timestep (top) is slightly more noisy and the minima
     are more prominent than the timestep computed with a running
-    average of the last two timesteps (right).  The points show every
+    average of the last two timesteps (bottom).  The points show every
     tenth timestep taken into account for the running average.  The
@@
     into the next neutral cell in the overdensity.}
-\end{figure*}
+\end{figure}
 
@@
 
-\textbf{Reorganize to be more clear!}
-
 Ionization front velocities can approach significant fractions of the
@@
 %
-based on the incident radiation field at a particular position.  The
-timestep is then chosen so that the ionization front only crosses one
-cell per timestep $dt_{\rm P, cell} = dx / v_{\rm IF}$, and the global
-timestep is $dt_{\rm P} = \min(dt_{\rm P, cell})$.
-
-To make this approach computationally straightforward, we consider a
-spherically symmetric case without recombinations.  Thus all photons
-emitted from the source result in an ionization (also see
-\S\ref{sec:dt_hi}).  Ultimately in any approach, we are focused on
-accurately following the time evolution of the radiation field.  In
-this method, we base the timestep directly on the change in radiation
-field, the specific intensity, $I/\dot{I}$.  We consider the field
-after propagating through the cell, so $I = I_0 \exp(-\tau)$, where
-$\tau = n_{\rm H} \sigma dl$ is the optical depth through the cell.
-The change in specific intensity is
+based on the incident radiation field at a particular position.
+Alternatively, the propagation of the ionization front can be
+restricted by limiting the change in specific intensity $I$ to a
+safety factor $C_{\rm RT,cfl}$, resulting in a timestep of
+%
+\begin{equation}
+  \label{eqn:vifront1}
+  dt_P = C_{\rm RT,cfl} \frac{I}{|dI/dt|}.
+\end{equation}
+%
+We consider the specific intensity after the ray travels through the
+cell, so $I = I_0 \exp(-\tau)$, where $\tau = n_{\rm H} \sigma dl$ is
+the optical depth through the cell.  The time derivative of $I$ is
 %
@@
 %
-This results in a local timestep
+$\dot{n}_{\rm H}$ is computed with the same formula as
+Eq. \ref{eqn:dtelec}. Substituting in Eq. \ref{eqn:vifront1} gives
 %
@@
   \label{eqn:vifront4}
-  dt_P = \frac{I}{|dI/dt|} = C_{\rm RT,cfl} \frac{n_{\rm H}}{\tau \dot{n}_{\rm H}},
-\end{equation}
-%
-where $C_{\rm RT,cfl}$ is a safety factor that restricts the change in
-intensity to its inverse.  In practice, we have found that a ceiling
-of 3 can be placed on the optical depth, so optically thick cells do
-not create a very small timestep.  We still find excellent agreement
-with analytical solutions with this approximation.  We show the
-accuracy using this timestep method in \S\ref{sec:dt_dep}.
+  dt_P = C_{\rm RT,cfl} \frac{n_{\rm H}}{\tau \dot{n}_{\rm H}}.
+\end{equation}
+%
+In practice, we have found that a ceiling of 3 can be placed on the
+optical depth, so optically thick cells do not create a very small
+timestep.  We still find excellent agreement with analytical solutions
+with this approximation.  We show the accuracy using this timestep
+method in \S\ref{sec:dt_dep}.
 
@@
 
-\begin{figure*}
-  \epsscale{2}
+\begin{figure}
   \plottwo{fig/test1_ionfrac.eps}{fig/test1_ifront.eps}
-  \epsscale{1}
   \caption{\label{fig:test1_ifront} Test 1 (\hii region
-    expansion with a monochromatic spectrum of 13.6 eV).  Left:
+    expansion with a monochromatic spectrum of 13.6 eV).  Top:
     Radially averaged profile of neutral (solid) and ionized (dashed)
-    fraction at 10, 30, 100, and 500 Myr.  Right: Evolution of the
+    fraction at 10, 30, 100, and 500 Myr.  Bottom: Evolution of the
     calculated (top, dashed) and analytical (top, solid) Str\"{o}mgren
     radius.  The ratio of these radii are plotted in the bottom panel.}
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{figure*}
-  \epsscale{2}
-  \plottwo{fig/test2_ionfrac.eps}{fig/test2_neutral.eps}
-  \epsscale{1}
-  \caption{\label{fig:test2_1} Test 2. (\hii region
-    expansion with a $T=10^5$ K blackbody spectrum).  Left:
-    Radially averaged profile of neutral (solid) and ionized (dashed)
-    fraction at 10, 30, 100, and 500 Myr.  Right: Evolution of the
-    average neutral fraction.}
-\end{figure*}
+\begin{figure}
+  \plotone{fig/test2_ionfrac.eps}
+  \caption{\label{fig:test2_1a} Test 2. (\hii region expansion with a
+    $T=10^5$ K blackbody spectrum).  Radially averaged profile of
+    neutral (solid) and ionized (dashed) fraction at 10, 30, 100, and
+    500 Myr.}
+\end{figure}
+
+\begin{figure}
+  \plotone{fig/test2_neutral.eps}
+  \caption{\label{fig:test2_1b} Test 2. (\hii region expansion with a
+    $T=10^5$ K blackbody spectrum).  Evolution of the average neutral
+    fraction.}
+\end{figure}
 
@@
 
-In Figure \ref{fig:test2_1}, we show the radially averaged neutral and
-ionized fraction at $t = $ 10, 30, 100, and 500 Myr, and the total
-neutral fraction of the domain.  Compared with Test 1, the ionization
-front is thicker, as expected with the harder spectrum.  The total
-neutral fraction decreases to 0.67 over 4$t_{\rm rec} = 500$ Myr,
-which is in agreement with the analytical expectation and other codes
-in RT06.  In Figure \ref{fig:test2_2}, we show slices of neutral
-fraction and temperature through the origin at $t = $ 10 and 100 Myr.
-Here one sees the spherically symmetric \hii regions and a smooth
-temperature transition to the neutral ambient medium.  In Figure
-\ref{fig:test2_3}, we show the ratio of the ionization front radius
-$r_{\rm IF}$ in our simulation and $R_s$.  Before $1.5t_{\rm rec}$,
-$r_{\rm IF}$ lags behind $R_s$, initially by 10\% and then increases
-to $R_s$; however afterwards, this ratio asymptotes to a solution that
-is 4\% greater than $R_s$.  This behavior is approximately the median
-result in RT06, where this ratio varies between 1 and 1.1, and the
-early evolution of $r_{\rm IF}$ is under-predicted by almost all of
-the codes.  If we use one energy group with the mean energy (29.6 eV)
-of a $T=10^5$ K blackbody, we find that $r_{\rm IF}/R_s$ = 1.08, which
-is representative of the codes in the upper range of RT06.
+In Figure \ref{fig:test2_1a}, we show the radially averaged neutral
+and ionized fraction at $t = $ 10, 30, 100, and 500 Myr, and the total
+neutral fraction of the domain in Figure \ref{fig:test2_1b}.  Compared
+with Test 1, the ionization front is thicker, as expected with the
+harder spectrum.  The total neutral fraction decreases to 0.67 over
+4$t_{\rm rec} = 500$ Myr, which is in agreement with the analytical
+expectation and other codes in RT06.  In Figure \ref{fig:test2_2}, we
+show slices of neutral fraction and temperature through the origin at
+$t = $ 10 and 100 Myr.  Here one sees the spherically symmetric \hii
+regions and a smooth temperature transition to the neutral ambient
+medium.  In Figure \ref{fig:test2_3}, we show the ratio of the
+ionization front radius $r_{\rm IF}$ in our simulation and $R_s$.
+Before $1.5t_{\rm rec}$, $r_{\rm IF}$ lags behind $R_s$, initially by
+10\% and then increases to $R_s$; however afterwards, this ratio
+asymptotes to a solution that is 4\% greater than $R_s$.  This
+behavior is approximately the median result in RT06, where this ratio
+varies between 1 and 1.1, and the early evolution of $r_{\rm IF}$ is
+under-predicted by almost all of the codes.  If we use one energy
+group with the mean energy (29.6 eV) of a $T=10^5$ K blackbody, we
+find that $r_{\rm IF}/R_s$ = 1.08, which is representative of the
+codes in the upper range of RT06.
 
@@
 
-\begin{figure*}
-  \epsscale{2}
+\begin{figure}
   \plottwo{fig/test3_HI.eps}{fig/test3_temp.eps}
-  \epsscale{1}
   \caption{\label{fig:test3_1} Test 3. (I-front trapping in a dense
-    clump and shadowing).  Left panel: Line cut from the point source
-    through the middle of the dense clump at $t = 1, 3, 5, 15$ Myr.
-    of the average neutral fraction (left) and temperature
-    (right) of the clump.}
-\end{figure*}
+    clump and shadowing).  Line cut from the point source through the
+    middle of the dense clump at $t = 1, 3, 5, 15$ Myr.  of the
+    average neutral fraction (top) and temperature (bottom) of the
+    clump.}
+\end{figure}
 
@@
 dense gas is optically thick.
-
-\li Perhaps add more description?
 
@@
 
-\begin{figure*}
+\begin{figure}
   %\epsscale{1.15}
-  \epsscale{2}
   \plottwo{fig/test12_kph}{fig/test12_radial}
-  \epsscale{1}
   \caption{\label{fig:test12_kph} Test 12 (Time variations of the
-    source luminosity).  Left: Slice of the photo-ionization rate
+    source luminosity).  Top: Slice of the photo-ionization rate
     \kph~through the origin.  The source has a duty cycle of 0.5 Myr,
@@
     source was at its peak luminosity, illustrating the
-    time-dependence of the radiative transfer equation.  Right: Radial
-    profile \kph~with the inverse square law overplotted.}
+    time-dependence of the radiative transfer equation.  Bottom:
+    Radial profile \kph~with the inverse square law overplotted.}
   %\epsscale{1}
-\end{figure*}
+\end{figure}
 
@@
 \end{figure}
+
+\begin{figure*}
+  \epsscale{2}
+  \plotone{fig/test14_slices_xy}
+  \epsscale{1}
+  \caption{\label{fig:test14_1} Test 14. (\hii region with MHD).
+    Left to right: slices of density at $t = 0.18, 0.53, 1.58$ Myr in
+    the x-y plane.  The streamlines show the magnetic field.}
+\end{figure*}
+
+\begin{figure*}
+  \epsscale{2}
+  \plotone{fig/test14_slices_yz}
+  \epsscale{1}
+  \caption{\label{fig:test14_2} Test 14. (\hii region with
+    MHD). Slices of density (top) and the x-component of the magnetic
+    field (bottom) in the y-z plane at $t = 0.18, 0.53, 1.58$ Myr
+    (left to right).}
+\end{figure*}
 
@@
 
-\li Add more description of the problem.
-
 \subsection{Test 14. \hii region with MHD}
-
-\begin{figure*}
-  \epsscale{2}
-  \plotone{fig/test14_slices_xy}
-  \epsscale{1}
-  \caption{\label{fig:test14_1} Test 14. (\hii region with MHD).
-    Left to right: slices of density at $t = 0.18, 0.53, 1.58$ Myr in
-    the x-y plane.  The streamlines show the magnetic field.}
-\end{figure*}
-
-\begin{figure*}
-  \epsscale{2}
-  \plotone{fig/test14_slices_yz}
-  \epsscale{1}
-  \caption{\label{fig:test14_2} Test 14. (\hii region with
-    MHD). Slices of density (top) and the x-component of the magnetic
-    field (bottom) in the y-z plane at $t = 0.18, 0.53, 1.58$ Myr
-    (left to right).}
-\end{figure*}
 
@@
 
-\begin{figure*}
+\begin{figure}
   %\epsscale{1}
-  \epsscale{2}
+  %\epsscale{2}
   \plotone{fig/phic_slices}
@@
   %\epsscale{1}
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{figure*}
+\begin{figure}
   %\epsscale{1.05}
-  \epsscale{2}
   \plottwo{fig/nures040}{fig/nures100}
-  \epsscale{1}
   \caption{\label{fig:nu_dep} Radial profiles of (clockwise from the
@@
     bins sampling the $T=10^5$ K blackbody spectrum.  The data are
-    shown at $t = 200$ Myr (left) and $t = 500$ Myr (right).  The
+    shown at $t = 200$ Myr (top) and $t = 500$ Myr (bottom).  The
     double-peaked structure in the shock only appears with a
@@
 
-\begin{figure*}
+\begin{figure}
   %\epsscale{1.075}
-  \epsscale{2}
   \plottwo{fig/noRP_profiles.eps}{fig/RP_profiles.eps}
-  \epsscale{1}
   \caption{\label{fig:rp_profiles} (a) No radiation pressure.

### 2010-11-16 mnras.tex
Completed and alphabetized symbol table.

@@
 \input macros.tex
-\voffset=-2cm
+\voffset=-1.4cm
 
@@
   \label{eqn:Rstr}
-  R_s = \left(\frac{3\dot{N}_\gamma}{4\pi \alpha_{\rm B} n_H^2}\right)^{1/3},
+  R_s = \left(\frac{3\dot{N}_\gamma}{4\pi \alpha_{\rm B} n_{\rm
+        H}^2}\right)^{1/3},
 \end{equation}
@@
 \section{Treatment of Radiative Transfer}
+\label{sec:rt}
 
@@
 \begin{equation}
+\label{eqn:dndt}
 \frac{dn_{\rm H}}{dt} = \alpha_B n_e n_p - C_{\rm H} n_e n_{\rm
@@
 geometry cell face and HEALPix pixel when the pixel does not cover the
-entire cell face, which is illustrated in Figure \ref{fig:covering}.
+entire cell face, which is illustrated in Fig. \ref{fig:covering}.
 This mismatch causes non-spherical artifacts and is most apparent in
@@
 segment midpoint to the closest cell boundary $D_{\rm c,i}$, which is
-depicted in Figure \ref{fig:covering}.  To estimate $f_c$, we first
+depicted in Fig. \ref{fig:covering}.  To estimate $f_c$, we first
 find the distance $d_{\rm center,i}$ from the midpoint of the ray
@@
 \begin{equation}
+  \label{eqn:compton}
   \frac{dP_C}{P} = (1 - e^{-\tau_e}) \frac{\Delta(T_e)}{E_{ph}},
@@
 \begin{equation}
+  \label{eqn:radpres}
   d\mathbf{p}_\gamma = \frac{dP \; E_{\rm ph}}{c} \; \hat{r}
@@
 \section{Numerical Implementation in Enzo}
+\label{sec:numerical}
 
@@
     coupling with the hydrodynamics.  The ray tracing algorithm, which
-    is contained in the ``Trace Rays'' is detailed in Figure
+    is contained in the ``Trace Rays'' is detailed in Fig.
     \ref{fig:RTalgorithm}.}
@@
 We illustrate the underlying algorithm of the ray tracing module in
-\enzo~in Figure \ref{fig:MainAlgorithm} and the ray tracing algorithm
-is shown in Figure \ref{fig:RTalgorithm}.  The module is only called
+\enzo~in Fig. \ref{fig:MainAlgorithm} and the ray tracing algorithm
+is shown in Fig. \ref{fig:RTalgorithm}.  The module is only called
 when advancing the finest AMR level.  We describe its steps below.
@@
 \end{equation}
-Figure \ref{fig:dtsmooth} shows the smooth evolution of $dt_{\rm P}$
+Fig. \ref{fig:dtsmooth} shows the smooth evolution of $dt_{\rm P}$
 in a growing Str\"{o}mgren sphere when compared to the values of
@@
 idle time of each processor when it is waiting to receive data.  In
-the loop shown in Figure \ref{fig:MainAlgorithm} with the conditional
+the loop shown in Fig. \ref{fig:MainAlgorithm} with the conditional
 that checks whether we have traced all of the rays, we aggressively
@@
 
-In Figure \ref{fig:test1_ifront}, we show (a) the evolution of the
+In Fig. \ref{fig:test1_ifront}, we show (a) the evolution of the
 neutral and ionization fraction as a function of radius at $t = $ 10,
@@
 neutral fraction increases to 0.2, which is close to its equilibrium
-value.  In the right panel of Figure \ref{fig:test1_ifront}, the
+value.  In the right panel of Fig. \ref{fig:test1_ifront}, the
 ionization front radius exceeds $R_s$ by a few percent for most of the
@@
 results are in excellent agreement with this more accurate analytical
-solution.  In Figure \ref{fig:test1_HI}, we show a slice of the
+solution.  In Fig. \ref{fig:test1_HI}, we show a slice of the
 neutral fraction through the origin.  Other than the ray splitting
@@
 
-In Figure \ref{fig:test2_1a}, we show the radially averaged neutral
+In Fig. \ref{fig:test2_1a}, we show the radially averaged neutral
 and ionized fraction at $t = $ 10, 30, 100, and 500 Myr, and the total
-neutral fraction of the domain in Figure \ref{fig:test2_1b}.  Compared
+neutral fraction of the domain in Fig. \ref{fig:test2_1b}.  Compared
 with Test 1, the ionization front is thicker, as expected with the
@@
 4$t_{\rm rec} = 500$ Myr, which is in agreement with the analytical
-expectation and other codes in RT06.  In Figure \ref{fig:test2_2}, we
+expectation and other codes in RT06.  In Fig. \ref{fig:test2_2}, we
 show slices of neutral fraction and temperature through the origin at
@@
 regions and a smooth temperature transition to the neutral ambient
-medium.  In Figure \ref{fig:test2_3}, we show the ratio of the
+medium.  In Fig. \ref{fig:test2_3}, we show the ratio of the
 ionization front radius $r_{\rm IF}$ in our simulation and $R_s$.
@@
 
-In Figure \ref{fig:test3_1}, we show neutral fraction and temperature
+In Fig. \ref{fig:test3_1}, we show neutral fraction and temperature
 of a one-dimensional cut through the center of the dense clump at $z =
@@
 10,000 and 20,000 K, but decreases sharply with the ionized fraction.
-Figure \ref{fig:test3_2} depicts the average ionized fraction and
+Fig. \ref{fig:test3_2} depicts the average ionized fraction and
 temperature inside the dense clump, which both gradually increase as
@@
 are consistent with RT06.  Finally we show slices of neutral fraction
-and temperature in the $z = 0.5$ plane in Figure \ref{fig:test3_3}.
+and temperature in the $z = 0.5$ plane in Fig. \ref{fig:test3_3}.
 The neutral fraction slices prominently show the sharp shadows created
@@
 mass-averaged $x_m$ and volume-averaged $x_v$ ionized fraction in
-Figure \ref{fig:test4_1}.  Initially $x_m$ is larger than $x_v$, and
+Fig. \ref{fig:test4_1}.  Initially $x_m$ is larger than $x_v$, and
 at $t \sim 170$ kyr, the $x_v$ becomes larger.  This is indicative of
@@
 representations of the electron fraction slices]{Pawlik10}.  In the
-slices of electron fraction and temperature, Figure \ref{fig:test4_2},
+slices of electron fraction and temperature, Fig. \ref{fig:test4_2},
 the photo-heated regions are larger than the ionized regions by a
@@
 
-The growth of the ionization front radius is shown in Figure
+The growth of the ionization front radius is shown in Fig.
 \ref{fig:test5_1}, using both $T = 10^4$ K and $x_e = 0.5$ as
@@
 because the ionization front becomes broad as the D-type front creates
-a shock.  Densities in this shock, as seen in Figure
+a shock.  Densities in this shock, as seen in Fig.
 \ref{fig:test5_2}, are high enough for the gas to recombine but not
@@
 
-Figure \ref{fig:test5_2} shows the progression of the ionization front
+Fig. \ref{fig:test5_2} shows the progression of the ionization front
 at times $t$ = 10, 200, and 500 Myr in radial profiles of density,
@@
 creates the double-peaked features in the density profiles at 200 and
-500 Myr.  Figure \ref{fig:test5_3} shows slices through the origin of
+500 Myr.  Fig. \ref{fig:test5_3} shows slices through the origin of
 the same quantities, including neutral fraction.  These depict the
@@
 Because this problem does not have an analytical solution, we compare
-our calculated ionization front radius and velocity, shown in Figure
+our calculated ionization front radius and velocity, shown in Fig.
 \ref{fig:test6_1}, to the RT09 results.  Their evolution are in
@@
 ionization front velocity from the radii at 50 outputs, which causes
-the noise seen Figure \ref{fig:test6_1}.
+the noise seen Fig. \ref{fig:test6_1}.
 
@@
 the radial profiles of density, temperature, ionized fraction, and
-pressure in Figure \ref{fig:test6_2}.  The inner density decreases
+pressure in Fig. \ref{fig:test6_2}.  The inner density decreases
 over two order of magnitude after 25 Myr.  To illustrate any
-deviations in spherical symmetry, we show in Figure \ref{fig:test6_3}
+deviations in spherical symmetry, we show in Fig. \ref{fig:test6_3}
 slices of density, temperature, neutral fraction, and ionized fraction
@@
   \caption{\label{fig:test7_3} Test 7. (Photo-evaporation of a dense
-    clump).  Same as Figure \ref{fig:test7_1} but at $t = 50$ Myr.}
+    clump).  Same as Fig. \ref{fig:test7_1} but at $t = 50$ Myr.}
 \end{figure*}
@@
 
-Figure \ref{fig:test7_1} shows cuts of density, temperature, neutral
+Fig. \ref{fig:test7_1} shows cuts of density, temperature, neutral
 fraction, and pressure in a line connecting the source and the clump
@@
 propagated through the left-most 500 pc of the clump.  This heated gas
-is now over-pressurized, as seen in the pressure plot in Figure
+is now over-pressurized, as seen in the pressure plot in Fig.
 \ref{fig:test7_1}, and then expands into the ambient medium.  This
@@
 dense overdensities.  These flows become evident in the density at 10
-Myr, seen both in the line cuts and slices (Figure \ref{fig:test7_2}).
+Myr, seen both in the line cuts and slices (Fig. \ref{fig:test7_2}).
 They have temperatures up to 50,000 K.  At this time, the front has
@@
 the rear surface of the clump.  At the end of the test ($t = 50$ Myr),
-only the core and its associated shadow is neutral, seen in Figure
+only the core and its associated shadow is neutral, seen in Fig.
 \ref{fig:test7_3}.  The core has been compressed by the surrounding
@@
 
-We show slices in the x-y and x-z planes of density in Figure
+We show slices in the x-y and x-z planes of density in Fig.
 \ref{fig:test8_1} at $t = 10, 40, 100, 150$ kyr.  In the direction of
@@
   \plotone{fig/test9thin_efrac}
-  \caption{\label{fig:test9_thin} Same as Figure \ref{fig:test9_thick}
+  \caption{\label{fig:test9_thin} Same as Fig. \ref{fig:test9_thick}
     but for the optically thin case.}
@@
 the evolution of the density, temperature, and ionized fraction of the
-optically thick and optically thin cases in Figures
+optically thick and optically thin cases in Figs.
 \ref{fig:test9_thick} and \ref{fig:test9_thin}.  The initial state of
@@
 
-Figure \ref{fig:test10} shows the ionization front overtaking and
+Fig. \ref{fig:test10} shows the ionization front overtaking and
 disrupting the blastwave.  We show the blastwave before the source is
@@
 We illustrate the expansion of the \hii region created by the
-beamed radiation in Figure \ref{fig:test11}.  Before $t = 3$ Myr, the
+beamed radiation in Fig. \ref{fig:test11}.  Before $t = 3$ Myr, the
 \hii region is conical and contained within the dense clump,
@@
 The variability of the source is clearly illustrated in the
-photo-ionization rates, shown in Figure \ref{fig:test12_kph}.  The
+photo-ionization rates, shown in Fig. \ref{fig:test12_kph}.  The
 shells of relative maximum \kph~corresponds to radiation that was
@@
 simulation is run for 200 Myr.  We show the radial profiles of
-density, temperature, ionized fraction, and pressure in Figure
+density, temperature, ionized fraction, and pressure in Fig.
 \ref{fig:test12_profiles}.  The variable source has little effect on
@@
 As the \hii region grows in the magnetized medium, shown in
-Figures \ref{fig:test14_1} and \ref{fig:test14_2}, it transforms from
+Figs. \ref{fig:test14_1} and \ref{fig:test14_2}, it transforms from
 spherical to oblate as it is magnetically confined in directions
@@
 keep all aspects of the test the same, but use resolutions of 16$^3$,
-32$^3$, 64$^3$, and 128$^3$.  In Figure \ref{fig:dx_dep1}, we show the
-ratio $r_{\rm IF}/r_{\rm anyl}$, similar to Figure
+32$^3$, 64$^3$, and 128$^3$.  In Fig. \ref{fig:dx_dep1}, we show the
+ratio $r_{\rm IF}/r_{\rm anyl}$, similar to Fig.
 \ref{fig:test1_ifront}, using these different resolutions.  The radii
@@
 10.1, 25.1)$.  Slices of the photo-ionization rates through the origin
-are shown in Figure \ref{fig:ang_dep1} for these values of $\Phi_c$.
+are shown in Fig. \ref{fig:ang_dep1} for these values of $\Phi_c$.
 In this figure, we limit the colormap range to a factor of 3 to show
@@
 photo-ionization rate and a 1/$r^2$ field, and then plot the standard
-deviation of this difference field versus angular resolution in Figure
+deviation of this difference field versus angular resolution in Fig.
 \ref{fig:ang_dep2}.  We plot this relation for resolutions of $32^3$,
@@
 
-Figure \ref{fig:nu_dep} shows the radial profiles of density,
+Fig. \ref{fig:nu_dep} shows the radial profiles of density,
 temperature, ionized fraction, and radial velocity at $t = 200$ Myr
@@
 and based on incident radiation ($dI/dt$ based; \S\ref{sec:dt_tau}).
-The growth of the ionization front radius is shown in Figure
+The growth of the ionization front radius is shown in Fig.
 \ref{fig:dt_dep1}.  Both the \hii restricted and incident
@@
 adjust accordingly to the physical situation, as seen in the plot of
-timestep versus time (Figure \ref{fig:dt_dep2}).  They provide high
+timestep versus time (Fig. \ref{fig:dt_dep2}).  They provide high
 accuracy when the source first starts to shine.  At later times, the
@@
 Slices of the photo-ionization rates through the origin are shown in
-Figure \ref{fig:fc_slices}, depicting the improvements in spherical
+Fig. \ref{fig:fc_slices}, depicting the improvements in spherical
 symmetry and a closer agreement to a smooth $1/r^2$ profile.  Previous
@@
 (\S\ref{sec:ang_dep}) with $\Phi_c = 5.1$ to show these artifacts in
-\kph~in Figure \ref{fig:rayopt}.  The radiation field strictly follows
+\kph~in Fig. \ref{fig:rayopt}.  The radiation field strictly follows
 a $1/r^2$ profile until it reaches $\tau_{\rm thin} \equiv 0.1$, which
@@
 necessarily equal to each other, creating the angular artifacts seen
-in Figure \ref{fig:rayopt}.  We are continuing to formulate a scheme
+in Fig. \ref{fig:rayopt}.  We are continuing to formulate a scheme
 that avoids these artifacts because this approximation will be very
@@
 use the same setup as Test 5 but with an increased luminosity $L =
-10^{50}$ erg s$^{-1}$ and a mono-chromatic spectrum of 1 keV.  Figure
+10^{50}$ erg s$^{-1}$ and a mono-chromatic spectrum of 1 keV.  Fig.
 \ref{fig:xray_fig} compares the density, temperature, ionized
@@
 
-Figure \ref{fig:xray_fig} shows the main effects of secondary
+Fig. \ref{fig:xray_fig} shows the main effects of secondary
 ionizations from the 1 keV spectrum on the ionization and thermal
@@
 Radial profiles of density, temperature, neutral fraction, and radial
-velocity are shown in Figure \ref{fig:rp_profiles} for both
+velocity are shown in Fig. \ref{fig:rp_profiles} for both
 simulations at several times.  Without radiation pressure, the
@@
 the two sources are enveloped in a common, elongated \hii
-region.  To illustrate this, we show the neutral fraction in Figure
+region.  To illustrate this, we show the neutral fraction in Fig.
 \ref{fig:twosrc}.  Our method keeps spherical symmetry close to the
@@
 the original (Harpertown CPUs) nodes of the NASA NAS machine,
-Pleiades, with 8 cores per node.  Figure \ref{fig:weak} shows the
+Pleiades, with 8 cores per node.  Fig. \ref{fig:weak} shows the
 performance timings of various parts of the code.  From one to two
@@
 
-Figure \ref{fig:strong} shows the strong scaling results of this
+Fig. \ref{fig:strong} shows the strong scaling results of this
 calculation.  The hydrodynamics and non-equilbrium chemistry routines

### 2010-11-16 mnras.tex
Converted to British spelling.

@@
-\documentclass[useAMS,usenatbib,a4paper]{mn2e}
+\documentclass[useAMS,usenatbib]{mn2e}
 
@@
   equation and non-equilibrium chemistry network, our radiation
-  hydrodynamics framework can be utilized to study a broad range of
+  hydrodynamics framework can be utilised to study a broad range of
   astrophysical problems, such as stellar and black hole (BH)
@@
   \citet{RT06, Iliev09}.  We further test our method with more
-  dynamical situations, for example, the propagation of an ionization
+  dynamical situations, for example, the propagation of an ionisation
   front through a Rayleigh-Taylor instability, time-varying
   luminosities, and collimated radiation.  The test suite also
-  includes an expanding \hii region in a magnetized medium, utilizing
+  includes an expanding \hii region in a magnetised medium, utilising
   the newly implemented magnetohydrodynamics module in \enzo.  This
@@
   distributed memory machines and can include radiation pressure and
-  secondary ionizations from X-ray radiation.  It is included in the
+  secondary ionisations from X-ray radiation.  It is included in the
   newest public release of Enzo.
@@
 An important case was considered by \citet{Stroemgren39} for an
-ultraviolet (UV) radiation source photoionizing a static uniform
-neutral medium.  When recombinations balance photo-ionizations, the
+ultraviolet (UV) radiation source photo-ionising a static uniform
+neutral medium.  When recombinations balance photo-ionisations, the
 radius of a so-called \hii region,
@@
 \end{equation}
-where $\dot{N}_\gamma$ is the ionizing photon luminosity, $\alpha_{\rm
+where $\dot{N}_\gamma$ is the ionising photon luminosity, $\alpha_{\rm
   B}$ is the recombination rate, and $n_H$ is the ambient hydrogen
 number density.  Furthermore he found that the delineation between the
-neutral and ionized medium to be approximately the mean free path of
-the ionizing radiation.  His seminal work was expanded upon by
+neutral and ionised medium to be approximately the mean free path of
+the ionising radiation.  His seminal work was expanded upon by
 \citet{Spitzer48, Spitzer49, Spitzer54} and \citet{Spitzer50}, who
-showed that the ionizing radiation heated the medium to $T \sim 10^4$
-K.  If the density is equal on both sides of the ionization front,
-then this over-pressurized region would expand and drive a shock
+showed that the ionising radiation heated the medium to $T \sim 10^4$
+K.  If the density is equal on both sides of the ionisation front,
+then this over-pressurised region would expand and drive a shock
 outwards \citep[e.g.][]{Oort54, Schatzman55}.  These early works
@@
 models of \hii regions in spherical symmetry and plane-parallel
-ionization fronts were developed \citep[e.g.][]{Mathews65, Lasker66,
-  Hjellming66}.  They described the expansion of the ionization front
+ionisation fronts were developed \citep[e.g.][]{Mathews65, Lasker66,
+  Hjellming66}.  They described the expansion of the ionisation front
 and the evolution of its associated shock wave that carries most of
 the gas away from the source.  At the same time, theoretical models of
-ionization fronts matured and were classified by \citet{Kahn54} and
+ionisation fronts matured and were classified by \citet{Kahn54} and
 \citet{Axford61} as either R-type (rare) or D-type (dense).  In R-type
-fronts, the ionized gas density is higher than the neutral gas
+fronts, the ionised gas density is higher than the neutral gas
 density, and in D-type fronts, the opposite is true.  R-type fronts
@@
 fronts move supersonically and subsonically with respect to the
-ionized gas, respectively.  The same terminology conversely applies to
+ionised gas, respectively.  The same terminology conversely applies to
 D-type fronts.  ``Critical'' fronts are defined as moving exactly at
@@
 \item Weak R-type:  When the star (gradually) starts to shine, the
-  ionization front will move supersonically through the ambient
-  medium.  The gas is heated and ionized, but otherwise left
+  ionisation front will move supersonically through the ambient
+  medium.  The gas is heated and ionised, but otherwise left
   undisturbed.  This stage continues until $r \sim 0.02R_s$.
-\item Critical R-type:  As the ionization front moves outwards, it
+\item Critical R-type:  As the ionisation front moves outwards, it
   begins to slow because of the geometric dilution of the radiation.
@@
   strong D-type front, and then a critical D-type front.  From this
-  point forward, it is moving subsonically with respect to the ionized
+  point forward, it is moving subsonically with respect to the ionised
   gas, i.e. a weak D-type front.  Thus sound waves can travel across
-  the ionization front and form a shock.  The ionization front
-  detaches from the shock, putting the shock ahead of the ionization
+  the ionisation front and form a shock.  The ionisation front
+  detaches from the shock, putting the shock ahead of the ionisation
   front.
@@
   recombination rates.  This increases the number of photons available
-  for ionizing the gas.  The sphere expands until it reaches pressure
+  for ionising the gas.  The sphere expands until it reaches pressure
   equilibrium with the ambient medium at $r \sim 5R_s$.
@@
 medium was usually set up to be a constant pressure boundary.  When
-the ionization front passes this boundary, the dense, ionized gas is
+the ionisation front passes this boundary, the dense, ionised gas is
 orders of magnitude out of pressure equilibrium as the temperatures on
@@
 calculations were performed with static density distributions.  One
-example is calculating cosmological reionization by post-processing of
+example is calculating cosmological reionisation by post-processing of
 density fields from N-body simulations \citep{Ciardi01, Sokasian01,
@@
   OShea2004}.  The radiation field is coupled to the hydrodynamics
-solver at small timescales, enabling it to study radiation
+solver at small time-scales, enabling it to study radiation
 hydrodynamical problems.  We have used this code to investigate the
 growth of an \hii region from a 100\Ms~Population III (Pop III) star
-\citep{Abel07}, the early stages of reionization from Pop III stars
+\citep{Abel07}, the early stages of reionisation from Pop III stars
 \citep{Wise08_Reion}, radiative feedback on the formation of high
 redshift dwarf galaxies \citep{Wise08_Gal, Wise10_Gal}, ultraviolet
-radiation escape fractions from dwarf galaxies before reionization
+radiation escape fractions from dwarf galaxies before reionisation
 \citep{Wise09}, negative radiative feedback from accreting Pop III
@@
 radiative transfer equation.  Furthermore, we detail how physics other
-than photo-ionization and photo-heated are included.  We then derive a
+than photo-ionisation and photo-heated are included.  We then derive a
 geometric correction factor to any ray tracing method to improve
@@
 solver, (3) several methods to calculate the radiative transfer
-timestep, and (4) our parallelization strategy.  We present our
+timestep, and (4) our parallelisation strategy.  We present our
 results from the RT06 radiative transfer tests in Section 4.
@@
 8, we demonstrate the parallel scalability of Enzo+Moray.  Last
-Section 9 summarizes our method and results.
+Section 9 summarises our method and results.
 
@@
 propagated along the direction $\hat{n}$.  Next we describe this
-discretization and its contribution to the radiation field.
+discretisation and its contribution to the radiation field.
 
@@
 
-We avoid this inefficiency by utilizing adaptive ray tracing
+We avoid this inefficiency by utilising adaptive ray tracing
 \citep{Abel02_RT}, which progressively splits rays when the sampling
@@
 Pixelation \citep[HEALPix;][]{HEALPix}.  In this scheme, the rays are
-traced along normal directions of the centers of HEALPix pixels, which
-evenly divides a sphere into equal areas.  The rays are initialized at
+traced along normal directions of the centres of HEALPix pixels, which
+evenly divides a sphere into equal areas.  The rays are initialised at
 each point source with the photon luminosity (ph s$^{-1}$) equally
@@
 timestep.  In the next timestep, the photon will encounter a different
-hydrodynamical and ionization state, hence $\kappa$, in its path.
+hydrodynamical and ionisation state, hence $\kappa$, in its path.
 Furthermore any time variations of the luminosities will be retained
@@
 (\ref{eqn:rtray}) along each ray, which is done by considering the
-discretization of the ray into segments.  In the following section, we
+discretisation of the ray into segments.  In the following section, we
 assume the rays are monochromatic.  For convenience, we express the
@@
 number density of the absorbing medium, respectively.  We use the
-cell-centered density in our calculations.  Using trilinearly
+cell-centred density in our calculations.  Using trilinearly
 interpolated densities \citep[see][]{Mellema06} did not produce
@@
 \end{equation}
-as it crosses a cell.  We equate the photo-ionization rate to the
+as it crosses a cell.  We equate the photo-ionisation rate to the
 absorption rate, resulting in photon conservation \citep{Abel99_RT,
-  Mellema06}.  Thus the photo-ionization $k_{\rm ph}$ and
+  Mellema06}.  Thus the photo-ionisation $k_{\rm ph}$ and
 photo-heating $\Gamma_{\rm ph}$ rates associated with a single ray are
@@
 where $V_{\rm cell}$ is the cell volume, $E_{\rm ph}$ is the photon
-energy, and $E_i$ is the ionization energy of the absorbing material.
-In each cell, the photo-ionization and photo-heating rates from each
+energy, and $E_i$ is the ionisation energy of the absorbing material.
+In each cell, the photo-ionisation and photo-heating rates from each
 ray in the calculation are summed, and after the ray tracing is
-complete, these rates can be used to update the ionization state and
+complete, these rates can be used to update the ionisation state and
 energy of the cells.  Considering a system with only hydrogen
-photo-ionizations and radiative recombinations, these changes are very
+photo-ionisations and radiative recombinations, these changes are very
 straightforward and is useful for illustrative purposes.  The change
@@
 locally reabsorbed, \citep{Spitzer78}, and $C_{\rm H}$ is the
-collisional ionization rate.  However, for more accurate solutions in
+collisional ionisation rate.  However, for more accurate solutions in
 calculations that consider several chemical species, the
-photo-ionization rates are terms in the relevant chemical networks
+photo-ionisation rates are terms in the relevant chemical networks
 \citep[e.g.][]{Abel97}.
@@
     where the full area $(dr \times L_{\rm pix})$ is colored by the
-    dark and light grey.  The photo-ionization and photo-heating rates
+    dark and light grey.  The photo-ionisation and photo-heating rates
     should be corrected by the ratio of these areas, i.e. the overlap
@@
 calculation of the radiation field.  This correction is not unique to
-the HEALPix formalism but can be applied to any type of pixelization.
+the HEALPix formalism but can be applied to any type of pixelisation.
 
@@
 depicted in Fig. \ref{fig:covering}.  To estimate $f_c$, we first
-find the distance $d_{\rm center,i}$ from the midpoint of the ray
-segment to the cell center $x_{\rm 0,i}$ in orthogonal directions,
+find the distance $d_{\rm centre,i}$ from the midpoint of the ray
+segment to the cell centre $x_{\rm 0,i}$ in orthogonal directions,
 %
@@
 would consider the distance between the cell boundary and ray segment
-midpoint in the direction between the midpoint and cell center of
+midpoint in the direction between the midpoint and cell centre of
 $\mathbf{x}_{\rm mid} - \mathbf{x}_0$.  We find that the method
@@
 depth $\tau$ traversed by the photon.  If $\tau < \tau_{\rm thin} \sim
-0.1$ after the ray exits the cell, we calculate the photo-ionization
+0.1$ after the ray exits the cell, we calculate the photo-ionisation
 and photo-heating rates directly from the incoming ray instead of the
@@
 $r_{\rm ray}$ are the radii from the radiation source to the cell
-center and where the ray exits the cell.  Thus the last factor
-corrects the flux to a value appropriate for the cell center.  The
+centre and where the ray exits the cell.  Thus the last factor
+corrects the flux to a value appropriate for the cell centre.  The
 photo-heating ray is calculated in the same manner as the general
@@
 rays enter a single cell.  In the case of a single radiation source,
-the solution is simple -- only assign the cell the photo-ionization
+the solution is simple -- only assign the cell the photo-ionisation
 and photo-heating rates when $k_{\rm ph} = 0$.  However in the case
@@
 \texttt{i} by evaluating \texttt{(MarkerField[i] $\gg$ n \& 1)}.  If
-false, then we can add the optically thin approximation
-(Eq. \ref{eqn:optthin}) to the cell and set \texttt{MarkerField[i] |=
-  (1 $\gg$ n);} to mark the cell.
+false, then we can add the optically thin approximation [equation
+(\ref{eqn:optthin})] to the cell and set \texttt{MarkerField[i] |= (1
+  $\gg$ n);} to mark the cell.
 
@@
 such as attenuation of radiation in the Lyman-Werner bands, secondary
-ionizations from X-ray radiation, Compton heating of from scattered
+ionisations from X-ray radiation, Compton heating of from scattered
 photons, and radiation pressure.  We describe our implementation of
@@
 
-\subsubsection{Secondary Ionizations from X-rays}
+\subsubsection{Secondary Ionisations from X-rays}
 \label{sec:xrays}
@@
 At the other end of the spectrum, a high-energy ($E_{\rm ph} \gsim
-100$ eV) photon can ionize multiple neutral hydrogen and helium atoms,
+100$ eV) photon can ionise multiple neutral hydrogen and helium atoms,
 and this should be considered in such radiation fields.
@@
 varying electron fractions and photon energies up to 3 keV.  They find
-that the excitation of hydrogen and helium and the ionization of
-He {\sc ii} is negligible.  The number of secondary ionizations of H
-and He is reduced from the ratio of the photon and ionization energies
+that the excitation of hydrogen and helium and the ionisation of
+He {\sc ii} is negligible.  The number of secondary ionisations of H
+and He is reduced from the ratio of the photon and ionisation energies
 ($E_{\rm ph} / E_i$) by a factor of
@@
 and approaches one as $x \rightarrow 1$.  Thus in gas with low
-electron fractions, most of the energy results in ionizations of
-hydrogen and helium, and in nearly ionized gas, the energy goes into
+electron fractions, most of the energy results in ionisations of
+hydrogen and helium, and in nearly ionised gas, the energy goes into
 photo-heating.
@@
 hydrodynamics and then the importance of correct time-stepping.  Last
-we give our parallelization strategy of tracing rays through an AMR
+we give our parallelisation strategy of tracing rays through an AMR
 hierarchy.  This implementation is included in the \texttt{v2.0}
@@
 
-\step{2} Initialize all radiation fields to zero.
+\step{2} Initialise all radiation fields to zero.
 
@@
 the optical depth of the current cell (Equation \ref{eqn:dtau}),
-photo-ionization and photo-heating rates (Equations \ref{eqn:kph} and
+photo-ionisation and photo-heating rates (Equations \ref{eqn:kph} and
 \ref{eqn:gamma}), and add the column density of the cell to the total
@@
 \step{3g} Add the effects of any optional physics modules
-(\S\ref{sec:addphysics}) -- secondary ionizations from X-rays, Compton
+(\S\ref{sec:addphysics}) -- secondary ionisations from X-rays, Compton
 heating from scattering, and radiation pressure.
@@
 groups \citep[][Ch. 6]{Mihalas84}, and are assigned a photon type that
-corresponds whether it is a photon that (1) ionizes hydrogen, (2)
-singly ionizes helium, (3) doubly ionizes helium, (4) has an X-ray
+corresponds whether it is a photon that (1) ionises hydrogen, (2)
+singly ionises helium, (3) doubly ionises helium, (4) has an X-ray
 energy, or (5) dissociates molecular hydrogen (Lyman-Werner
@@
 for early termination of rays that are fully absorbed, which are
-likely to have high absorption cross-sections (e.g. \hi ionizations
-near 13.6 eV) or a low initial intensity (e.g. He {\sc ii} ionizing
+likely to have high absorption cross-sections (e.g. \hi ionisations
+near 13.6 eV) or a low initial intensity (e.g. He {\sc ii} ionising
 photons in typical stellar populations).  The other approach used by
@@
 For example when modeling Population III stellar radiation
-\citep[e.g.][for hydrogen ionizing radiation only]{Abel07,
+\citep[e.g.][for hydrogen ionising radiation only]{Abel07,
   Wise08_Gal}, we have 3 energy groups -- H {\sc i}, He {\sc i}, He
 {\sc ii} -- each with an energy that equals the average photon energy
-above the ionization threshold.
+above the ionisation threshold.
 
@@
 but coupling the effects of radiation to the gas dynamics is even more
-difficult because the radiation fields must be updated on a timescale
+difficult because the radiation fields must be updated on a time-scale
 such that it can react to the radiative heating, i.e. sound-crossing
@@
 being solved.  In simulations with radiative transfer, the radiation
-field can change on much faster timescales than the normal
+field can change on much faster time-scales than the normal
 hydrodynamical timesteps.
@@
 For example, a grid on level $L$ might have no radiation in its
-initial evaluation, but the ionization front exists just outside its
+initial evaluation, but the ionisation front exists just outside its
 boundary.  Then radiation permeates the grid in the time between
@@
 chemical state of the cells must be updated with each radiation update
-to advance the ionization front accurately.  If one does not update
-these cells, it will appear that the ionization front does not enter
+to advance the ionisation front accurately.  If one does not update
+these cells, it will appear that the ionisation front does not enter
 the grid until the next hydrodynamical timestep!  Visually this
@@
 
-For cells that transition from zero to non-zero photo-ionization
+For cells that transition from zero to non-zero photo-ionisation
 rates, the initial state that enters into the chemistry and energy
@@
 if the cell is on the finest level.  However in practice, the
-timescales in gas without radiation are small compared to the
-ionization and heating timescales when radiation is introduced.
+time-scales in gas without radiation are small compared to the
+ionisation and heating time-scales when radiation is introduced.
 Therefore, we do not perform this correction and find that this does
@@
 with radiation and are stored between timesteps, excessively consuming
-memory.  On the shortest timescale, one can safely set the timestep to
+memory.  On the shortest time-scale, one can safely set the timestep to
 the light-crossing time of a cell \citep{Abel99_RT, Trac07} but
@@
 If the timestep is too large, the solution will become inaccurate;
-specifically, ionization fronts will advance too slowly, as radiation
+specifically, ionisation fronts will advance too slowly, as radiation
 intensity exponentially drops with a scale length of the mean free
@@
 \end{equation}
-past the ionization front.  For example in our implementation, the
+past the ionisation front.  For example in our implementation, the
 chemo-thermal state of the system remains constant as the rays are
 traced through the cells.  In the case of a single \hii region,
-the speed of the ionization front is limited to approximately
+the speed of the ionisation front is limited to approximately
 $\lambda_{\rm mfp} / dt_P$.
@@
     in shadowing test (Test 3; \S\ref{sec:test3}) while restricting
-    the neutral fraction change to 5\% in the ionization front.  The
+    the neutral fraction change to 5\% in the ionisation front.  The
     unmodified timestep (top) is slightly more noisy and the minima
@@
     tenth timestep taken into account for the running average.  The
-    sawtooth behavior is created by the ionization front advancing
+    sawtooth behavior is created by the ionisation front advancing
     into the next neutral cell in the overdensity.}
@@
 fraction.  \citet{Shapiro04} found that this limited the speed of the
-ionization front.  We can investigate this further by evaluating the
-ionization front velocity in a growing Str\"{o}mgren sphere without
+ionisation front.  We can investigate this further by evaluating the
+ionisation front velocity in a growing Str\"{o}mgren sphere without
 recombinations, 
@@
 respectively on both sides of Equation (\ref{eqn:ndot}) to arrive at
-the ionization front velocity $v_{\rm IF} \propto n_{\rm H}
+the ionisation front velocity $v_{\rm IF} \propto n_{\rm H}
 /\dot{n}_{\rm H}$.
@@
 We have implemented this method but we only consider cells within the
-ionization front (by experiment we choose $\tau > 0.5$) because we are
-interested in evolving ionization fronts at the correct speed.  In the
-ionized region, the absolute changes in neutral fraction are small and
-will not significantly affect the ionization front evolution.  In
+ionisation front (by experiment we choose $\tau > 0.5$) because we are
+interested in evolving ionisation fronts at the correct speed.  In the
+ionised region, the absolute changes in neutral fraction are small and
+will not significantly affect the ionisation front evolution.  In
 other words, $n_{\rm HI}/(dn_{\rm HI}/dt)$ may be large but $(dn_{\rm
@@
 modifications as the timestep, but there is considerable noise both
-spatially and temporally.  In order to stabilize this technique, we
+spatially and temporally.  In order to stabilise this technique, we
 first spatially smooth the values of $dt_{\rm P,cell}$ with a Gaussian
 filter over a $3^3$ cube.  Because we only consider the cells within
-the ionization front, we set $dt_{\rm P,cell}$ to the hydrodynamical
+the ionisation front, we set $dt_{\rm P,cell}$ to the hydrodynamical
 timestep outside the front during the smoothing.  After we have
@@
 depth, which is added to the total time-averaged optical depth.  With
-these quantities, one can compute a photo-ionization rate and update
+these quantities, one can compute a photo-ionisation rate and update
 the electron density.  This process is repeated until convergence is
@@
 than a method without time-averaging.  Another advantage of this
-method is the use of pre-calculated tables for the photo-ionization
+method is the use of pre-calculated tables for the photo-ionisation
 rates as a function of optical depth, based on a given spectrum.  This
@@
 radiative transfer equation in Enzo+Moray.  It should be small enough
-to evolve ionization fronts accurately, as discussed earlier.  The
+to evolve ionisation fronts accurately, as discussed earlier.  The
 timestep can be based on physical arguments, for example, the
-sound-crossing time of an ionized region at $T > 10^4$ K.  To be
+sound-crossing time of an ionised region at $T > 10^4$ K.  To be
 conservative, one may choose the sound-crossing time of a cell
@@
 the smallest relevant system (e.g., an accretion radius, transition
-radius to a D-type ionization front, etc.) in the simulation may be
+radius to a D-type ionisation front, etc.) in the simulation may be
 chosen to calculate the sound-crossing time.
 
-If the timestep is too large, the ionization front will propagate too
+If the timestep is too large, the ionisation front will propagate too
 slowly, but it eventually approaches the correct radius at late times
@@
 region in a power-law density gradient.  After a brief, initial R-type
-phase, the I-front becomes D-type phase, where the ionization and
-shock front progress jointly at the sound speed of the ionized region.
+phase, the I-front becomes D-type phase, where the ionisation and
+shock front progress jointly at the sound speed of the ionised region.
 A moderately large (0.1 Myr) timestep can accurately follow its
@@
 accelerates, and transitions back to an R-type front.  This can also
-occur in champagne flows when the ionization front passes a density
+occur in champagne flows when the ionisation front passes a density
 discontinuity.  The I-front velocities in these two stages differ up
@@
 
-Ionization front velocities can approach significant fractions of the
+Ionisation front velocities can approach significant fractions of the
 speed of light in steep density gradients and in the early expansion
-of the \hii region.  If the ionization front position is
+of the \hii region.  If the ionisation front position is
 critical to the calculation, the radiation transport timestep can be
-derived from an estimate of the ionization front velocity
+derived from an estimate of the ionisation front velocity
 %
@@
 based on the incident radiation field at a particular position.
-Alternatively, the propagation of the ionization front can be
+Alternatively, the propagation of the ionisation front can be
 restricted by limiting the change in specific intensity $I$ to a
@@
 %
-$\dot{n}_{\rm H}$ is computed with the same formula as
-Eq. \ref{eqn:dtelec}. Substituting in Eq. \ref{eqn:vifront1} gives
+$\dot{n}_{\rm H}$ is computed with the same formula as equation
+(\ref{eqn:dtelec}). Substituting in equation (\ref{eqn:vifront1})
+gives
 %
@@
 
-\subsection{Parallelization Strategy}
+\subsection{Parallelisation Strategy}
 \label{sec:parallel}
 
-Parallelization of the ray tracing code is essential when exploring
+Parallelisation of the ray tracing code is essential when exploring
 problems that require high resolution and thus large memory
-requirements.  Furthermore, \enzo~is already parallelized and scalable
+requirements.  Furthermore, \enzo~is already parallelised and scalable
 to $O(10^2)$ processors in AMR simulations, and $O(10^3)$ in unigrid
@@
 processor as the source grid, where we move the ray as in the serial
-case.  For all other rays, we organize the rays by destination
+case.  For all other rays, we organise the rays by destination
 processors and send them in groups.  We also send the destination grid
@@
 ``non-blocking'' MPI communication, where each processor does not wait
-for synchronization with other processors.  We use this technique for
+for synchronisation with other processors.  We use this technique for
 the sending and receiving of rays.  Here we desire to minimize the
@@
 make the ray tracing routine to be totally non-blocking, the
-processors will most likely not be synchronized on the same loop
+processors will most likely not be synchronised on the same loop
 (Steps 3--5 in \S\ref{sec:design}).  Therefore, there might be
@@
 where workload is partitioned over grids on each MPI process.  We
-found that parallelization over grids for the photon transport does
+found that parallelisation over grids for the photon transport does
 not scale well, and threading over the rays in each grid is a better
@@
 radiation transport: ray tracing with short, long, and hybrid
-characteristics, Monte Carlo casting; ionization front tracking
+characteristics, Monte Carlo casting; ionisation front tracking
 \citep{Alvarez06_IFT}; variable Eddington Tensor formalism
@@
     expansion with a monochromatic spectrum of 13.6 eV).  Top:
-    Radially averaged profile of neutral (solid) and ionized (dashed)
+    Radially averaged profile of neutral (solid) and ionised (dashed)
     fraction at 10, 30, 100, and 500 Myr.  Bottom: Evolution of the
@@
 
-The expansion of an ionizing region with a central source in a uniform
+The expansion of an ionising region with a central source in a uniform
 medium is a classic problem first studied by \citet{Stroemgren39}.
@@
 that may arise from deficiencies in the method or newly introduced
-bugs in the development process.  In this problem, the ionized region
-grows until recombinations balance photo-ionizations
-(Eq. \ref{eqn:Rstr}).  The evolution of the radius $r_s$ and velocity
-$v_s$ of the ionization front has an exact solution of
+bugs in the development process.  In this problem, the ionised region
+grows until recombinations balance photo-ionisations [equation
+(\ref{eqn:Rstr})].  The evolution of the radius $r_s$ and velocity
+$v_s$ of the ionisation front has an exact solution of
 %
@@
 
-We adopt the problem parameters used in RT06.  The ionizing
+We adopt the problem parameters used in RT06.  The ionising
 source emits $5 \times 10^{48}$ ph s$^{-1}$ of monochromatic radiation
@@
 mimic an isothermal behavior, we set the adiabatic index $\gamma =
-1.0001$, which ensures an isothermal state but not a fixed ionization
+1.0001$, which ensures an isothermal state but not a fixed ionisation
 fraction outside of the Str\"{o}mgren sphere.
@@
 In Fig. \ref{fig:test1_ifront}, we show (a) the evolution of the
-neutral and ionization fraction as a function of radius at $t = $ 10,
-30, 100, and 500 Myr, and (b) the growth of the ionization front
+neutral and ionisation fraction as a function of radius at $t = $ 10,
+30, 100, and 500 Myr, and (b) the growth of the ionisation front
 radius as a function of time and its ratio with the analytical
-Str\"{o}mgren radius (Eq. \ref{eqn:rstr}).  The ionization front has a
-width of $\sim0.7$ kpc, which is in agreement with the inherent
-thickness of $\sim18 \lambda_{\rm mfp} = 0.74$ kpc, given a 13.6 eV
-mono-chromatic spectrum.  There are small kinks in the neutral
+Str\"{o}mgren radius [equation (\ref{eqn:rstr})].  The ionisation
+front has a width of $\sim0.7$ kpc, which is in agreement with the
+inherent thickness of $\sim18 \lambda_{\rm mfp} = 0.74$ kpc, given a
+13.6 eV mono-chromatic spectrum.  There are small kinks in the neutral
 fraction at 1.5 and 3 kpc that corresponds to artifacts created by the
@@
 codes presented in RT06 is the increasing neutral fraction outside of
-the \hii.  This occurs because the initial ionized fraction and
+the \hii.  This occurs because the initial ionised fraction and
 temperature is set to $1.3 \times 10^{-3}$ and 8000 K, which are not
@@
 value.  In the right panel of Fig. \ref{fig:test1_ifront}, the
-ionization front radius exceeds $R_s$ by a few percent for most of the
+ionisation front radius exceeds $R_s$ by a few percent for most of the
 calculation.  This difference happens because the analytical solution
-(Eq. \ref{eqn:rstr}) assumes the \hii region has a constant
-ionized fraction.  The evolution of the ionized fraction as a function
+[equation (\ref{eqn:rstr})] assumes the \hii region has a constant
+ionised fraction.  The evolution of the ionised fraction as a function
 of radius can be analytically calculated \citep[e.g.][]{Osterbrock89,
-  Petkova09}, causing the ionization front radius to be slightly
+  Petkova09}, causing the ionisation front radius to be slightly
 larger, increasing from 0 to 3\% in the interval 80--350 Myr.  Our
 results are in excellent agreement with this more accurate analytical
-solution.  In Fig. \ref{fig:test1_HI}, we show a slice of the
-neutral fraction through the origin.  Other than the ray splitting
-artifacts that generate the plateaus at 1.5 and 3 kpc, one sees
-spherical symmetry without any noise in our solution.
+solution.  In Fig. \ref{fig:test1_HI}, we show a slice of the neutral
+fraction through the origin.  Other than the ray splitting artifacts
+that generate the plateaus at 1.5 and 3 kpc, one sees spherical
+symmetry without any noise in our solution.
 
@@
     $T=10^5$ K blackbody spectrum).  Radially averaged profile of
-    neutral (solid) and ionized (dashed) fraction at 10, 30, 100, and
+    neutral (solid) and ionised (dashed) fraction at 10, 30, 100, and
     500 Myr.}
@@
     with a $T=10^5$ K blackbody spectrum).  Top: Evolution of the
-    radius of the simulated ionization front (dashed) and analytical
+    radius of the simulated ionisation front (dashed) and analytical
     (solid) Str\"{o}mgren radius.  Bottom: The ratio of the calculated
@@
 photons have a longer mean free path than the photons at the
-ionization threshold in Test 1.  Thus the ionization front is thicker
+ionisation threshold in Test 1.  Thus the ionisation front is thicker
 as the photons can penetrate deeper into the neutral medium.  Here we
@@
 In Fig. \ref{fig:test2_1a}, we show the radially averaged neutral
-and ionized fraction at $t = $ 10, 30, 100, and 500 Myr, and the total
+and ionised fraction at $t = $ 10, 30, 100, and 500 Myr, and the total
 neutral fraction of the domain in Fig. \ref{fig:test2_1b}.  Compared
-with Test 1, the ionization front is thicker, as expected with the
+with Test 1, the ionisation front is thicker, as expected with the
 harder spectrum.  The total neutral fraction decreases to 0.67 over
@@
 medium.  In Fig. \ref{fig:test2_3}, we show the ratio of the
-ionization front radius $r_{\rm IF}$ in our simulation and $R_s$.
+ionisation front radius $r_{\rm IF}$ in our simulation and $R_s$.
 Before $1.5t_{\rm rec}$, $r_{\rm IF}$ lags behind $R_s$, initially by
@@
   \caption{\label{fig:test3_2} Test 3. (I-front trapping in a dense
-    clump and shadowing).  Evolution of the average ionized fraction
+    clump and shadowing).  Evolution of the average ionised fraction
     (top) and temperature (bottom) of the overdense clump.}
@@
 The diffusivity and angular resolution of a radiative transport method
-can be tested with the trapping of an ionization front by a dense,
-neutral clump.  In this situation, the ionization front will uniformly
+can be tested with the trapping of an ionisation front by a dense,
+neutral clump.  In this situation, the ionisation front will uniformly
 propagate until it reaches the clump surface.  Then the radiation in
@@
 medium.  If the clump is optically thick, a shadow will form behind
-the clump.  The sharpness of the ionization front at the shadow
+the clump.  The sharpness of the ionisation front at the shadow
 surface can be used to determine the diffusivity of the method.
@@
 The clump is in pressure equilibrium with $n_H = 0.04\; \cubecm$ and
-$T = 40$ K.  It has a radius of $r_c = 0.8$ kpc and is centered at
+$T = 40$ K.  It has a radius of $r_c = 0.8$ kpc and is centred at
 $(x,y,z) = (5, 3.3, 3.3)$ kpc.  In RT06, the test considered a plane
@@
 consider point sources, so we use a single radiation source located in
-the center of the $y=0$ boundary.  The luminosity of $\dot{N}_\gamma =
+the centre of the $y=0$ boundary.  The luminosity of $\dot{N}_\gamma =
 3 \times 10^{51}$ ph s$^{-1}$ corresponds to the same flux $F_0$ at 5
-kpc.  The location where the ionization front trapping can be
+kpc.  The location where the ionisation front trapping can be
 calculated analytically \citep{Shapiro04}, and with these parameters,
-it should halt at approximately the center of the clump.  We use the
+it should halt at approximately the centre of the clump.  We use the
 same four energy groups as in Test 2.
@@
 In Fig. \ref{fig:test3_1}, we show neutral fraction and temperature
-of a one-dimensional cut through the center of the dense clump at $z =
-0.5$ at $t = 1, 3, 5, 15$ Myr.  The ionization front is halted at a
+of a one-dimensional cut through the centre of the dense clump at $z =
+0.5$ at $t = 1, 3, 5, 15$ Myr.  The ionisation front is halted at a
 little more than halfway through the clump, which is consistent with
 the analytical expectation.  The hardness of the $T = 10^5$ K
-blackbody spectrum allows the gas outside of the ionization front to
-be photo-heated.  Where the gas is ionized, the temperature is between
-10,000 and 20,000 K, but decreases sharply with the ionized fraction.
-Fig. \ref{fig:test3_2} depicts the average ionized fraction and
+blackbody spectrum allows the gas outside of the ionisation front to
+be photo-heated.  Where the gas is ionised, the temperature is between
+10,000 and 20,000 K, but decreases sharply with the ionised fraction.
+Fig. \ref{fig:test3_2} depicts the average ionised fraction and
 temperature inside the dense clump, which both gradually increase as
-the ionization front propagates through the overdensity.  Our results
+the ionisation front propagates through the overdensity.  Our results
 are consistent with RT06.  Finally we show slices of neutral fraction
@@
 by the clump and demonstrates the non-diffusivity behavior of ray
-tracing.  The discretization of the sphere creates one neutral cell on
+tracing.  The discretisation of the sphere creates one neutral cell on
 the left side of the sphere.  This inherent artifact to the initial
@@
     sources).  Evolution of the mass- (dashed) and volume-averaged
-    (solid) ionized fraction.}
+    (solid) ionised fraction.}
   %\epsscale{1}
@@
 $z=9$.  The simulation comoving box size is 0.5 $h^{-1}$ Mpc and has a
-resolution of 128$^3$.  There are 16 point sources that are centered
-in the 16 most massive halos.  They emit $f_\gamma = 250$ ionizing
+resolution of 128$^3$.  There are 16 point sources that are centred
+in the 16 most massive haloes.  They emit $f_\gamma = 250$ ionising
 photons per baryon in a blackbody spectrum with an effective
@@
 We show the growth of the \hii regions by computing the
-mass-averaged $x_m$ and volume-averaged $x_v$ ionized fraction in
+mass-averaged $x_m$ and volume-averaged $x_v$ ionised fraction in
 Fig. \ref{fig:test4_1}.  Initially $x_m$ is larger than $x_v$, and
 at $t \sim 170$ kyr, the $x_v$ becomes larger.  This is indicative of
-inside-out reionization \citep[e.g.][]{Gnedin00, Miralda00,
-  Sokasian03}, where the dense regions around halos are ionized first,
-then the voids are ionized last.  At the end of the simulation, 65\%
-of the simulation is ionized.  However by visual inspection in the
+inside-out reionisation \citep[e.g.][]{Gnedin00, Miralda00,
+  Sokasian03}, where the dense regions around haloes are ionised first,
+then the voids are ionised last.  At the end of the simulation, 65\%
+of the simulation is ionised.  However by visual inspection in the
 slices of electron fraction (Fig. \ref{fig:test4_2}), there appears to
@@
 slices of electron fraction and temperature, Fig. \ref{fig:test4_2},
-the photo-heated regions are larger than the ionized regions by a
+the photo-heated regions are larger than the ionised regions by a
 factor of 2--3 because of the hardness of the $T = 10^5$ K blackbody
@@
   \caption{\label{fig:test5_1} Test 5. (\hii region in a uniform
-    medium).  Top: Growth of the computed ionization front radius at
-    an ionized fraction $x_e = 0.5$ (dashed) and at a temperature $T =
-    10^4$ K (dotted) compared to the analytical estimate (solid;
-    Eq. \ref{eqn:test5_r}).  Bottom: The ratio of the computed
-    ionization front radii to the analytical estimate.} 
+    medium).  Top: Growth of the computed ionisation front radius at
+    an ionised fraction $x_e = 0.5$ (dashed) and at a temperature $T =
+    10^4$ K (dotted) compared to the analytical estimate [solid;
+    equation (\ref{eqn:test5_r})].  Bottom: The ratio of the computed
+    ionisation front radii to the analytical estimate.} 
   %\epsscale{1}
@@
     medium).  Clockwise from the upper left: Radial profiles of
-    density, temperature, ionized fraction, and pressure at times $t
+    density, temperature, ionised fraction, and pressure at times $t
     =$ 10, 200, and 500 Myr.}
@@
     medium).  Clockwise from the upper left: Slices through the origin
-    of ionized fraction, neutral fraction, temperature, and density at
+    of ionised fraction, neutral fraction, temperature, and density at
     time $t =$ 500 Myr.}
@@
 neutral medium including the hydrodynamical response to the heated
-gas.  The ionized region has a greater pressure than the ambient
+gas.  The ionised region has a greater pressure than the ambient
 medium, causing it to expand.  This is a well-studied problem
-\citep{Spitzer78} with an analytical solution, where the ionization
+\citep{Spitzer78} with an analytical solution, where the ionisation
 front moves as
@@
 \end{equation}
-where $c_s$ is the sound speed of the ionized gas and $r_{s,0}$ is the
+where $c_s$ is the sound speed of the ionised gas and $r_{s,0}$ is the
 $r_s$ in Equation \ref{eqn:rstr}.  The bubble eventually reaches
@@
 \end{equation}
-where $T$ and $T_0$ are the ionized and ambient temperatures,
+where $T$ and $T_0$ are the ionised and ambient temperatures,
 respectively.  These solutions only describe the evolution at late
@@
 
-The growth of the ionization front radius is shown in Fig.
+The growth of the ionisation front radius is shown in Fig.
 \ref{fig:test5_1}, using both $T = 10^4$ K and $x_e = 0.5$ as
-ionization front definitions, compared to the analytical solution
-(Eq. \ref{eqn:test5_final}).  We define this alternative measure
-because the ionization front becomes broad as the D-type front creates
-a shock.  Densities in this shock, as seen in Fig.
+ionisation front definitions, compared to the analytical solution
+[equation (\ref{eqn:test5_final})].  We define this alternative
+measure because the ionisation front becomes broad as the D-type front
+creates a shock.  Densities in this shock, as seen in Fig.
 \ref{fig:test5_2}, are high enough for the gas to recombine but not
@@
 times, it provides a good match to the $t^{4/7}$ growth at late times.
-With the $x_e = 0.5$ criterion for the ionization front, the radius is
+With the $x_e = 0.5$ criterion for the ionisation front, the radius is
 always underestimated by $\sim20\%$.  This behavior was also seen in
@@
 
-Fig. \ref{fig:test5_2} shows the progression of the ionization front
+Fig. \ref{fig:test5_2} shows the progression of the ionisation front
 at times $t$ = 10, 200, and 500 Myr in radial profiles of density,
-temperature, pressure, and ionized fraction.  The initial \hii
-region is over-pressurized and creates an forward shock wave.  The
+temperature, pressure, and ionised fraction.  The initial \hii
+region is over-pressurised and creates an forward shock wave.  The
 high-energy photons can penetrate through the shock and partially
-ionizes and heats the exterior gas, clearly seen in the profiles.  As
+ionises and heats the exterior gas, clearly seen in the profiles.  As
 noted in RT09, this heated exterior gas creates an photo-evaporative
@@
 artifact is a very slight diagonal line, which is caused by the
-HEALPix pixelization differences between the polar and equatorial
+HEALPix pixelisation differences between the polar and equatorial
 regions.  This artifact diminishes as the ray-to-cell sampling is
@@
   \caption{\label{fig:test6_1} Test 6. (\hii region in a 1/$r^2$
-    density profile).  Top: Growth of the computed ionization front
+    density profile).  Top: Growth of the computed ionisation front
     radius as $T=10^4$ K and $x_e = 0.5$ as definitions for the front.
-    Bottom: Velocity of the ionization front, computed from outputs at
+    Bottom: Velocity of the ionisation front, computed from outputs at
     0.5 Myr intervals.  The velocity is calculated from $r_{\rm IF}$,
@@
     density profile).  Clockwise from the upper left: Radial profiles of
-    density, temperature, ionized fraction, and pressure at times $t
+    density, temperature, ionised fraction, and pressure at times $t
     =$ 3, 10, and 25 Myr.}
@@
     density profile).  Clockwise from the upper left: Slices through the origin
-    of ionized fraction, neutral fraction, temperature, and density at
+    of ionised fraction, neutral fraction, temperature, and density at
     time $t =$ 25 Myr.}
@@
 constant density $n_c$ core, which is applicable to collapsing
-molecular clouds and cosmological halos.  The radial density profile
+molecular clouds and cosmological haloes.  The radial density profile
 is described by
@@
 smaller than the core radius, then the resulting \hii region
-never escapes into the steep density slope.  When the ionization front
+never escapes into the steep density slope.  When the ionisation front
 propagates out of the core, it accelerates as it travels down the
@@
 problem with full gas dynamics but was extensively studied by
-\citet{Franco90}.  After the gas is ionized and photo-heated, the
+\citet{Franco90}.  After the gas is ionised and photo-heated, the
 density gradient provides the pressure imbalance to drive the gas
@@
 simulation focuses on small-scale, not long term, behavior of the
-ionization front.  The simulation box has a side length $L = 0.8$ kpc
+ionisation front.  The simulation box has a side length $L = 0.8$ kpc
 with core density $n_0 = 3.2\;\cubecm$, core radius $r_0 = 91.5$ pc
 (15 cells), and temperature $T = 100$ K throughout the box.  The
-ionization fraction is initially zero, and the point source is located
+ionisation fraction is initially zero, and the point source is located
 at the origin with a luminosity of $10^{50}$ ph s$^{-1}$ \cubecm.  The
@@
 Because this problem does not have an analytical solution, we compare
-our calculated ionization front radius and velocity, shown in Fig.
+our calculated ionisation front radius and velocity, shown in Fig.
 \ref{fig:test6_1}, to the RT09 results.  Their evolution are in
 agreement within 5\% of RT09.  As in Test 5, we use an extra
-definition of $T=10^4$ K for the ionization front.  We compute the
-ionization front velocity from the radii at 50 outputs, which causes
+definition of $T=10^4$ K for the ionisation front.  We compute the
+ionisation front velocity from the radii at 50 outputs, which causes
 the noise seen Fig. \ref{fig:test6_1}.
@@
 For the first Myr, the radiation source creates a weak R-type front
-where the medium is heated and ionized but does not expand because
+where the medium is heated and ionised but does not expand because
 $v_{\rm IF} > c_s$.  When $v_{\rm IF}$ becomes subsonic, the medium
-can react to the passing ionization front and creates a shock, leaving
+can react to the passing ionisation front and creates a shock, leaving
 behind a heated an rarefied medium.  This behavior is clearly seen in
-the radial profiles of density, temperature, ionized fraction, and
+the radial profiles of density, temperature, ionised fraction, and
 pressure in Fig. \ref{fig:test6_2}.  The inner density decreases
@@
 deviations in spherical symmetry, we show in Fig. \ref{fig:test6_3}
-slices of density, temperature, neutral fraction, and ionized fraction
+slices of density, temperature, neutral fraction, and ionised fraction
 at the final time.  The only artifact apparent to us is the slight
 broadening of the shock near the $x=0$ and $y=0$ planes.  This causes
-the ionization front radius to be slightly smaller in those
+the ionisation front radius to be slightly smaller in those
 directions.  In the diagonal direction, the neutral column density
 through the shock is slightly smaller, allowing the high-energy
-photons to photoionize and photoheat the gas to $x_e = 5 \times
+photons to photo-ionise and photo-heat the gas to $x_e = 5 \times
 10^{-3}$ and $T = 2000$ K out to $\sim50$ pc from the shock.  The
 reflecting boundaries are responsible for this artifact because this
-is not seen when the problem is centered in the domain, removing any
+is not seen when the problem is centred in the domain, removing any
 boundary effects.
@@
     clump).  Clockwise from the upper left: Slices through the clump
-    center of neutral fraction, pressure, temperature, and density at
+    centre of neutral fraction, pressure, temperature, and density at
     time $t =$ 10 Myr.}
@@
 very differently when radiation hydrodynamics is considered instead of
-a static density field.  The ionization front first proceeds as a very
+a static density field.  The ionisation front first proceeds as a very
 fast R-type front, then it slows to a D-type front when it encounters
-the dense clump.  As the clump is gradually photoionized and heated,
+the dense clump.  As the clump is gradually photo-ionised and heated,
 it expands into the ambient medium.  The test presented here is
 exactly like Test 3 but with gas dynamics.  In this setup, the
-ionization front overtakes the entire clump, which is then completely
+ionisation front overtakes the entire clump, which is then completely
 photo-evaporated.
@@
 fraction, and pressure in a line connecting the source and the clump
-center at $t = 1$, 10, and 50 Myr.  At 1 Myr, the ionization front has
+centre at $t = 1$, 10, and 50 Myr.  At 1 Myr, the ionisation front has
 propagated through the left-most 500 pc of the clump.  This heated gas
-is now over-pressurized, as seen in the pressure plot in Fig.
+is now over-pressurised, as seen in the pressure plot in Fig.
 \ref{fig:test7_1}, and then expands into the ambient medium.  This
@@
 The non-spherical artifacts on the inner boundary of the warm
-outermost shell are caused by the initial discretization of the
+outermost shell are caused by the initial discretisation of the
 sphere, as discussed in \S\ref{sec:test3}.
@@
   \caption{\label{fig:test8_1} Test 8. (Champagne flow from a dense
-    clump).  Slices of density through the initial clump center in the
+    clump).  Slices of density through the initial clump centre in the
     x-y plane (top) and x-z plane (bottom) at $t = 10, 40, 100, 150$
@@
 box of 8 pc.  The ambient medium has $\rho = 290$ \cubecm~and $T =
-100$ K.  The radiation source is offset from the overdensity center by
+100$ K.  The radiation source is offset from the overdensity centre by
 0.4 pc.  It has a luminosity of \tento{49} ph s$^{-1}$ and a $T=10^5$
@@
 just inside of the overdense clump.  These parameters are the same
-used in \citet{Bisbas09}.  The entire domain initially has an ionized
+used in \citet{Bisbas09}.  The entire domain initially has an ionised
 fraction of \tento{-6}.  We do not consider self-gravity.  The
@@
 \ref{fig:test8_1} at $t = 10, 40, 100, 150$ kyr.  In the direction of
-the clump center, the ionization front shape transitions from
+the clump centre, the ionisation front shape transitions from
 spherical to parabolic after it escapes from the clump in the opposite
@@
 Cartesian grid, even with our geometric correction.  After the
-ionization front escapes from the clump in the negative x-direction,
+ionisation front escapes from the clump in the negative x-direction,
 these perturbations grow from Rayleigh-Taylor instabilities as the gas
@@
 equilibrium, we set $P = P_0 - g \rho(z) z$ with $P_0 = 2.5$.  In
-order to consider a radiation source with a ionizing photon luminosity
+order to consider a radiation source with a ionising photon luminosity
 of $10^{42}$ ph s$^{-1}$, we scale the domain to a physical size of
@@
 $m_h$, resulting in an initial temperature of $(T_0, T_1) = (363,
-726)$ K.  The radiation source is placed at the center of lower
+726)$ K.  The radiation source is placed at the centre of lower
 $z$-boundary face and starts to shine at $t = 10$ Myr.
@@
 bottom medium with $T > 10^4$ K and $x_e \sim 1$.  Furthermore, the
-ionization front remains R-type before interacting with the
+ionisation front remains R-type before interacting with the
 instability.  A possible physical analogue could be a radiation source
@@
 provide a stress test on a radiation hydrodynamics solver.  We show
-the evolution of the density, temperature, and ionized fraction of the
+the evolution of the density, temperature, and ionised fraction of the
 optically thick and optically thin cases in Figs.
@@
 instability as strongly.  The radiation source provides further
-buoyancy in the already $T=10^4$ K gas.  The gas first to be ionized
+buoyancy in the already $T=10^4$ K gas.  The gas first to be ionised
 and photo-evaporated are the outer regions of the instability.  The
@@
 $z$-boundary and creates a warm $T = 5 \times 10^3$ K, partially
-ionized ($x_e \sim 10^{-2}$), turbulent medium, seen in the slices $t
+ionised ($x_e \sim 10^{-2}$), turbulent medium, seen in the slices $t
 \ge 0.67$ Myr.  The slices of electron fraction also show that the
@@
     $t = 2.5, 3, 5, 7.5$ Myr in the $x-z$ plane.  As the R-type
-    ionization front propagates through the blastwave center,
+    ionisation front propagates through the blastwave centre,
     instabilities grow from the slightly inhomogeneous hot and rarefied
     medium.  Note that the dense shell of the blastwave also creates
-    dense inward fingers in the ionization front shock.}
+    dense inward fingers in the ionisation front shock.}
   %\epsscale{1}
@@
 occurrence in massive-star forming regions.  In this test, we set up an
-idealized test that mimics this scenario.  The ambient medium has a
+idealised test that mimics this scenario.  The ambient medium has a
 density $\rho_0 = 0.1~\cubecm$ and temperature $T_0 = 10$ K.  The
@@
 64$^3$ that is refined if the density or total energy slope is greater
-than 0.4.  The blastwave is initialized at the beginning of the
+than 0.4.  The blastwave is initialised at the beginning of the
 Sedov-Taylor phase when the mass of the swept-up material equals the
@@
 eV per particle or $E/k_b = 3.66 \times 10^6$ K.  The radiation source
-is located at the center of the left $x$-boundary and has a luminosity
+is located at the centre of the left $x$-boundary and has a luminosity
 of $10^{50}$ erg s$^{-1}$.  We use a $T=10^5$ K blackbody spectrum
@@
 
-Fig. \ref{fig:test10} shows the ionization front overtaking and
+Fig. \ref{fig:test10} shows the ionisation front overtaking and
 disrupting the blastwave.  We show the blastwave before the source is
@@
 10^{-3}~\cubecm$) and is heated to $T \sim 5 \times 10^5$ K by the
-reverse shock.  At $t = 3$ Myr, the ionization front is still R-type,
-and it ionizes the rear side of the dense shell.  Because the interior
-is ionized and diffuse, the ionization front rapidly propagates
+reverse shock.  At $t = 3$ Myr, the ionisation front is still R-type,
+and it ionises the rear side of the dense shell.  Because the interior
+is ionised and diffuse, the ionisation front rapidly propagates
 through it until it reaches the opposite shell surface.  Shortly
-afterward, the ionization front transitions from R-type to D-type at a
+afterward, the ionisation front transitions from R-type to D-type at a
 radius of 0.5 kpc, seen in the formation of a shock in the 5 Myr
@@
 problem not by the interaction with the blastwave.  The surfaces of
-the blastwave that are perpendicular to the ionization front have the
-highest column density and thus are last to be fully ionized.  The
+the blastwave that are perpendicular to the ionisation front have the
+highest column density and thus are last to be fully ionised.  The
 pressure forces from warm ambient medium and blastwave interior
@@
 similar to Test 7.  They survive until the final time $t = 7.5$ Myr.
-As the R-type ionization front interacts with the blastwave interior,
-the density perturbations create ionization front instabilities
+As the R-type ionisation front interacts with the blastwave interior,
+the density perturbations create ionisation front instabilities
 \citep{Whalen08_Instab} that are seen on the \hii region surface
-at the coordinate $z=0.5$.  Behind the ionization front, the dense
+at the coordinate $z=0.5$.  Behind the ionisation front, the dense
 shell of the blastwave is photo-evaporated, and a smooth overdensity
-is left in the initial blastwave center.
+is left in the initial blastwave centre.
 
@@
     polar champagne flows.  The ambient medium is heated to $T \sim 3
-    \times 10^4$ K as the ionization front passes the
-    constant-pressure cloud surface.  The ionization front changes
+    \times 10^4$ K as the ionisation front passes the
+    constant-pressure cloud surface.  The ionisation front changes
     from D-type to R-type after it enters the ambient medium.}
@@
 protostars, for example.  Simulating collimated radiation with ray
-tracing is trivially accomplished by only initializing rays that are
+tracing is trivially accomplished by only initialising rays that are
 within some opening angle $\theta_c$.
@@
 dense clump with $\rho/\rho_0 = 100$, $T = 100$ K, $x_e = 10^{-3}$,
-and $r = 250$ pc, at the center of the box.  Radiation is emitted in
+and $r = 250$ pc, at the centre of the box.  Radiation is emitted in
 two polar cones with $\theta_c = \pi/6$ with 768 (HEALPix level 3)
@@
 depicted in the $t = 0.1$ Myr snapshot of the system.  At this time,
-the ionization front is transitioning from R-type to D-type in the
+the ionisation front is transitioning from R-type to D-type in the
 transverse direction of the cone.  This can be seen in the minute
@@
 out of the overdensity, a champagne flow develops, where the
-ionization front transitions back to a weak R-type front.  The cloud
+ionisation front transitions back to a weak R-type front.  The cloud
 surface is a constant-pressure contact discontinuity (CD) with a
@@
 \times 10^4$ K.  Additionally a rarefaction wave travels towards the
-clump center.  At later times, the transverse D-type front continues
-through the clump, eventually forming a disk-like structure at the
+clump centre.  At later times, the transverse D-type front continues
+through the clump, eventually forming a disc-like structure at the
 final time.  The polar champagne flows proceed to flow outwards and
@@
 % = 1.3 \times 10^6 \Ms$.  The sphere and radiation source are located
-% in the center of the domain.  The sphere is in pressure equilibrium
+% in the centre of the domain.  The sphere is in pressure equilibrium
 % with the ambient medium that has $\rho_0 = 1 \cubecm$, $T = 10^4$ K,
-% and $x_e = 0.99$.  The radiation source has an ionizing luminosity $L
+% and $x_e = 0.99$.  The radiation source has an ionising luminosity $L
 % = 10^{50}$ ph s$^{-1}$ with a 17.6 eV mono-chromatic spectrum.  The
@@
 % 10^{48}$ ph s$^{-1}$ and a mono-chromatic spectrum of 14.6 eV.  We
-% choose this energy so the ionization front is relatively sharp but
+% choose this energy so the ionisation front is relatively sharp but
 % still heats the gas to $10^4$ K.  The ambient medium has a density of
@@
   \caption{\label{fig:test12_kph} Test 12 (Time variations of the
-    source luminosity).  Top: Slice of the photo-ionization rate
+    source luminosity).  Top: Slice of the photo-ionisation rate
     \kph~through the origin.  The source has a duty cycle of 0.5 Myr,
@@
     source luminosity).  Radial profiles of (clockwise from upper
-    left) density, temperature, pressure, and ionized fraction at $t =
+    left) density, temperature, pressure, and ionised fraction at $t =
     50, 100, 150, 200, 250$ Myr.  In this problem, the time variations
     in the source have little effect on the overall \hii region
-    expansion.  Inside the ionization front at $t = 50$ Myr, there are
+    expansion.  Inside the ionisation front at $t = 50$ Myr, there are
     small density perturbations that are created by the variable
@@
 Our implementation retains the time derivative of the radiative
-transfer equation (Eq. \ref{eqn:rteqn}) if we choose a constant ray
-tracing timestep, which saves the photon packages between timesteps if
-$c\;dt_{\rm P} < L_{\rm box}$.  This effect only becomes apparent when
-the variation timescale of the point source is smaller than the light
-crossing time of the simulation.  Furthermore, the timestep should
-resolve the variation timescale by at least a few times.  This
-property might be important in large box simulations with variable
-sources, e.g. AGN radiative feedback.  To test this, we can use an
-exponentially varying source with some duty cycle $t_0$.  In a
+transfer equation [equation (\ref{eqn:rteqn})] if we choose a constant
+ray tracing timestep, which saves the photon packages between
+timesteps if $c\;dt_{\rm P} < L_{\rm box}$.  This effect only becomes
+apparent when the variation time-scale of the point source is smaller
+than the light crossing time of the simulation.  Furthermore, the
+timestep should resolve the variation time-scale by at least a few
+times.  This property might be important in large box simulations with
+variable sources, e.g. AGN radiative feedback.  To test this, we can
+use an exponentially varying source with some duty cycle $t_0$.  In a
 functional form, this can be described as
@@
 The variability of the source is clearly illustrated in the
-photo-ionization rates, shown in Fig. \ref{fig:test12_kph}.  The
+photo-ionisation rates, shown in Fig. \ref{fig:test12_kph}.  The
 shells of relative maximum \kph~corresponds to radiation that was
@@
 separated by $ct_0$ Mpc and are geometrically diluted with increasing
-radius.  Averaged over shells of the same width, photo-ionization
+radius.  Averaged over shells of the same width, photo-ionisation
 rates decrease as $1/r^2$.
@@
 The spectrum is mono-chromatic with an energy of 29.6 eV.  We set the
-variation timescale $t_f = cL_{\rm box}/3 = 16.3$ kyr and use a
+variation time-scale $t_f = cL_{\rm box}/3 = 16.3$ kyr and use a
 constant radiative transfer timestep $t_P = t_f/4 = 4.07$ kyr.  The
 simulation is run for 200 Myr.  We show the radial profiles of
-density, temperature, ionized fraction, and pressure in Fig.
+density, temperature, ionised fraction, and pressure in Fig.
 \ref{fig:test12_profiles}.  The variable source has little effect on
@@
 variable source creates density perturbations with an average size of
-500 pc inside the ionized region, seen in the $t = 50$ Myr profiles.
+500 pc inside the ionised region, seen in the $t = 50$ Myr profiles.
 They do not create any instabilities and are smoothed out over its
@@
 Another prevalent physical component in astrophysics is a magnetic
-field.  We utilize the new magnetohydrodynamics (MHD) framework
+field.  We utilise the new magnetohydrodynamics (MHD) framework
 \citep{Wang09} in \enzo~v2.0 that uses an unsplit conservative
@@
 \mu\mathrm{G}$.  The Alfv\'{e}n speed is 2.6 \kms.  The radiation
-source is located in the center of the box with a luminosity $L = 4
+source is located in the centre of the box with a luminosity $L = 4
 \times 10^{46}$ ph s$^{-1}$ with a 17.6 eV mono-chromatic spectrum,
@@
 
-As the \hii region grows in the magnetized medium, shown in
+As the \hii region grows in the magnetised medium, shown in
 Figs. \ref{fig:test14_1} and \ref{fig:test14_2}, it transforms from
@@
 gas can only flow along field lines.  \citeauthor{Krumholz07_ART}
-observed some carbuncle artifacts along the ionization front; whereas
+observed some carbuncle artifacts along the ionisation front; whereas
 we see smooth density gradients, which is most likely caused by both
@@
   \plotone{fig/ifront_res}
-  \caption{\label{fig:dx_dep1} Growth of the ionization front radius,
+  \caption{\label{fig:dx_dep1} Growth of the ionisation front radius,
     compared to the analytical radius, in Test 1 with varying spatial
-    resolutions.  At resolutions of $16^3$ and $32^3$, the ionization
+    resolutions.  At resolutions of $16^3$ and $32^3$, the ionisation
     front is underestimated for the first $\sim25$ Myr but converges
@@
   \epsscale{1}
-  \caption{\label{fig:ang_dep1} Variations in the photo-ionization
+  \caption{\label{fig:ang_dep1} Variations in the photo-ionisation
     rates for different ray-to-cell samplings $\Phi_c$.  The colormap
     only spans a factor of 3 to enhance the contrast.  In comparison,
-    the photo-ionization rate actually spans 4 orders of magnitude in
+    the photo-ionisation rate actually spans 4 orders of magnitude in
     this test.}
@@
   \caption{\label{fig:ang_dep2} Standard deviations of the difference
-    between the computed photo-ionization rates and an inverse square
+    between the computed photo-ionisation rates and an inverse square
     law as a function of ray-to-cell samplings $\Phi_c$ for different
@@
 We consider minimum ray-to-cell ratios $\Phi_c = (1.1, 2.1, 3.1, 5.1,
-10.1, 25.1)$.  Slices of the photo-ionization rates through the origin
+10.1, 25.1)$.  Slices of the photo-ionisation rates through the origin
 are shown in Fig. \ref{fig:ang_dep1} for these values of $\Phi_c$.
@@
 with ray sampling, we take the difference between the calculated
-photo-ionization rate and a 1/$r^2$ field, and then plot the standard
+photo-ionisation rate and a 1/$r^2$ field, and then plot the standard
 deviation of this difference field versus angular resolution in Fig.
@@
   \caption{\label{fig:nu_dep} Radial profiles of (clockwise from the
-    upper left) density, temperature, radial velocity, and ionized
+    upper left) density, temperature, radial velocity, and ionised
     fraction for Test 5 with $n_\nu = 1$, 2, 4, 8, and 16 frequency
@@
 
-The ionization front radius is within 5--10\% of analytical solutions
+The ionisation front radius is within 5--10\% of analytical solutions
 in Tests 1, 2, and 5 with only one energy group; however a
@@
 demonstrate the effect of a multi-frequency spectrum on the dynamics
-of the ionization front in this test.  Instead of a single shock seen
+of the ionisation front in this test.  Instead of a single shock seen
 in the mono-chromatic spectrum, the shock obtains a double-peaked
@@
 Fig. \ref{fig:nu_dep} shows the radial profiles of density,
-temperature, ionized fraction, and radial velocity at $t = 200$ Myr
+temperature, ionised fraction, and radial velocity at $t = 200$ Myr
 and $t = 500$ Myr.  All of the runs with $n_\nu > 1$ show the double
@@
 runs are indistinguishable, and the $n_\nu = 2$ spectrum only leads to
-a marginally higher density in the outer shock and lower ionized
+a marginally higher density in the outer shock and lower ionised
 fractions and temperatures in the ambient medium.  In effect, a
 mono-chromatic spectrum can be sufficient if the problem focuses on
-large-scale quantities, e.g. ionized filling fractions in reionization
+large-scale quantities, e.g. ionised filling fractions in reionisation
 calculations.  Conversely these effects may be important when studying
@@
   \plotone{fig/ifront_dt}
-  \caption{\label{fig:dt_dep1} Growth of the ionization front radius,
+  \caption{\label{fig:dt_dep1} Growth of the ionisation front radius,
     compared to the analytical radius, in Test 1 with varying
@@
     final time, all but the $t = 5$ Myr constant timestep produce
-    identical ionization front radii.}
+    identical ionisation front radii.}
   %\epsscale{1}
@@
     that limit change in neutral fraction (solid) and specific
-    intensity (dotted).  The horizontal lines show the constant
+    intensity (dotted).  The horisontal lines show the constant
     timesteps that were used in the tests.  The crossing time of a
-    mean free path by the ionization front is plotted for reference.}
+    mean free path by the ionisation front is plotted for reference.}
   %\epsscale{1}
@@
 The previous three dependencies did not affect the propagation of the
-ionization front greatly.  However in our and others' past experience
+ionisation front greatly.  However in our and others' past experience
 \citep[e.g.][]{Shapiro04, Mellema06, Petkova09}, the timestep,
 especially too small a one, can drastically underestimate the
-ionization front velocity.  Here we use Test 1 but with $64^3$
+ionisation front velocity.  Here we use Test 1 but with $64^3$
 resolution to compare different time-stepping methods -- restricted
@@
 and based on incident radiation ($dI/dt$ based; \S\ref{sec:dt_tau}).
-The growth of the ionization front radius is shown in Fig.
+The growth of the ionisation front radius is shown in Fig.
 \ref{fig:dt_dep1}.  Both the \hii restricted and incident
@@
 solutions at early times because the photon energy gradient is large,
-and thus so is the ionization front velocity.  To understand this, the
-ionization front can be considered static in a given timestep.  Here
-the ionizing radiation can only penetrate into the neutral gas by
+and thus so is the ionisation front velocity.  To understand this, the
+ionisation front can be considered static in a given timestep.  Here
+the ionising radiation can only penetrate into the neutral gas by
 roughly a photon mean path $\lambda_{\rm mfp}$.  Only in the next
-timestep, the ionization front can advance.  If the timestep is larger
+timestep, the ionisation front can advance.  If the timestep is larger
 than $\lambda_{\rm mfp} / v_{\rm IF, anyl}$, then the numerical
@@
 accuracy when the source first starts to shine.  At later times, the
-ionization front slows as it approaches the Str\"{o}mgren radius, and
+ionisation front slows as it approaches the Str\"{o}mgren radius, and
 large timesteps are no longer necessary.  The $dI/dt$ method has a
@@
   \plotone{fig/fc_slices}
-  \caption{\label{fig:fc_slices} Slices of the photo-ionization rate
+  \caption{\label{fig:fc_slices} Slices of the photo-ionisation rate
     in the x-y plane (top row) and x-z plane (bottom row) with (left
@@
 As discussed in \S\ref{sec:meth_fc}, non-spherical artifacts are
-created by a mismatch between the HEALPix pixelization and the
+created by a mismatch between the HEALPix pixelisation and the
 Cartesian grid.  This is especially apparent in optically-thin
@@
 angular resolution tests in \S\ref{sec:ang_dep} with $\Phi_c = 5.1$.
-Slices of the photo-ionization rates through the origin are shown in
+Slices of the photo-ionisation rates through the origin are shown in
 Fig. \ref{fig:fc_slices}, depicting the improvements in spherical
@@
 attempts to reduce these artifacts either introduced a random rotation
-of the HEALPix pixelization \citep[e.g.][]{Abel02_RT, Trac07,
+of the HEALPix pixelisation \citep[e.g.][]{Abel02_RT, Trac07,
   Krumholz07_ART} or by increasing the ray-to-cell sampling.
@@
 In the x-y plane without the correction, there exists shell artifacts
-where the photo-ionization rates abruptly drops when the rays are
+where the photo-ionisation rates abruptly drops when the rays are
 split.  This occurs because the photon flux in the rays are constant,
@@
 optically-thin approximation to the optically-thick regime without
-producing artifacts in the photo-ionization rate \kph.  We use the
+producing artifacts in the photo-ionisation rate \kph.  We use the
 optically thin problem used in the angular resolution test
@@
 that avoids these artifacts because this approximation will be very
-advantageous in simulations with large ionized filling factors.
-
-\subsection{X-Ray secondary ionizations and reduced photo-heating}
+advantageous in simulations with large ionised filling factors.
+
+\subsection{X-Ray secondary ionisations and reduced photo-heating}
 
@@
   \caption{\label{fig:xray_fig} Radial profiles of temperature and
-    ionized fraction showing the effects of secondary ionizations from
+    ionised fraction showing the effects of secondary ionisations from
     a mono-chromatic 1 keV spectrum.  The discontinuity at $r \sim
     0.4$ is caused by artifacts in the ray tracing, which is described
-    in Test 1.  The high energy photons can ionize multiple hydrogen
-    atoms, increasing the ionized fraction.  In part, less radiation
+    in Test 1.  The high energy photons can ionise multiple hydrogen
+    atoms, increasing the ionised fraction.  In part, less radiation
     goes into thermal energy, lowering the temperature.}
@@
 
-Here we test our implementation of secondary ionizations from
+Here we test our implementation of secondary ionisations from
 high-energy photons above 100 eV, described in \S\ref{sec:xrays} and
@@
 10^{50}$ erg s$^{-1}$ and a mono-chromatic spectrum of 1 keV.  Fig.
-\ref{fig:xray_fig} compares the density, temperature, ionized
+\ref{fig:xray_fig} compares the density, temperature, ionised
 fraction, and neutral fraction of the expanding \hii region
-considering secondary ionizations and reduced photo-heating and
-considering only one ionization per photon and the remaining energy
-being thermalized.
+considering secondary ionisations and reduced photo-heating and
+considering only one ionisation per photon and the remaining energy
+being thermalised.
 
 Fig. \ref{fig:xray_fig} shows the main effects of secondary
-ionizations from the 1 keV spectrum on the ionization and thermal
-state of the system.  Without secondary ionizations, each absorption
-results in one ionization with the remaining energy transferred into
-thermal energy.  But with secondary ionizations, recall that most of
-the radiation energy goes into hydrogen and helium ionizations in
-neutral gas; whereas in ionized gas, most of the energy is
-thermalized.  In this test, only the inner 300 pc is completely
-ionized because of the small cross-section of hydrogen at $E_{\rm ph}
-= 1$ keV.  Beyond this core, the medium is only partially ionized.
+ionisations from the 1 keV spectrum on the ionisation and thermal
+state of the system.  Without secondary ionisations, each absorption
+results in one ionisation with the remaining energy transferred into
+thermal energy.  But with secondary ionisations, recall that most of
+the radiation energy goes into hydrogen and helium ionisations in
+neutral gas; whereas in ionised gas, most of the energy is
+thermalised.  In this test, only the inner 300 pc is completely
+ionised because of the small cross-section of hydrogen at $E_{\rm ph}
+= 1$ keV.  Beyond this core, the medium is only partially ionised.
 This process expands the hot $T = 10^5$ K core by a factor of 2.  In
-the outer neutral regions, the ionization fraction is larger by a
+the outer neutral regions, the ionisation fraction is larger by a
 factor of $\sim 10$, which in turn results in less photo-heating,
@@
     velocities than without radiation pressure.  Afterwards the
-    central region is under-pressurized, and the gas infalls toward the
-    center, as seen at t = 60 kyr.  Then the radiation pressure
+    central region is under-pressurised, and the gas infalls toward the
+    centre, as seen at t = 60 kyr.  Then the radiation pressure
     continues to force the gas outwards, increasing gas velocities up
@@
 $\mathbf{a}_{\rm rp} = E_{\rm ph}/c$.  This is especially important
-when the ionization front is in its initial R-type phase, where the
+when the ionisation front is in its initial R-type phase, where the
 gas has not reacted to the thermal pressure yet.  Thus we construct a
@@
 described in \S\ref{sec:test5}.  At $t=140$ kyr with radiation
-pressure, the ionization front radius is increased by $\sim5\% = 0.16$
+pressure, the ionisation front radius is increased by $\sim5\% = 0.16$
 pc.  However radiation pressure impacts the system the greatest inside
-the ionization front.  At $t = 40$ kyr, the central density is smaller
+the ionisation front.  At $t = 40$ kyr, the central density is smaller
 by a factor of 20 with radiation pressure, but the temperatures are
-almost equal.  A rarefaction wave thus propagates toward the center,
+almost equal.  A rarefaction wave thus propagates toward the centre,
 depicted by the negative radial velocities at $t = 60$ kyr.  This
@@
 Afterwards, the radiation continues to force gas outwards.  From $t =
-100$ kyr to $t = 140$ kyr, the maximum radial velocity of the ionized
+100$ kyr to $t = 140$ kyr, the maximum radial velocity of the ionised
 gas increases from 10 \kms~to 50 \kms.  This leaves behind an even
@@
 = 140$ kyr.  Thus the recombination rates are lower, resulting in
-increased ionization fractions and temperatures in the \hii
+increased ionisation fractions and temperatures in the \hii
 region.
@@
     There are no artifacts associated with rays being emitted from two
-    sources.  Both of the ionized regions are spherically symmetric
+    sources.  Both of the ionised regions are spherically symmetric
     before they overlap.}
@@
 and initial temperature $T = 100$ K.  Each block has the same size of
-15 kpc as Test 5.  At the center of each grid, there exists a
+15 kpc as Test 5.  At the centre of each grid, there exists a
 radiation source with a luminosity $L = 5 \times 10^{48}$ ph s$^{-1}$
@@
   \caption{\label{fig:strong} Strong scaling test with a $256^3$ AMR
-    calculation of cosmological reionization with $\sim329^3$ zones.
+    calculation of cosmological reionisation with $\sim329^3$ zones.
     The error bars represent the minimum and maximum time spent on a
@@
 of Enzo+Moray in a demanding, research application.  Here we use a
-small-box reionization calculation with $L_{\rm box} = 3$ Mpc/h, a
+small-box reionisation calculation with $L_{\rm box} = 3$ Mpc/h, a
 resolution of $256^3$, and six levels of refinement.  We measure the
@@
 this redshift.  On average, $4.6 \times 10^8$ ray segments are traced
-each timestep.  The ionized volume fraction is 0.10.  The calculations
+each timestep.  The ionised volume fraction is 0.10.  The calculations
 are performed on the Nehalam nodes on Pleiades on 2$^n$ cores, where
@@
 transfer timestep that are based on the variations in specific
-intensity or changes in neutral fraction inside the ionization front.
+intensity or changes in neutral fraction inside the ionisation front.
 Both methods give very accurate results and provide the largest
@@
 problems with $\sim10^9$ computational cells and $\sim10^4$ sources,
-such as reionization calculations.  We have also shown that the code
+such as reionisation calculations.  We have also shown that the code
 shows good strong scaling in AMR calculations, given a large enough
@@
 formation, and \hii regions of Population III stars.  Furthermore, we
-have included Lyman-Werner absorption, secondary ionizations from
+have included Lyman-Werner absorption, secondary ionisations from
 X-ray radiation, Compton heating from photon scattering, and radiation
@@
 
-Support for this work was provided by NASA through Hubble Fellowship
-grant \#120-6370 awarded by the Space Telescope Science Institute,
-which is operated by the Association of Universities for Research in
-Astronomy, Inc., for NASA, under contract NAS 5-26555.  Computational
-resources were provided by NASA/NCCS award SMD-09-1439.  The majority
-of the analysis and plots were done with \texttt{yt}
-\citep{yt_full_paper}.
+J.~H.~W. is supported by NASA through Hubble Fellowship grant
+\#120-6370 awarded by the Space Telescope Science Institute, which is
+operated by the Association of Universities for Research in Astronomy,
+Inc., for NASA, under contract NAS 5-26555.  Computational resources
+were provided by NASA/NCCS award SMD-09-1439.  The majority of the
+analysis and plots were done with \texttt{yt} \citep{yt_full_paper}.
 

### 2010-12-13 mnras.tex
Changed to British spelling in flow-charts.
Incorporating Richard Klein's comments.

@@
 transfer equation been coupled to the hydrodynamics in
-three-dimensions.  In the second comparison paper \citep[hereafter
-  RT09]{Iliev09}, results from these radiation hydrodynamics codes
-were compared.  Even more rare are ones that couple it with
-magneto-hydrodynamics \citep[e.g.][]{Krumholz07_ART}.  The tests in
-RT06 and RT09 were kept relatively simple to ease the comparison.
+three-dimensions \citep[e.g.][]{Krumholz07_FLD}.  In the second
+comparison paper \citep[hereafter RT09]{Iliev09}, results from these
+radiation hydrodynamics codes were compared.  Even more rare are ones
+that couple it with magneto-hydrodynamics
+\citep[e.g.][]{Krumholz07_ART}.  The tests in RT06 and RT09 were kept
+relatively simple to ease the comparison.
 
@@
 $j_\nu \equiv j_\nu(\mathbf{x},\nu,t)$ is the emission coefficient
-that includes any point sources of radiation or diffuse radiation.
+that includes any point sources of radiation or diffuse radiation.  We
+neglect any $(v/c)$ terms in equation (\ref{eqn:rteqn}) that become
+important in the dynamic diffusion limit ($l \kappa (v/c) \gg 1$).
+This occurs in relativistic flows or very optically thick systems,
+such as stellar interiors or radiation-dominated shocks
+\citep[see][for a rigorous derivation that includes $(v/c)$ terms to
+second-order]{Krumholz07_FLD}.
 
@@
 interpolated densities \citep[see][]{Mellema06} did not produce
-improved results.  Equation (\ref{eqn:rtray}) has a simple exponential
-analytic solution, and the photon flux of a ray is reduced by
+improved results.  In the static case, equation (\ref{eqn:rtray}) has
+a simple exponential analytic solution, and the photon flux of a ray
+is reduced by
 %
@@
 the optically thin case, where the area of the pixel is dominant over
-$(1 - e^\tau)$ when calculating $k_{\rm ph}$.  One can avoid these
+$(1 - e^{-\tau})$ when calculating $k_{\rm ph}$.  One can avoid these
 artifacts by increasing the sampling $\Phi_c$ to high values ($>10$)
@@
   \caption{\label{fig:strong} Strong scaling test with a $256^3$ AMR
-    calculation of cosmological reionisation with $\sim329^3$ zones.
+    calculation of cosmological reionisation with $\sim392^3$ zones.
     The error bars represent the minimum and maximum time spent on a
@@
 
+We thank Richard Klein for helpful comments on the manuscript.
 J.~H.~W. is supported by NASA through Hubble Fellowship grant

### 2010-12-13 mnras.tex
Putting Enzo in small caps, per MNRAS formatting.

@@
   implementation into the adaptive mesh refinement (AMR) cosmological
-  hydrodynamics code, Enzo.  By coupling the solver with the energy
+  hydrodynamics code, \enzo.  By coupling the solver with the energy
   equation and non-equilibrium chemistry network, our radiation
@@
   secondary ionisations from X-ray radiation.  It is included in the
-  newest public release of Enzo.
+  newest public release of \enzo.
 
@@
 
-In this paper, we present our implementation, Enzo+Moray, of adaptive
-ray tracing \citep{Abel02_RT} in the cosmological hydrodynamics
-adaptive mesh refinement (AMR) code, \enzo~\citep{BryanNorman1997,
-  OShea2004}.  The radiation field is coupled to the hydrodynamics
-solver at small time-scales, enabling it to study radiation
-hydrodynamical problems.  We have used this code to investigate the
-growth of an \hii region from a 100\Ms~Population III (Pop III) star
-\citep{Abel07}, the early stages of reionisation from Pop III stars
-\citep{Wise08_Reion}, radiative feedback on the formation of high
-redshift dwarf galaxies \citep{Wise08_Gal, Wise10_Gal}, ultraviolet
-radiation escape fractions from dwarf galaxies before reionisation
-\citep{Wise09}, negative radiative feedback from accreting Pop III
-seed black holes \citep{Alvarez09}, and radiative feedback in
-accreting supermassive black holes \citep[][in prep.]{Kim11}.  We have
-included Enzo+Moray in the latest public release of
-\enzo\footnote{http://enzo.googlecode.com}, and it is also coupled
-with the newly added MHD solver in \enzo~\citep{Wang09}.
+In this paper, we present our implementation, \moray, of adaptive ray
+tracing \citep{Abel02_RT} in the cosmological hydrodynamics adaptive
+mesh refinement (AMR) code, \enzo~\citep{BryanNorman1997, OShea2004}.
+The radiation field is coupled to the hydrodynamics solver at small
+time-scales, enabling it to study radiation hydrodynamical problems.
+We have used this code to investigate the growth of an \hii region
+from a 100\Ms~Population III (Pop III) star \citep{Abel07}, the early
+stages of reionisation from Pop III stars \citep{Wise08_Reion},
+radiative feedback on the formation of high redshift dwarf galaxies
+\citep{Wise08_Gal, Wise10_Gal}, ultraviolet radiation escape fractions
+from dwarf galaxies before reionisation \citep{Wise09}, negative
+radiative feedback from accreting Pop III seed black holes
+\citep{Alvarez09}, and radiative feedback in accreting supermassive
+black holes \citep[][in prep.]{Kim11}.  We have included \moray in the
+latest public release of \enzo\footnote{http://enzo.googlecode.com},
+and it is also coupled with the newly added MHD solver in
+\enzo~\citep{Wang09}.
 
@@
 dynamical and complex setups to demonstrate the flexibility and high
-fidelity of Enzo+Moray.  Section 6 gives the results from spatial,
+fidelity of \moray.  Section 6 gives the results from spatial,
 angular, frequency, and temporal resolution tests.  In Section 7, we
@@
 radiation and radiation pressure in this section.  Finally in Section
-8, we demonstrate the parallel scalability of Enzo+Moray.  Last
-Section 9 summarises our method and results.
+8, we demonstrate the parallel scalability of \moray.  Last Section 9
+summarises our method and results.
 
@@
 neglect any $(v/c)$ terms in equation (\ref{eqn:rteqn}) that become
-important in the dynamic diffusion limit ($l \kappa (v/c) \gg 1$).
-This occurs in relativistic flows or very optically thick systems,
-such as stellar interiors or radiation-dominated shocks
-\citep[see][for a rigorous derivation that includes $(v/c)$ terms to
+important in the dynamic diffusion limit ($l \kappa (v/c) \gg 1$),
+where $l$ is the characteristic size of the system.  This occurs in
+relativistic flows or very optically thick systems, such as stellar
+interiors or radiation-dominated shocks \citep[see][for a rigorous
+derivation that includes $(v/c)$ terms to
 second-order]{Krumholz07_FLD}.
@@
 minimizes the energy groups needed to accurately sample a spectrum.
-We are currently implementing this method into Enzo+Moray.
+We are currently implementing this method into \moray.
 
@@
 A constant timestep is necessary when solving the time-dependent
-radiative transfer equation in Enzo+Moray.  It should be small enough
+radiative transfer equation in \moray.  It should be small enough
 to evolve ionisation fronts accurately, as discussed earlier.  The
@@
 We have completed presenting results from the RT06 and RT09 test
-suites.  Next we test Enzo+Moray with five additional tests that
-further demonstrate its capabilities and accuracy.
+suites.  Next we test \moray with five additional tests that further
+demonstrate its capabilities and accuracy.
 
@@
 perturbation grows considerably and then turn on the radiation source.
-These tests demonstrate that Enzo+Moray can follow a highly dynamic
+These tests demonstrate that \moray can follow a highly dynamic
 system and resolve fine density structures.
@@
 
-Here we show tests that evaluate new features in Enzo+Moray, such as
-the improvements from the geometric correction factor, optically-thin
+Here we show tests that evaluate new features in \moray, such as the
+improvements from the geometric correction factor, optically-thin
 approximations, treatment of X-ray radiation, and radiation pressure.
@@
 
-Last we demonstrate the parallel performance of Enzo+Moray in weak and
+Last we demonstrate the parallel performance of \moray in weak and
 strong scaling tests.  For large simulations to consider radiative
@@
 Overall it scales already well to 512 processes, and there is room to
-enhance the weak scalability of Enzo+Moray in the near future.
+enhance the weak scalability of \moray in the near future.
 
@@
 communication.  We use an AMR simulation to demonstrate the scability
-of Enzo+Moray in a demanding, research application.  Here we use a
+of \moray in a demanding, research application.  Here we use a
 small-box reionisation calculation with $L_{\rm box} = 3$ Mpc/h, a
@@
 based on the ray tracing work.  This could impact the performance of
-the rest of Enzo by increasing the number of boundaries and thus
+the rest of \enzo by increasing the number of boundaries and thus
 communication.  Nevertheless in simulations that are dominated by
@@
 
-In this paper, we have presented our implementation, Enzo+Moray, of
+In this paper, we have presented our implementation, \moray, of
 adaptive ray tracing \citep{Abel02_RT} and its coupling to the
@@
 time-varying source, and an \hii region with MHD -- to
-demonstrate the flexibility and fidelity of Enzo+Moray.  Because
+demonstrate the flexibility and fidelity of \moray.  Because
 production simulations may not have the resolution afforded in these
@@
 X-ray radiation, Compton heating from photon scattering, and radiation
-pressure into the code, which extends the reach of Enzo+Moray to study
+pressure into the code, which extends the reach of \moray to study
 AGN feedback, stellar winds, and local star formation.  Coupling the

### 2010-12-13 mnras/mnras.tex
Massive figure filename renaming change.
Fixing spelling mistakes.

--- 2010-12-13 mnras.tex
@@
 Radiation from stars and black holes strongly affects their
-surroundings and plays a crucical role in topics such as stellar
+surroundings and plays a crucial role in topics such as stellar
 atmospheres, the interstellar medium (ISM), star formation, galaxy
@@
 \begin{figure}
-  \plotone{fig/geo_corr.eps}
+  \plotone{f1.eps}
   \caption{\label{fig:covering} (a) A two-dimensional illustration of
@@
 of rays is wasteful, however these rays must be propagated because the
-the medium farther awap can be optically thick.  Here we describe a
+the medium farther away can be optically thick.  Here we describe a
 method that minimizes the computational work of ray tracing in the
@@
   \epsscale{2}
-  \plotone{fig/RTcoupling.eps}
+  \plotone{f2.eps}
   \epsscale{1}
@@
   \epsscale{2}
-  \plotone{fig/RTalgorithm.eps}
+  \plotone{f3.eps}
   \epsscale{1}
@@
 \begin{figure}
-  \plottwo{fig/dtp_test3noavg.eps}{fig/dtp_test3.eps}
+  \plottwo{f4a.eps}{f4b.eps}
   \caption{\label{fig:dtsmooth} Radiative transfer adaptive timestep
@@
 \begin{figure}
-  \plottwo{fig/test1_ionfrac.eps}{fig/test1_ifront.eps}
+  \plottwo{f5a.eps}{f5b.eps}
   \caption{\label{fig:test1_ifront} Test 1 (\hii region
@@
   %\epsscale{0.8}
-  \plotone{fig/test1_HI500.eps}
+  \plotone{f6.eps}
   \caption{\label{fig:test1_HI} Test 1 (\hii region expansion
@@
 \begin{figure}
-  \plotone{fig/test2_ionfrac.eps}
+  \plotone{f7.eps}
   \caption{\label{fig:test2_1a} Test 2. (\hii region expansion with a
@@
 \begin{figure}
-  \plotone{fig/test2_neutral.eps}
+  \plotone{f8.eps}
   \caption{\label{fig:test2_1b} Test 2. (\hii region expansion with a
@@
   \epsscale{2}
-  \plotone{fig/test2_slices}
+  \plotone{f9}
   \epsscale{1}
@@
 \begin{figure}
-  \plotone{fig/test2_ifront.eps}
+  \plotone{f10}
   \caption{\label{fig:test2_3} Test 2. (\hii region expansion
@@
 \begin{figure}
-  \plottwo{fig/test3_HI.eps}{fig/test3_temp.eps}
+  \plottwo{f11a}{f11b}
   \caption{\label{fig:test3_1} Test 3. (I-front trapping in a dense
@@
   %\epsscale{0.85}
-  \plotone{fig/test3_clump.eps}
+  \plotone{f12}
   \caption{\label{fig:test3_2} Test 3. (I-front trapping in a dense
@@
   \epsscale{2}
-  \plotone{fig/test3_slices}
+  \plotone{f13}
   \epsscale{1}
@@
   %\epsscale{0.75}
-  \plotone{fig/test4_ion}
+  \plotone{f14}
   \caption{\label{fig:test4_1} Test 4. (Multiple cosmological
@@
   \epsscale{2}
-  \plotone{fig/test4_slices}
+  \plotone{f15}
   \epsscale{1}
@@
   %\epsscale{0.8}
-  \plotone{fig/test5_ifront}
+  \plotone{f16}
   \caption{\label{fig:test5_1} Test 5. (\hii region in a uniform
@@
 \begin{figure}
-  \plotone{fig/test5_profiles}
+  \plotone{f17}
   \caption{\label{fig:test5_2} Test 5. (\hii region in a uniform
@@
   \epsscale{2}
-  \plotone{fig/test5_slices}
+  \plotone{f18}
   \epsscale{1}
@@
   %\epsscale{0.8}
-  \plotone{fig/test6_ifront}
+  \plotone{f19}
   \caption{\label{fig:test6_1} Test 6. (\hii region in a 1/$r^2$
@@
 \begin{figure}
-  \plotone{fig/test6_profiles}
+  \plotone{f20}
   \caption{\label{fig:test6_2} Test 6. (\hii region in a 1/$r^2$
@@
   \epsscale{2}
-  \plotone{fig/test6_slices}
+  \plotone{f21}
   \epsscale{1}
@@
   %\epsscale{0.9}
-  \plotone{fig/test7_lines}
+  \plotone{f22}
   \caption{\label{fig:test7_1} Test 7. (Photo-evaporation of a dense
@@
   \epsscale{2}
-  \plotone{fig/test7_slices10}
+  \plotone{f23}
   \epsscale{1}
@@
   \epsscale{2}
-  \plotone{fig/test7_slices50}
+  \plotone{f24}
   \epsscale{1}
@@
   \epsscale{2}
-  \plotone{fig/test8_slices}
+  \plotone{f25}
   \epsscale{1}
@@
   %\epsscale{0.75}
-  \plotone{fig/test9thick_rho}
-  \plotone{fig/test9thick_temp}
-  \plotone{fig/test9thick_efrac}
+  \plotone{f26a}
+  \plotone{f26b}
+  \plotone{f26c}
   \caption{\label{fig:test9_thick} Test 9. (Irradiated Rayleigh-Taylor
@@
   %\epsscale{0.75}
-  \plotone{fig/test9thin_rho}
-  \plotone{fig/test9thin_temp}
-  \plotone{fig/test9thin_efrac}
+  \plotone{f27a}
+  \plotone{f27b}
+  \plotone{f27c}
   \caption{\label{fig:test9_thin} Same as Fig. \ref{fig:test9_thick}
@@
   \epsscale{2}
-  \plotone{fig/test10_slices}
+  \plotone{f28}
   \epsscale{1}
@@
   \epsscale{2}
-  \plotone{fig/test11_slices}
+  \plotone{f29}
   \epsscale{1}
@@
   %\epsscale{1.15}
-  \plottwo{fig/test12_kph}{fig/test12_radial}
+  \plottwo{f30a}{f30b}
   \caption{\label{fig:test12_kph} Test 12 (Time variations of the
@@
   %\epsscale{0.8}
-  \plotone{fig/test12_profiles}
+  \plotone{f31}
   \caption{\label{fig:test12_profiles} Test 12 (Time variations of the
@@
   \epsscale{2}
-  \plotone{fig/test14_slices_xy}
+  \plotone{f32}
   \epsscale{1}
@@
   \epsscale{2}
-  \plotone{fig/test14_slices_yz}
+  \plotone{f33}
   \epsscale{1}
@@
   %\epsscale{0.75}
-  \plotone{fig/ifront_res}
+  \plotone{f34}
   \caption{\label{fig:dx_dep1} Growth of the ionisation front radius,
@@
   %\epsscale{2}
-  \plotone{fig/phic_slices}
+  \plotone{f35}
   \epsscale{1}
@@
   %\epsscale{0.75}
-  \plotone{fig/phic_dep}
+  \plotone{f36}
   \caption{\label{fig:ang_dep2} Standard deviations of the difference
@@
   %\epsscale{1.05}
-  \plottwo{fig/nures040}{fig/nures100}
+  \plottwo{f37a}{f37b}
   \caption{\label{fig:nu_dep} Radial profiles of (clockwise from the
@@
   %\epsscale{0.75}
-  \plotone{fig/ifront_dt}
+  \plotone{f38}
   \caption{\label{fig:dt_dep1} Growth of the ionisation front radius,
@@
   %\epsscale{0.75}
-  \plotone{fig/vary_dt}
+  \plotone{f39}
   \caption{\label{fig:dt_dep2} Variable time-stepping for the methods
     that limit change in neutral fraction (solid) and specific
-    intensity (dotted).  The horisontal lines show the constant
+    intensity (dotted).  The horizontal lines show the constant
     timesteps that were used in the tests.  The crossing time of a
@@
   %\epsscale{0.7}
-  \plotone{fig/fc_slices}
+  \plotone{f40}
   \caption{\label{fig:fc_slices} Slices of the photo-ionisation rate
@@
   %\epsscale{0.6}
-  \plotone{fig/rayopt}
+  \plotone{f41}
   \caption{\label{fig:rayopt} Optically-thin approximation to the
@@
   %\epsscale{0.6}
-  \plotone{fig/xray_profiles.eps}
+  \plotone{f42}
   \caption{\label{fig:xray_fig} Radial profiles of temperature and
@@
   %\epsscale{1.075}
-  \plottwo{fig/noRP_profiles.eps}{fig/RP_profiles.eps}
+  \plottwo{f43a}{f43b}
   \caption{\label{fig:rp_profiles} (a) No radiation pressure.
@@
   %\epsscale{0.6}
-  \plotone{fig/two_sources.eps}
+  \plotone{f44}
   \caption{\label{fig:twosrc} Slice of neutral fraction at $t = 500$
@@
   %\epsscale{0.8}
-  \plotone{fig/weak_v1.eps}
+  \plotone{f45}
   \caption{\label{fig:weak} Weak scaling test with one $64^3$ block
@@
   %\epsscale{0.8}
-  \plotone{fig/strong_v1.eps}
+  \plotone{f46}
   \caption{\label{fig:strong} Strong scaling test with a $256^3$ AMR
@@
 scaling than AMR ones because of reduced inter-processor
-communication.  We use an AMR simulation to demonstrate the scability
+communication.  We use an AMR simulation to demonstrate the scalability
 of \moray in a demanding, research application.  Here we use a
@@
 Fig. \ref{fig:strong} shows the strong scaling results of this
-calculation.  The hydrodynamics and non-equilbrium chemistry routines
+calculation.  The hydrodynamics and non-equilibrium chemistry routines
 scale very well in this range because they depend on local phenomena.
@@
 radiation transport, it will be advantageous to construct such a
-scheme to increase the feasbility of running larger problems.
+scheme to increase the feasibility of running larger problems.
 

### 2011-02-02 mnras/mnras.tex
Started to respond to the referee report.

@@
 \citep{Alvarez09}, and radiative feedback in accreting supermassive
-black holes \citep[][in prep.]{Kim11}.  We have included \moray in the
+black holes \citep[][in prep.]{Kim11}.  We have included \moray~in the
 latest public release of \enzo\footnote{http://enzo.googlecode.com},
@@
 Afterwards in Section 5, we show the results from the RT09 radiation
-hydrodynamics tests.  We expand on these tests to include more
-dynamical and complex setups to demonstrate the flexibility and high
-fidelity of \moray.  Section 6 gives the results from spatial,
-angular, frequency, and temporal resolution tests.  In Section 7, we
-illustrate the improvements from the geometric correction factor and
-our optically-thin approximation.  We also show the effects of X-ray
-radiation and radiation pressure in this section.  Finally in Section
-8, we demonstrate the parallel scalability of \moray.  Last Section 9
-summarises our method and results.
+hydrodynamics tests.  In Section 6, we expand on these tests to
+include more dynamical and complex setups to demonstrate the
+flexibility and high fidelity of \moray.  Section 7 gives the results
+from spatial, angular, frequency, and temporal resolution tests.  In
+Section 8, we illustrate the improvements from the geometric
+correction factor and our optically-thin approximation.  We also show
+the effects of X-ray radiation and radiation pressure in this section.
+Finally in Section 9, we demonstrate the parallel scalability of
+\moray.  Last Section 10 summarises our method and results.
 
@@
 in the radiation field.  This is how this method retains the time
-derivative of the radiative transfer equation.
+derivative of the radiative transfer equation.  The last restriction
+prevents our method from considering sources external to the
+computational domain, but a uniform radiation background can be used
+in conjunction with ray tracing in \moray~that adds the local
+radiation field to the background intensity.
 
@@
 speed of light in steep density gradients and in the early expansion
-of the \hii region.  If the ionisation front position is
-critical to the calculation, the radiation transport timestep can be
-derived from an estimate of the ionisation front velocity
+of the \hii region.  If the ionisation front position is critical to
+the calculation, the radiation transport timestep can be derived from
+a non-relativistic estimate of the ionisation front velocity
 %
@@
 %
-based on the incident radiation field at a particular position.
-Alternatively, the propagation of the ionisation front can be
-restricted by limiting the change in specific intensity $I$ to a
-safety factor $C_{\rm RT,cfl}$, resulting in a timestep of
+based on the incident radiation field at a particular
+position\footnote{See \citet{Shapiro06} for the exact calculation of a
+  relativistic ionisation front.  Neglecting relativistic terms do not
+  affect the solution because the front velocity is only considered in
+  the timestep calculation.}.  Alternatively, the propagation of the
+ionisation front can be restricted by limiting the change in specific
+intensity $I$ to a safety factor $C_{\rm RT,cfl}$, resulting in a
+timestep of
 %
@@
 the \hii.  This occurs because the initial ionised fraction and
-temperature is set to $1.3 \times 10^{-3}$ and 8000 K, which are not
+temperature is set to $1.2 \times 10^{-3}$ and $10^4$ K, which are not
 the equilibrium values.  Over the 500 Myr in the calculation, the
@@
 
+\section{Radiation Hydrodynamics Applications}
+\label{sec:apps}
+
 We have completed presenting results from the RT06 and RT09 test
-suites.  Next we test \moray with five additional tests that further
+suites.  Next we test \moray~with six applications that further
 demonstrate its capabilities and accuracy.
 
-\subsection{Test 8. Champagne flow from a dense clump}
+\subsection{Application 1. Champagne flow from a dense clump}
 
@@
   \epsscale{1}
-  \caption{\label{fig:test8_1} Test 8. (Champagne flow from a dense
+  \caption{\label{fig:test8_1} Application 1. (Champagne flow from a dense
     clump).  Slices of density through the initial clump centre in the
@@
 
-\subsection{Test 9. Irradiated Rayleigh-Taylor instability}
-
-\begin{figure}
-  %\epsscale{0.75}
-  \plotone{f26a}
-  \plotone{f26b}
-  \plotone{f26c}
-  \caption{\label{fig:test9_thick} Test 9. (Irradiated Rayleigh-Taylor
-    instability; optically thick case).  Slices at $y=0$ of density
-    (top), temperature (middle), and electron fraction (bottom).  The
-    source turns on at $t=0$.}
-  %\epsscale{1}
-\end{figure}
-
-\begin{figure}
-  %\epsscale{0.75}
-  \plotone{f27a}
-  \plotone{f27b}
-  \plotone{f27c}
-  \caption{\label{fig:test9_thin} Same as Fig. \ref{fig:test9_thick}
-    but for the optically thin case.}
-  %\epsscale{1}
-\end{figure}
+\subsection{Application 2. Irradiated Rayleigh-Taylor instability}
 
@@
 perturbation grows considerably and then turn on the radiation source.
-These tests demonstrate that \moray can follow a highly dynamic
+These tests demonstrate that \moray~can follow a highly dynamic
 system and resolve fine density structures.
@@
 
-\subsection{Test 10. Photo-evaporation of a blastwave}
+\begin{figure}
+  %\epsscale{0.75}
+  \plotone{f26a}
+  \plotone{f26b}
+  \plotone{f26c}
+  \caption{\label{fig:test9_thick} Application 2. (Irradiated Rayleigh-Taylor
+    instability; optically thick case).  Slices at $y=0$ of density
+    (top), temperature (middle), and electron fraction (bottom).  The
+    source turns on at $t=0$.}
+  %\epsscale{1}
+\end{figure}
+
+\begin{figure}
+  %\epsscale{0.75}
+  \plotone{f27a}
+  \plotone{f27b}
+  \plotone{f27c}
+  \caption{\label{fig:test9_thin} Same as Fig. \ref{fig:test9_thick}
+    but for the optically thin case.}
+  %\epsscale{1}
+\end{figure}
+
+\subsection{Application 3. Photo-evaporation of a blastwave}
 
@@
   \epsscale{1}
-  \caption{\label{fig:test10} Test 10 (Photo-evaporation of a
+  \caption{\label{fig:test10} Application 3 (Photo-evaporation of a
     blastwave).  Slices of density (top) and temperature (bottom) at
@@
 
-\subsection{Test 11. Collimated radiation from a dense clump}
+\subsection{Application 4. Collimated radiation from a dense clump}
 
@@
   \epsscale{1}
-  \caption{\label{fig:test11} Test 11 (Collimated radiation from a
+  \caption{\label{fig:test11} Application 4 (Collimated radiation from a
     dense clump).  Slices of density (top) and temperature (bottom) at
@@
 resolution of 64$^3$, and it is refined with the same overdensity
-criterion as Test 8.  We run this test for 25 Myr.
+criterion as Application 1.  We run this test for 25 Myr.
+
+\begin{figure}
+  %\epsscale{1.15}
+  \plottwo{f30a}{f30b}
+  \caption{\label{fig:test12_kph} Application 4 (Time variations of the
+    source luminosity).  Top: Slice of the photo-ionisation rate
+    \kph~through the origin.  The source has a duty cycle of 0.5 Myr,
+    and the box has a light crossing time of 3.3 Myr.  The shells of
+    high \kph~originate from radiation that was emitted when the
+    source was at its peak luminosity, illustrating the
+    time-dependence of the radiative transfer equation.  Bottom:
+    Radial profile \kph~with the inverse square law overplotted.}
+  %\epsscale{1}
+\end{figure}
+
+\begin{figure}
+  %\epsscale{0.8}
+  \plotone{f31}
+  \caption{\label{fig:test12_profiles} Application 4 (Time variations of the
+    source luminosity).  Radial profiles of (clockwise from upper
+    left) density, temperature, pressure, and ionised fraction at $t =
+    50, 100, 150, 200, 250$ Myr.  In this problem, the time variations
+    in the source have little effect on the overall \hii region
+    expansion.  Inside the ionisation front at $t = 50$ Myr, there are
+    small density perturbations that are created by the variable
+    source that are later smoothed out over a sound crossing time.}
+  %\epsscale{1}
+\end{figure}
 
@@
 
-\subsection{Test 12. Time variations of the source luminosity}
-
-\begin{figure}
-  %\epsscale{1.15}
-  \plottwo{f30a}{f30b}
-  \caption{\label{fig:test12_kph} Test 12 (Time variations of the
-    source luminosity).  Top: Slice of the photo-ionisation rate
-    \kph~through the origin.  The source has a duty cycle of 0.5 Myr,
-    and the box has a light crossing time of 3.3 Myr.  The shells of
-    high \kph~originate from radiation that was emitted when the
-    source was at its peak luminosity, illustrating the
-    time-dependence of the radiative transfer equation.  Bottom:
-    Radial profile \kph~with the inverse square law overplotted.}
-  %\epsscale{1}
-\end{figure}
-
-\begin{figure}
-  %\epsscale{0.8}
-  \plotone{f31}
-  \caption{\label{fig:test12_profiles} Test 12 (Time variations of the
-    source luminosity).  Radial profiles of (clockwise from upper
-    left) density, temperature, pressure, and ionised fraction at $t =
-    50, 100, 150, 200, 250$ Myr.  In this problem, the time variations
-    in the source have little effect on the overall \hii region
-    expansion.  Inside the ionisation front at $t = 50$ Myr, there are
-    small density perturbations that are created by the variable
-    source that are later smoothed out over a sound crossing time.}
-  %\epsscale{1}
-\end{figure}
+\subsection{Application 5. Time variations of the source luminosity}
 
@@
   \epsscale{1}
-  \caption{\label{fig:test14_1} Test 14. (\hii region with MHD).
+  \caption{\label{fig:test14_1} Application 5. (\hii region with MHD).
     Left to right: slices of density at $t = 0.18, 0.53, 1.58$ Myr in
@@
   \epsscale{1}
-  \caption{\label{fig:test14_2} Test 14. (\hii region with
+  \caption{\label{fig:test14_2} Application 5. (\hii region with
     MHD). Slices of density (top) and the x-component of the magnetic
@@
 
-\subsection{Test 14. \hii region with MHD}
+\subsection{Application 6. \hii region with MHD}
 
@@
 
-Last we demonstrate the parallel performance of \moray in weak and
+Last we demonstrate the parallel performance of \moray~in weak and
 strong scaling tests.  For large simulations to consider radiative
@@
 Overall it scales already well to 512 processes, and there is room to
-enhance the weak scalability of \moray in the near future.
+enhance the weak scalability of \moray~in the near future.
 
@@
 communication.  We use an AMR simulation to demonstrate the scalability
-of \moray in a demanding, research application.  Here we use a
+of \moray~in a demanding, research application.  Here we use a
 small-box reionisation calculation with $L_{\rm box} = 3$ Mpc/h, a
@@
 based on the ray tracing work.  This could impact the performance of
-the rest of \enzo by increasing the number of boundaries and thus
+the rest of \enzo~by increasing the number of boundaries and thus
 communication.  Nevertheless in simulations that are dominated by
@@
 X-ray radiation, Compton heating from photon scattering, and radiation
-pressure into the code, which extends the reach of \moray to study
+pressure into the code, which extends the reach of \moray~to study
 AGN feedback, stellar winds, and local star formation.  Coupling the

### 2011-02-08 mnras/mnras.tex
Updating figures for updated tests 3 and 7.  Adding Mach number plot of test 7.
Minor changes to text.  Adding PDFs to repo but not paper yet.
Adding PDF figures into the manuscript along with their descriptions in the text.

@@
 \begin{figure}
-  %\epsscale{0.8}
+  \plotone{test1_pdf.eps}
+  \caption{\label{fig:test1_pdf} Test 1 (\hii region expansion with a
+    monochromatic spectrum of 13.6 eV). Probability distribution
+    function for neutral fraction at 10 Myr (solid), 100 Myr (dashed),
+    and 500 Myr (dotted).  Recombination of hydrogren at T = $10^4$ K
+    causes the maximum neutral fraction to decrease from 1 to 0.75.}
+\end{figure}
+
+\begin{figure}
   \plotone{f6.eps}
@@
     fraction at the origin at 500 Myr.}
-  %\epsscale{1.0}
 \end{figure}
@@
 codes presented in RT06 is the increasing neutral fraction outside of
-the \hii.  This occurs because the initial ionised fraction and
+the \hii region.  This occurs because the initial ionised fraction and
 temperature is set to $1.2 \times 10^{-3}$ and $10^4$ K, which are not
@@
 results are in excellent agreement with this more accurate analytical
-solution.  In Fig. \ref{fig:test1_HI}, we show a slice of the neutral
-fraction through the origin.  Other than the ray splitting artifacts
-that generate the plateaus at 1.5 and 3 kpc, one sees spherical
-symmetry without any noise in our solution.
+solution.  We show the distribution of neutral fraction in the domain
+for $t$ = 10, 100, and 500 Myr in Fig. \ref{fig:test1_pdf} that agrees
+well with the results in RT06.  In Fig. \ref{fig:test1_HI}, we show a
+slice of the neutral fraction through the origin.  Other than the ray
+splitting artifacts that generate the plateaus at 1.5 and 3 kpc, one
+sees spherical symmetry without any noise in our solution.
 
@@
     fraction.}
+\end{figure}
+
+\begin{figure}
+  \plotone{test2_pdf}
+  \caption{\label{fig:test2_pdf} Test 2. (\hii region expansion with a
+    $T=10^5$ K blackbody spectrum).  Probability distribution function
+    for ionized fraction (left) and temperature (right) at 10 Myr
+    (solid), 100 Myr (dashed), and 500 Myr (dotted).}
 \end{figure}
@@
 
-In Fig. \ref{fig:test2_1a}, we show the radially averaged neutral
-and ionised fraction at $t = $ 10, 30, 100, and 500 Myr, and the total
+In Fig. \ref{fig:test2_1a}, we show the radially averaged neutral and
+ionised fraction at $t = $ 10, 30, 100, and 500 Myr, and the total
 neutral fraction of the domain in Fig. \ref{fig:test2_1b}.  Compared
 with Test 1, the ionisation front is thicker, as expected with the
-harder spectrum.  The total neutral fraction decreases to 0.67 over
-4$t_{\rm rec} = 500$ Myr, which is in agreement with the analytical
-expectation and other codes in RT06.  In Fig. \ref{fig:test2_2}, we
-show slices of neutral fraction and temperature through the origin at
-$t = $ 10 and 100 Myr.  Here one sees the spherically symmetric \hii
-regions and a smooth temperature transition to the neutral ambient
-medium.  In Fig. \ref{fig:test2_3}, we show the ratio of the
-ionisation front radius $r_{\rm IF}$ in our simulation and $R_s$.
-Before $1.5t_{\rm rec}$, $r_{\rm IF}$ lags behind $R_s$, initially by
-10\% and then increases to $R_s$; however afterwards, this ratio
-asymptotes to a solution that is 4\% greater than $R_s$.  This
-behavior is approximately the median result in RT06, where this ratio
-varies between 1 and 1.1, and the early evolution of $r_{\rm IF}$ is
-under-predicted by almost all of the codes.  If we use one energy
-group with the mean energy (29.6 eV) of a $T=10^5$ K blackbody, we
-find that $r_{\rm IF}/R_s$ = 1.08, which is representative of the
-codes in the upper range of RT06.
+harder spectrum.  Artifacts originating from ray splitting, similar to
+Test 1, appear at $r \sim 1$ and 3 kpc as kinks in the neutral
+fraction.  The total neutral fraction decreases to 0.67 over 4$t_{\rm
+  rec} = 500$ Myr, which is in agreement with the analytical
+expectation and other codes in RT06.  Fig. \ref{fig:test2_pdf} shows
+the distribution of ionized fraction and temperature in Test 2.  The
+overall trends agree with the codes presented in RT06 with the
+exception of the ray splitting artifacts that appear as slight rises
+in the distribution at $\log x_e \sim -1$ and $\log T \sim 3$. In
+Fig. \ref{fig:test2_2}, we show slices of neutral fraction and
+temperature through the origin at $t = $ 10 and 100 Myr.  Here one
+sees the spherically symmetric \hii regions and a smooth temperature
+transition to the neutral ambient medium.  In Fig. \ref{fig:test2_3},
+we show the ratio of the ionisation front radius $r_{\rm IF}$ in our
+simulation and $R_s$.  Before $1.5t_{\rm rec}$, $r_{\rm IF}$ lags
+behind $R_s$, initially by 10\% and then increases to $R_s$; however
+afterwards, this ratio asymptotes to a solution that is 4\% greater
+than $R_s$.  This behavior is approximately the median result in RT06,
+where this ratio varies between 1 and 1.1, and the early evolution of
+$r_{\rm IF}$ is under-predicted by almost all of the codes.  If we use
+one energy group with the mean energy (29.6 eV) of a $T=10^5$ K
+blackbody, we find that $r_{\rm IF}/R_s$ = 1.08, which is
+representative of the codes in the upper range of RT06.
 
@@
 \begin{figure}
-  \plottwo{f11a}{f11b}
+  \plotone{f11}
   \caption{\label{fig:test3_1} Test 3. (I-front trapping in a dense
@@
 \begin{figure}
-  %\epsscale{0.85}
   \plotone{f12}
@@
     (top) and temperature (bottom) of the overdense clump.}
-  %\epsscale{1}
+\end{figure}
+
+\begin{figure}
+  \plotone{test3_pdf}
+  \caption{\label{fig:test3_pdf} Test 3. (I-front trapping in a dense
+    clump and shadowing). Probability distribution function for
+    ionized fraction (left) and temperature (right) at 1 Myr (solid),
+    3 Myr (dashed), and 15 Myr (dotted) within the dense clump.}
 \end{figure}
@@
 $T = 40$ K.  It has a radius of $r_c = 0.8$ kpc and is centred at
-$(x,y,z) = (5, 3.3, 3.3)$ kpc.  In RT06, the test considered a plane
-parallel radiation field with a flux $F_0 = 10^6$ ph s$^{-1}$
-cm$^{-2}$ originating from the $y=0$ plane.  Our code can only
-consider point sources, so we use a single radiation source located in
-the centre of the $y=0$ boundary.  The luminosity of $\dot{N}_\gamma =
-3 \times 10^{51}$ ph s$^{-1}$ corresponds to the same flux $F_0$ at 5
-kpc.  The location where the ionisation front trapping can be
-calculated analytically \citep{Shapiro04}, and with these parameters,
-it should halt at approximately the centre of the clump.  We use the
-same four energy groups as in Test 2.
-
-In Fig. \ref{fig:test3_1}, we show neutral fraction and temperature
-of a one-dimensional cut through the centre of the dense clump at $z =
+$(x,y,z) = (5, 3.3, 3.3)$ kpc.  The ionized fraction of the entire
+domain is zero.  In RT06, the test considered a plane parallel
+radiation field with a flux $F_0 = 10^6$ ph s$^{-1}$ cm$^{-2}$
+originating from the $y=0$ plane.  Our code can only consider point
+sources, so we use a single radiation source located in the centre of
+the $y=0$ boundary.  The luminosity of $\dot{N}_\gamma = 3 \times
+10^{51}$ ph s$^{-1}$ corresponds to the same flux $F_0$ at 5 kpc.  The
+location where the ionisation front trapping can be calculated
+analytically \citep{Shapiro04}, and with these parameters, it should
+halt at approximately the centre of the clump.  We use the same four
+energy groups as in Test 2.
+
+In Fig. \ref{fig:test3_1}, we show neutral fraction and temperature of
+a one-dimensional cut through the centre of the dense clump at $z =
 0.5$ at $t = 1, 3, 5, 15$ Myr.  The ionisation front is halted at a
@@
 the ionisation front propagates through the overdensity.  Our results
-are consistent with RT06.  Finally we show slices of neutral fraction
-and temperature in the $z = 0.5$ plane in Fig. \ref{fig:test3_3}.
-The neutral fraction slices prominently show the sharp shadows created
-by the clump and demonstrates the non-diffusivity behavior of ray
-tracing.  The discretisation of the sphere creates one neutral cell on
-the left side of the sphere.  This inherent artifact to the initial
-setup carries through the calculation.  We did not smooth the clump
-surface like in some of the RT06 codes, in order to remove this
-artifact.  It is seen in the neutral fraction and temperature states
-at all times and is not a caused by our ray tracing algorithm.
+are consistent with RT06.  The distribution of ionized fraction and
+temperature within the clump are shown in Fig. \ref{fig:test3_pdf} and
+agree well with the other codes in RT06.  Finally we show slices of
+neutral fraction and temperature in the $z = 0.5$ plane in
+Fig. \ref{fig:test3_3}.  The neutral fraction slices prominently show
+the sharp shadows created by the clump and demonstrates the
+non-diffusivity behavior of ray tracing.  The discretisation of the
+sphere creates one neutral cell on the left side of the sphere.  This
+inherent artifact to the initial setup carries through the
+calculation.  We did not smooth the clump surface like in some of the
+RT06 codes, in order to remove this artifact.  It is seen in the
+neutral fraction and temperature states at all times and is not a
+caused by our ray tracing algorithm.
 
@@
 \begin{figure}
-  %\epsscale{0.75}
+  \plotone{test4_pdf}
+  \caption{\label{fig:test4_pdf} Test 4. (Multiple cosmological
+    sources). Probability distribution function for neutral fraction
+    (left) and temperature (right) at 50 kyr (solid) and 200 kyr
+    (dashed).}
+\end{figure}
+
+\begin{figure}
   \plotone{f14}
@@
     (solid) ionised fraction.}
-  %\epsscale{1}
 \end{figure}
@@
 
-We show the growth of the \hii regions by computing the
-mass-averaged $x_m$ and volume-averaged $x_v$ ionised fraction in
-Fig. \ref{fig:test4_1}.  Initially $x_m$ is larger than $x_v$, and
-at $t \sim 170$ kyr, the $x_v$ becomes larger.  This is indicative of
-inside-out reionisation \citep[e.g.][]{Gnedin00, Miralda00,
-  Sokasian03}, where the dense regions around haloes are ionised first,
-then the voids are ionised last.  At the end of the simulation, 65\%
-of the simulation is ionised.  However by visual inspection in the
-slices of electron fraction (Fig. \ref{fig:test4_2}), there appears to
-be very good agreement with C$^2$-ray and FTTE.  By first glance, our
-result appears to be different than the RT06 because of the
-color-mapping.  Our results are also in good agreement with the
-multi-frequency version of TRAPHIC \citep[][see also for better
-representations of the electron fraction slices]{Pawlik10}.  In the
-slices of electron fraction and temperature, Fig. \ref{fig:test4_2},
-the photo-heated regions are larger than the ionised regions by a
-factor of 2--3 because of the hardness of the $T = 10^5$ K blackbody
-spectrum.
+Fig. \ref{fig:test4_pdf} depicts the distribution of the neutral
+fraction and temperature of the entire domain and shows good agreement
+with the codes presented in RT06.  We show the growth of the \hii
+regions by computing the mass-averaged $x_m$ and volume-averaged $x_v$
+ionised fraction in Fig. \ref{fig:test4_1}.  Initially $x_m$ is larger
+than $x_v$, and at $t \sim 170$ kyr, the $x_v$ becomes larger.  This
+is indicative of inside-out reionisation \citep[e.g.][]{Gnedin00,
+  Miralda00, Sokasian03}, where the dense regions around haloes are
+ionised first, then the voids are ionised last.  At the end of the
+simulation, 65\% of the simulation is ionised.  However by visual
+inspection in the slices of electron fraction
+(Fig. \ref{fig:test4_2}), there appears to be very good agreement with
+C$^2$-ray and FTTE.  By first glance, our result appears to be
+different than the RT06 because of the color-mapping.  Our results are
+also in good agreement with the multi-frequency version of TRAPHIC
+\citep[][see also for better representations of the electron fraction
+slices]{Pawlik10}.  In the slices of electron fraction and
+temperature, Fig. \ref{fig:test4_2}, the photo-heated regions are
+larger than the ionised regions by a factor of 2--3 because of the
+hardness of the $T = 10^5$ K blackbody spectrum.
 
@@
 
+\begin{figure}
+  \plotone{test7_pdf}
+  \caption{\label{fig:test7_pdf} Test 7. (Photo-evaporation of a dense
+    clump).  Probability distribution function for temperature (left)
+    and flow Mach number (right) at 10 Myr (solid) and 50 Myr
+    (dashed).}
+\end{figure}
+
+\begin{figure}
+  \plotone{test7_Mach}
+  \caption{\label{fig:test7_4} Test 7. (Photo-evaporation of a dense
+    clump).  Slices through the clump centre of the flow Mach number
+    at t = 10 Myr (left) and 50 Myr (right).}
+\end{figure}
+
 The photo-evaporation of a dense clump in a uniform medium proceeds
@@
 outermost shell are caused by the initial discretisation of the
-sphere, as discussed in \S\ref{sec:test3}.
+sphere, as discussed in \S\ref{sec:test3}.  Next
+Fig. \ref{fig:test7_pdf} shows the distributions of temperature and
+flow Mach number in the entire domain at 10 Myr and 50 Myr, showing
+similar behavior as the codes in RT09.  Lastly in
+Fig. \ref{fig:test7_4}, we show slices of the flow Mach number at 10
+Myr and 50 Myr, showing the supersonic photo-evaporative flows that
+originate from the clump.
 
@@
 
-We thank Richard Klein for helpful comments on the manuscript.
-J.~H.~W. is supported by NASA through Hubble Fellowship grant
-\#120-6370 awarded by the Space Telescope Science Institute, which is
-operated by the Association of Universities for Research in Astronomy,
-Inc., for NASA, under contract NAS 5-26555.  Computational resources
-were provided by NASA/NCCS award SMD-09-1439.  The majority of the
-analysis and plots were done with \texttt{yt} \citep{yt_full_paper}.
+We thank Ji-hoon Kim, Richard Klein, and Jeff Oishi for helpful
+comments on the manuscript.  J.~H.~W. is supported by NASA through
+Hubble Fellowship grant \#120-6370 awarded by the Space Telescope
+Science Institute, which is operated by the Association of
+Universities for Research in Astronomy, Inc., for NASA, under contract
+NAS 5-26555.  Computational resources were provided by NASA/NCCS award
+SMD-09-1439.  The majority of the analysis and plots were done with
+\texttt{yt} \citep{yt_full_paper}.
 

### 2011-02-08 mnras/mnras.tex
Finished responding to referee report.

@@
 radiative transfer equation.  Furthermore, we detail how physics other
-than photo-ionisation and photo-heated are included.  We then derive a
+than photo-ionisation and photo-heating are included.  We then derive a
 geometric correction factor to any ray tracing method to improve
@@
 presented in \citet[][hereafter RT09]{Iliev09}.  They involve (1) the
-expansion of an \hii region in a uniform medium, similar to Test
-2, (2) an \hii region in an isothermal sphere, and (3) the
-photo-evaporation of a dense, cold clump, similar to Test 3.  We
-expand on this test suite to include more complex situations, such as
-a Rayleigh-Taylor problem illuminated by a radiation source, champagne
-flows, an irradiated blast wave, collimated radiation, and an
-\hii with a variable source.  For the \citeauthor{Iliev09}
-tests, we turn off self-gravity and AMR in accordance with them.  In
-the latter tests, we will indicate whether we use those capabilities
-of \enzo.  Last we use the new MHD implementation in \enzo~v2.0 in the
-problem of a growing \hii region in a magnetic field.
+expansion of an \hii region in a uniform medium, similar to Test 2,
+(2) an \hii region in an isothermal sphere, and (3) the
+photo-evaporation of a dense, cold clump, similar to Test 3.  We turn
+off self-gravity and AMR in accordance with RT09.
 
@@
 We have completed presenting results from the RT06 and RT09 test
-suites.  Next we test \moray~with six applications that further
-demonstrate its capabilities and accuracy.
+suites.  We expand on these test suites to include more complex
+situations, such as a Rayleigh-Taylor problem illuminated by a
+radiation source, champagne flows, an irradiated blast wave,
+collimated radiation, and an \hii with a variable source that further
+demonstrate its capabilities and accuracy.  Last we use the new MHD
+implementation in \enzo~v2.0 in the problem of a growing \hii region
+in a magnetic field.
 
@@
 simulation is run for 7.5 Myr.
+
+\begin{figure*}
+  %\epsscale{1}
+  \epsscale{2}
+  \plotone{f29}
+  \epsscale{1}
+  \caption{\label{fig:test11} Application 4 (Collimated radiation from a
+    dense clump).  Slices of density (top) and temperature (bottom) at
+    $t = 0.1, 3.25, 10.75, 23.25$ Myr.  The conical \hii region
+    drives shocks transversely into the overdense sphere and creates
+    polar champagne flows.  The ambient medium is heated to $T \sim 3
+    \times 10^4$ K as the ionisation front passes the
+    constant-pressure cloud surface.  The ionisation front changes
+    from D-type to R-type after it enters the ambient medium.}
+  %\epsscale{1}
+\end{figure*}
 
@@
 
-\begin{figure*}
-  %\epsscale{1}
-  \epsscale{2}
-  \plotone{f29}
-  \epsscale{1}
-  \caption{\label{fig:test11} Application 4 (Collimated radiation from a
-    dense clump).  Slices of density (top) and temperature (bottom) at
-    $t = 0.1, 3.25, 10.75, 23.25$ Myr.  The conical \hii region
-    drives shocks transversely into the overdense sphere and creates
-    polar champagne flows.  The ambient medium is heated to $T \sim 3
-    \times 10^4$ K as the ionisation front passes the
-    constant-pressure cloud surface.  The ionisation front changes
-    from D-type to R-type after it enters the ambient medium.}
-  %\epsscale{1}
-\end{figure*}
-
-Some astrophysical systems produce collimated radiation either
-intrinsically by relativistic beaming or by an optically-thick torus
-absorbing radiation in the equatorial plane.  The latter case would be
-applicable in a subgrid model of active galactic nuclei (AGN) or
-protostars, for example.  Simulating collimated radiation with ray
-tracing is trivially accomplished by only initialising rays that are
-within some opening angle $\theta_c$.
-
-We use a domain that is 2 kpc wide and has an ambient medium with
-$\rho_0 = 10^{-3}$ \cubecm, $T = 10^4$ K, $x_e = 0.99$.  We place a
-dense clump with $\rho/\rho_0 = 100$, $T = 100$ K, $x_e = 10^{-3}$,
-and $r = 250$ pc, at the centre of the box.  Radiation is emitted in
-two polar cones with $\theta_c = \pi/6$ with 768 (HEALPix level 3)
-initial rays, a total luminosity of $10^{49}$ erg s$^{-1}$, and a 17.6
-eV mono-chromatic spectrum.  This results in $t_{\rm rec} = 1.22$ Myr
-and $R_s = 315$ pc, just outside of the sphere.  The base grid has a
-resolution of 64$^3$, and it is refined with the same overdensity
-criterion as Application 1.  We run this test for 25 Myr.
-
 \begin{figure}
@@
 \end{figure}
+
+Some astrophysical systems produce collimated radiation either
+intrinsically by relativistic beaming or by an optically-thick torus
+absorbing radiation in the equatorial plane.  The latter case would be
+applicable in a subgrid model of active galactic nuclei (AGN) or
+protostars, for example.  Simulating collimated radiation with ray
+tracing is trivially accomplished by only initialising rays that are
+within some opening angle $\theta_c$.
+
+We use a domain that is 2 kpc wide and has an ambient medium with
+$\rho_0 = 10^{-3}$ \cubecm, $T = 10^4$ K, $x_e = 0.99$.  We place a
+dense clump with $\rho/\rho_0 = 100$, $T = 100$ K, $x_e = 10^{-3}$,
+and $r = 250$ pc, at the centre of the box.  Radiation is emitted in
+two polar cones with $\theta_c = \pi/6$ with 768 (HEALPix level 3)
+initial rays, a total luminosity of $10^{49}$ erg s$^{-1}$, and a 17.6
+eV mono-chromatic spectrum.  This results in $t_{\rm rec} = 1.22$ Myr
+and $R_s = 315$ pc, just outside of the sphere.  The base grid has a
+resolution of 64$^3$, and it is refined with the same overdensity
+criterion as Application 1.  We run this test for 25 Myr.
 

### 2011-02-09 mnras/mnras.tex
Massive figure filename renaming because of figure number changes with the new figures.
Proofread.

@@
 \begin{figure}
-  \plotone{test1_pdf.eps}
+  \plotone{f6.eps}
   \caption{\label{fig:test1_pdf} Test 1 (\hii region expansion with a
@@
     function for neutral fraction at 10 Myr (solid), 100 Myr (dashed),
-    and 500 Myr (dotted).  Recombination of hydrogren at T = $10^4$ K
+    and 500 Myr (dotted).  Recombination of hydrogen at T = $10^4$ K
     causes the maximum neutral fraction to decrease from 1 to 0.75.}
@@
 \begin{figure}
-  \plotone{f6.eps}
+  \plotone{f7.eps}
   \caption{\label{fig:test1_HI} Test 1 (\hii region expansion
@@
 \begin{figure}
-  \plotone{test2_pdf}
+  \plotone{f10}
   \caption{\label{fig:test2_pdf} Test 2. (\hii region expansion with a
@@
   \epsscale{2}
-  \plotone{f9}
+  \plotone{f11}
   \epsscale{1}
@@
 \begin{figure}
-  \plotone{f10}
+  \plotone{f12}
   \caption{\label{fig:test2_3} Test 2. (\hii region expansion
@@
 \begin{figure}
-  \plotone{f11}
+  \plotone{f13}
   \caption{\label{fig:test3_1} Test 3. (I-front trapping in a dense
@@
 \begin{figure}
-  \plotone{f12}
+  \plotone{f14}
   \caption{\label{fig:test3_2} Test 3. (I-front trapping in a dense
@@
 \begin{figure}
-  \plotone{test3_pdf}
+  \plotone{f15}
   \caption{\label{fig:test3_pdf} Test 3. (I-front trapping in a dense
@@
   \epsscale{2}
-  \plotone{f13}
+  \plotone{f16}
   \epsscale{1}
@@
 \begin{figure}
-  \plotone{test4_pdf}
+  \plotone{f17}
   \caption{\label{fig:test4_pdf} Test 4. (Multiple cosmological
@@
 \begin{figure}
-  \plotone{f14}
+  \plotone{f18}
   \caption{\label{fig:test4_1} Test 4. (Multiple cosmological
@@
   \epsscale{2}
-  \plotone{f15}
+  \plotone{f19}
   \epsscale{1}
@@
   %\epsscale{0.8}
-  \plotone{f16}
+  \plotone{f20}
   \caption{\label{fig:test5_1} Test 5. (\hii region in a uniform
@@
 \begin{figure}
-  \plotone{f17}
+  \plotone{f21}
   \caption{\label{fig:test5_2} Test 5. (\hii region in a uniform
@@
   \epsscale{2}
-  \plotone{f18}
+  \plotone{f22}
   \epsscale{1}
@@
   %\epsscale{0.8}
-  \plotone{f19}
+  \plotone{f23}
   \caption{\label{fig:test6_1} Test 6. (\hii region in a 1/$r^2$
@@
 \begin{figure}
-  \plotone{f20}
+  \plotone{f24}
   \caption{\label{fig:test6_2} Test 6. (\hii region in a 1/$r^2$
@@
   \epsscale{2}
-  \plotone{f21}
+  \plotone{f25}
   \epsscale{1}
@@
 can react to the passing ionisation front and creates a shock, leaving
-behind a heated an rarefied medium.  This behavior is clearly seen in
-the radial profiles of density, temperature, ionised fraction, and
-pressure in Fig. \ref{fig:test6_2}.  The inner density decreases
-over two order of magnitude after 25 Myr.  To illustrate any
-deviations in spherical symmetry, we show in Fig. \ref{fig:test6_3}
-slices of density, temperature, neutral fraction, and ionised fraction
-at the final time.  The only artifact apparent to us is the slight
-broadening of the shock near the $x=0$ and $y=0$ planes.  This causes
-the ionisation front radius to be slightly smaller in those
-directions.  In the diagonal direction, the neutral column density
-through the shock is slightly smaller, allowing the high-energy
-photons to photo-ionise and photo-heat the gas to $x_e = 5 \times
-10^{-3}$ and $T = 2000$ K out to $\sim50$ pc from the shock.  The
-reflecting boundaries are responsible for this artifact because this
-is not seen when the problem is centred in the domain, removing any
-boundary effects.
+behind a heated rarefied medium.  This behavior is clearly seen in the
+radial profiles of density, temperature, ionised fraction, and
+pressure in Fig. \ref{fig:test6_2}.  The inner density decreases over
+two order of magnitude after 25 Myr.  To illustrate any deviations in
+spherical symmetry, we show in Fig. \ref{fig:test6_3} slices of
+density, temperature, neutral fraction, and ionised fraction at the
+final time.  The only artifact apparent to us is the slight broadening
+of the shock near the $x=0$ and $y=0$ planes.  This causes the
+ionisation front radius to be slightly smaller in those directions.
+In the diagonal direction, the neutral column density through the
+shock is slightly smaller, allowing the high-energy photons to
+photo-ionise and photo-heat the gas to $x_e = 5 \times 10^{-3}$ and $T
+= 2000$ K out to $\sim50$ pc from the shock.  The reflecting
+boundaries are responsible for this artifact because this is not seen
+when the problem is centred in the domain, removing any boundary
+effects.
 
@@
   %\epsscale{0.9}
-  \plotone{f22}
+  \plotone{f26}
   \caption{\label{fig:test7_1} Test 7. (Photo-evaporation of a dense
@@
   \epsscale{2}
-  \plotone{f23}
+  \plotone{f27}
   \epsscale{1}
@@
   \epsscale{2}
-  \plotone{f24}
+  \plotone{f28}
   \epsscale{1}
@@
 \begin{figure}
-  \plotone{test7_pdf}
+  \plotone{f29}
   \caption{\label{fig:test7_pdf} Test 7. (Photo-evaporation of a dense
@@
 \begin{figure}
-  \plotone{test7_Mach}
+  \plotone{f30}
   \caption{\label{fig:test7_4} Test 7. (Photo-evaporation of a dense
@@
   \epsscale{2}
-  \plotone{f25}
+  \plotone{f31}
   \epsscale{1}
@@
 The $x$ and $y$-boundaries are periodic, and the $z$-boundaries are
-reflecting.  These will cause artifical features, in particular,
+reflecting.  These will cause artificial features, in particular,
 because of the top reflecting boundary; nevertheless, these tests
@@
   %\epsscale{0.75}
-  \plotone{f26a}
-  \plotone{f26b}
-  \plotone{f26c}
+  \plotone{f32a}
+  \plotone{f32b}
+  \plotone{f32c}
   \caption{\label{fig:test9_thick} Application 2. (Irradiated Rayleigh-Taylor
@@
   %\epsscale{0.75}
-  \plotone{f27a}
-  \plotone{f27b}
-  \plotone{f27c}
+  \plotone{f33a}
+  \plotone{f33b}
+  \plotone{f33c}
   \caption{\label{fig:test9_thin} Same as Fig. \ref{fig:test9_thick}
@@
   \epsscale{2}
-  \plotone{f28}
+  \plotone{f34}
   \epsscale{1}
@@
   \epsscale{2}
-  \plotone{f29}
+  \plotone{f35}
   \epsscale{1}
@@
   %\epsscale{1.15}
-  \plottwo{f30a}{f30b}
+  \plottwo{f36a}{f36b}
   \caption{\label{fig:test12_kph} Application 4 (Time variations of the
@@
   %\epsscale{0.8}
-  \plotone{f31}
+  \plotone{f37}
   \caption{\label{fig:test12_profiles} Application 4 (Time variations of the
@@
   \epsscale{2}
-  \plotone{f32}
+  \plotone{f38}
   \epsscale{1}
@@
   \epsscale{2}
-  \plotone{f33}
+  \plotone{f39}
   \epsscale{1}
@@
   %\epsscale{0.75}
-  \plotone{f34}
+  \plotone{f40}
   \caption{\label{fig:dx_dep1} Growth of the ionisation front radius,
@@
   %\epsscale{2}
-  \plotone{f35}
+  \plotone{f41}
   \epsscale{1}
@@
   %\epsscale{0.75}
-  \plotone{f36}
+  \plotone{f42}
   \caption{\label{fig:ang_dep2} Standard deviations of the difference
@@
   %\epsscale{1.05}
-  \plottwo{f37a}{f37b}
+  \plottwo{f43a}{f43b}
   \caption{\label{fig:nu_dep} Radial profiles of (clockwise from the
@@
   %\epsscale{0.75}
-  \plotone{f38}
+  \plotone{f44}
   \caption{\label{fig:dt_dep1} Growth of the ionisation front radius,
@@
   %\epsscale{0.75}
-  \plotone{f39}
+  \plotone{f45}
   \caption{\label{fig:dt_dep2} Variable time-stepping for the methods
@@
   %\epsscale{0.7}
-  \plotone{f40}
+  \plotone{f46}
   \caption{\label{fig:fc_slices} Slices of the photo-ionisation rate
@@
   %\epsscale{0.6}
-  \plotone{f41}
+  \plotone{f47}
   \caption{\label{fig:rayopt} Optically-thin approximation to the
@@
   %\epsscale{0.6}
-  \plotone{f42}
+  \plotone{f48}
   \caption{\label{fig:xray_fig} Radial profiles of temperature and
@@
   %\epsscale{1.075}
-  \plottwo{f43a}{f43b}
+  \plottwo{f49a}{f49b}
   \caption{\label{fig:rp_profiles} (a) No radiation pressure.
@@
   %\epsscale{0.6}
-  \plotone{f44}
+  \plotone{f50}
   \caption{\label{fig:twosrc} Slice of neutral fraction at $t = 500$
@@
   %\epsscale{0.8}
-  \plotone{f45}
+  \plotone{f51}
   \caption{\label{fig:weak} Weak scaling test with one $64^3$ block
@@
   %\epsscale{0.8}
-  \plotone{f46}
+  \plotone{f52}
   \caption{\label{fig:strong} Strong scaling test with a $256^3$ AMR
